### 2012-08-27 ms.tex
first commit

% TODO (lots of stuff!!!!)
%
% -- Write presubmission inquiry (Nature, Science, PLOS Biology).
%
% -- People to Contact:
% ---- The guys from Haldane's Sieve
% ---- Jonathan Eisein
% ---- Carl Boettinger
% ---- Jarrett Byrnes
% ---- Twitter call (?)
%
% -- Journals to contact:
% ---- Evolution
% ---- Journal of Evolutionary Biology
% ---- British Ecological Society

\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

\begin{document}

\title{Preprints in Ecology \& Evolution}
% Alternative title: arXiv or die!

\author{Philippe Desjardins-Proulx}
\email[E-mail: ]{philippe.d.proulx@gmail.com}
\affiliation{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
\affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
\affiliation{D\'epartement des sciences biologiques, Universit\'e du Qu\'ebec \`a Montr\'eal, Canada.}

\author{Timoth\'ee Poisot}
\affiliation{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
\affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}

\author{Ethan P. White}
\affiliation{Departement of Bology, Utah State University, United-States of America.}

\author{Dominique Gravel}
\affiliation{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
\affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}

\keywords{Publishing; arXiv; Green Open Access.}

\begin{abstract}

...

\end{abstract}

\maketitle

\section{The case for open preprints}

% Main arguments:

%% Take a look at arXiv usage and how its impact (Tim's suggestion)
% I know some papers were published on the impact of articles on arXiv
% in high-particle physics.

%% Speed up science.

%% Essentially an open equivalent to sharing preprints between colleagues.

\begin{figure}[ht!]

\centering\includegraphics[width=0.50\textwidth]{map.pdf}
\caption
{
    Since the time between submission and
}
\label{fig:map}

\end{figure}

%% Establish priority in a fair way:

% I think this argument is important since biologists often think people will
% "steal" their ideas, while physicists and mathematicians see arXiv as a way to
% establish priority.

\section{Preprints, Ecology \& Evolution}

While the practice is still rare, preprints are becoming more common in
biological sciences, which is experiencing faster growth in arXiv submission
than any other fields \cite{cal12}. Also, most scientific journals are
preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly), and all the
journals from Elsevier and Springer. Very recently, the Ecological Society of
America recently changed its policy to allow public preprints (REF). In our
field, very few scientific publications will not consider a manuscript submitted
to arXiv. Many ecology \& evolution journals hostile to preprints are from
Wiley-Blackwell, which has no official policy on the subject. Ecology Letters,

% A table?

\section{Current offer}

% Short paragraphs on the current open preprint repositories.

\subsection{arXiv}

arXiv (\href{http://arxiv.org/}{http://arxiv.org/})

arXiv is funded by a network of universities.

\subsection{Figshare}

Figshare (\href{http://figshare.com/}{http://figshare.com/})

All figshare content (article, figures, datasets) have a unique digital object
identifier (DOI) like any journal article.

\subsection{PeerJ}

% Ethan P. White's section

\subsection{F1000Research}

% Not really the same, but worth mentionning.

\section{Conclusion}

% A short paragraph to conclude.

Responding to the rumour that their refused manuscripts submitted to arXiv,
Nature responded that ``Nature never wishes to stand in the way of communication
between researchers. We seek rather to add value for authors and the community
at large in our peer review, selection and editing'' \cite{nat05}.

\newpage
\bibliography{refs}
\bibliographystyle{plain}

\end{document}

### 2012-08-28 ms.tex
Small edits

@@
 
+\author{Ethan P. White}
+\affiliation{Departement of Bology, Utah State University, United-States of America.}
+
 \author{Timoth\'ee Poisot}
@@
 \affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
-
-\author{Ethan P. White}
-\affiliation{Departement of Bology, Utah State University, United-States of America.}
+\affiliation{International Network for Next-Generation Ecology.}
 
@@
 America recently changed its policy to allow public preprints (REF). In our
-field, very few scientific publications will not consider a manuscript submitted
-to arXiv. Many ecology \& evolution journals hostile to preprints are from
-Wiley-Blackwell, which has no official policy on the subject. Ecology Letters,
+field, very few scientific publications will not consider a manuscript
+submitted to arXiv. Many ecology \& evolution journals adopt a ``by default''
+hostile attitude towards preprints, mostly due to the lack of clear policy of
+the publishers. As an example, Wiley-Blackwell, which publishes some of the
+leading journal in the field (a quick lsit), has no official policy on the
+subject.
 
 % A table?
+%% Journal | Publisher | ISI rank | Official policy ?
 

### 2012-08-28 ms.tex
merge + table

@@
 \begin{figure}[ht!]
-
 \centering\includegraphics[width=0.50\textwidth]{map.pdf}
@@
 {
-    Since the time between submission and
+    Since the time between submission and ...
 }
 \label{fig:map}
-
 \end{figure}
@@
 
-% A table?
-%% Journal | Publisher | ISI rank | Official policy ?
+\begin{table*}
+    \centering
+    \begin{tabular}{|lll|}
+    \hline
+    Journal                 			&   Publisher                           & Policy \\
+    \hline
+    \emph{All journals}     			& Springer                            	& OK \\
+    \emph{All journals}     			& BMC                                 	& OK \\
+    \emph{All journals}            		& Elsevier                            	& OK \\
+    \emph{All journals}            		& Nature Publishing Group             	& OK \\
+    \emph{All journals}            		& Public Library of Science           	& OK \\
+    \emph{All journals}            		& Science                             	& Ambiguous \\
+    \emph{All journals}            		& Ecological Society of America       	& OK \\
+    \emph{All journals}            		& Royal Society                       	& OK \\
+    Ecology Letters						& Wiley-Blackwell                   	& Refuse \\
+    Evolution   						& Wiley-Blackwell                     	& ? \\
+    Journal of Evolutionary Biology 	& Wiley-Blackwell   					& ? \\
+    The American Naturalist 			& University of Chicago Press           & OK \\
+    \hline
+    \end{tabular}
+    \caption{Policies for many publishers and some specific journals in ecology
+\& evolution.}
+    \label{table:policies}
+\end{table*}
 

### 2012-09-03 ms.tex
presub and modifs

--- 2012-08-28 ms.tex
@@
-% TODO (lots of stuff!!!!)
-%
-% -- Write presubmission inquiry (Nature, Science, PLOS Biology).
-%
-% -- People to Contact:
-% ---- The guys from Haldane's Sieve
-% ---- Jonathan Eisein
-% ---- Carl Boettinger
-% ---- Jarrett Byrnes
-% ---- Twitter call (?)
-%
-% -- Journals to contact:
-% ---- Evolution
-% ---- Journal of Evolutionary Biology
-% ---- British Ecological Society
-
 \documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4}
@@
 
-\title{Preprints in Ecology \& Evolution}
-% Alternative title: arXiv or die!
+\title{Open Preprints in Ecology \& Evolution}
 
@@
 
-% Main arguments:
+We will highlight advantages for both scientists and publishers.
 
-%% Take a look at arXiv usage and how its impact (Tim's suggestion)
-% I know some papers were published on the impact of articles on arXiv
-% in high-particle physics.
+The first and most often discussed advantage is speed \ref{fig:map}.
 
-%% Speed up science.
+%% Allows papers to be cited earlier (greater immediacy)
 
@@
 
-\begin{figure}[ht!]
+%% @Tim: how can it improve the review process?
 
-\centering\includegraphics[width=0.50\textwidth]{map.pdf}
-\caption
-{
-    Since the time between submission and
-}
-\label{fig:map}
-
+\begin{figure}[ht!] \centering\includegraphics[width=0.50\textwidth]{map.pdf}
+\caption { It can take several months, and even a few years, before a submitted
+paper is officially published. During this time, few people are aware of the
+research that has been done. With public preprint servers, the science is
+immediately available and can be openly discussed, analysed, and integrated into
+current research. It benefits both science and publishers. Both want the papers
+to be well-known and cited, and public preprints make it possible to integrate
+research even before publication, improving immediacy.  } \label{fig:map}
 \end{figure}
 
-%% Establish priority in a fair way:
-
-% I think this argument is important since biologists often think people will
-% "steal" their ideas, while physicists and mathematicians see arXiv as a way to
-% establish priority.
+Preprint servers also establish priority in a fair way. Some manuscript will
+spend much more time in the review process. Public preprints server offer a much
+fairer way to establish intellectual priority By making the manuscript available
+when it is ready. Surprisingly, there is perception in biology that public
+preprints make it easier to steal ideas, as if scientific ideas only took form
+in published material. Mathematicians and physicists have embraced arXiv in part
+to establish priority in a fair way\cite{cal12}.
 
@@
 than any other fields \cite{cal12}. Also, most scientific journals are
-preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly), and all the
-journals from Elsevier and Springer. Very recently, the Ecological Society of
-America recently changed its policy to allow public preprints (REF). In our
-field, very few scientific publications will not consider a manuscript
-submitted to arXiv. Many ecology \& evolution journals adopt a ``by default''
-hostile attitude towards preprints, mostly due to the lack of clear policy of
-the publishers. As an example, Wiley-Blackwell, which publishes some of the
-leading journal in the field (a quick lsit), has no official policy on the
-subject.
+preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly)
+\ref{table:policies}, and all the journals from Elsevier and Springer. Very
+recently, the Ecological Society of America recently changed its policy to allow
+public preprints (REF). In our field, very few scientific publications will not
+consider a manuscript submitted to arXiv. Many ecology \& evolution journals
+adopt a ``by default'' hostile attitude towards preprints, mostly due to the
+lack of clear policy of the publishers. As an example, Wiley-Blackwell, which
+publishes some of the leading journal in the field, has no official policy on
+the subject.
 
-% A table?
-%% Journal | Publisher | ISI rank | Official policy ?
+\begin{table*}
+    \centering
+    \begin{tabular}{|ll|}
+    \hline
+    Publisher                                   & Policy \\
+    \hline
+    Springer                            	& Accept \\
+    BMC                                 	& Accept \\
+    Elsevier                            	& Accept \\
+    Nature Publishing Group             	& Accept \\
+    Public Library of Science           	& Accept \\
+    Royal Society                       	& Accept \\
+    National Academy of Science (USA)           & Accept \\
+    Science                             	& Accept/Ambiguous \\
+    Wiley-Blackwell                       	& No general policy \\
+    Ecological Society of America       	& Refuse \\
+    British Ecological Society                  & ? \\
+    \hline
+    \end{tabular}
+    \caption{Policies for important publishers in ecology and evolution.}
+    \label{table:policies}
+\end{table*}
 
@@
 
-Responding to the rumour that their refused manuscripts submitted to arXiv,
+Responding to the rumour that they refused manuscripts submitted to arXiv,
 Nature responded that ``Nature never wishes to stand in the way of communication

### 2012-09-03 ms.tex
main text

@@
 
+Preprints servers such as arXiv are common in mathematics and physics, but still
+a minority of papers in ecology and evolution use them. Preprints servers allow
+author to make their manuscripts publicly available before submitting them to
+journals for peer-review. ... The idea became popular with arXiv, and many
+physicists start their day with a look at the new papers in arXiv \cite{gin11}
+
 We will highlight advantages for both scientists and publishers.
@@
 %% Allows papers to be cited earlier (greater immediacy)
-
-%% Essentially an open equivalent to sharing preprints between colleagues.
 
@@
 
+Some of the responses to public preprints are surprisingly since they are,
+essentially, the same as exchanging preprints among colleagues. Prepublication
+reviews by a small network of colleagues is an important part of the scientific
+process. Preprints servers simply offer a way to extend this network of
+colleagues to the entire scientific community. It ensures that science is not
+constrained by small networks of scientists exchanging ideas. Ginsparg made
+arXiv.org in part for democratic reasons: he wanted everyone from graduate
+students in small universities to Princeton professors to have access to the
+most recent scientific ideas. Ginsparg revolutionary idea was simply to use the
+power of the internet for preprints, not just for the end product, so the
+process can be open from A to Z, instead of being just open at the end of the
+process.
+
 \section{Preprints, Ecology \& Evolution}
@@
 While the practice is still rare, preprints are becoming more common in
-biological sciences, which is experiencing faster growth in arXiv submission
+biological sciences, which is experiencing faster growth in arXiv submissions
 than any other fields \cite{cal12}. Also, most scientific journals are
@@
 recently, the Ecological Society of America recently changed its policy to allow
-public preprints (REF). In our field, very few scientific publications will not
-consider a manuscript submitted to arXiv. Many ecology \& evolution journals
+public preprints (REF). In our field, few scientific publications will not
+consider a manuscript submitted to arXiv. Still, many ecology \& evolution journals
 adopt a ``by default'' hostile attitude towards preprints, mostly due to the
@@
 publishes some of the leading journal in the field, has no official policy on
-the subject.
+the subject \ref{table:policies}.
 
@@
 
-% Short paragraphs on the current open preprint repositories.
+We briefly discuss the main options to submit preprints to open servers:
+arXiv.org, Figshare, and the upcoming PeerJ and F1000Research.
 
@@
 
-arXiv (\href{http://arxiv.org/}{http://arxiv.org/})
-
+arXiv (\href{http://arxiv.org/}{http://arxiv.org/}).
 arXiv is funded by a network of universities.
 
+...
+
+% @Joel
+
 \subsection{Figshare}
+
+% @PhDP
 
@@
 
-% Ethan P. White's section
+% @Ethan
 
@@
 
-% Not really the same, but worth mentionning.
+% Written from memory: to verify!
+
+F1000Research is not a public preprint server like the previous three servers.
+Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
+without having it reviewed, papers submitted to F1000Research will eventually be
+reviewed. Thus, F1000Research offers a hybrid model with publicly available
+manuscripts at time of submission and standard peer-reviews. Manuscripts are
+considered ``accepted'' and will only be indexed after two positive referee
+response.
 

### 2012-09-04 ms.tex

@@
 
-Preprints servers such as arXiv are common in mathematics and physics, but still
-a minority of papers in ecology and evolution use them. Preprints servers allow
-author to make their manuscripts publicly available before submitting them to
-journals for peer-review. ... The idea became popular with arXiv, and many
-physicists start their day with a look at the new papers in arXiv \cite{gin11}
+Preprints servers such as arXiv are common in mathematics and physics, but
+still a minority of papers in ecology and evolution use them. Preprints
+servers allow author to make their manuscripts publicly available before, or
+in parallel to, submitting them to journals for traditional peer-review. ...
+The idea became popular with arXiv, and many physicists start their day with a
+look at the new papers in arXiv \cite{gin11}
 
@@
 
+The review process as a whole is critically over-loaded, because the number of
+active scientists increases, because the pressure to publish increases, and
+because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  In
+the same times, rejection rates are high in most journals (REF), and when the
+not invited to submit a revisions, authors are left with the impression that
+they must start the whole process all over again. It's thus no surprize that
+different initiatives emerged over the last few years, to decrease the time
+spent in review. XXX et coll. (REF) called for the recycling and reuse of
+peer-reviews: by attaching previous reviews, and detailed replies, to a new
+submission, both the editor and the referees can jauge the work done on the
+manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
+\emph{Peerage of Science} initiative allows authors to seek anonymous pre-
+review by their peers. Some journals (LIST?) now accept to publish papers
+which received good evaluations, effectively outsourcing the review process. A
+widespread use of preprint servers can achieve the same goal of reducing the
+time spent in review. By putting a manuscript out there for open comments and
+criticisms, the authors will receive valuable feedback, and can improve the
+version which will be submitted. With a rich enough community of scientists
+depositing preprints, and commenting on them, the process of an open pre-
+review can become widespread, and will overall increase the quality of first
+submissions.
+% Assuming that the quality of the paper is a good prior of its acceptance probability :-)
+
 \begin{figure}[ht!] \centering\includegraphics[width=0.50\textwidth]{map.pdf}
 \caption { It can take several months, and even a few years, before a submitted
-paper is officially published. During this time, few people are aware of the
-research that has been done. With public preprint servers, the science is
-immediately available and can be openly discussed, analysed, and integrated into
-current research. It benefits both science and publishers. Both want the papers
-to be well-known and cited, and public preprints make it possible to integrate
-research even before publication, improving immediacy.  } \label{fig:map}
+paper is officially published and citable. During this time, few people are
+aware of the research that has been done (typically, close colleagues are
+given access to the preprints). With public preprint servers, the science is
+immediately available and can be openly discussed, analysed, and integrated
+into current research. It benefits both science and publishers. Both want the
+papers to be well-known and cited, and public preprints make it possible to
+integrate research even before publication, greatly improving immediacy.  }
+\label{fig:map}
 \end{figure}
@@
 Preprint servers also establish priority in a fair way. Some manuscript will
-spend much more time in the review process. Public preprints server offer a much
-fairer way to establish intellectual priority By making the manuscript available
-when it is ready. Surprisingly, there is perception in biology that public
-preprints make it easier to steal ideas, as if scientific ideas only took form
-in published material. Mathematicians and physicists have embraced arXiv in part
+spend much more time in the review process. Public preprints server offer a
+much fairer way to establish intellectual priority by making the work
+available when done, and even if the exact organisation of the manuscript may
+change. Surprisingly, there is perception in biology that public preprints
+make it easier to steal ideas, as if scientific ideas only took form in
+published material.
+% TP This needs more development, I'm not sure I get your point
+Mathematicians and physicists have embraced arXiv in part
 to establish priority in a fair way\cite{cal12}.
 
-Some of the responses to public preprints are surprisingly since they are,
-essentially, the same as exchanging preprints among colleagues. Prepublication
-reviews by a small network of colleagues is an important part of the scientific
-process. Preprints servers simply offer a way to extend this network of
-colleagues to the entire scientific community. It ensures that science is not
-constrained by small networks of scientists exchanging ideas. Ginsparg made
-arXiv.org in part for democratic reasons: he wanted everyone from graduate
-students in small universities to Princeton professors to have access to the
-most recent scientific ideas. Ginsparg revolutionary idea was simply to use the
-power of the internet for preprints, not just for the end product, so the
-process can be open from A to Z, instead of being just open at the end of the
-process.
+Some of the responses to public preprints are surprising since they are,
+essentially, the same as exchanging preprints among colleagues.
+% TP Well, no. You trust your colleagues, and you trust that they will not give your
+%    MS to anyone!
+Prepublication reviews by a small network of colleagues is an important part
+of the scientific process, which is attested by the fact that nearly all
+published papers acknowledge comments by people not listed as co-authors.
+Preprints servers simply offer a way to extend this network of colleagues to
+the entire scientific community. It ensures that science is not constrained by
+small networks of scientists exchanging ideas. Ginsparg made arXiv.org in part
+for democratic reasons: he wanted everyone from graduate students in small
+universities to Princeton professors to have access to the most recent
+scientific \emph{ideas}.
+% TP One important point to make: the MS and the idea are different things.
+%    We should focus more on the later...
+Ginsparg revolutionary idea was simply to use the power of the internet for
+preprints, not just for the end product, so the process can be open from A to
+Z, instead of being just open at the end of the process.
+% TP Since when is the publishing buisness an open process? :-)
 

### 2012-09-05 ms.tex
Added my byline and affiliation
New branch; brief outline of my section
This branch is for my description of arXiv.  I have inserted a comment
about the basic structure of the two or three paragraph passage.
a few small modifications

@@
 
+\section{Introduction}
+
+Open preprints servers allow authors to make their manuscripts publicly
+available before, or in parallel to, submitting them to journals for traditional
+peer-review. The idea became popular with arXiv, an open preprint server, that
+started 20 years ago \cite{gin11}. The idea is fundamentally simple: to make the
+science available to the entire scientific community as soon as its done instead
+of having to wait for the peer-review process. The point of arXiv and open
+preprints servers is not to avoid the peer-review process. Almost all
+manuscripts on arXiv are submitted to peer-review. The point is to open an
+important phase of the publication cycle ...
+
+In this article, we will first highlight the advantages of open preprints
+servers for both scientists and publishers. We will also debunk a few
+misconceptions, discuss the policies of major publishers in ecology an
+evolution, and briefly review the most popular open preprint servers.
+
 \section{The case for open preprints}
 
-Preprints servers such as arXiv are common in mathematics and physics, but
-still a minority of papers in ecology and evolution use them. Preprints
-servers allow author to make their manuscripts publicly available before, or
-in parallel to, submitting them to journals for traditional peer-review. ...
-The idea became popular with arXiv, and many physicists start their day with a
-look at the new papers in arXiv \cite{gin11}
-
-We will highlight advantages for both scientists and publishers.
-
-The first and most often discussed advantage is speed \ref{fig:map}.
+The first and most often discussed advantage of arXiv and open preprints is
+speed \ref{fig:map}. The time between submission and the official publication of
+a manuscript can be measured in months, sometime in years. For all this time,
+the research is only known to a select few: colleagues, editors, reviewers.
+Thus, the science cannot be used, discussed, or reviewed by the wider scientific
+community. ...
 
@@
 
-%% @Tim: how can it improve the review process?
-
+% Tim's section:
 The review process as a whole is critically over-loaded, because the number of
@@
 not invited to submit a revisions, authors are left with the impression that
-they must start the whole process all over again. It's thus no surprize that
+they must start the whole process all over again. It's thus no surprise that
 different initiatives emerged over the last few years, to decrease the time
@@
 peer-reviews: by attaching previous reviews, and detailed replies, to a new
-submission, both the editor and the referees can jauge the work done on the
+submission, both the editor and the referees can gauge the work done on the
 manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
@@
 submissions.
-% Assuming that the quality of the paper is a good prior of its acceptance probability :-)
 
@@
 
-Preprint servers also establish priority in a fair way. Some manuscript will
-spend much more time in the review process. Public preprints server offer a
-much fairer way to establish intellectual priority by making the work
-available when done, and even if the exact organisation of the manuscript may
-change. Surprisingly, there is perception in biology that public preprints
-make it easier to steal ideas, as if scientific ideas only took form in
-published material.
-% TP This needs more development, I'm not sure I get your point
-Mathematicians and physicists have embraced arXiv in part
-to establish priority in a fair way\cite{cal12}.
-
+% @to myself: rewrite this paragraph:
 Some of the responses to public preprints are surprising since they are,
@@
 preprints, not just for the end product, so the process can be open from A to
-Z, instead of being just open at the end of the process.
+Z, instead of being just open at the end of the process (and often not open at
+all).
 % TP Since when is the publishing buisness an open process? :-)
+% PhDP: Wishful thinking :) Corrected...
+
+Preprint servers also establish priority in a fair way. Since some manuscripts
+will spend much more time in the review process, public preprints servers offer
+a fairer way to establish intellectual priority by making the work available
+when done. Surprisingly, there is perception in biology that public preprints
+make it easier to steal ideas, while mathematicians and physicists have embraced
+arXiv in part to establish intellectual priority in a fair way \cite{cal12}.
 
@@
 
-While the practice is still rare, preprints are becoming more common in
-biological sciences, which is experiencing faster growth in arXiv submissions
-than any other fields \cite{cal12}. Also, most scientific journals are
-preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly)
+While submitting to public preprints servers is still uncommon in ecology and
+evolution, preprints are becoming more common in biological sciences. The
+quantitative biology section in arXiv is experiencing faster growth in
+submissions than any other fields \cite{cal12}. Also, most scientific journals
+are preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly)
 \ref{table:policies}, and all the journals from Elsevier and Springer. Very
@@
 public preprints (REF). In our field, few scientific publications will not
-consider a manuscript submitted to arXiv. Still, many ecology \& evolution journals
-adopt a ``by default'' hostile attitude towards preprints, mostly due to the
-lack of clear policy of the publishers. As an example, Wiley-Blackwell, which
-publishes some of the leading journal in the field, has no official policy on
-the subject \ref{table:policies}.
+consider a manuscript submitted to arXiv.  Still, many ecology \& evolution
+journals adopt a ``by default'' hostile attitude towards preprints, mostly due
+to the lack of clear policy of the publishers. As an example, Wiley-Blackwell,
+which publishes some of the leading journal in the field, has no official policy
+on the subject \ref{table:policies}.
 
@@
     National Academy of Science (USA)           & Accept \\
+    Ecological Society of America       	& Accept \\ % Victory!
     Science                             	& Accept/Ambiguous \\
-    Wiley-Blackwell                       	& No general policy \\
-    Ecological Society of America       	& Refuse \\
-    British Ecological Society                  & ? \\
+    Wiley-Blackwell                       	& No general policy \\ % grrrrrr
+    British Ecological Society                  & ? \\ % Waiting for their answer...
+    % Oxford worth mentionning?
     \hline
@@
 
-Figshare (\href{http://figshare.com/}{http://figshare.com/})
+Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open servers
+that allow scientists to submit any research output: manuscript, figures,
+datasets, videos, theses, presentations, and so on. There are no rules to limit
+what constitutes a research output: anything
 
@@
 identifier (DOI) like any journal article.
+
+All content is licensed under the Creative Commons (CC-BY) license, except
+datasets which are published under CC0.
+% Small explanation
 
@@
 
-% A short paragraph to conclude.
-
+% Poorly written:
 Responding to the rumour that they refused manuscripts submitted to arXiv,
@@
 at large in our peer review, selection and editing'' \cite{nat05}.
+
+Open preprints server offer a great opportunity for open science, especially if
+the community embrace the idea of discussing preprints. Initiatives like
+Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
+new blog discussing arXiv papers in population genetics, will help make arXiv
+attractive for scientists looking to promote their work. These initiatives are
+important to fully exploit the potential of open preprints servers.
 

### 2012-09-05 ms.tex
Basic sketch
A basic sketch of my section on arXiv.  The ideas that I want to present
are all there, but the wording needs working.

--- 2012-09-04 ms.tex
@@
 \affiliation{Departement of Bology, Utah State University, United-States of America.}
+
+\author{Joel J. Adamson}
+\affiliation{Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill}
 
@@
 
-\section{Current offer}
+\section{Current offerings}
 
@@
 
-arXiv (\href{http://arxiv.org/}{http://arxiv.org/}).
-arXiv is funded by a network of universities.
+% @Joel
+% Rough outline:
+% 1. Description of arXiv (origins, funding, maintenance)
+% 2. Submission process
+% 3. Role within math and physics community (nearly universal), including recent changes
+% 4. Nature of citations and "priority"
+%
+% My biggest problem here is how to cite my sources: the information
+% on funding comes from a press release from Cornell University
+% Libraries; other basic "raw data" comes straight from the arXiv
+% webpages. How do I cite that?
 
-...
+arXiv (\href{http://arxiv.org/}{http://arxiv.org/}) is the most
+widely-used preprint server available today, and its use is almost
+universal in mathematics and most branches of physics.  arXiv receives
+over 7,000 submissions per month
+(http://arxiv.org/show_monthly_submissions).  Paul Ginsparg originated
+ArXiv for high-energy physicists to communicate preprints via email
+and ftp.  Soon after its origination the world-wide web became
+available.
 
-% @Joel
+Submission to arXiv is fully automated via the world-wide web.
+Authors can submit LaTeX documents or directly in PDF format.  A
+moderation system was put in place in 2004: papers must be categorized
+by a moderator.  At least one author of a paper must be an
+``endorser'' that has previously submitted a paper or has received
+permission to submit.  Endorser status is automatic for members of
+recognized academic institutions.
+
+Most papers posted to arXiv are eventually printed in journals.  There
+are notable exceptions, including Perelman's landmark paper solving
+the Poincar\'{e} conjecture \cite{2002math.....11159P}.
+
+arXiv is now administered by the Cornell University Libraries.
+Funding comes from voluntary pledges by academic institutions along
+with matching funds from the Simons Foundation \cite{arxiv_future}.
+One-hundred twenty six of the top two-hundred institutions in terms of
+downloads have provided the operating budget for arXiv over the next
+five years.  This plan reduces the financial burden on Cornell
+University and transfers governance to a collaborative community in
+accordance with arXiv's key principles.
 

### 2012-09-07 ms.tex
Fleshed out paragraphs

@@
 
-arXiv (\href{http://arxiv.org/}{http://arxiv.org/}) is the most
-widely-used preprint server available today, and its use is almost
-universal in mathematics and most branches of physics.  arXiv receives
-over 7,000 submissions per month
-(http://arxiv.org/show_monthly_submissions).  Paul Ginsparg originated
-ArXiv for high-energy physicists to communicate preprints via email
-and ftp.  Soon after its origination the world-wide web became
-available.
+arXiv (\url{http://arxiv.org/}) is the most widely-used preprint
+server today, and its use is almost universal in mathematics and most
+branches of physics.  Physicist Paul Ginsparg originated arXiv in 1991
+for theoretical high-energy physicists to communicate preprints via
+email and ftp, and soon thereafter adopted the newly created
+world-wide web\cite{jackson2002preprints}.  arXiv now receives over
+7,000 submissions per month
+(\url{http://arxiv.org/show_monthly_submissions}).  arXiv divides its
+submissions into subcategories of physics, mathematics, computer
+science, quantitative biology, finance and statistics.  The
+quantitative biology category includes subcategories for Populations
+and Evolution, Quantitative Methods and other categories that may be
+of interest to ecologists and evolutionary biologists.
+% Check me on this @Pierre!  Not only is this vague, but I'm not sure
+% how to verify it; I want to give people the impression that a
+% "Quantitative ecology" or "General ecology" category could be
+% created easily
+The creation of new categories is regulated by the same system that
+categorizes papers.
 
 Submission to arXiv is fully automated via the world-wide web.
-Authors can submit LaTeX documents or directly in PDF format.  A
+Authors can submit \TeX{}/\LaTeX{} documents or directly in PDF or
+PostScript (for example, as exported by a word processor).  A
 moderation system was put in place in 2004: papers must be categorized
-by a moderator.  At least one author of a paper must be an
-``endorser'' that has previously submitted a paper or has received
-permission to submit.  Endorser status is automatic for members of
-recognized academic institutions.
+by an ``endorser.''  At least one author of a paper must be an
+endorser that has previously submitted a paper or has received
+permission to submit to a particular category.  Many authors in
+mathematics and physics submit papers as soon as they are ready for
+review by colleagues, although another popular option is submitting
+simultaneously to a journal and arXiv.
 
 Most papers posted to arXiv are eventually printed in journals.  There
-are notable exceptions, including Perelman's landmark paper solving
-the Poincar\'{e} conjecture \cite{2002math.....11159P}.
+are notable exceptions, including Perelman's landmark paper leading to
+the proof of the Poincar\'{e} conjecture \cite{2002math.....11159P}.
+arXiv provides a reliable citation system for all eprints (see our
+citation \cite{2002math.....11159P}), lending a form of ``intellectual
+priority'' to works posted there.  Despite these marks of arXiv 
+functioning as a scientific journal, arXiv has never sought to replace
+scientific journals and explicitly states that it serves a different
+function as ``an openly accessible, moderated repository for scholarly
+articles in specific scientific disciplines.''
 
@@
 University and transfers governance to a collaborative community in
-accordance with arXiv's key principles.
+accordance with arXiv's key principles.  arXiv takes numerous measures
+to ensure that the repository will remain permanently available and
+submissions will be readable.
 

### 2012-09-07 ms.tex
Added section on cultural barriers to adoption of preprint servers

@@
 
+There are other ``cultural'' barriers to adoption of preprint servers
+by ecologists and evolutionary biologists.  The most notable preprint
+server, arXiv, is designed to work best with \TeX{}, a nearly
+universal document preparation system among physicists and
+mathematicians.  Jackson \cite{jackson2002preprints} further argues
+that \TeX{} introduced an ``open source mindset'' to its users, who
+now freely share their research findings as well as their software.
+Many biologists instead use proprietary software to prepare their
+research findings, and many ecology and evolution journals officially
+prefer Microsoft Word documents as submissions.  The recent
+discipline-wide adoption of free software packages such as R, as well
+as interest in open access publishing, has coincided with recent use
+of preprint servers by biologists, supporting Jackson's claims.
+
 \section{Current offerings}

### 2012-09-10 ms.tex
Added paragraph on using arXiv for communication
Physicists and biologists will benefit from having biologists post their
papers to arXiv, since physicists all read arXiv and they don't read
evolution journals.  Added citations for deVladar and Barton, and Frank's
series on natural selection.

@@
 
+Physicists and other quantitative scientists have recently developed a
+great interest in evolutionary theory, quantitative ecological theory
+and epidemiological modeling.  Unfortunately this has led to a lot of
+repeated work (``reinventing the wheel''; \cite{de2011contribution})
+that could be avoided by better communication across disciplines.  The
+near-universal adoption of preprint servers in physics provides this
+vital communication channel.  We suggest that biologists reach out to
+physicists and mathematicians by posting papers to arXiv: a physicist
+who does not read \emph{Evolution} certainly checks arXiv at least
+weekly.  This benefits both disciplines, as biologists will reach new
+readers, and physicists will learn the terminology, tools and ideas
+common in existing evolutionary theory.  A recent series of papers on
+the theory of natural selection was posted to arXiv simultaneously
+with its publication in the \emph{Journal of Evolutionary Biology}
+\cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}.
+
 \section{Current offerings}

### 2012-09-10 ms.tex
Reviewed and edited; added a bit to conclusion
I reviewed and edited for minor grammar and corrected a few things of the
existing text.  I also added more to the conclusion paragraph, but This
paragraph still needs a little more.

@@
 
-Preprints servers such as arXiv are common in mathematics and physics, but
-still a minority of papers in ecology and evolution use them. Preprints
-servers allow author to make their manuscripts publicly available before, or
-in parallel to, submitting them to journals for traditional peer-review. ...
-The idea became popular with arXiv, and many physicists start their day with a
-look at the new papers in arXiv \cite{gin11}
+Preprint servers such as arXiv are common in mathematics and physics,
+but still a minority of papers in ecology and evolution use
+them. Preprint servers allow authors to make their manuscripts
+publicly available before, or at the same time as, submitting them to
+journals for traditional peer-review. ...  The idea became popular
+with arXiv, and many physicists start their day with a look at the new
+papers in ArXiv \cite{gin11}
 
@@
 
-The review process as a whole is critically over-loaded, because the number of
-active scientists increases, because the pressure to publish increases, and
-because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  In
-the same times, rejection rates are high in most journals (REF), and when the
-not invited to submit a revisions, authors are left with the impression that
-they must start the whole process all over again. It's thus no surprize that
-different initiatives emerged over the last few years, to decrease the time
-spent in review. XXX et coll. (REF) called for the recycling and reuse of
-peer-reviews: by attaching previous reviews, and detailed replies, to a new
-submission, both the editor and the referees can jauge the work done on the
-manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
-\emph{Peerage of Science} initiative allows authors to seek anonymous pre-
-review by their peers. Some journals (LIST?) now accept to publish papers
-which received good evaluations, effectively outsourcing the review process. A
-widespread use of preprint servers can achieve the same goal of reducing the
-time spent in review. By putting a manuscript out there for open comments and
-criticisms, the authors will receive valuable feedback, and can improve the
-version which will be submitted. With a rich enough community of scientists
-depositing preprints, and commenting on them, the process of an open pre-
-review can become widespread, and will overall increase the quality of first
-submissions.
+The review process as a whole is critically over-loaded, because the
+number of active scientists increases, because the pressure to publish
+increases, and because of an effect dubbed ``the tragedy of the
+reviewers commons'' REF.  At the same time, rejection rates are high
+in most journals (REF), and when not invited to submit revisions,
+authors are left with the impression that they must start the whole
+process all over again. It's thus no surprise that different
+initiatives emerged over the last few years to decrease the time spent
+in review. XXX et coll. (REF) called for the recycling and reuse of
+peer-reviews: by attaching previous reviews, and detailed replies, to
+a new submission, both the editor and the referees can gauge the work
+done on the manuscript, and perhaps evaluate it with less
+prejudice. In a similar way, the \emph{Peerage of Science} initiative
+allows authors to seek anonymous pre- review by their peers. Some
+journals (LIST?) now accept papers for publication that received good
+evaluations, effectively outsourcing the review process. A widespread
+use of preprint servers can achieve the same goal of reducing the time
+spent in review. By putting a manuscript out there for open comments
+and criticisms, the authors will receive valuable feedback, and can
+improve the version which will be submitted. With a rich enough
+community of scientists depositing preprints, and commenting on them,
+the process of an open pre- review can become widespread, and will
+overall increase the quality of first submissions.
 % Assuming that the quality of the paper is a good prior of its acceptance probability :-)
@@
 
-Preprint servers also establish priority in a fair way. Some manuscript will
-spend much more time in the review process. Public preprints server offer a
-much fairer way to establish intellectual priority by making the work
-available when done, and even if the exact organisation of the manuscript may
-change. Surprisingly, there is perception in biology that public preprints
-make it easier to steal ideas, as if scientific ideas only took form in
-published material.
+Preprint servers also establish priority in a fair way.  Some
+manuscripts will spend much more time in the review process than
+others.  Public preprint servers offer a much fairer way to establish
+intellectual priority by making the work available when done, even if
+the exact organisation of the manuscript may change. Surprisingly,
+there is a perception in biology that public preprints make it easier
+to steal ideas, as if scientific ideas only took form in published
+material.
 % TP This needs more development, I'm not sure I get your point
-Mathematicians and physicists have embraced arXiv in part
-to establish priority in a fair way\cite{cal12}.
+Mathematicians and physicists have embraced arXiv in part to establish
+priority in a fair way\cite{cal12}.
 
@@
 essentially, the same as exchanging preprints among colleagues.
-% TP Well, no. You trust your colleagues, and you trust that they will not give your
-%    MS to anyone!
-Prepublication reviews by a small network of colleagues is an important part
-of the scientific process, which is attested by the fact that nearly all
-published papers acknowledge comments by people not listed as co-authors.
-Preprints servers simply offer a way to extend this network of colleagues to
-the entire scientific community. It ensures that science is not constrained by
-small networks of scientists exchanging ideas. Ginsparg made arXiv.org in part
-for democratic reasons: he wanted everyone from graduate students in small
-universities to Princeton professors to have access to the most recent
-scientific \emph{ideas}.
+% TP Well, no. You trust your colleagues, and you trust that they will
+% not give your MS to anyone!
+Prepublication reviews by a small network of colleagues is an
+important part of the scientific process, which is attested by the
+fact that nearly all published papers acknowledge comments by people
+not listed as co-authors.  Preprint servers simply offer a way to
+extend this network of colleagues to the entire scientific
+community. It ensures that science is not constrained by small
+networks of scientists exchanging ideas.  Paul Ginsparg created
+arXiv.org in part for democratic reasons: he wanted everyone from
+students in small universities to Ivy-League professors to have access
+to the most recent scientific \emph{ideas}.
 % TP One important point to make: the MS and the idea are different things.
 %    We should focus more on the later...
-Ginsparg revolutionary idea was simply to use the power of the internet for
-preprints, not just for the end product, so the process can be open from A to
-Z, instead of being just open at the end of the process.
+Ginsparg's revolutionary idea was simply to use the power of the
+internet for preprints, not just for the end product, so the process
+can be open from A to Z, instead of being just open at the end of the
+process.
 % TP Since when is the publishing buisness an open process? :-)
@@
 at large in our peer review, selection and editing'' \cite{nat05}.
+Posting preprints online increases the community of available informal
+peer reviewers, and uses the internet for its original
+community-building purposes.  Preprint servers also facilitate
+communication between disciplines, bridging cultural as well as
+geographic divides.
+% JA: perhaps something less advertising-like should go here:
+The advantages are clear and the costs are low.
+% BUY NOW!
 

### 2012-09-10 ms.tex
started adding Karthik's notes to the ms

--- 2012-09-07 ms.tex
@@
 
-\author{Joel J. Adamson}
-\affiliation{Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill}
-
 \author{Timoth\'ee Poisot}
@@
 \affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
+
+\author{Karthik Ram}
+\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley. Berkeley, CA. United-States of America.}
 
@@
 
+\section{Introduction}
+
+Open preprints servers allow authors to make their manuscripts publicly available before, or in parallel to, submitting them to journals for traditional
+peer-review.
+This idea gained popularity 20 years ago with the advent of arXiv, an open preprint server, widely used in the physical sciences \cite{gin11}.
+The idea behind pre-print servers is fundamentally simple: to make the results of a scientific endavour available to the scientific community as soon as possible rather than wait until the peer-review process is fully completed.
+The point of arXiv and open preprints servers is not to avoid the peer-review.
+Almost all manuscripts submitted to arXiv undergo formal peer-review at a journal.
+The point is to open an important phase of the publication cycle ...
+
+In this article, we will first highlight the advantages of open preprints
+servers for both scientists and publishers. We will also debunk a few
+misconceptions, discuss the policies of major publishers in ecology an
+evolution, and briefly review the most popular open preprint servers.
+
 \section{The case for open preprints}
 
-Preprints servers such as arXiv are common in mathematics and physics, but
-still a minority of papers in ecology and evolution use them. Preprints
-servers allow author to make their manuscripts publicly available before, or
-in parallel to, submitting them to journals for traditional peer-review. ...
-The idea became popular with arXiv, and many physicists start their day with a
-look at the new papers in arXiv \cite{gin11}
-
-We will highlight advantages for both scientists and publishers.
-
-The first and most often discussed advantage is speed \ref{fig:map}.
+The first and most often discussed advantage of arXiv and open preprints is
+speed \ref{fig:map}. The time between submission and the official publication of
+a manuscript can be measured in months, sometime in years. For all this time,
+the research is only known to a select few: colleagues, editors, reviewers.
+Thus, the science cannot be used, discussed, or reviewed by the wider scientific
+community. ...
 
@@
 preprints, not just for the end product, so the process can be open from A to
-Z, instead of being just open at the end of the process.
+Z, instead of being just open at the end of the process (and often not open at
+all).
 % TP Since when is the publishing buisness an open process? :-)
+% PhDP: Wishful thinking :) Corrected...
+
+Preprint servers also establish priority in a fair way. Since some manuscripts
+will spend much more time in the review process, public preprints servers offer
+a fairer way to establish intellectual priority by making the work available
+when done. Surprisingly, there is perception in biology that public preprints
+make it easier to steal ideas, while mathematicians and physicists have embraced
+arXiv in part to establish intellectual priority in a fair way \cite{cal12}.
+
+Preprint servers also provide additional opportunities for review, often from members outside the list of authors or their immediate peers (cite).
+This process can further improve the quality of a manuscript before it reaches potential reviewers.
+pre-prints servers can therefore reduce reviewer load/burden by opening up oppportunities for additional feedback.
+
+% Karthik's section
+% I'll need to flesh this section out a bit more but here are the two main points
+% pre-print servers enrich the review process by providing a venue to solicit comments from anyone.
+Manuscripts can undergo several rounds of revision during this stage, resulting in a higher quality manuscrpt reaching reviewers than ones that have not undergone this process.
+There are various benefits here.
+First, it can reduce the time burden on reviewers, the need for multile rounds of revision.
+
+% Second point, pre-publication provides a scaffolding the possibility of a implementing a reward system for reviewers and publishers.
+Open reviews can be judged on their quality and usefulness both by the authors and by other members of the community.
+Reviews and comments deemed useful by the community can be used to reward contributers with reputation, which then provides a measure of trustworthiness.
+The reputation system can also serve to deter malicious reviews and personal attacks, and such penalties can limit  @PhDP: Do you think this is a useful direction to go?
+It could be moved into the discussion or stay with the benefits of pre-print servers.
 
@@
 
-While the practice is still rare, preprints are becoming more common in
-biological sciences, which is experiencing faster growth in arXiv submissions
-than any other fields \cite{cal12}. Also, most scientific journals are
-preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly)
+While submitting to public preprints servers is still uncommon in ecology and
+evolution, preprints are becoming more common in biological sciences. The
+quantitative biology section in arXiv is experiencing faster growth in
+submissions than any other fields \cite{cal12}. Also, most scientific journals
+are preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly)
 \ref{table:policies}, and all the journals from Elsevier and Springer. Very
-recently, the Ecological Society of America recently changed its policy to allow
+recently, the Ecological Society of America amended its policy to allow
 public preprints (REF). In our field, few scientific publications will not
-consider a manuscript submitted to arXiv. Still, many ecology \& evolution journals
-adopt a ``by default'' hostile attitude towards preprints, mostly due to the
-lack of clear policy of the publishers. As an example, Wiley-Blackwell, which
-publishes some of the leading journal in the field, has no official policy on
-the subject \ref{table:policies}.
+consider a manuscript submitted to arXiv.  Still, many ecology \& evolution
+journals adopt a ``by default'' hostile attitude towards preprints, mostly due
+to the lack of clear policy of the publishers. As an example, Wiley-Blackwell,
+which publishes some of the leading journal in the field, has no official policy
+on the subject \ref{table:policies}.
 
@@
 
-There are other ``cultural'' barriers to adoption of preprint servers
-by ecologists and evolutionary biologists.  The most notable preprint
-server, arXiv, is designed to work best with \TeX{}, a nearly
-universal document preparation system among physicists and
-mathematicians.  Jackson \cite{jackson2002preprints} further argues
-that \TeX{} introduced an ``open source mindset'' to its users, who
-now freely share their research findings as well as their software.
-Many biologists instead use proprietary software to prepare their
-research findings, and many ecology and evolution journals officially
-prefer Microsoft Word documents as submissions.  The recent
-discipline-wide adoption of free software packages such as R, as well
-as interest in open access publishing, has coincided with recent use
-of preprint servers by biologists, supporting Jackson's claims.
-
-\section{Current offerings}
+\section{Current offer}
 
@@
 
+arXiv (\href{http://arxiv.org/}{http://arxiv.org/}).
+arXiv is funded by a network of universities.
+
+...
+
 % @Joel
-% Rough outline:
-% 1. Description of arXiv (origins, funding, maintenance)
-% 2. Submission process
-% 3. Role within math and physics community (nearly universal), including recent changes
-% 4. Nature of citations and "priority"
-%
-% My biggest problem here is how to cite my sources: the information
-% on funding comes from a press release from Cornell University
-% Libraries; other basic "raw data" comes straight from the arXiv
-% webpages. How do I cite that?
-
-arXiv (\url{http://arxiv.org/}) is the most widely-used preprint
-server today, and its use is almost universal in mathematics and most
-branches of physics.  Physicist Paul Ginsparg originated arXiv in 1991
-for theoretical high-energy physicists to communicate preprints via
-email and ftp, and soon thereafter adopted the newly created
-world-wide web\cite{jackson2002preprints}.  arXiv now receives over
-7,000 submissions per month
-(\url{http://arxiv.org/show_monthly_submissions}).  arXiv divides its
-submissions into subcategories of physics, mathematics, computer
-science, quantitative biology, finance and statistics.  The
-quantitative biology category includes subcategories for Populations
-and Evolution, Quantitative Methods and other categories that may be
-of interest to ecologists and evolutionary biologists.
-% Check me on this @Pierre!  Not only is this vague, but I'm not sure
-% how to verify it; I want to give people the impression that a
-% "Quantitative ecology" or "General ecology" category could be
-% created easily
-The creation of new categories is regulated by the same system that
-categorizes papers.
-
-Submission to arXiv is fully automated via the world-wide web.
-Authors can submit \TeX{}/\LaTeX{} documents or directly in PDF or
-PostScript (for example, as exported by a word processor).  A
-moderation system was put in place in 2004: papers must be categorized
-by an ``endorser.''  At least one author of a paper must be an
-endorser that has previously submitted a paper or has received
-permission to submit to a particular category.  Many authors in
-mathematics and physics submit papers as soon as they are ready for
-review by colleagues, although another popular option is submitting
-simultaneously to a journal and arXiv.
-
-Most papers posted to arXiv are eventually printed in journals.  There
-are notable exceptions, including Perelman's landmark paper leading to
-the proof of the Poincar\'{e} conjecture \cite{2002math.....11159P}.
-arXiv provides a reliable citation system for all eprints (see our
-citation \cite{2002math.....11159P}), lending a form of ``intellectual
-priority'' to works posted there.  Despite these marks of arXiv 
-functioning as a scientific journal, arXiv has never sought to replace
-scientific journals and explicitly states that it serves a different
-function as ``an openly accessible, moderated repository for scholarly
-articles in specific scientific disciplines.''
-
-arXiv is now administered by the Cornell University Libraries.
-Funding comes from voluntary pledges by academic institutions along
-with matching funds from the Simons Foundation \cite{arxiv_future}.
-One-hundred twenty six of the top two-hundred institutions in terms of
-downloads have provided the operating budget for arXiv over the next
-five years.  This plan reduces the financial burden on Cornell
-University and transfers governance to a collaborative community in
-accordance with arXiv's key principles.  arXiv takes numerous measures
-to ensure that the repository will remain permanently available and
-submissions will be readable.
 

### 2012-09-14 ms.tex

--- 2012-09-10 ms.tex
@@
 
+\section{Introduction}
+
+Open preprints servers allow authors to make their manuscripts publicly
+available before, or in parallel to, submitting them to journals for traditional
+peer-review. The idea became popular with arXiv, an open preprint server, that
+started 20 years ago \cite{gin11}. The idea is fundamentally simple: to make the
+science available to the entire scientific community as soon as its done instead
+of having to wait for the peer-review process. The point of arXiv and open
+preprints servers is not to avoid the peer-review process. Almost all
+manuscripts on arXiv are submitted to peer-review. The point is to open an
+important phase of the publication cycle ...
+
+In this article, we will first highlight the advantages of open preprints
+servers for both scientists and publishers. We will also debunk a few
+misconceptions, discuss the policies of major publishers in ecology an
+evolution, and briefly review the most popular open preprint servers.
+
 \section{The case for open preprints}
 
-Preprint servers such as arXiv are common in mathematics and physics,
-but still a minority of papers in ecology and evolution use
-them. Preprint servers allow authors to make their manuscripts
-publicly available before, or at the same time as, submitting them to
-journals for traditional peer-review. ...  The idea became popular
-with arXiv, and many physicists start their day with a look at the new
-papers in ArXiv \cite{gin11}
-
-We will highlight advantages for both scientists and publishers.
-
-The first and most often discussed advantage is speed \ref{fig:map}.
+The first and most often discussed advantage of arXiv and open preprints is
+speed \ref{fig:map}. The time between submission and the official publication of
+a manuscript can be measured in months, sometime in years. For all this time,
+the research is only known to a select few: colleagues, editors, reviewers.
+Thus, the science cannot be used, discussed, or reviewed by the wider scientific
+community. ...
 
 %% Allows papers to be cited earlier (greater immediacy)
-
-%% @Tim: how can it improve the review process?
 
@@
 % TP Since when is the publishing buisness an open process? :-)
+% PhDP: Wishful thinking :) Corrected...
+
+Preprint servers also establish priority in a fair way. Since some manuscripts
+will spend much more time in the review process, public preprints servers offer
+a fairer way to establish intellectual priority by making the work available
+when done. Surprisingly, there is perception in biology that public preprints
+make it easier to steal ideas, while mathematicians and physicists have embraced
+arXiv in part to establish intellectual priority in a fair way \cite{cal12}.
 
@@
 
-% A short paragraph to conclude.
-
 Responding to the rumour that they refused manuscripts submitted to arXiv,
@@
 at large in our peer review, selection and editing'' \cite{nat05}.
+
+Open preprints server offer a great opportunity for open science, especially if
+the community embrace the idea of discussing preprints. Initiatives like
+Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
+new blog discussing arXiv papers in population genetics, will help make arXiv
+attractive for scientists looking to promote their work. These initiatives are
+important to fully exploit the potential of open preprints servers.
+
 Posting preprints online increases the community of available informal

### 2012-09-15 ms.tex
added some edits to the intro, notes (in comments) about further discussion points, and added some comments to the discussion.

@@
 
-\keywords{Publishing; arXiv; Green Open Access.}
+\author{Karthik Ram}
+\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley. Berkeley, CA. United-States of America.}
+
+\keywords{Publishing; arXiv; pre print server, Green Open Access.}
 
@@
 
-Open preprints servers allow authors to make their manuscripts publicly
-available before, or in parallel to, submitting them to journals for traditional
-peer-review. The idea became popular with arXiv, an open preprint server, that
-started 20 years ago \cite{gin11}. The idea is fundamentally simple: to make the
-science available to the entire scientific community as soon as its done instead
-of having to wait for the peer-review process. The point of arXiv and open
-preprints servers is not to avoid the peer-review process. Almost all
-manuscripts on arXiv are submitted to peer-review. The point is to open an
-important phase of the publication cycle ...
+Open preprints servers allow authors to make their manuscripts publicly available before, or in parallel to, submitting them to journals for traditional peer-review.
+This idea gained popularity 20 years ago with the advent of arXiv, an open preprint server, widely used in the physical sciences \cite{gin11}.
+The idea behind pre-print servers is fundamentally simple: to make the results of a scientific endavour available to the scientific community as soon as possible rather than wait until the peer-review process is fully completed.
+The point of arXiv and open preprints servers is not to avoid the peer-review process.
+Almost all manuscripts on arXiv are submitted to peer-review.
+Sharing drafts of research papers on pre-print servers has numerous advantages.
+These include rapid dissemination of work in progress to a wider audience that includes not only scientists and the general public, but also readers in developing countries where access to subscription journals are often a limiting factor.
+Further, pre-prints provide the opportunity to solicit feedback from a larger pool of reviewers.
+As a consequence, pre print servers increase the number of opportunities for review and revision prior to publication, resulting in higher quality submissions which could also alleviate reviewer burden.
 
@@
 prefer Microsoft Word documents as submissions.  The recent
-discipline-wide adoption of free software packages such as R, as well
-as interest in open access publishing, has coincided with recent use
+discipline-wide adoption of free software packages such as R and associated  document generation systems \cite{xie2012}, as well
+as interest in open access publishing, has coincided with recent rise in use
 of preprint servers by biologists, supporting Jackson's claims.
+% Please add this to your citation list: Xie Y (2012). knitr: A general-purpose pack­age for dynamic report gen­er­a­tion in R. R pack­age ver­sion 0.4.1, .
 
@@
 The advantages are clear and the costs are low.
+
+% Karthik's comments: 
+% It would be worthwhile to mention that not everyone is stoked about pre-print servers (crazy people). So maybe cite something to that effect?
+% ACS Journal Editors’ Policy on Preprints at http://pubs.acs.org/cen/ preprint.% html. Criticisms include: 
+% flooding the web with too many repetitive pubs
+% premature results without any support from data
+% etc.
+
 % BUY NOW!

### 2012-09-22 ms.tex
minor modif
merge

@@
 
+\author{Karthik Ram}
+\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley. Berkeley, CA. United-States of America.}
+
 \author{Dominique Gravel}
@@
 \affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
-
-\author{Karthik Ram}
-\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley. Berkeley, CA. United-States of America.}
 
@@
 
-The review process as a whole is critically over-loaded, because the
-number of active scientists increases, because the pressure to publish
-increases, and because of an effect dubbed ``the tragedy of the
-reviewers commons'' REF.  At the same time, rejection rates are high
-in most journals (REF), and when not invited to submit revisions,
-authors are left with the impression that they must start the whole
-process all over again. It's thus no surprise that different
-initiatives emerged over the last few years to decrease the time spent
-in review. XXX et coll. (REF) called for the recycling and reuse of
-peer-reviews: by attaching previous reviews, and detailed replies, to
-a new submission, both the editor and the referees can gauge the work
-done on the manuscript, and perhaps evaluate it with less
-prejudice. In a similar way, the \emph{Peerage of Science} initiative
-allows authors to seek anonymous pre- review by their peers. Some
-journals (LIST?) now accept papers for publication that received good
-evaluations, effectively outsourcing the review process. A widespread
-use of preprint servers can achieve the same goal of reducing the time
-spent in review. By putting a manuscript out there for open comments
-and criticisms, the authors will receive valuable feedback, and can
-improve the version which will be submitted. With a rich enough
-community of scientists depositing preprints, and commenting on them,
-the process of an open pre- review can become widespread, and will
-overall increase the quality of first submissions.
-% Assuming that the quality of the paper is a good prior of its acceptance probability :-)
+% Tim's section:
+The review process as a whole is critically over-loaded, because the number of
+active scientists increases, because the pressure to publish increases, and
+because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  In
+the same times, rejection rates are high in most journals (REF), and when the
+not invited to submit a revisions, authors are left with the impression that
+they must start the whole process all over again. It's thus no surprise that
+different initiatives emerged over the last few years, to decrease the time
+spent in review. XXX et coll. (REF) called for the recycling and reuse of
+peer-reviews: by attaching previous reviews, and detailed replies, to a new
+submission, both the editor and the referees can gauge the work done on the
+manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
+\emph{Peerage of Science} initiative allows authors to seek anonymous pre-
+review by their peers. Some journals (LIST?) now accept to publish papers
+which received good evaluations, effectively outsourcing the review process. A
+widespread use of preprint servers can achieve the same goal of reducing the
+time spent in review. By putting a manuscript out there for open comments and
+criticisms, the authors will receive valuable feedback, and can improve the
+version which will be submitted. With a rich enough community of scientists
+depositing preprints, and commenting on them, the process of an open pre-
+review can become widespread, and will overall increase the quality of first
+submissions.
 

### 2012-09-22 ms.tex
starting to integrate all parts into a coherent text

@@
 \author{Joel J. Adamson}
-\affiliation{Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill}
+\affiliation{Ecology, Evolution and Organismic Biology, University of North
+Carolina at Chapel Hill, United-States of America}
 
@@
 
-\keywords{Publishing; arXiv; pre print server, Green Open Access.}
+\keywords{Publishing; preprint server; arXiv; Green Open Access.}
 
@@
 
-Open preprints servers allow authors to make their manuscripts publicly available before, or in parallel to, submitting them to journals for traditional peer-review.
-This idea gained popularity 20 years ago with the advent of arXiv, an open preprint server, widely used in the physical sciences \cite{gin11}.
-The idea behind pre-print servers is fundamentally simple: to make the results of a scientific endavour available to the scientific community as soon as possible rather than wait until the peer-review process is fully completed.
-The point of arXiv and open preprints servers is not to avoid the peer-review process.
-Almost all manuscripts on arXiv are submitted to peer-review.
-Sharing drafts of research papers on pre-print servers has numerous advantages.
-These include rapid dissemination of work in progress to a wider audience that includes not only scientists and the general public, but also readers in developing countries where access to subscription journals are often a limiting factor.
-Further, pre-prints provide the opportunity to solicit feedback from a larger pool of reviewers.
-As a consequence, pre print servers increase the number of opportunities for review and revision prior to publication, resulting in higher quality submissions which could also alleviate reviewer burden.
+Public preprints servers allow authors to make their manuscripts publicly
+available before, or in parallel to, submitting them to journals for traditional
+peer-review. This idea gained popularity 20 years ago with the advent of arXiv,
+an open preprint server widely used in the physical sciences \cite{gin11}, but
+it also part of other fields' culture. Paul Krugman noted that, in economy, the
+\emph{traditional model of submit, get refereed, publish, and then people will
+read your work broke down a long time ago. In fact, it had more or less fallen
+apart by the early 80s} \cite{kru12}. In addition to a section in arXiv,
+economists have also the RePEc (Research Papers in Economics) initiative, which
+aims to create an archive of working papers, manuscripts, and book chapters.
 
+The idea behind preprint servers is fundamentally simple: to make the results
+available to the scientific community as soon as possible rather than wait until
+the peer-review process is fully completed. The point of arXiv and open
+preprints servers is not to avoid the peer-review process. Almost all
+manuscripts on arXiv are submitted to peer-review.  Sharing drafts of research
+papers on preprint servers has numerous advantages. These include rapid
+dissemination of work in progress to a wider audience that includes not only
+scientists and the general public, but also readers in developing countries
+where access to subscription journals are often a limiting factor. Further,
+preprints provide the opportunity to solicit feedback from a larger pool of
+reviewers. As a consequence, preprint servers increase the number of
+opportunities for review and revision prior to publication, resulting in higher
+quality submissions which could also alleviate reviewer burden.
+
+Yet, despite the success of the approach in other fields of inquiry, most
+manuscripts in ecology and evolution are never submitted to any public archive.
 In this article, we will first highlight the advantages of open preprints
@@
 Thus, the science cannot be used, discussed, or reviewed by the wider scientific
-community. ...
+community. It is a problem for both scientists and publishers. Manuscripts that
+are unknown cannot be integrated and thus take more time to be cited.
 
-%% Allows papers to be cited earlier (greater immediacy)
-
-% Tim's section:
 The review process as a whole is critically over-loaded, because the number of
@@
 
-Preprint servers also establish priority in a fair way.  Some
-manuscripts will spend much more time in the review process than
-others.  Public preprint servers offer a much fairer way to establish
-intellectual priority by making the work available when done, even if
-the exact organisation of the manuscript may change. Surprisingly,
-there is a perception in biology that public preprints make it easier
-to steal ideas, as if scientific ideas only took form in published
-material.
-% TP This needs more development, I'm not sure I get your point
-Mathematicians and physicists have embraced arXiv in part to establish
-priority in a fair way\cite{cal12}.
+Preprint servers also establish priority in a fair way.  Some manuscripts will
+spend much more time in the review process than others.  Public preprint servers
+offer a much fairer way to establish intellectual priority by making the work
+available when done, even if the exact organisation of the manuscript may
+change. Surprisingly, there is a perception in biology that public preprints
+make it easier to steal ideas, as if scientific ideas only took form in
+published material.  Mathematicians and physicists have embraced arXiv in part
+to establish priority in a fair way\cite{cal12}.
 
 Some of the responses to public preprints are surprising since they are,
-essentially, the same as exchanging preprints among colleagues.
-% TP Well, no. You trust your colleagues, and you trust that they will
-% not give your MS to anyone!
-Prepublication reviews by a small network of colleagues is an
-important part of the scientific process, which is attested by the
-fact that nearly all published papers acknowledge comments by people
-not listed as co-authors.  Preprint servers simply offer a way to
-extend this network of colleagues to the entire scientific
-community. It ensures that science is not constrained by small
-networks of scientists exchanging ideas.  Paul Ginsparg created
-arXiv.org in part for democratic reasons: he wanted everyone from
-students in small universities to Ivy-League professors to have access
-to the most recent scientific \emph{ideas}.
-% TP One important point to make: the MS and the idea are different things.
-%    We should focus more on the later...
-Ginsparg's revolutionary idea was simply to use the power of the
-internet for preprints, not just for the end product, so the process
-can be open from A to Z, instead of being just open at the end of the
-process.
-% TP Since when is the publishing buisness an open process? :-)
-% PhDP: Wishful thinking :) Corrected...
+essentially, the same as exchanging preprints among colleagues.  Prepublication
+reviews by a small network of colleagues is an important part of the scientific
+process, which is attested by the fact that nearly all published papers
+acknowledge comments by people not listed as co-authors.  Preprint servers
+simply offer a way to extend this network of colleagues to the entire scientific
+community. It ensures that science is not constrained by small networks of
+scientists exchanging ideas.  Paul Ginsparg created arXiv.org in part for
+democratic reasons: he wanted everyone from students in small universities to
+Ivy-League professors to have access to the most recent scientific \emph{ideas}.
+Ginsparg's revolutionary idea was simply to use the power of the internet for
+preprints, not just for the end product, so the process can be open from A to Z,
+instead of being just open at the end of the process.
+% TP One important point to make: the MS and the idea are different things.  We
+% should focus more on the later...
 
@@
     National Academy of Science (USA)           & Accept \\
-    Ecological Society of America       	& Accept \\ % Victory!
-    Science                             	& Accept/Ambiguous \\
-    Wiley-Blackwell                       	& No general policy \\ % grrrrrr
-    British Ecological Society                  & ? \\ % Waiting for their answer...
-    % Oxford worth mentionning?
+    Ecological Society of America       	& Accept \\
+    Oxford Journals                             & Accept \\
+    Science                             	& Ambiguous \\
+    Wiley-Blackwell                       	& No general policy \\
+    British Ecological Society                  & No answer to our query \\
     \hline
@@
 
-There are other ``cultural'' barriers to adoption of preprint servers
-by ecologists and evolutionary biologists.  The most notable preprint
-server, arXiv, is designed to work best with \TeX{}, a nearly
-universal document preparation system among physicists and
-mathematicians.  Jackson \cite{jackson2002preprints} further argues
-that \TeX{} introduced an ``open source mindset'' to its users, who
-now freely share their research findings as well as their software.
-Many biologists instead use proprietary software to prepare their
-research findings, and many ecology and evolution journals officially
-prefer Microsoft Word documents as submissions.  The recent
-discipline-wide adoption of free software packages such as R and associated  document generation systems \cite{xie2012}, as well
-as interest in open access publishing, has coincided with recent rise in use
-of preprint servers by biologists, supporting Jackson's claims.
-% Please add this to your citation list: Xie Y (2012). knitr: A general-purpose pack­age for dynamic report gen­er­a­tion in R. R pack­age ver­sion 0.4.1, .
+There are other ``cultural'' barriers to adoption of preprint servers by
+ecologists and evolutionary biologists.  The most notable preprint server,
+arXiv, is designed to work best with \TeX{}, a nearly universal document
+preparation system among physicists and mathematicians.  Jackson
+\cite{jackson2002preprints} further argues that \TeX{} introduced an ``open
+source mindset'' to its users, who now freely share their research findings as
+well as their software.  Many biologists instead use proprietary software to
+prepare their research findings, and many ecology and evolution journals
+officially prefer Microsoft Word documents as submissions.  The recent
+discipline-wide adoption of free software packages such as R and associated
+document generation systems \cite{xie2012}, as well as interest in open access
+publishing, has coincided with recent rise in use of preprint servers by
+biologists, supporting Jackson's claims. \cite{xie12}
 
@@
 
-% @Joel
 % Rough outline:
@@
 % webpages. How do I cite that?
+% -- Joel
 
-arXiv (\url{http://arxiv.org/}) is the most widely-used preprint
-server today, and its use is almost universal in mathematics and most
-branches of physics.  Physicist Paul Ginsparg originated arXiv in 1991
-for theoretical high-energy physicists to communicate preprints via
-email and ftp, and soon thereafter adopted the newly created
-world-wide web\cite{jackson2002preprints}.  arXiv now receives over
-7,000 submissions per month
+arXiv (\url{http://arxiv.org/}) is the most widely-used preprint server today,
+and its use is almost universal in mathematics and most branches of physics.
+Physicist Paul Ginsparg originated arXiv in 1991 for theoretical high-energy
+physicists to communicate preprints via email and ftp, and soon thereafter
+adopted the newly created world-wide web\cite{jackson2002preprints}.  arXiv now
+receives over 7,000 submissions per month
 (\url{http://arxiv.org/show_monthly_submissions}).  arXiv divides its
-submissions into subcategories of physics, mathematics, computer
-science, quantitative biology, finance and statistics.  The
-quantitative biology category includes subcategories for Populations
-and Evolution, Quantitative Methods and other categories that may be
-of interest to ecologists and evolutionary biologists.
-% Check me on this @Pierre!  Not only is this vague, but I'm not sure
-% how to verify it; I want to give people the impression that a
-% "Quantitative ecology" or "General ecology" category could be
-% created easily
-The creation of new categories is regulated by the same system that
-categorizes papers.
+submissions into subcategories of physics, mathematics, computer science,
+quantitative biology, finance and statistics.  The quantitative biology category
+includes subcategories for Populations and Evolution, Quantitative Methods and
+other categories that may be of interest to ecologists and evolutionary
+biologists.
 
-Submission to arXiv is fully automated via the world-wide web.
-Authors can submit \TeX{}/\LaTeX{} documents or directly in PDF or
-PostScript (for example, as exported by a word processor).  A
-moderation system was put in place in 2004: papers must be categorized
-by an ``endorser.''  At least one author of a paper must be an
-endorser that has previously submitted a paper or has received
-permission to submit to a particular category.  Many authors in
-mathematics and physics submit papers as soon as they are ready for
+Submission to arXiv is fully automated via the world-wide web.  Authors can
+submit \TeX/\LaTeX documents that are compiled on the server, or directly submit
+in PDF/PS format (for example, as exported by a word processor).  A moderation
+system was put in place in 2004: papers must be categorized by an ``endorser.''
+At least one author of a paper must be an endorser that has previously submitted
+a paper or has received permission to submit to a particular category.  Many
+authors in mathematics and physics submit papers as soon as they are ready for
 review by colleagues, although another popular option is submitting
@@
 
-Most papers posted to arXiv are eventually printed in journals.  There
-are notable exceptions, including Perelman's landmark paper leading to
-the proof of the Poincar\'{e} conjecture \cite{2002math.....11159P}.
-arXiv provides a reliable citation system for all eprints (see our
-citation \cite{2002math.....11159P}), lending a form of ``intellectual
-priority'' to works posted there.  Despite these marks of arXiv 
-functioning as a scientific journal, arXiv has never sought to replace
-scientific journals and explicitly states that it serves a different
-function as ``an openly accessible, moderated repository for scholarly
-articles in specific scientific disciplines.''
+Most papers posted to arXiv are eventually printed in journals.  There are
+notable exceptions, including Perelman's landmark paper leading to the proof of
+the Poincar\'{e} conjecture \cite{2002math.....11159P}.  arXiv provides a
+reliable citation system for all eprints (see our citation
+\cite{2002math.....11159P}), lending a form of ``intellectual priority'' to
+works posted there.  Despite these marks of arXiv functioning as a scientific
+journal, arXiv has never sought to replace scientific journals and explicitly
+states that it serves a different function as ``an openly accessible, moderated
+repository for scholarly articles in specific scientific disciplines.''
 
-arXiv is now administered by the Cornell University Libraries.
-Funding comes from voluntary pledges by academic institutions along
-with matching funds from the Simons Foundation \cite{arxiv_future}.
-One-hundred twenty six of the top two-hundred institutions in terms of
-downloads have provided the operating budget for arXiv over the next
-five years.  This plan reduces the financial burden on Cornell
-University and transfers governance to a collaborative community in
-accordance with arXiv's key principles.  arXiv takes numerous measures
-to ensure that the repository will remain permanently available and
+arXiv is now administered by the Cornell University Libraries.  Funding comes
+from voluntary pledges by academic institutions along with matching funds from
+the Simons Foundation \cite{arxiv_future}.  One-hundred twenty six of the top
+two-hundred institutions in terms of downloads have provided the operating
+budget for arXiv over the next five years.  This plan reduces the financial
+burden on Cornell University and transfers governance to a collaborative
+community in accordance with arXiv's key principles.  arXiv takes numerous
+measures to ensure that the repository will remain permanently available and
 submissions will be readable.
@@
 
-% @PhDP
-
-Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open servers
-that allow scientists to submit any research output: manuscript, figures,
+Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
+that allows scientists to submit any research output: manuscript, figures,
 datasets, videos, theses, presentations, and so on. There are no rules to limit
-what constitutes a research output: anything
-
-All figshare content (article, figures, datasets) have a unique digital object
-identifier (DOI) like any journal article.
-
-All content is licensed under the Creative Commons (CC-BY) license, except
-datasets which are published under CC0.
-% Small explanation
+what constitutes a research output and, unlike arXiv, there is no endorser
+system (although the administrator reserve the right to remove inappropriate
+content). All figshare content (article, figures, datasets) have a unique
+digital object identifier (DOI) like any journal article. Tags are used to
+classify the content and new tags can be made. All content can be commented and
+is licensed under the Creative Commons (CC-BY) license, except datasets which
+are published under CC0.
 
@@
 
-Posting preprints online increases the community of available informal
-peer reviewers, and uses the internet for its original
-community-building purposes.  Preprint servers also facilitate
-communication between disciplines, bridging cultural as well as
-geographic divides.
-% JA: perhaps something less advertising-like should go here:
-The advantages are clear and the costs are low.
+Posting preprints online increases the community of available informal peer
+reviewers, and uses the internet for its original community-building purposes.
+Preprint servers also facilitate communication between disciplines, bridging
+cultural as well as geographic divides. The advantages are clear and the costs are low.
 
-% Karthik's comments: 
-% It would be worthwhile to mention that not everyone is stoked about pre-print servers (crazy people). So maybe cite something to that effect?
-% ACS Journal Editors’ Policy on Preprints at http://pubs.acs.org/cen/ preprint.% html. Criticisms include: 
-% flooding the web with too many repetitive pubs
-% premature results without any support from data
-% etc.
-
-% BUY NOW!
+% Short list of disadvantages
 

### 2012-09-25 ms.tex

@@
 an open preprint server widely used in the physical sciences \cite{gin11}, but
-it also part of other fields' culture. Paul Krugman noted that, in economy, the
-\emph{traditional model of submit, get refereed, publish, and then people will
-read your work broke down a long time ago. In fact, it had more or less fallen
-apart by the early 80s} \cite{kru12}. In addition to a section in arXiv,
+it also part of other fields' culture. Paul Krugman noted that, in economics,
+the \emph{traditional model of submit, get refereed, publish, and then people
+will read your work broke down a long time ago. In fact, it had more or less
+fallen apart by the early 80s} \cite{kru12}. In addition to a section in arXiv,
 economists have also the RePEc (Research Papers in Economics) initiative, which
@@
 
-Preprint servers also establish priority in a fair way. Since some manuscripts
-will spend much more time in the review process, public preprints servers offer
-a fairer way to establish intellectual priority by making the work available
-when done. Surprisingly, there is perception in biology that public preprints
-make it easier to steal ideas, while mathematicians and physicists have embraced
-arXiv in part to establish intellectual priority in a fair way \cite{cal12}.
-
 \section{Preprints, Ecology \& Evolution}
@@
 quantitative biology section in arXiv is experiencing faster growth in
-submissions than any other fields \cite{cal12}. Also, most scientific journals
+submissions than any other field \cite{cal12}. Also, most scientific journals
 are preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly)

### 2012-09-26 ms.tex
change title
merging ethans branch
minor edits

@@
 
-\title{Open Preprints in Ecology \& Evolution}
+\title{Developing a preprint culture in biology}
 
@@
 Yet, despite the success of the approach in other fields of inquiry, most
-manuscripts in ecology and evolution are never submitted to any public archive.
-In this article, we will first highlight the advantages of open preprints
-servers for both scientists and publishers. We will also debunk a few
-misconceptions, discuss the policies of major publishers in ecology an
-evolution, and briefly review the most popular open preprint servers.
+manuscripts in biology are never submitted to any public archive.  In this
+article, we will first highlight the advantages of open preprints servers for
+both scientists and publishers. We will also debunk a few misconceptions,
+discuss the policies of major publishers in biology, and briefly review the most
+popular open preprint servers.
 
@@
 
-\section{Preprints, Ecology \& Evolution}
+\section{Preprints in biological sciences}
 
-While submitting to public preprints servers is still uncommon in ecology and
-evolution, preprints are becoming more common in biological sciences. The
-quantitative biology section in arXiv is experiencing faster growth in
-submissions than any other field \cite{cal12}. Also, most scientific journals
-are preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly)
-\ref{table:policies}, and all the journals from Elsevier and Springer. Very
-recently, the Ecological Society of America recently changed its policy to allow
-public preprints (REF). In our field, few scientific publications will not
-consider a manuscript submitted to arXiv.  Still, many ecology \& evolution
-journals adopt a ``by default'' hostile attitude towards preprints, mostly due
-to the lack of clear policy of the publishers. As an example, Wiley-Blackwell,
-which publishes some of the leading journal in the field, has no official policy
-on the subject \ref{table:policies}.
+While submitting to public preprints servers is still uncommon in biology,
+preprints are becoming more common in biological sciences. The quantitative
+biology section in arXiv is experiencing faster growth in submissions than any
+other field \cite{cal12}. Also, most scientific journals are preprint-friendly:
+Nature, PLOS, BMC, PNAS, Science (mostly) \ref{table:policies}, and all the
+journals from Elsevier and Springer. Very recently, the Ecological Society of
+America recently changed its policy to allow public preprints (REF). In our
+field, few scientific publications will not consider a manuscript submitted to
+arXiv.  Still, many journals adopt a ``by default'' hostile attitude towards
+preprints, mostly due to the lack of clear policy of the publishers. As an
+example, Wiley-Blackwell, which publishes some of the leading journal in the
+field, has no official policy on the subject \ref{table:policies}.
 
@@
     \end{tabular}
-    \caption{Policies for important publishers in ecology and evolution.}
+    \caption{Policies for important publishers in biology. Some publishers
+tolerate preprints except for a few of their medical journals, e.g.: Journal
+of the National Cancer Institute from Oxford and The Lancer from Elsevier.}
     \label{table:policies}
@@
 There are other ``cultural'' barriers to adoption of preprint servers by
-ecologists and evolutionary biologists.  The most notable preprint server,
+biologists.  The most notable preprint server,
 arXiv, is designed to work best with \TeX{}, a nearly universal document
@@
 well as their software.  Many biologists instead use proprietary software to
-prepare their research findings, and many ecology and evolution journals
-officially prefer Microsoft Word documents as submissions.  The recent
-discipline-wide adoption of free software packages such as R and associated
-document generation systems \cite{xie2012}, as well as interest in open access
-publishing, has coincided with recent rise in use of preprint servers by
-biologists, supporting Jackson's claims. \cite{xie12}
+prepare their research findings, and many journals officially prefer Microsoft
+Word documents as submissions.  The recent discipline-wide adoption of free
+software packages such as R and associated document generation systems
+\cite{xie2012}, as well as interest in open access publishing, has coincided
+with recent rise in use of preprint servers by biologists, supporting Jackson's
+claims. \cite{xie12}
 
@@
 includes subcategories for Populations and Evolution, Quantitative Methods and
-other categories that may be of interest to ecologists and evolutionary
-biologists.
+other categories that may be of interest to biologists.
 
@@
 \end{document}
+
+%The average time to publication vary a lot between journal and can be as low as
+%104 days (Evolution for 2011) to 213 (PLOS One in 2010)

### 2012-09-26 ms.tex
first round of editing for the first two sections

@@
 
-\begin{abstract}
-
-...
-
-\end{abstract}
+% No abstract needed.
 
@@
 peer-review. This idea gained popularity 20 years ago with the advent of arXiv,
-an open preprint server widely used in the physical sciences \cite{gin11}, but
-it also part of other fields' culture. Paul Krugman noted that, in economics,
+an open preprint server widely used in physics and mathematics \cite{gin11}. 
+It is also part of other fields' culture. Paul Krugman noted that, in economics,
 the \emph{traditional model of submit, get refereed, publish, and then people
@@
 preprints servers is not to avoid the peer-review process. Almost all
-manuscripts on arXiv are submitted to peer-review.  Sharing drafts of research
-papers on preprint servers has numerous advantages. These include rapid
-dissemination of work in progress to a wider audience that includes not only
-scientists and the general public, but also readers in developing countries
+manuscripts on arXiv are submitted to peer-review.  The point is that sharing
+ideas as quickly as possible using preprint servers has numerous advantages.
+These include rapid dissemination of work in progress to a wider audience, not
+only scientists and the general public but also readers in developing countries
 where access to subscription journals are often a limiting factor. Further,
@@
 community. It is a problem for both scientists and publishers. Manuscripts that
-are unknown cannot be integrated and thus take more time to be cited.
+are unknown cannot be integrated and thus take more time to be cited. It has
+been shown that high-energy physics, with its high arXiv submission rate, had
+the highest immediacy among physics and mathematics \cite{pra05}.
 
@@
 active scientists increases, because the pressure to publish increases, and
-because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  In
-the same times, rejection rates are high in most journals (REF), and when the
-not invited to submit a revisions, authors are left with the impression that
-they must start the whole process all over again. It's thus no surprise that
-different initiatives emerged over the last few years, to decrease the time
-spent in review. XXX et coll. (REF) called for the recycling and reuse of
-peer-reviews: by attaching previous reviews, and detailed replies, to a new
-submission, both the editor and the referees can gauge the work done on the
-manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
-\emph{Peerage of Science} initiative allows authors to seek anonymous pre-
-review by their peers. Some journals (LIST?) now accept to publish papers
-which received good evaluations, effectively outsourcing the review process. A
-widespread use of preprint servers can achieve the same goal of reducing the
-time spent in review. By putting a manuscript out there for open comments and
-criticisms, the authors will receive valuable feedback, and can improve the
-version which will be submitted. With a rich enough community of scientists
-depositing preprints, and commenting on them, the process of an open pre-
-review can become widespread, and will overall increase the quality of first
-submissions.
+because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  At
+the same times, rejection rates are high in most journals (REF), and when not
+invited to submit a revisions, authors must start the whole process all over
+again. It's thus no surprise that different initiatives emerged over the last
+few years, to decrease the time spent in review. XXX et coll. (REF) called for
+the recycling and reuse of peer-reviews: by attaching previous reviews, and
+detailed replies, to a new submission, both the editor and the referees can
+gauge the work done on the manuscript, and perhaps evaluate it with less
+prejudice. In a similar way, the \emph{Peerage of Science} initiative allows
+authors to seek anonymous pre-review by their peers. Some journals now accept
+to publish papers which received good evaluations, effectively outsourcing the
+review process. A widespread use of preprint servers can achieve the same goal
+of reducing the time spent in review. By putting a manuscript for open
+comments and criticisms, the authors will receive valuable feedback and can
+improve the version which will be submitted. With a rich enough community of
+scientists depositing preprints, and commenting on them, the process of an open
+pre-review can become widespread and will overall increase the quality of
+first submissions.
 
@@
 \caption { It can take several months, and even a few years, before a submitted
-paper is officially published and citable. During this time, few people are
-aware of the research that has been done (typically, close colleagues are
-given access to the preprints). With public preprint servers, the science is
-immediately available and can be openly discussed, analysed, and integrated
-into current research. It benefits both science and publishers. Both want the
-papers to be well-known and cited, and public preprints make it possible to
-integrate research even before publication, greatly improving immediacy.  }
-\label{fig:map}
-\end{figure}
+paper is officially published and citable.  The average time to publication
+varies greatly between journals and can be as low as 104 days (Evolution for
+2011) to 213 (PLOS One in 2010).  Meanwhile, few people are aware of the
+research that has been done since, typically, only close colleagues are given
+access to the preprints. With public preprint servers, the science is
+immediately available and can be openly discussed, analysed, and integrated into
+current research. It benefits both science and publishers. Both want the papers
+to be well-known and cited, and public preprints make it possible to integrate
+research even before publication, greatly improving immediacy.  }
+\label{fig:map} \end{figure}
 
-Preprint servers also establish priority in a fair way.  Some manuscripts will
-spend much more time in the review process than others.  Public preprint servers
-offer a much fairer way to establish intellectual priority by making the work
-available when done, even if the exact organisation of the manuscript may
-change. Surprisingly, there is a perception in biology that public preprints
-make it easier to steal ideas, as if scientific ideas only took form in
-published material.  Mathematicians and physicists have embraced arXiv in part
-to establish priority in a fair way\cite{cal12}.
+Public preprint servers offer a much fairer way to establish intellectual
+priority by making the work available when done. Some manuscripts will spend
+much more time in the review process than others. Surprisingly, there is a
+perception in biology that public preprints make it easier to steal ideas, as if
+a scientific idea was only complete once published in a peer-reviewed journal.
+Mathematicians and physicists have embraced arXiv in part to establish priority
+in a fair way and biologists should do so too, or at least not be afraid to
+submit to make their research public for fear of been snooped \cite{cal12}.
 
@@
 instead of being just open at the end of the process.
-% TP One important point to make: the MS and the idea are different things.  We
-% should focus more on the later...
 
@@
 journals from Elsevier and Springer. Very recently, the Ecological Society of
-America recently changed its policy to allow public preprints (REF). In our
-field, few scientific publications will not consider a manuscript submitted to
-arXiv.  Still, many journals adopt a ``by default'' hostile attitude towards
-preprints, mostly due to the lack of clear policy of the publishers. As an
-example, Wiley-Blackwell, which publishes some of the leading journal in the
-field, has no official policy on the subject \ref{table:policies}.
+America and the Genetics Society of America changed their policies to allow
+public preprints. Few scientific publications will not consider a manuscript
+submitted to a public preprint server.  Still, a few journals adopt a ``by
+default'' hostile attitude towards preprints, mostly due to the lack of clear
+policy of the publishers, or perhaps because a preprint culture has not
+developed in biology. As an example, Wiley-Blackwell, which publishes some of
+the leading journal in the field, has no official policy on the subject
+\ref{table:policies}.
 
@@
     Public Library of Science           	& Accept \\
+    Genetics Society of America                 & Accept \\
     Royal Society                       	& Accept \\
@@
 
-There are other ``cultural'' barriers to adoption of preprint servers by
-biologists.  The most notable preprint server,
-arXiv, is designed to work best with \TeX{}, a nearly universal document
-preparation system among physicists and mathematicians.  Jackson
-\cite{jackson2002preprints} further argues that \TeX{} introduced an ``open
-source mindset'' to its users, who now freely share their research findings as
-well as their software.  Many biologists instead use proprietary software to
-prepare their research findings, and many journals officially prefer Microsoft
-Word documents as submissions.  The recent discipline-wide adoption of free
-software packages such as R and associated document generation systems
+There are other barriers to adoption of preprint servers by biologists.  The
+most notable preprint server, arXiv, is designed to work best with \LaTeX, the
+dominant document preparation system among physicists and mathematicians.
+Jackson \cite{jackson2002preprints} further argues that \LaTeX introduced an
+open source mindset to its users, who now freely share their research
+findings as well as their software.  Many biologists instead use proprietary
+software to prepare their research findings, and many journals officially prefer
+Microsoft Word documents as submissions.  The recent discipline-wide adoption of
+free software packages such as R and associated document generation systems
 \cite{xie2012}, as well as interest in open access publishing, has coincided
 with recent rise in use of preprint servers by biologists, supporting Jackson's
-claims. \cite{xie12}
-
-Physicists and other quantitative scientists have recently developed a
-great interest in evolutionary theory, quantitative ecological theory
-and epidemiological modeling.  Unfortunately this has led to a lot of
-repeated work (``reinventing the wheel''; \cite{de2011contribution})
-that could be avoided by better communication across disciplines.  The
-near-universal adoption of preprint servers in physics provides this
-vital communication channel.  We suggest that biologists reach out to
-physicists and mathematicians by posting papers to arXiv: a physicist
-who does not read \emph{Evolution} certainly checks arXiv at least
-weekly.  This benefits both disciplines, as biologists will reach new
-readers, and physicists will learn the terminology, tools and ideas
-common in existing evolutionary theory.  A recent series of papers on
-the theory of natural selection was posted to arXiv simultaneously
-with its publication in the \emph{Journal of Evolutionary Biology}
-\cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}.
+claims \cite{xie12}.
 
@@
 \subsection{arXiv}
-
-% Rough outline:
-% 1. Description of arXiv (origins, funding, maintenance)
-% 2. Submission process
-% 3. Role within math and physics community (nearly universal), including recent changes
-% 4. Nature of citations and "priority"
-%
-% My biggest problem here is how to cite my sources: the information
-% on funding comes from a press release from Cornell University
-% Libraries; other basic "raw data" comes straight from the arXiv
-% webpages. How do I cite that?
-% -- Joel
 
@@
 what constitutes a research output and, unlike arXiv, there is no endorser
-system (although the administrator reserve the right to remove inappropriate
-content). All figshare content (article, figures, datasets) have a unique
-digital object identifier (DOI) like any journal article. Tags are used to
-classify the content and new tags can be made. All content can be commented and
-is licensed under the Creative Commons (CC-BY) license, except datasets which
-are published under CC0.
+system. All figshare content has a unique digital object identifier (DOI) like
+any journal article, thus offering a permanent and stable link to the content.
+A flexible tag system is used to classify the content. All content can
+be commented and is licensed under the Creative Commons (CC-BY) license, except
+datasets which are published under CC0.
+
+One of the biggest advantage of figshare over arXiv is that is it not limited to
+quantitative sciences. arXiv.org has sections on quantitative biology but might
+not be appropriate for non-quantitative work. With its flexible approach to
+preprints, figshare offer an important alternative to arXiv for empirical
+biologists. Furthermore, by allowing all
 
@@
 \subsection{F1000Research}
-
-% Written from memory: to verify!
 
@@
 response.
+
+\subsection{Github et al.?}
+
+This manuscript was developed entirely as an open project on github. github is a
+hosting service for projects under the git revision control tool. git is a
+decentralized revision control system used primarily to develop software. It
+allows the users to share code, track changes, and merge versions. For example,
+during the development of this manuscript, one author would fork the project
+(that is: make a personal copy), modify it, and then the changes were merged
+back into the main branch. These techniques are widely used in open source
+software development. It goes even farther than submitting preprints by opening
+the entire writing process.
 
@@
 Preprint servers also facilitate communication between disciplines, bridging
-cultural as well as geographic divides. The advantages are clear and the costs are low.
+cultural as well as geographic divides. The advantages are clear and the costs
+are low.
 
-% Short list of disadvantages
+Physicists and other quantitative scientists have recently developed a great
+interest in evolutionary theory, quantitative ecological theory and
+epidemiological modeling.  Unfortunately this has led to a lot of repeated work
+(``reinventing the wheel''; \cite{de2011contribution}) that could be avoided by
+better communication across disciplines.  The near-universal adoption of
+preprint servers in physics provides this vital communication channel.  We
+suggest that biologists reach out to physicists and mathematicians by posting
+papers to arXiv: a physicist who does not read \emph{Evolution} certainly checks
+arXiv at least weekly.  This benefits both disciplines, as biologists will reach
+new readers, and physicists will learn the terminology, tools and ideas common
+in existing evolutionary theory.  A recent series of papers on the theory of
+natural selection was posted to arXiv simultaneously with its publication in the
+\emph{Journal of Evolutionary Biology}
+\cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}.
+
+\section{Funding}
+
+PDP is funded by an Alexander Graham Bell scholarship from the National Sciences
+and Engineering Council of Canada.
+
+DG is funded by a Discovery Grand from the National Sciences and Engineering
+Council of Canada and by the Canada Research Chair program.
+
+\section{Acknowledgements}
+
+...
 
@@
 \end{document}
-
-%The average time to publication vary a lot between journal and can be as low as
-%104 days (Evolution for 2011) to 213 (PLOS One in 2010)

### 2012-09-26 ms.tex
peerage of science

@@
 prejudice. In a similar way, the \emph{Peerage of Science} initiative allows
-authors to seek anonymous pre-review by their peers. Some journals now accept
-to publish papers which received good evaluations, effectively outsourcing the
-review process. A widespread use of preprint servers can achieve the same goal
-of reducing the time spent in review. By putting a manuscript for open
-comments and criticisms, the authors will receive valuable feedback and can
-improve the version which will be submitted. With a rich enough community of
-scientists depositing preprints, and commenting on them, the process of an open
-pre-review can become widespread and will overall increase the quality of
-first submissions.
+authors to seek anonymous pre-review by their peers. Some journals now accept to
+publish papers which received good evaluations, with \emph{Animal Biology}
+having recently accepted first a paper reviewed entirely with the \emph{Peerage of
+Science} \cite{abb12}, effectively outsourcing the review process. A widespread
+use of preprint servers can achieve the same goal of reducing the time spent in
+review. By putting a manuscript for open comments and criticisms, the authors
+will receive valuable feedback and can improve the version which will be
+submitted. With a rich enough community of scientists depositing preprints, and
+commenting on them, the process of an open pre-review can become widespread and
+will overall increase the quality of first submissions.
 

### 2012-09-28 ms.tex
revision of the intro

@@
 
-\keywords{Publishing; preprint server; arXiv; Green Open Access.}
+\keywords{Publishing; preprint server; Green Open Access; arXiv.}
 
@@
 available before, or in parallel to, submitting them to journals for traditional
-peer-review. This idea gained popularity 20 years ago with the advent of arXiv,
-an open preprint server widely used in physics and mathematics \cite{gin11}. 
-It is also part of other fields' culture. Paul Krugman noted that, in economics,
-the \emph{traditional model of submit, get refereed, publish, and then people
-will read your work broke down a long time ago. In fact, it had more or less
-fallen apart by the early 80s} \cite{kru12}. In addition to a section in arXiv,
-economists have also the RePEc (Research Papers in Economics) initiative, which
-aims to create an archive of working papers, manuscripts, and book chapters.
-
-The idea behind preprint servers is fundamentally simple: to make the results
-available to the scientific community as soon as possible rather than wait until
-the peer-review process is fully completed. The point of arXiv and open
-preprints servers is not to avoid the peer-review process. Almost all
+peer-review. The idea behind preprint servers is fundamentally simple: to make
+the results available to the scientific community as soon as possible rather
+than wait until the peer-review process is fully completed. The point of arXiv
+and open preprints servers is not to avoid the peer-review process. Almost all
 manuscripts on arXiv are submitted to peer-review.  The point is that sharing
@@
 only scientists and the general public but also readers in developing countries
-where access to subscription journals are often a limiting factor. Further,
+where access to subscription journals are often a limiting factor. Furthermore,
 preprints provide the opportunity to solicit feedback from a larger pool of
-reviewers. As a consequence, preprint servers increase the number of
+reviewers and can be seen as an integral aspect of a vigorous peer-review
+process \cite{hoc12}. Thus, preprint servers increase the number of
 opportunities for review and revision prior to publication, resulting in higher
@@
 
+The idea gained popularity 20 years ago with the advent of arXiv, an open
+preprint server widely used in physics and mathematics \cite{gin11}.  It is also
+part of other fields' culture. Paul Krugman noted that, in economics, the
+\emph{traditional model of submit, get refereed, publish, and then people will
+read your work broke down a long time ago. In fact, it had more or less fallen
+apart by the early 80s} \cite{kru12}. In addition to a section in arXiv,
+economists have also the RePEc (Research Papers in Economics) initiative, which
+aims to create an archive of working papers, manuscripts, and book chapters.
 Yet, despite the success of the approach in other fields of inquiry, most

### 2012-09-28 ms.tex
comment

@@
 
-While submitting to public preprints servers is still uncommon in biology,
-preprints are becoming more common in biological sciences. The quantitative
-biology section in arXiv is experiencing faster growth in submissions than any
-other field \cite{cal12}. Also, most scientific journals are preprint-friendly:
-Nature, PLOS, BMC, PNAS, Science (mostly) \ref{table:policies}, and all the
-journals from Elsevier and Springer. Very recently, the Ecological Society of
-America and the Genetics Society of America changed their policies to allow
-public preprints. Few scientific publications will not consider a manuscript
-submitted to a public preprint server.  Still, a few journals adopt a ``by
-default'' hostile attitude towards preprints, mostly due to the lack of clear
-policy of the publishers, or perhaps because a preprint culture has not
-developed in biology. As an example, Wiley-Blackwell, which publishes some of
-the leading journal in the field, has no official policy on the subject
-\ref{table:policies}.
+Submitting to a preprint server is becoming more common in biology, even though
+it still involves a minority of papers. The quantitative biology section in
+arXiv is experiencing faster growth in submissions than any other field
+\cite{cal12}. Also, most scientific journals are preprint-friendly: Nature,
+PLOS, BMC, PNAS, Science (mostly) \ref{table:policies}, and all the journals
+from Elsevier and Springer. Very recently, the Ecological Society of America and
+the Genetics Society of America changed their policies to allow public
+preprints. Few scientific publications will not consider a manuscript submitted
+to a public preprint server.  Still, a few journals adopt a ``by default''
+hostile attitude towards preprints, mostly due to the lack of clear policy of
+the publishers, or perhaps because a preprint culture has not developed in
+biology and the practice is still considered unusual. As an example,
+Wiley-Blackwell, which publishes some leading journals, has no official policy
+on the subject \ref{table:policies}.
 
@@
 
+% Not sure about this paragraph, as much as I love to hate MS Office, I would
+% rather keep the thing as a "pro-preprint" paper only and not use it to promote
+% LaTeX/R.
+% -- PhDP
 There are other barriers to adoption of preprint servers by biologists.  The
@@
 dominant document preparation system among physicists and mathematicians.
-Jackson \cite{jackson2002preprints} further argues that \LaTeX introduced an
+Jackson \cite{jackson2002preprints} argues that \LaTeX introduced an
 open source mindset to its users, who now freely share their research

### 2012-09-28 ms.tex
editing arxiv section

@@
-\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4}
+\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4-1}
 \usepackage[utf8]{inputenc}
@@
 
-The review process as a whole is critically over-loaded, because the number of
-active scientists increases, because the pressure to publish increases, and
-because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  At
-the same times, rejection rates are high in most journals (REF), and when not
-invited to submit a revisions, authors must start the whole process all over
-again. It's thus no surprise that different initiatives emerged over the last
-few years, to decrease the time spent in review. XXX et coll. (REF) called for
-the recycling and reuse of peer-reviews: by attaching previous reviews, and
-detailed replies, to a new submission, both the editor and the referees can
-gauge the work done on the manuscript, and perhaps evaluate it with less
-prejudice. In a similar way, the \emph{Peerage of Science} initiative allows
-authors to seek anonymous pre-review by their peers. Some journals now accept to
-publish papers which received good evaluations, with \emph{Animal Biology}
-having recently accepted first a paper reviewed entirely with the \emph{Peerage of
-Science} \cite{abb12}, effectively outsourcing the review process. A widespread
-use of preprint servers can achieve the same goal of reducing the time spent in
-review. By putting a manuscript for open comments and criticisms, the authors
-will receive valuable feedback and can improve the version which will be
-submitted. With a rich enough community of scientists depositing preprints, and
-commenting on them, the process of an open pre-review can become widespread and
-will overall increase the quality of first submissions.
+Furthermore, the review process as a whole is critically over-loaded, because
+the number of active scientists increases, because the pressure to publish
+increases, and because of an effect dubbed ``the tragedy of the reviewers
+commons'' REF.  At the same times, rejection rates are high in most journals
+(REF), and when not invited to submit a revision, authors must start the whole
+process all over again. It's thus no surprise that different initiatives emerged
+over the last few years to decrease the time spent in review. XXX et coll.
+(REF) called for the recycling and reuse of peer-reviews: by attaching previous
+reviews and detailed replies to a new submission, both the editor and the
+referees can gauge the work done on the manuscript, and perhaps evaluate it with
+less prejudice. In a similar way, the \emph{Peerage of Science} initiative
+allows authors to seek anonymous pre-review by their peers. Some journals now
+accept to publish papers which received good evaluations, with \emph{Animal
+Biology} having recently accepted first a paper reviewed entirely with the
+\emph{Peerage of Science} \cite{abb12}, effectively outsourcing the review
+process. A widespread use of preprint servers can achieve the same goal of
+reducing the time spent in review. By putting a manuscript for open comments and
+criticisms, the authors will receive valuable feedback and can improve the
+version which will be submitted. With a rich enough community of scientists
+depositing preprints, and commenting on them, the process of an open pre-review
+can become widespread and will overall increase the quality of first
+submissions.
 
@@
 access to the preprints. With public preprint servers, the science is
-immediately available and can be openly discussed, analysed, and integrated into
+immediately available and can be openly discussed, analyzed, and integrated into
 current research. It benefits both science and publishers. Both want the papers
@@
 
-Some of the responses to public preprints are surprising since they are,
-essentially, the same as exchanging preprints among colleagues.  Prepublication
-reviews by a small network of colleagues is an important part of the scientific
-process, which is attested by the fact that nearly all published papers
-acknowledge comments by people not listed as co-authors.  Preprint servers
-simply offer a way to extend this network of colleagues to the entire scientific
-community. It ensures that science is not constrained by small networks of
-scientists exchanging ideas.  Paul Ginsparg created arXiv.org in part for
-democratic reasons: he wanted everyone from students in small universities to
-Ivy-League professors to have access to the most recent scientific \emph{ideas}.
-Ginsparg's revolutionary idea was simply to use the power of the internet for
-preprints, not just for the end product, so the process can be open from A to Z,
-instead of being just open at the end of the process.
+Prepublication reviews by a small network of colleagues is an important part of
+the scientific process, which is attested by the fact that nearly all published
+papers acknowledge comments by people not listed as co-authors.  Preprint
+servers simply offer a way to extend this network of colleagues to the entire
+scientific community. It ensures that science is not constrained by small
+networks of scientists exchanging ideas.  Paul Ginsparg created arXiv.org in
+part for democratic reasons: he wanted everyone from students in small
+universities to Ivy-League professors to have access to the most recent
+scientific \emph{ideas}.  Ginsparg's revolutionary idea was simply to use the
+power of the internet for preprints, not just for the end product, so the
+scientific process can be open as soon as possible.
 
@@
 % -- PhDP
-There are other barriers to adoption of preprint servers by biologists.  The
-most notable preprint server, arXiv, is designed to work best with \LaTeX, the
-dominant document preparation system among physicists and mathematicians.
-Jackson \cite{jackson2002preprints} argues that \LaTeX introduced an
-open source mindset to its users, who now freely share their research
-findings as well as their software.  Many biologists instead use proprietary
-software to prepare their research findings, and many journals officially prefer
-Microsoft Word documents as submissions.  The recent discipline-wide adoption of
-free software packages such as R and associated document generation systems
-\cite{xie2012}, as well as interest in open access publishing, has coincided
-with recent rise in use of preprint servers by biologists, supporting Jackson's
-claims \cite{xie12}.
+
+%There are other barriers to adoption of preprint servers by biologists.  The
+%most notable preprint server, arXiv, is designed to work best with \LaTeX, the
+%dominant document preparation system among physicists and mathematicians.
+%Jackson \cite{jackson2002preprints} argues that \LaTeX introduced an
+%open source mindset to its users, who now freely share their research
+%findings as well as their software.  Many biologists instead use proprietary
+%software to prepare their research findings, and many journals officially prefer
+%Microsoft Word documents as submissions.  The recent discipline-wide adoption of
+%free software packages such as R and associated document generation systems
+%\cite{xie2012}, as well as interest in open access publishing, has coincided
+%with recent rise in use of preprint servers by biologists, supporting Jackson's
+%claims \cite{xie12}.
 
@@
 arXiv (\url{http://arxiv.org/}) is the most widely-used preprint server today,
-and its use is almost universal in mathematics and most branches of physics.
-Physicist Paul Ginsparg originated arXiv in 1991 for theoretical high-energy
-physicists to communicate preprints via email and ftp, and soon thereafter
-adopted the newly created world-wide web\cite{jackson2002preprints}.  arXiv now
-receives over 7,000 submissions per month
-(\url{http://arxiv.org/show_monthly_submissions}).  arXiv divides its
+and its use is almost universal in some branches of mathematics and physics.  It
+provides a reliable citation system for all eprints and is especially popular in
+high-energy physics. Physicist Paul Ginsparg created arXiv in 1991 for
+theoretical high-energy physicists to communicate preprints via email and ftp,
+and soon thereafter adopted the newly created world-wide
+web\cite{jackson2002preprints}.  arXiv now receives over 7,000 submissions per
+month (\url{http://arxiv.org/show_monthly_submissions}) and divides its
 submissions into subcategories of physics, mathematics, computer science,
@@
 
-Submission to arXiv is fully automated via the world-wide web.  Authors can
-submit \TeX/\LaTeX documents that are compiled on the server, or directly submit
-in PDF/PS format (for example, as exported by a word processor).  A moderation
-system was put in place in 2004: papers must be categorized by an ``endorser.''
-At least one author of a paper must be an endorser that has previously submitted
-a paper or has received permission to submit to a particular category.  Many
-authors in mathematics and physics submit papers as soon as they are ready for
-review by colleagues, although another popular option is submitting
-simultaneously to a journal and arXiv.
+Submission to arXiv is fully automated.  Authors can submit \TeX/\LaTeX
+documents that are compiled on the server or directly submit in PDF/PS format
+(for example, as exported by a word processor).  A moderation system was put in
+place in 2004: papers must be categorized by an endorser. At least one
+author of a paper must be an endorser that has previously submitted a paper or
+has received permission to submit to a particular category.  Many authors in
+mathematics and physics submit papers as soon as they are ready for review by
+colleagues, although another popular option is submitting simultaneously to a
+journal and arXiv.
 
-Most papers posted to arXiv are eventually printed in journals.  There are
-notable exceptions, including Perelman's landmark paper leading to the proof of
-the Poincar\'{e} conjecture \cite{2002math.....11159P}.  arXiv provides a
-reliable citation system for all eprints (see our citation
-\cite{2002math.....11159P}), lending a form of ``intellectual priority'' to
-works posted there.  Despite these marks of arXiv functioning as a scientific
-journal, arXiv has never sought to replace scientific journals and explicitly
-states that it serves a different function as ``an openly accessible, moderated
-repository for scholarly articles in specific scientific disciplines.''
-
-arXiv is now administered by the Cornell University Libraries.  Funding comes
-from voluntary pledges by academic institutions along with matching funds from
-the Simons Foundation \cite{arxiv_future}.  One-hundred twenty six of the top
-two-hundred institutions in terms of downloads have provided the operating
-budget for arXiv over the next five years.  This plan reduces the financial
-burden on Cornell University and transfers governance to a collaborative
-community in accordance with arXiv's key principles.  arXiv takes numerous
-measures to ensure that the repository will remain permanently available and
-submissions will be readable.
+Most papers posted to arXiv are eventually printed in journals but there are
+notable exceptions, such as Perelman's landmark paper leading to the proof of
+the Poincar\'{e} conjecture \cite{2002math.....11159P}. Yet, arXiv has never
+sought to replace scientific journals and explicitly states that it serves a
+different function as ``an openly accessible, moderated repository for scholarly
+articles in specific scientific disciplines.'' arXiv is now administered by the
+Cornell University Libraries, with funding coming from voluntary pledges by academic
+institutions along with matching funds from the Simons Foundation
+\cite{arxiv_future}.  One-hundred twenty six of the top two-hundred institutions
+in terms of downloads have provided the operating budget for arXiv over the next
+five years.  This plan reduces the financial burden on Cornell University and
+transfers governance to a collaborative community in accordance with arXiv's key
+principles.  arXiv takes numerous measures to ensure that the repository will
+remain permanently available and submissions will be readable.
 

### 2012-09-28 ms.tex
add license discussion

@@
 
+% To review: 
+To submit to arXiv, the authors must either have their work available under an
+open license or grant arXiv a non-exclusive and irrevocable license to
+distribute the article. In either case, arXiv does not require copyright
+transfer and only requires the rights to distribute submitted articles in
+perpetuity. Thus, submitting to arXiv does not in itself prevent the authors
+from transferring their rights to a publisher, which is why most publishers
+tolerate arXiv, even though they ask the authors to transfer their right to them
+upon acceptance of the article.
+
 Most papers posted to arXiv are eventually printed in journals but there are
@@
 any journal article, thus offering a permanent and stable link to the content.
-A flexible tag system is used to classify the content. All content can
-be commented and is licensed under the Creative Commons (CC-BY) license, except
+A flexible tag system is used to classify each item. All content can be
+commented and is licensed under the Creative Commons (CC-BY) license, except
 datasets which are published under CC0.

### 2012-09-28 ms.tex
discussion

@@
 arXiv is experiencing faster growth in submissions than any other field
-\cite{cal12}. Also, most scientific journals are preprint-friendly: Nature,
-PLOS, BMC, PNAS, Science (mostly) \ref{table:policies}, and all the journals
-from Elsevier and Springer. Very recently, the Ecological Society of America and
-the Genetics Society of America changed their policies to allow public
-preprints. Few scientific publications will not consider a manuscript submitted
-to a public preprint server.  Still, a few journals adopt a ``by default''
-hostile attitude towards preprints, mostly due to the lack of clear policy of
-the publishers, or perhaps because a preprint culture has not developed in
-biology and the practice is still considered unusual. As an example,
-Wiley-Blackwell, which publishes some leading journals, has no official policy
-on the subject \ref{table:policies}.
+\cite{cal12}. Examples include a recent series of papers on the theory of
+natural selection that was posted to arXiv simultaneously with its publication
+in the \emph{Journal of Evolutionary Biology}
+\cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}.
+
+Most scientific journals are preprint-friendly: Nature, PLOS, BMC, PNAS, Science
+(mostly) \ref{table:policies}, and all the journals from Elsevier and Springer.
+Very recently, the Ecological Society of America and the Genetics Society of
+America changed their policies to allow public preprints. Few scientific
+publications will not consider a manuscript submitted to a public preprint
+server.  Still, a few journals adopt a ``by default'' hostile attitude towards
+preprints, mostly due to the lack of clear policy of the publishers, or perhaps
+because a preprint culture has not developed in biology and the practice is
+still considered unusual. As an example, Wiley-Blackwell, which publishes some
+leading journals, has no official policy on the subject \ref{table:policies}.
 
@@
 commented and is licensed under the Creative Commons (CC-BY) license, except
-datasets which are published under CC0.
+datasets which are published under CC0. The CC-BY license grant the rights to
+\emph{copy, distribute, display and perform the work and make derivative works
+based on it only if they give the author or licensor the credits in the manner
+specified by these.} The CC0 is the most permissive license and make the work
+public domain (no rights reserved) or, if it is not possible in the given
+jurisdiction, provides a simple permissive license.
 
@@
 preprints, figshare offer an important alternative to arXiv for empirical
-biologists. Furthermore, by allowing all
+biologists. Furthermore, by allowing all types of contents, figshare arguably
+provides an archive for early results (e.g.: figures, lab presentations).
 
@@
 
+Open preprints servers offer a great opportunity for open science, especially if
+the community embrace the idea of discussing preprints. Initiatives like
+Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
+new blog discussing arXiv papers in population genetics, will help make arXiv
+attractive for scientists looking to promote their work. These initiatives are
+important to fully exploit the potential of open preprints servers. Posting
+preprints online increases the community of available informal peer reviewers,
+and uses the internet for its original community-building purposes.  Preprint
+servers also facilitate communication between disciplines, bridging cultural as
+well as geographic divides. The advantages are clear and the costs are low.
 Responding to the rumour that they refused manuscripts submitted to arXiv,
@@
 at large in our peer review, selection and editing'' \cite{nat05}.
-
-Open preprints server offer a great opportunity for open science, especially if
-the community embrace the idea of discussing preprints. Initiatives like
-Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
-new blog discussing arXiv papers in population genetics, will help make arXiv
-attractive for scientists looking to promote their work. These initiatives are
-important to fully exploit the potential of open preprints servers.
-
-Posting preprints online increases the community of available informal peer
-reviewers, and uses the internet for its original community-building purposes.
-Preprint servers also facilitate communication between disciplines, bridging
-cultural as well as geographic divides. The advantages are clear and the costs
-are low.
-
-Physicists and other quantitative scientists have recently developed a great
-interest in evolutionary theory, quantitative ecological theory and
-epidemiological modeling.  Unfortunately this has led to a lot of repeated work
-(``reinventing the wheel''; \cite{de2011contribution}) that could be avoided by
-better communication across disciplines.  The near-universal adoption of
-preprint servers in physics provides this vital communication channel.  We
-suggest that biologists reach out to physicists and mathematicians by posting
-papers to arXiv: a physicist who does not read \emph{Evolution} certainly checks
-arXiv at least weekly.  This benefits both disciplines, as biologists will reach
-new readers, and physicists will learn the terminology, tools and ideas common
-in existing evolutionary theory.  A recent series of papers on the theory of
-natural selection was posted to arXiv simultaneously with its publication in the
-\emph{Journal of Evolutionary Biology}
-\cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}.
 

### 2012-09-28 ms.tex
start work on Ingelfinger, add refs
Ingelfinger

@@
 
+Part of the hostility to preprints servers comes from a certain interpretation
+of the Ingelfinger rule: scientists should not publish the same manuscript twice
+\cite{alt96}. However, papers submitted to arXiv or other preprints servers are
+only published in one peer-reviewed journal. A preprint is just a preprint, it
+is a document that allows ideas to spread and be discussed, but it is not yet
+formally validated by the peer-review system, which is why the majority of
+publishers does not see arXiv and similar services as a violation of the
+Ingelfinger rule. \emph{Nature} responded to the rumour that they refused
+manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
+stand in the way of communication between researchers. We seek rather to add
+value for authors and the community at large in our peer review, selection and
+editing'' \cite{nat05}.
+
+% Discuss embargoes?
+%A second potential problem is embargoes. Many publishers subject their article
+%to embargoes \cite{rea12}.
+
 \begin{table*}
@@
 well as geographic divides. The advantages are clear and the costs are low.
-Responding to the rumour that they refused manuscripts submitted to arXiv,
-Nature responded that ``Nature never wishes to stand in the way of communication
-between researchers. We seek rather to add value for authors and the community
-at large in our peer review, selection and editing'' \cite{nat05}.
 

### 2012-09-28 ms.tex

@@
 
-% @Ethan
+PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new publishing
+system that provides both a preprint server, and a peer reviewed journal.
+It is focused on the the biological and medical sciences, which may help
+overcome the perception that preprints do not have a home in biology.
+PeerJ allows commenting on posted preprints, improving the potential
+for pre-publication dialog. In addition, preprints can be made private if
+the authors choose, and shared only with selected colleagues. While this
+reduces some of the benefits of preprints described above, it may allow
+some researchers who would not otherwise post preprints to begin to explore
+the possibility in a manner appropriate to their current circumstances.
+
+In contrast to other preprint servers users cannot post unlimited public
+preprints for free. One preprint per year can be posted for free and a
+onetime (i.e. lifetime) fee of 99 dollars allows the posting of unlimited
+public preprints. It is also worth noting that the preprint server is not
+tied to the journal, so preprints can be posted regardless of where they
+will eventually be submitted for publication.
 

### 2012-09-28 ms.tex
Minor changes; added to a few sentences about git

@@
 
-Submission to arXiv is fully automated.  Authors can submit \TeX/\LaTeX
+Submission to arXiv is fully automated.  Authors can submit \TeX{}/\LaTeX{}
 documents that are compiled on the server or directly submit in PDF/PS format
@@
 
-Most papers posted to arXiv are eventually printed in journals but there are
-notable exceptions, such as Perelman's landmark paper leading to the proof of
-the Poincar\'{e} conjecture \cite{2002math.....11159P}. Yet, arXiv has never
-sought to replace scientific journals and explicitly states that it serves a
-different function as ``an openly accessible, moderated repository for scholarly
-articles in specific scientific disciplines.'' arXiv is now administered by the
-Cornell University Libraries, with funding coming from voluntary pledges by academic
-institutions along with matching funds from the Simons Foundation
-\cite{arxiv_future}.  One-hundred twenty six of the top two-hundred institutions
-in terms of downloads have provided the operating budget for arXiv over the next
-five years.  This plan reduces the financial burden on Cornell University and
-transfers governance to a collaborative community in accordance with arXiv's key
-principles.  arXiv takes numerous measures to ensure that the repository will
-remain permanently available and submissions will be readable.
+Most papers posted to arXiv are eventually printed in journals but
+there are notable exceptions, such as Perelman's landmark paper
+leading to the proof of the Poincar\'{e} conjecture
+\cite{2002math.....11159P}. Yet, arXiv has never sought to replace
+scientific journals and explicitly states that it serves a different
+function as ``an openly accessible, moderated repository for scholarly
+articles in specific scientific disciplines.'' arXiv is now
+administered by the Cornell University Libraries, with funding coming
+from voluntary pledges by academic institutions along with matching
+funds from the Simons Foundation \cite{arxiv_future}.  One-hundred
+twenty six of the top two-hundred institutions in terms of downloads
+have provided the operating budget for arXiv over the next five years.
+This plan reduces the financial burden on Cornell University and
+transfers governance to a collaborative community in accordance with
+arXiv's key principles.  arXiv takes numerous measures to ensure that
+the repository will remain permanently available and submissions will
+be readable.
 
@@
 
-This manuscript was developed entirely as an open project on github. github is a
-hosting service for projects under the git revision control tool. git is a
-decentralized revision control system used primarily to develop software. It
-allows the users to share code, track changes, and merge versions. For example,
-during the development of this manuscript, one author would fork the project
-(that is: make a personal copy), modify it, and then the changes were merged
-back into the main branch. These techniques are widely used in open source
-software development. It goes even farther than submitting preprints by opening
-the entire writing process.
+This manuscript was developed entirely as an open project on
+github. github is one of several hosting services for collaborative
+development using the git revision control software.  git is a
+decentralized revision control system created by Linus Torvalds used
+primarily to develop software, including the Linux kernel. It allows
+the users to share code, track changes, and merge versions. For
+example, during the development of this manuscript, one author would
+fork the project (that is: make a personal copy), modify it, and then
+the changes were merged back into the main branch. These techniques
+are widely used in open source software development. It goes even
+farther than submitting preprints by opening the entire writing
+process.
 
@@
 
+JJA is supported by NSF DEB-0614166 and NSF DEB-0919018.
+
 \section{Acknowledgements}

### 2012-09-28 ms.tex
Proofreading; demonic physics-enrichment programme
Gave this a thorough proof-reading for grammar (subject-verb and plural
agreement).  I also clarified and rearranged some sentences.  I
reinserted my idea about reaching physicists through submitting to ArXiv,
this time as a two-sentence comment.  This is a big problem in
evolutionary biology and it would be good to have more about it in
print.  I hope we can find some way to keep it.

@@
-\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4-1}
+\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4}
 \usepackage[utf8]{inputenc}
@@
 
-Public preprints servers allow authors to make their manuscripts publicly
-available before, or in parallel to, submitting them to journals for traditional
-peer-review. The idea behind preprint servers is fundamentally simple: to make
-the results available to the scientific community as soon as possible rather
-than wait until the peer-review process is fully completed. The point of arXiv
-and open preprints servers is not to avoid the peer-review process. Almost all
-manuscripts on arXiv are submitted to peer-review.  The point is that sharing
-ideas as quickly as possible using preprint servers has numerous advantages.
-These include rapid dissemination of work in progress to a wider audience, not
-only scientists and the general public but also readers in developing countries
-where access to subscription journals are often a limiting factor. Furthermore,
-preprints provide the opportunity to solicit feedback from a larger pool of
-reviewers and can be seen as an integral aspect of a vigorous peer-review
-process \cite{hoc12}. Thus, preprint servers increase the number of
-opportunities for review and revision prior to publication, resulting in higher
-quality submissions which could also alleviate reviewer burden.
+Public preprint servers allow authors to make manuscripts publicly
+available before, or in parallel to, submitting them to journals for
+traditional peer-review. The rationale for preprint servers is
+fundamentally simple: to make the results available to the scientific
+community as soon as possible rather than to wait until the
+peer-review process is fully completed. The goal of arXiv and open
+preprint servers is not to avoid the peer-review process; almost all
+manuscripts on arXiv are submitted to peer-review.  Sharing ideas as
+quickly as possible using preprint servers has numerous advantages.
+These include rapid dissemination of work in progress to a wider
+audience, including readers in developing countries where access to
+subscription journals is often a limiting factor in scientific
+research.  Furthermore, preprints provide the opportunity to solicit
+feedback from a larger pool of reviewers and can be seen as an
+integral aspect of a vigorous peer-review process \cite{hoc12}.
+Preprint servers therefore increase the number of opportunities for
+review and revision prior to publication, resulting in higher quality
+submissions and also could alleviate reviewer burden.
 
-The idea gained popularity 20 years ago with the advent of arXiv, an open
-preprint server widely used in physics and mathematics \cite{gin11}.  It is also
-part of other fields' culture. Paul Krugman noted that, in economics, the
-\emph{traditional model of submit, get refereed, publish, and then people will
-read your work broke down a long time ago. In fact, it had more or less fallen
-apart by the early 80s} \cite{kru12}. In addition to a section in arXiv,
-economists have also the RePEc (Research Papers in Economics) initiative, which
-aims to create an archive of working papers, manuscripts, and book chapters.
-Yet, despite the success of the approach in other fields of inquiry, most
-manuscripts in biology are never submitted to any public archive.  In this
-article, we will first highlight the advantages of open preprints servers for
-both scientists and publishers. We will also debunk a few misconceptions,
-discuss the policies of major publishers in biology, and briefly review the most
-popular open preprint servers.
+Preprints gained popularity 20 years ago with the advent of arXiv, an
+open preprint server widely used in physics and mathematics
+\cite{gin11}. Preprints are also integral to the culture of other
+scientific fields.  Paul Krugman noted that, in economics, the
+\emph{traditional model of submit, get refereed, publish, and then
+  people will read your work broke down a long time ago. In fact, it
+  had more or less fallen apart by the early 80s} \cite{kru12}. In
+addition to a section in arXiv, economists have also the RePEc
+(Research Papers in Economics) initiative, which aims to create an
+archive of working papers, manuscripts, and book chapters.  Despite
+the success of this approach in other fields, most manuscripts in
+biology are never submitted to any public archive.
+% JJA: This is a tenuous statement: MANY if not most biomedical labs
+% in the US are funded by NIH, which requires submission to Pubmed
+% Central, which many would consider a preprint archive.  In other
+% words, a biomedical editor might take issue with this statement,
+% especially if he considers "biology" to be just his part of biology
+% --- I know plenty of people who only think of "biology" as
+% biomedical science
+In this article, we will first highlight the advantages of open
+preprint servers for both scientists and publishers. We will also
+debunk a few misconceptions, discuss the policies of major publishers
+in biology, and briefly review the most popular open preprint servers.
 
@@
 
-The first and most often discussed advantage of arXiv and open preprints is
-speed \ref{fig:map}. The time between submission and the official publication of
-a manuscript can be measured in months, sometime in years. For all this time,
-the research is only known to a select few: colleagues, editors, reviewers.
-Thus, the science cannot be used, discussed, or reviewed by the wider scientific
-community. It is a problem for both scientists and publishers. Manuscripts that
-are unknown cannot be integrated and thus take more time to be cited. It has
-been shown that high-energy physics, with its high arXiv submission rate, had
-the highest immediacy among physics and mathematics \cite{pra05}.
+The first and most often discussed advantage of arXiv and open
+preprints is speed (Figure~\ref{fig:map}). The time between submission
+and the official publication of a manuscript can be measured in
+months, sometime in years. For all this time, the research is known
+only to a select few: colleagues, editors, reviewers.  Thus, the
+science cannot be used, discussed, or reviewed by the wider scientific
+community.  This stage of manuscript preparation is a problem for both
+scientists and publishers.  Manuscripts that are unknown cannot be
+used and thus take more time to be cited. It has been shown that
+high-energy physics, with its high ArXiv submission rate, had the
+highest immediacy among physics and mathematics \cite{pra05}.
+% JJA: Can you say what "immediacy" means?
 
-Furthermore, the review process as a whole is critically over-loaded, because
-the number of active scientists increases, because the pressure to publish
-increases, and because of an effect dubbed ``the tragedy of the reviewers
-commons'' REF.  At the same times, rejection rates are high in most journals
-(REF), and when not invited to submit a revision, authors must start the whole
-process all over again. It's thus no surprise that different initiatives emerged
-over the last few years to decrease the time spent in review. XXX et coll.
-(REF) called for the recycling and reuse of peer-reviews: by attaching previous
-reviews and detailed replies to a new submission, both the editor and the
-referees can gauge the work done on the manuscript, and perhaps evaluate it with
-less prejudice. In a similar way, the \emph{Peerage of Science} initiative
-allows authors to seek anonymous pre-review by their peers. Some journals now
-accept to publish papers which received good evaluations, with \emph{Animal
-Biology} having recently accepted first a paper reviewed entirely with the
-\emph{Peerage of Science} \cite{abb12}, effectively outsourcing the review
-process. A widespread use of preprint servers can achieve the same goal of
-reducing the time spent in review. By putting a manuscript for open comments and
-criticisms, the authors will receive valuable feedback and can improve the
-version which will be submitted. With a rich enough community of scientists
-depositing preprints, and commenting on them, the process of an open pre-review
-can become widespread and will overall increase the quality of first
-submissions.
+Furthermore, the review process as a whole is critically over-loaded,
+because as the number of active scientists increases, because the
+pressure to publish increases, and because of an effect dubbed ``the
+tragedy of the reviewers commons'' REF.  At the same time, rejection
+rates are high in most journals (REF), and when not invited to submit
+a revision, authors must start the whole process all over again.
+Initiatives to reduce time from submission to publication have emerged
+across the scientific community XXX et coll.  (REF) called for the
+recycling and reuse of peer-reviews: by attaching previous reviews and
+detailed replies to a new submission, both the editor and the referees
+can gauge the work done on the manuscript, and perhaps evaluate it
+with less prejudice. In a similar way, the \emph{Peerage of Science}
+initiative allows authors to seek anonymous pre-review by their
+peers. Some journals now accept to publish papers which received good
+evaluations, with \emph{Animal Biology} having recently accepted first
+a paper reviewed entirely with the \emph{Peerage of Science}
+\cite{abb12}, effectively outsourcing the review process. A widespread
+use of preprint servers can achieve the same goal of reducing the time
+spent in review. By putting a manuscript for open comments and
+criticisms, the authors will receive valuable feedback and can improve
+the version which will be submitted. With a rich enough community of
+scientists depositing preprints, and commenting on them, the process
+of an open pre-review can become widespread and will overall increase
+the quality of first submissions.
 
@@
 
-Public preprint servers offer a much fairer way to establish intellectual
-priority by making the work available when done. Some manuscripts will spend
-much more time in the review process than others. Surprisingly, there is a
-perception in biology that public preprints make it easier to steal ideas, as if
-a scientific idea was only complete once published in a peer-reviewed journal.
-Mathematicians and physicists have embraced arXiv in part to establish priority
-in a fair way and biologists should do so too, or at least not be afraid to
-submit to make their research public for fear of been snooped \cite{cal12}.
+Public preprint servers offer a much fairer way to establish
+intellectual priority by making the work available when done. Some
+manuscripts will spend much more time in the review process than
+others. Surprisingly, there is a perception in biology that public
+preprints make it easier to steal ideas, as if a scientific idea was
+only complete once published in a peer-reviewed journal.
+Mathematicians and physicists have embraced arXiv in part to establish
+priority in a fair way \cite{cal12}.
+% JJA: I snipped the part about getting "snooped" (do you mean
+% "scooped"?) as it seems normative and might annoy some readers.  The
+% "should" should be implicit.
 
-Prepublication reviews by a small network of colleagues is an important part of
-the scientific process, which is attested by the fact that nearly all published
-papers acknowledge comments by people not listed as co-authors.  Preprint
-servers simply offer a way to extend this network of colleagues to the entire
-scientific community. It ensures that science is not constrained by small
-networks of scientists exchanging ideas.  Paul Ginsparg created arXiv.org in
-part for democratic reasons: he wanted everyone from students in small
-universities to Ivy-League professors to have access to the most recent
-scientific \emph{ideas}.  Ginsparg's revolutionary idea was simply to use the
-power of the internet for preprints, not just for the end product, so the
-scientific process can be open as soon as possible.
+Prepublication reviews by a small network of colleagues is an
+important part of the scientific process, attested by the fact that
+nearly all published papers acknowledge comments by people not listed
+as co-authors.  Preprint servers simply offer a way to extend this
+network of colleagues to the entire scientific community. It ensures
+that science is not constrained by small networks of scientists
+exchanging ideas.  Paul Ginsparg created arXiv.org in part for
+democratic reasons: he wanted everyone from students in small
+universities to Ivy-League professors to have access to the most
+recent scientific \emph{ideas}.  Ginsparg's revolutionary idea was
+simply to use the power of the internet for preprints, not just for
+the end product, so the scientific process can be open as soon as
+possible.
 
@@
 
-Submitting to a preprint server is becoming more common in biology, even though
-it still involves a minority of papers. The quantitative biology section in
-arXiv is experiencing faster growth in submissions than any other field
-\cite{cal12}. Examples include a recent series of papers on the theory of
-natural selection that was posted to arXiv simultaneously with its publication
-in the \emph{Journal of Evolutionary Biology}
-\cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}.
+Submitting to a preprint server is becoming more common in biology,
+even though it still involves a minority of papers. The quantitative
+biology section in arXiv is experiencing faster growth in submissions
+than any other field \cite{cal12}.  Examples include a recent series
+of papers on the theory of natural selection that was posted to ArXiv
+simultaneously with its publication in the \emph{Journal of
+  Evolutionary Biology}
+\cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}.  Other
+submissions in this category include evolutionary and ecological
+theory by authors trained in physics and computer science.  Since
+authors in these fields regularly check ArXiv, submitting preprints
+may be the most effective way biologists can help others avoid
+``repeated work'' \cite{de2011contribution} and form a synthetic
+community of evolutionary theorists from disparate backgrounds.
 
-Most scientific journals are preprint-friendly: Nature, PLOS, BMC, PNAS, Science
-(mostly) \ref{table:policies}, and all the journals from Elsevier and Springer.
-Very recently, the Ecological Society of America and the Genetics Society of
-America changed their policies to allow public preprints. Few scientific
-publications will not consider a manuscript submitted to a public preprint
-server.  Still, a few journals adopt a ``by default'' hostile attitude towards
-preprints, mostly due to the lack of clear policy of the publishers, or perhaps
-because a preprint culture has not developed in biology and the practice is
-still considered unusual. As an example, Wiley-Blackwell, which publishes some
-leading journals, has no official policy on the subject \ref{table:policies}.
+Most scientific journals are preprint-friendly: Nature, PLOS, BMC,
+PNAS, Science (mostly) \ref{table:policies}, and all the journals from
+Elsevier and Springer.  The Ecological Society of America and the
+Genetics Society of America recently changed their policies to allow
+public preprints.  Few scientific publications will not consider a
+manuscript submitted to a public preprint server.  Still, a few
+journals adopt a ``by default'' hostile attitude towards preprints,
+mostly due to the lack of clear policy of the publishers, or perhaps
+because a preprint culture has not developed in biology and the
+practice is still considered unusual. As an example, Wiley-Blackwell,
+which publishes some leading journals, has no official policy on the
+subject \ref{table:policies}.
 
-Part of the hostility to preprints servers comes from a certain interpretation
-of the Ingelfinger rule: scientists should not publish the same manuscript twice
-\cite{alt96}. However, papers submitted to arXiv or other preprints servers are
-only published in one peer-reviewed journal. A preprint is just a preprint, it
-is a document that allows ideas to spread and be discussed, but it is not yet
-formally validated by the peer-review system, which is why the majority of
-publishers does not see arXiv and similar services as a violation of the
-Ingelfinger rule. \emph{Nature} responded to the rumour that they refused
-manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
-stand in the way of communication between researchers. We seek rather to add
-value for authors and the community at large in our peer review, selection and
-editing'' \cite{nat05}.
+Part of the hostility to preprints servers comes from a certain
+interpretation of the Ingelfinger rule: scientists should not publish
+the same manuscript twice \cite{alt96}. However, papers submitted to
+arXiv or other preprints servers are only published in one
+peer-reviewed journal. A preprint is just a preprint, it is a document
+that allows ideas to spread and be discussed, but it is not yet
+formally validated by the peer-review system, which is why the
+majority of publishers does not see arXiv and similar services as a
+violation of the Ingelfinger rule. \emph{Nature} responded to the
+rumour that they refused manuscripts submitted to arXiv by saying that
+``\emph{Nature} never wishes to stand in the way of communication
+between researchers. We seek rather to add value for authors and the
+community at large in our peer review, selection and editing''
+\cite{nat05}.
 
@@
 
+% JJA: It's not crucial.  My main point was that there are certain
+% non-obvious cultural reasons that arXiv submissions are common.
+% It's not just because arXiv started in theoretical physics.  It's
+% also that people who use TeX tend to have a certain attitude, I
+% would argue inherited from Don Knuth, and people who use TeX and
+% LaTeX _talk to each other_.  So perhaps this was a polite way of
+% saying that people in math and physics are more community-oriented,
+% and people in biology tend to walk around paranoid about getting
+% scooped.  Some people also might think that they can't submit to
+% arXiv because they use Word.
+
 %There are other barriers to adoption of preprint servers by biologists.  The
@@
 arXiv (\url{http://arxiv.org/}) is the most widely-used preprint server today,
-and its use is almost universal in some branches of mathematics and physics.  It
-provides a reliable citation system for all eprints and is especially popular in
-high-energy physics. Physicist Paul Ginsparg created arXiv in 1991 for
-theoretical high-energy physicists to communicate preprints via email and ftp,
-and soon thereafter adopted the newly created world-wide
-web\cite{jackson2002preprints}.  arXiv now receives over 7,000 submissions per
-month (\url{http://arxiv.org/show_monthly_submissions}) and divides its
-submissions into subcategories of physics, mathematics, computer science,
-quantitative biology, finance and statistics.  The quantitative biology category
-includes subcategories for Populations and Evolution, Quantitative Methods and
-other categories that may be of interest to biologists.
+and its use is almost universal in some branches of mathematics and physics.
+% Ni!!!!  I really don't like starting sentences with "it"
+arXiv provides a reliable citation system for all eprints and is
+especially popular in high-energy physics. Physicist Paul Ginsparg
+created arXiv in 1991 for theoretical high-energy physicists to
+communicate preprints via email and ftp, and soon thereafter adopted
+the newly created world-wide web\cite{jackson2002preprints}.  ArXiv
+now receives over 7,000 submissions per month
+(\url{http://arxiv.org/show_monthly_submissions}) and divides its
+submissions into subcategories of physics, mathematics, computer
+science, quantitative biology, finance and statistics.  The
+quantitative biology category includes subcategories for Populations
+and Evolution, Quantitative Methods and other categories that may be
+of interest to biologists.
 
-Submission to arXiv is fully automated.  Authors can submit \TeX{}/\LaTeX{}
-documents that are compiled on the server or directly submit in PDF/PS format
-(for example, as exported by a word processor).  A moderation system was put in
-place in 2004: papers must be categorized by an endorser. At least one
-author of a paper must be an endorser that has previously submitted a paper or
-has received permission to submit to a particular category.  Many authors in
-mathematics and physics submit papers as soon as they are ready for review by
-colleagues, although another popular option is submitting simultaneously to a
-journal and arXiv.
+Submission to arXiv is fully automated.  Authors can submit
+\TeX{}/\LaTeX{} documents that are compiled on the server or directly
+submit in PDF/PS format (for example, as exported by a word
+processor).  A moderation system was put in place in 2004: papers must
+be categorized by an endorser. At least one author of a paper must be
+an endorser that has previously submitted a paper or has received
+permission to submit to a particular category.  Many authors in
+mathematics and physics submit papers as soon as they are ready for
+review by colleagues, although another popular option is submitting
+simultaneously to a journal and arXiv.
 
 % To review: 
-To submit to arXiv, the authors must either have their work available under an
+Authors must either have their arXiv submission available under an
 open license or grant arXiv a non-exclusive and irrevocable license to
-distribute the article. In either case, arXiv does not require copyright
-transfer and only requires the rights to distribute submitted articles in
-perpetuity. Thus, submitting to arXiv does not in itself prevent the authors
-from transferring their rights to a publisher, which is why most publishers
-tolerate arXiv, even though they ask the authors to transfer their right to them
-upon acceptance of the article.
+distribute the work. In either case, arXiv does not require copyright
+transfer and only requires the rights to distribute submitted articles
+in perpetuity. Thus, submitting to arXiv does not in itself prevent
+the authors from transferring their rights to a publisher, which is
+why most publishers tolerate arXiv, even though they ask the authors
+to transfer their right to them upon acceptance of the article.
 
@@
 leading to the proof of the Poincar\'{e} conjecture
-\cite{2002math.....11159P}. Yet, arXiv has never sought to replace
-scientific journals and explicitly states that it serves a different
-function as ``an openly accessible, moderated repository for scholarly
-articles in specific scientific disciplines.'' arXiv is now
+\cite{2002math.....11159P}.  However, arXiv has never sought to
+replace scientific journals and explicitly states that it serves a
+different function as ``an openly accessible, moderated repository for
+scholarly articles in specific scientific disciplines.'' arXiv is now
 administered by the Cornell University Libraries, with funding coming
@@
 
-Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
-that allows scientists to submit any research output: manuscript, figures,
-datasets, videos, theses, presentations, and so on. There are no rules to limit
-what constitutes a research output and, unlike arXiv, there is no endorser
-system. All figshare content has a unique digital object identifier (DOI) like
-any journal article, thus offering a permanent and stable link to the content.
-A flexible tag system is used to classify each item. All content can be
-commented and is licensed under the Creative Commons (CC-BY) license, except
-datasets which are published under CC0. The CC-BY license grant the rights to
-\emph{copy, distribute, display and perform the work and make derivative works
-based on it only if they give the author or licensor the credits in the manner
-specified by these.} The CC0 is the most permissive license and make the work
-public domain (no rights reserved) or, if it is not possible in the given
+Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an
+open server that allows scientists to submit any research output:
+manuscript, figures, datasets, videos, theses, presentations, and so
+on. There are no rules to limit what constitutes a research output
+and, unlike arXiv, there is no endorser system. All figshare content
+has a unique digital object identifier (DOI) like any journal article,
+thus offering a permanent and stable link to the content.  A flexible
+tag system is used to classify each item. All content can be commented
+and is licensed under the Creative Commons (CC-BY) license, except
+datasets which are published under CC0. The CC-BY license grants
+rights to \emph{copy, distribute, display and perform the work and
+  make derivative works based on it only if they give the author or
+  licensor the credits in the manner specified by these.}  CC0 is the
+most permissive license and effectively puts the work in public domain
+(no rights reserved) or, if it is not possible in the given
 jurisdiction, provides a simple permissive license.
 
-One of the biggest advantage of figshare over arXiv is that is it not limited to
-quantitative sciences. arXiv.org has sections on quantitative biology but might
-not be appropriate for non-quantitative work. With its flexible approach to
-preprints, figshare offer an important alternative to arXiv for empirical
-biologists. Furthermore, by allowing all types of contents, figshare arguably
-provides an archive for early results (e.g.: figures, lab presentations).
+One of the biggest advantage of figshare over arXiv is that is it not
+limited to quantitative sciences. arXiv.org has sections on
+quantitative biology but might not be appropriate for non-quantitative
+work. With its flexible approach to preprints, figshare offers an
+important alternative to arXiv for empirical biologists. Furthermore,
+by allowing all types of content, figshare arguably provides an
+archive for early results (e.g.: figures, lab presentations).
 
@@
 
-PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new publishing
-system that provides both a preprint server, and a peer reviewed journal.
-It is focused on the the biological and medical sciences, which may help
-overcome the perception that preprints do not have a home in biology.
-PeerJ allows commenting on posted preprints, improving the potential
-for pre-publication dialog. In addition, preprints can be made private if
-the authors choose, and shared only with selected colleagues. While this
-reduces some of the benefits of preprints described above, it may allow
-some researchers who would not otherwise post preprints to begin to explore
-the possibility in a manner appropriate to their current circumstances.
+PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new
+publishing system that provides both a preprint server, and a peer
+reviewed journal.  It is focused on the the biological and medical
+sciences, which may help overcome the perception that preprints do not
+have a home in biology.  PeerJ allows commenting on posted preprints,
+improving the potential for pre-publication dialog. In addition,
+preprints can be made private if the authors choose, and shared only
+with selected colleagues. While this reduces some of the benefits of
+preprints described above, it may allow some researchers who would not
+otherwise post preprints to begin to explore the possibility in a
+manner appropriate to their current circumstances.
 
-In contrast to other preprint servers users cannot post unlimited public
-preprints for free. One preprint per year can be posted for free and a
-onetime (i.e. lifetime) fee of 99 dollars allows the posting of unlimited
-public preprints. It is also worth noting that the preprint server is not
-tied to the journal, so preprints can be posted regardless of where they
-will eventually be submitted for publication.
+In contrast to other preprint servers users cannot post unlimited
+public preprints for free. One preprint per year can be posted for
+free and a onetime (i.e. lifetime) fee of 99 dollars allows the
+posting of unlimited public preprints. It is also worth noting that
+the preprint server is not tied to the journal, so preprints can be
+posted regardless of where they will eventually be submitted for
+publication.
 
@@
 
-F1000Research is not a public preprint server like the previous three servers.
-Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
-without having it reviewed, papers submitted to F1000Research will eventually be
-reviewed. Thus, F1000Research offers a hybrid model with publicly available
-manuscripts at time of submission and standard peer-reviews. Manuscripts are
-considered ``accepted'' and will only be indexed after two positive referee
+F1000Research is not a public preprint server like the previous three
+servers.  Whereas arXiv, Figshare, and PeerJ offer an option to submit
+a manuscript without having it reviewed, papers submitted to
+F1000Research will eventually be reviewed. Thus, F1000Research offers
+a hybrid model with publicly available manuscripts at time of
+submission and standard peer-reviews. Manuscripts are considered
+``accepted'' and will only be indexed after two positive referee
 response.
@@
 
-Open preprints servers offer a great opportunity for open science, especially if
-the community embrace the idea of discussing preprints. Initiatives like
-Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
-new blog discussing arXiv papers in population genetics, will help make arXiv
-attractive for scientists looking to promote their work. These initiatives are
-important to fully exploit the potential of open preprints servers. Posting
-preprints online increases the community of available informal peer reviewers,
-and uses the internet for its original community-building purposes.  Preprint
-servers also facilitate communication between disciplines, bridging cultural as
-well as geographic divides. The advantages are clear and the costs are low.
+Open preprint servers offer a great opportunity for open science,
+especially if the community embraces the idea of discussing
+preprints. Initiatives like Haldane's Sieve
+(\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a new
+blog discussing arXiv papers in population genetics, will help make
+arXiv attractive for scientists looking to promote their work. These
+initiatives are important to fully exploit the potential of open
+preprints servers. Posting preprints online increases the community of
+available informal peer reviewers, and uses the internet for its
+original community-building purposes.  Preprint servers also
+facilitate communication between disciplines, bridging cultural as
+well as geographic divides. The advantages are clear and the costs are
+low.
 

### 2012-09-28 ms.tex
review the text

@@
 \author{Karthik Ram}
-\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley. Berkeley, CA. United-States of America.}
+\affiliation{Environmental Science, Policy, and Management. University of
+California, Berkeley. Berkeley, CA. United-States of America.}
 
@@
 
-% No abstract needed.
-
 \maketitle
@@
 
-Public preprint servers allow authors to make manuscripts publicly
-available before, or in parallel to, submitting them to journals for
-traditional peer-review. The rationale for preprint servers is
-fundamentally simple: to make the results available to the scientific
-community as soon as possible rather than to wait until the
-peer-review process is fully completed. The goal of arXiv and open
-preprint servers is not to avoid the peer-review process; almost all
-manuscripts on arXiv are submitted to peer-review.  Sharing ideas as
-quickly as possible using preprint servers has numerous advantages.
-These include rapid dissemination of work in progress to a wider
-audience, including readers in developing countries where access to
-subscription journals is often a limiting factor in scientific
-research.  Furthermore, preprints provide the opportunity to solicit
-feedback from a larger pool of reviewers and can be seen as an
-integral aspect of a vigorous peer-review process \cite{hoc12}.
-Preprint servers therefore increase the number of opportunities for
-review and revision prior to publication, resulting in higher quality
-submissions and also could alleviate reviewer burden.
+Public preprint servers allow authors to make manuscripts publicly available
+before, or in parallel to, submitting them to journals for traditional
+peer-review. The rationale for preprint servers is fundamentally simple: to make
+the results available to the scientific community as soon as possible rather
+than to wait until the peer-review process is fully completed. The goal of arXiv
+and open preprint servers is not to avoid the peer-review process; almost all
+manuscripts on arXiv are submitted to peer-review.  Sharing ideas as quickly as
+possible using preprint servers has numerous advantages.  These include rapid
+dissemination of work in progress to a wider audience, including readers in
+developing countries where access to subscription journals is often a limiting
+factor in scientific research.  Furthermore, preprints provide the opportunity
+to solicit feedback from a larger pool of reviewers and can be seen as an
+integral aspect of a vigorous peer-review process \cite{hoc12}.  Preprint
+servers therefore increase the number of opportunities for review and revision
+prior to publication, resulting in higher quality submissions and also could
+alleviate reviewer burden.
 
-Preprints gained popularity 20 years ago with the advent of arXiv, an
-open preprint server widely used in physics and mathematics
-\cite{gin11}. Preprints are also integral to the culture of other
-scientific fields.  Paul Krugman noted that, in economics, the
-\emph{traditional model of submit, get refereed, publish, and then
-  people will read your work broke down a long time ago. In fact, it
-  had more or less fallen apart by the early 80s} \cite{kru12}. In
-addition to a section in arXiv, economists have also the RePEc
-(Research Papers in Economics) initiative, which aims to create an
-archive of working papers, manuscripts, and book chapters.  Despite
-the success of this approach in other fields, most manuscripts in
-biology are never submitted to any public archive.
-% JJA: This is a tenuous statement: MANY if not most biomedical labs
-% in the US are funded by NIH, which requires submission to Pubmed
-% Central, which many would consider a preprint archive.  In other
-% words, a biomedical editor might take issue with this statement,
-% especially if he considers "biology" to be just his part of biology
-% --- I know plenty of people who only think of "biology" as
-% biomedical science
-In this article, we will first highlight the advantages of open
-preprint servers for both scientists and publishers. We will also
-debunk a few misconceptions, discuss the policies of major publishers
-in biology, and briefly review the most popular open preprint servers.
+Preprints gained popularity 20 years ago with the advent of arXiv, an open
+preprint server widely used in physics and mathematics \cite{gin11}. Preprints
+are also integral to the culture of other scientific fields.  Paul Krugman noted
+that, in economics, the \emph{traditional model of submit, get refereed,
+publish, and then people will read your work broke down a long time ago. In
+fact, it had more or less fallen apart by the early 80s} \cite{kru12}. In
+addition to a section in arXiv, economists have also the RePEc (Research Papers
+in Economics) initiative, which aims to create an archive of working papers,
+manuscripts, and book chapters.  Despite the success of this approach in other
+fields, most manuscripts in biology are not submitted to a public archive before
+being submitted to peer-review.  In this article, we will first highlight the
+advantages of open preprint servers for both scientists and publishers. We will
+also debunk a few misconceptions, discuss the policies of major publishers in
+biology, and briefly review the most popular open preprint servers.
 
-\section{The case for open preprints}
+\section{The case for public preprints}
 
-The first and most often discussed advantage of arXiv and open
-preprints is speed (Figure~\ref{fig:map}). The time between submission
-and the official publication of a manuscript can be measured in
-months, sometime in years. For all this time, the research is known
-only to a select few: colleagues, editors, reviewers.  Thus, the
-science cannot be used, discussed, or reviewed by the wider scientific
-community.  This stage of manuscript preparation is a problem for both
-scientists and publishers.  Manuscripts that are unknown cannot be
-used and thus take more time to be cited. It has been shown that
-high-energy physics, with its high ArXiv submission rate, had the
-highest immediacy among physics and mathematics \cite{pra05}.
-% JJA: Can you say what "immediacy" means?
+The first and most often discussed advantage of arXiv and open preprints is
+speed (Figure~\ref{fig:map}). The time between submission and the official
+publication of a manuscript can be measured in months, sometime in years. For
+all this time, the research is known only to a select few: colleagues, editors,
+reviewers.  Thus, the science cannot be used, discussed, or reviewed by the
+wider scientific community.  This stage of manuscript preparation is a problem
+for both scientists and publishers.  Manuscripts that are unknown cannot be used
+and thus take more time to be cited. It has been shown that high-energy physics,
+with its high arXiv submission rate, had the highest immediacy among physics and
+mathematics \cite{pra05}. Immediacy measures how quickly articles are cited.
 
-Furthermore, the review process as a whole is critically over-loaded,
-because as the number of active scientists increases, because the
-pressure to publish increases, and because of an effect dubbed ``the
-tragedy of the reviewers commons'' REF.  At the same time, rejection
-rates are high in most journals (REF), and when not invited to submit
-a revision, authors must start the whole process all over again.
-Initiatives to reduce time from submission to publication have emerged
-across the scientific community XXX et coll.  (REF) called for the
-recycling and reuse of peer-reviews: by attaching previous reviews and
-detailed replies to a new submission, both the editor and the referees
-can gauge the work done on the manuscript, and perhaps evaluate it
-with less prejudice. In a similar way, the \emph{Peerage of Science}
-initiative allows authors to seek anonymous pre-review by their
-peers. Some journals now accept to publish papers which received good
-evaluations, with \emph{Animal Biology} having recently accepted first
-a paper reviewed entirely with the \emph{Peerage of Science}
-\cite{abb12}, effectively outsourcing the review process. A widespread
-use of preprint servers can achieve the same goal of reducing the time
-spent in review. By putting a manuscript for open comments and
-criticisms, the authors will receive valuable feedback and can improve
-the version which will be submitted. With a rich enough community of
-scientists depositing preprints, and commenting on them, the process
-of an open pre-review can become widespread and will overall increase
-the quality of first submissions.
+Furthermore, the review process as a whole is critically over-loaded, because as
+the number of active scientists increases, because the pressure to publish
+increases, and because of an effect dubbed ``the tragedy of the reviewers
+commons'' REF.  At the same time, rejection rates are high in most journals
+(REF), and when not invited to submit a revision, authors must start the whole
+process all over again.  Initiatives to reduce time from submission to
+publication have emerged across the scientific community XXX et coll.  (REF)
+called for the recycling and reuse of peer-reviews: by attaching previous
+reviews and detailed replies to a new submission, both the editor and the
+referees can gauge the work done on the manuscript, and perhaps evaluate it with
+less prejudice. In a similar way, the \emph{Peerage of Science} initiative
+allows authors to seek anonymous pre-review by their peers. Some journals now
+accept to publish papers which received good evaluations, with \emph{Animal
+Biology} having recently accepted first a paper reviewed entirely with the
+\emph{Peerage of Science} \cite{abb12}, effectively outsourcing the review
+process. A widespread use of preprint servers can achieve the same goal of
+reducing the time spent in review. By putting a manuscript for open comments and
+criticisms, the authors will receive valuable feedback and can improve the
+version which will be submitted. With a rich enough community of scientists
+depositing preprints, and commenting on them, the process of an open pre-review
+can become widespread and will overall increase the quality of first
+submissions.
 
@@
 
-Public preprint servers offer a much fairer way to establish
-intellectual priority by making the work available when done. Some
-manuscripts will spend much more time in the review process than
-others. Surprisingly, there is a perception in biology that public
-preprints make it easier to steal ideas, as if a scientific idea was
-only complete once published in a peer-reviewed journal.
-Mathematicians and physicists have embraced arXiv in part to establish
-priority in a fair way \cite{cal12}.
-% JJA: I snipped the part about getting "snooped" (do you mean
-% "scooped"?) as it seems normative and might annoy some readers.  The
-% "should" should be implicit.
+Public preprint servers offer a much fairer way to establish intellectual
+priority by making the work available when done. Some manuscripts will spend
+much more time in the review process than others. Surprisingly, there is a
+perception in biology that public preprints make it easier to steal ideas, as if
+a scientific idea was only complete once published in a peer-reviewed journal
+\cite{gin11}. Ironically, mathematicians and physicists have embraced arXiv in
+part to establish priority in a fair way \cite{gin11,cal12}.
 
-Prepublication reviews by a small network of colleagues is an
-important part of the scientific process, attested by the fact that
-nearly all published papers acknowledge comments by people not listed
-as co-authors.  Preprint servers simply offer a way to extend this
-network of colleagues to the entire scientific community. It ensures
-that science is not constrained by small networks of scientists
-exchanging ideas.  Paul Ginsparg created arXiv.org in part for
-democratic reasons: he wanted everyone from students in small
-universities to Ivy-League professors to have access to the most
-recent scientific \emph{ideas}.  Ginsparg's revolutionary idea was
-simply to use the power of the internet for preprints, not just for
-the end product, so the scientific process can be open as soon as
-possible.
+Prepublication reviews by a small network of colleagues is an important part of
+the scientific process, attested by the fact that nearly all published papers
+acknowledge comments by people not listed as co-authors.  Preprint servers
+simply offer a way to extend this network of colleagues to the entire scientific
+community. It ensures that science is not constrained by small networks of
+scientists exchanging ideas.  Paul Ginsparg created arXiv.org in part for
+democratic reasons: he wanted everyone from students in small universities to
+Ivy-League professors to have access to the most recent scientific \emph{ideas}.
+Ginsparg's revolutionary idea was simply to use the power of the internet for
+preprints, not just for the end product, so the scientific process can be open
+as soon as possible.
 
@@
 
-Submitting to a preprint server is becoming more common in biology,
-even though it still involves a minority of papers. The quantitative
-biology section in arXiv is experiencing faster growth in submissions
-than any other field \cite{cal12}.  Examples include a recent series
-of papers on the theory of natural selection that was posted to ArXiv
-simultaneously with its publication in the \emph{Journal of
-  Evolutionary Biology}
-\cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}.  Other
-submissions in this category include evolutionary and ecological
-theory by authors trained in physics and computer science.  Since
-authors in these fields regularly check ArXiv, submitting preprints
-may be the most effective way biologists can help others avoid
-``repeated work'' \cite{de2011contribution} and form a synthetic
-community of evolutionary theorists from disparate backgrounds.
+Submitting to a preprint server is becoming more common in biology, even though
+it still involves a minority of papers. The quantitative biology section in
+arXiv is experiencing faster growth in submissions than any other field
+\cite{cal12}. Most scientific journals are preprint-friendly: Nature, PLOS, BMC,
+PNAS, Science (mostly) \ref{table:policies}, and all the journals from Elsevier
+and Springer.  The Ecological Society of America and the Genetics Society of
+America recently changed their policies to allow public preprints.  Few
+scientific publications will not consider a manuscript submitted to a public
+preprint server.  Still, a few journals adopt a ``by default'' hostile attitude
+towards preprints, mostly due to the lack of clear policy of the publishers, or
+perhaps because a preprint culture has not developed in biology and the practice
+is still considered unusual. As an example, Wiley-Blackwell, which publishes
+some leading journals, has no official policy on the subject
+\ref{table:policies}.
 
-Most scientific journals are preprint-friendly: Nature, PLOS, BMC,
-PNAS, Science (mostly) \ref{table:policies}, and all the journals from
-Elsevier and Springer.  The Ecological Society of America and the
-Genetics Society of America recently changed their policies to allow
-public preprints.  Few scientific publications will not consider a
-manuscript submitted to a public preprint server.  Still, a few
-journals adopt a ``by default'' hostile attitude towards preprints,
-mostly due to the lack of clear policy of the publishers, or perhaps
-because a preprint culture has not developed in biology and the
-practice is still considered unusual. As an example, Wiley-Blackwell,
-which publishes some leading journals, has no official policy on the
-subject \ref{table:policies}.
-
-Part of the hostility to preprints servers comes from a certain
-interpretation of the Ingelfinger rule: scientists should not publish
-the same manuscript twice \cite{alt96}. However, papers submitted to
-arXiv or other preprints servers are only published in one
-peer-reviewed journal. A preprint is just a preprint, it is a document
-that allows ideas to spread and be discussed, but it is not yet
-formally validated by the peer-review system, which is why the
-majority of publishers does not see arXiv and similar services as a
-violation of the Ingelfinger rule. \emph{Nature} responded to the
-rumour that they refused manuscripts submitted to arXiv by saying that
-``\emph{Nature} never wishes to stand in the way of communication
-between researchers. We seek rather to add value for authors and the
-community at large in our peer review, selection and editing''
-\cite{nat05}.
-
-% Discuss embargoes?
-%A second potential problem is embargoes. Many publishers subject their article
-%to embargoes \cite{rea12}.
+Part of the hostility to preprints servers comes from a certain interpretation
+of the Ingelfinger rule: scientists should not publish the same manuscript twice
+\cite{alt96}. However, papers submitted to arXiv or other preprints servers are
+only published in one peer-reviewed journal. A preprint is just a preprint, it
+is a document that allows ideas to spread and be discussed, but it is not yet
+formally validated by the peer-review system, which is why the majority of
+publishers does not see arXiv and similar services as a violation of the
+Ingelfinger rule. \emph{Nature} responded to the rumour that they refused
+manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
+stand in the way of communication between researchers. We seek rather to add
+value for authors and the community at large in our peer review, selection and
+editing'' \cite{nat05}.
 
@@
 
-% Not sure about this paragraph, as much as I love to hate MS Office, I would
-% rather keep the thing as a "pro-preprint" paper only and not use it to promote
-% LaTeX/R.
-% -- PhDP
-
-% JJA: It's not crucial.  My main point was that there are certain
-% non-obvious cultural reasons that arXiv submissions are common.
-% It's not just because arXiv started in theoretical physics.  It's
-% also that people who use TeX tend to have a certain attitude, I
-% would argue inherited from Don Knuth, and people who use TeX and
-% LaTeX _talk to each other_.  So perhaps this was a polite way of
-% saying that people in math and physics are more community-oriented,
-% and people in biology tend to walk around paranoid about getting
-% scooped.  Some people also might think that they can't submit to
-% arXiv because they use Word.
-
-%There are other barriers to adoption of preprint servers by biologists.  The
-%most notable preprint server, arXiv, is designed to work best with \LaTeX, the
-%dominant document preparation system among physicists and mathematicians.
-%Jackson \cite{jackson2002preprints} argues that \LaTeX introduced an
-%open source mindset to its users, who now freely share their research
-%findings as well as their software.  Many biologists instead use proprietary
-%software to prepare their research findings, and many journals officially prefer
-%Microsoft Word documents as submissions.  The recent discipline-wide adoption of
-%free software packages such as R and associated document generation systems
-%\cite{xie2012}, as well as interest in open access publishing, has coincided
-%with recent rise in use of preprint servers by biologists, supporting Jackson's
-%claims \cite{xie12}.
-
 \section{Current offerings}
@@
 and its use is almost universal in some branches of mathematics and physics.
-% Ni!!!!  I really don't like starting sentences with "it"
-arXiv provides a reliable citation system for all eprints and is
-especially popular in high-energy physics. Physicist Paul Ginsparg
-created arXiv in 1991 for theoretical high-energy physicists to
-communicate preprints via email and ftp, and soon thereafter adopted
-the newly created world-wide web\cite{jackson2002preprints}.  ArXiv
-now receives over 7,000 submissions per month
-(\url{http://arxiv.org/show_monthly_submissions}) and divides its
-submissions into subcategories of physics, mathematics, computer
-science, quantitative biology, finance and statistics.  The
-quantitative biology category includes subcategories for Populations
-and Evolution, Quantitative Methods and other categories that may be
-of interest to biologists.
+arXiv provides a reliable citation system for all eprints and is especially
+popular in high-energy physics. Physicist Paul Ginsparg created arXiv in 1991
+for theoretical high-energy physicists to communicate preprints via email and
+ftp, and soon thereafter adopted the newly created world-wide
+web\cite{jackson2002preprints}.  arXiv now receives over 7 000 submissions per
+month (\url{http://arxiv.org/show_monthly_submissions}) and divides its
+submissions into subcategories of physics, mathematics, computer science,
+quantitative biology, finance and statistics.  The quantitative biology category
+includes subcategories for Populations and Evolution, Quantitative Methods and
+other categories that may be of interest to biologists.
 
-Submission to arXiv is fully automated.  Authors can submit
-\TeX{}/\LaTeX{} documents that are compiled on the server or directly
-submit in PDF/PS format (for example, as exported by a word
-processor).  A moderation system was put in place in 2004: papers must
-be categorized by an endorser. At least one author of a paper must be
-an endorser that has previously submitted a paper or has received
-permission to submit to a particular category.  Many authors in
-mathematics and physics submit papers as soon as they are ready for
-review by colleagues, although another popular option is submitting
-simultaneously to a journal and arXiv.
+Submission to arXiv is fully automated.  Authors can submit \TeX{}/\LaTeX{}
+documents that are compiled on the server or directly submit in PDF/PS format
+(for example, as exported by a word processor).  A moderation system was put in
+place in 2004: papers must be categorized by an endorser. At least one author of
+a paper must be an endorser that has previously submitted a paper or has
+received permission to submit to a particular category.  Many authors in
+mathematics and physics submit papers as soon as they are ready for review by
+colleagues, although another popular option is submitting simultaneously to a
+journal and arXiv.
 
-% To review: 
-Authors must either have their arXiv submission available under an
-open license or grant arXiv a non-exclusive and irrevocable license to
-distribute the work. In either case, arXiv does not require copyright
-transfer and only requires the rights to distribute submitted articles
-in perpetuity. Thus, submitting to arXiv does not in itself prevent
-the authors from transferring their rights to a publisher, which is
-why most publishers tolerate arXiv, even though they ask the authors
-to transfer their right to them upon acceptance of the article.
+Authors must either have their arXiv submission available under an open license
+or grant arXiv a non-exclusive and irrevocable license to distribute the work.
+In either case, arXiv does not require copyright transfer and only requires the
+rights to distribute submitted articles in perpetuity. Thus, submitting to arXiv
+does not in itself prevent the authors from transferring their rights to a
+publisher, which is why most publishers tolerate arXiv, even though they ask the
+authors to transfer their right to them upon acceptance of the article.
 
-Most papers posted to arXiv are eventually printed in journals but
-there are notable exceptions, such as Perelman's landmark paper
-leading to the proof of the Poincar\'{e} conjecture
-\cite{2002math.....11159P}.  However, arXiv has never sought to
-replace scientific journals and explicitly states that it serves a
-different function as ``an openly accessible, moderated repository for
+Most papers posted to arXiv are eventually printed in journals but there are
+notable exceptions, such as Perelman's landmark paper leading to the proof of
+the Poincar\'{e} conjecture \cite{2002math.....11159P}.  However, arXiv has
+never sought to replace scientific journals and explicitly states that it serves
+a different function as ``an openly accessible, moderated repository for
 scholarly articles in specific scientific disciplines.'' arXiv is now
-administered by the Cornell University Libraries, with funding coming
-from voluntary pledges by academic institutions along with matching
-funds from the Simons Foundation \cite{arxiv_future}.  One-hundred
-twenty six of the top two-hundred institutions in terms of downloads
-have provided the operating budget for arXiv over the next five years.
-This plan reduces the financial burden on Cornell University and
-transfers governance to a collaborative community in accordance with
-arXiv's key principles.  arXiv takes numerous measures to ensure that
-the repository will remain permanently available and submissions will
-be readable.
+administered by the Cornell University Libraries, with funding coming from
+voluntary pledges by academic institutions along with matching funds from the
+Simons Foundation \cite{arxiv_future}.  One-hundred twenty six of the top
+two-hundred institutions in terms of downloads have provided the operating
+budget for arXiv over the next five years.  This plan reduces the financial
+burden on Cornell University and transfers governance to a collaborative
+community in accordance with arXiv's key principles.  arXiv takes numerous
+measures to ensure that the repository will remain permanently available and
+submissions will be readable.
 
@@
 
-Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an
-open server that allows scientists to submit any research output:
-manuscript, figures, datasets, videos, theses, presentations, and so
-on. There are no rules to limit what constitutes a research output
-and, unlike arXiv, there is no endorser system. All figshare content
-has a unique digital object identifier (DOI) like any journal article,
-thus offering a permanent and stable link to the content.  A flexible
-tag system is used to classify each item. All content can be commented
-and is licensed under the Creative Commons (CC-BY) license, except
-datasets which are published under CC0. The CC-BY license grants
-rights to \emph{copy, distribute, display and perform the work and
-  make derivative works based on it only if they give the author or
-  licensor the credits in the manner specified by these.}  CC0 is the
-most permissive license and effectively puts the work in public domain
-(no rights reserved) or, if it is not possible in the given
-jurisdiction, provides a simple permissive license.
+Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
+that allows scientists to submit any research output: manuscript, figures,
+datasets, videos, theses, presentations, and so on. There are no rules to limit
+what constitutes a research output and, unlike arXiv, there is no endorser
+system. All figshare content has a unique digital object identifier (DOI) like
+any journal article, thus offering a permanent and stable link to the content.
+A flexible tag system is used to classify each item. All content can be
+commented and is licensed under the Creative Commons (CC-BY) license, except
+datasets which are published under CC0. The CC-BY license grants rights to
+\emph{copy, distribute, display and perform the work and make derivative works
+based on it only if they give the author or licensor the credits in the manner
+specified by these.}  CC0 is the most permissive license and effectively puts
+the work in public domain (no rights reserved) or, if it is not possible in the
+given jurisdiction, provides a simple permissive license.
 
-One of the biggest advantage of figshare over arXiv is that is it not
-limited to quantitative sciences. arXiv.org has sections on
-quantitative biology but might not be appropriate for non-quantitative
-work. With its flexible approach to preprints, figshare offers an
-important alternative to arXiv for empirical biologists. Furthermore,
-by allowing all types of content, figshare arguably provides an
-archive for early results (e.g.: figures, lab presentations).
+One of the biggest advantage of figshare over arXiv is that is it not limited to
+quantitative sciences. arXiv.org has sections on quantitative biology but might
+not be appropriate for non-quantitative work. With its flexible approach to
+preprints, figshare offers an important alternative to arXiv for empirical
+biologists. Furthermore, by allowing all types of content, figshare arguably
+provides an archive for early results (e.g.: figures, lab presentations).
 
@@
 
-PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new
-publishing system that provides both a preprint server, and a peer
-reviewed journal.  It is focused on the the biological and medical
-sciences, which may help overcome the perception that preprints do not
-have a home in biology.  PeerJ allows commenting on posted preprints,
-improving the potential for pre-publication dialog. In addition,
-preprints can be made private if the authors choose, and shared only
-with selected colleagues. While this reduces some of the benefits of
-preprints described above, it may allow some researchers who would not
-otherwise post preprints to begin to explore the possibility in a
-manner appropriate to their current circumstances.
+PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new publishing system
+that provides both a preprint server, and a peer reviewed journal.  It is
+focused on the biological and medical sciences, which may help overcome the
+perception that preprints do not have a home in biology.  PeerJ allows
+commenting on posted preprints, improving the potential for pre-publication
+dialog. In addition, preprints can be made private if the authors choose, and
+shared only with selected colleagues. While this reduces some of the benefits of
+preprints described above, it may allow some researchers who would not otherwise
+post preprints to begin to explore the possibility in a manner appropriate to
+their current circumstances.
 
-In contrast to other preprint servers users cannot post unlimited
-public preprints for free. One preprint per year can be posted for
-free and a onetime (i.e. lifetime) fee of 99 dollars allows the
-posting of unlimited public preprints. It is also worth noting that
-the preprint server is not tied to the journal, so preprints can be
-posted regardless of where they will eventually be submitted for
-publication.
+In contrast to other preprint servers users cannot post unlimited public
+preprints for free. One preprint per year can be posted for free and a onetime
+(i.e. lifetime) fee of 99 dollars allows the posting of unlimited public
+preprints. It is also worth noting that the preprint server is not tied to the
+journal, so preprints can be posted regardless of where they will eventually be
+submitted for publication.
+
+PeerJ uses the CC-BY-SA 3.0 license, which is similar to the CC-BY license used
+by Figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
+needs a license identical to the license that governs the original work.
 
@@
 
-F1000Research is not a public preprint server like the previous three
-servers.  Whereas arXiv, Figshare, and PeerJ offer an option to submit
-a manuscript without having it reviewed, papers submitted to
-F1000Research will eventually be reviewed. Thus, F1000Research offers
-a hybrid model with publicly available manuscripts at time of
-submission and standard peer-reviews. Manuscripts are considered
-``accepted'' and will only be indexed after two positive referee
+F1000Research is not a public preprint server like the previous three servers.
+Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
+without having it reviewed, papers submitted to F1000Research will eventually be
+reviewed. Thus, F1000Research offers a hybrid model with publicly available
+manuscripts at time of submission and standard peer-reviews. Manuscripts are
+considered ``accepted'' and will only be indexed after two positive referee
 response.
@@
 
-This manuscript was developed entirely as an open project on
-github. github is one of several hosting services for collaborative
-development using the git revision control software.  git is a
-decentralized revision control system created by Linus Torvalds used
-primarily to develop software, including the Linux kernel. It allows
-the users to share code, track changes, and merge versions. For
-example, during the development of this manuscript, one author would
-fork the project (that is: make a personal copy), modify it, and then
-the changes were merged back into the main branch. These techniques
-are widely used in open source software development. It goes even
-farther than submitting preprints by opening the entire writing
-process.
+This manuscript was developed entirely as an open project on github. github is
+one of several hosting services for collaborative development using the git
+revision control software.  git is a decentralized revision control system
+created by Linus Torvalds and is used primarily to develop software, including
+the Linux kernel. It allows the users to share code, track changes, and merge
+versions. For example, during the development of this manuscript, one author
+would fork the project (i.e.: make a personal copy), modify it, and then the
+changes were merged back into the main branch. These techniques are widely used
+in open source software development. It goes even farther than submitting
+preprints by opening the entire writing process.
 
@@
 
-Open preprint servers offer a great opportunity for open science,
-especially if the community embraces the idea of discussing
-preprints. Initiatives like Haldane's Sieve
-(\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a new
-blog discussing arXiv papers in population genetics, will help make
-arXiv attractive for scientists looking to promote their work. These
-initiatives are important to fully exploit the potential of open
-preprints servers. Posting preprints online increases the community of
-available informal peer reviewers, and uses the internet for its
-original community-building purposes.  Preprint servers also
-facilitate communication between disciplines, bridging cultural as
-well as geographic divides. The advantages are clear and the costs are
-low.
+Open preprint servers offer a great opportunity for open science, especially if
+the community embraces the idea of discussing preprints. Initiatives like
+Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
+new blog discussing arXiv papers in population genetics, will help make arXiv
+attractive for scientists looking to promote their work. These initiatives are
+important to fully exploit the potential of open preprints servers. Posting
+preprints online increases the community of available informal peer reviewers,
+and uses the internet for its original community-building purposes.
+
+Preprint servers also facilitate communication between disciplines, bridging
+cultural as well as geographic divides. Examples include a recent series of
+papers on the theory of natural selection that was posted to arXiv
+simultaneously with its publication in the \emph{Journal of Evolutionary
+Biology} \cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}. Other
+submissions in this category include evolutionary and ecological theory by
+authors trained in physics and computer science.  Since authors in these fields
+regularly check arXiv, submitting preprints may be the most effective way
+biologists can help others avoid ``repeated work'' \cite{de2011contribution} and
+form a synthetic community of evolutionary theorists from disparate backgrounds.
+The advantages are clear and the costs are low.
 
@@
 
-PDP is funded by an Alexander Graham Bell scholarship from the National Sciences
-and Engineering Council of Canada.
-
-DG is funded by a Discovery Grand from the National Sciences and Engineering
-Council of Canada and by the Canada Research Chair program.
-
-JJA is supported by NSF DEB-0614166 and NSF DEB-0919018.
+PDP is supported by an Alexander Graham Bell scholarship from the National
+Sciences and Engineering Council of Canada. JJA is supported by NSF DEB-0614166
+and NSF DEB-0919018. DG is funded by a Discovery Grand from the National
+Sciences and Engineering Council of Canada and by the Canada Research Chair
+program.
 
@@
 
-...
+We thank Carl Boettiger for helpful comments on an earlier version of this
+manuscript.
 

### 2012-09-28 ms.tex
typo

@@
 by Figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
-needs a license identical to the license that governs the original work.
+need a license identical to the license that governs the original work.
 

### 2012-09-29 ms.tex
formatting, bib file

@@
-\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys]{revtex4-1}
+\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4-1}
 \usepackage[utf8]{inputenc}
@@
 \author{Karthik Ram}
-\affiliation{Environmental Science, Policy, and Management. University of
-California, Berkeley. Berkeley, CA. United-States of America.}
+\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley, United-States of America.}
 
@@
 
-\keywords{Publishing; preprint server; Green Open Access; arXiv.}
+\keywords{Publishing; Preprint servers; Green Open Access; arXiv.}
 
@@
 Sciences and Engineering Council of Canada and by the Canada Research Chair
-program.
+program. EPW is supported by a CAREER Award from the National Science Foundation
+(DEB-0953694).
 
@@
 \bibliography{refs}
-\bibliographystyle{plain}
 

### 2012-10-01 ms.tex
add support KR
Tim modifs

--- 2012-09-28 ms.tex
@@
 
-Furthermore, the review process as a whole is critically over-loaded, because as
-the number of active scientists increases, because the pressure to publish
+Furthermore, the review process as a whole is critically over-loaded, because
+as the number of active scientists increases, because the pressure to publish
 increases, and because of an effect dubbed ``the tragedy of the reviewers
@@
 process all over again.  Initiatives to reduce time from submission to
-publication have emerged across the scientific community XXX et coll.  (REF)
-called for the recycling and reuse of peer-reviews: by attaching previous
-reviews and detailed replies to a new submission, both the editor and the
-referees can gauge the work done on the manuscript, and perhaps evaluate it with
-less prejudice. In a similar way, the \emph{Peerage of Science} initiative
-allows authors to seek anonymous pre-review by their peers. Some journals now
-accept to publish papers which received good evaluations, with \emph{Animal
-Biology} having recently accepted first a paper reviewed entirely with the
-\emph{Peerage of Science} \cite{abb12}, effectively outsourcing the review
-process. A widespread use of preprint servers can achieve the same goal of
-reducing the time spent in review. By putting a manuscript for open comments and
-criticisms, the authors will receive valuable feedback and can improve the
-version which will be submitted. With a rich enough community of scientists
-depositing preprints, and commenting on them, the process of an open pre-review
-can become widespread and will overall increase the quality of first
-submissions.
+publication have emerged across the scientific community. XXX et coll.  (TREE
+paper recylce, reuse, ...) called for the recycling and reuse of peer-reviews:
+by attaching previous reviews and detailed replies to a new submission, both
+the editor and the referees can gauge the work done on the manuscript, and
+perhaps evaluate it with less prejudice. In a similar way, the \emph{Peerage
+of Science} initiative allows authors to seek anonymous pre-review by their
+peers. Some journals now accept to publish papers which received good
+evaluations, with \emph{Animal Biology} having recently accepted first a paper
+reviewed entirely with the \emph{Peerage of Science} \cite{abb12}, effectively
+outsourcing the review process. A widespread use of preprint servers can
+achieve the same goal of reducing the time spent in review. By putting a
+manuscript for open comments and criticisms, the authors will receive valuable
+feedback and can improve the version which will be submitted. With a rich
+enough community of scientists depositing preprints, and commenting on them,
+the process of an open pre- review can become widespread and will overall
+increase the quality of first submissions.
 
@@
 Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
-without having it reviewed, papers submitted to F1000Research will eventually be
-reviewed. Thus, F1000Research offers a hybrid model with publicly available
+without having it reviewed, papers submitted to F1000Research will eventually
+be reviewed. Thus, F1000Research offers a hybrid model with publicly available
 manuscripts at time of submission and standard peer-reviews. Manuscripts are
 considered ``accepted'' and will only be indexed after two positive referee
-response.
+response. F1000Research works closely with data providers to integrate raw
+data to the paper. Forinstance, upon submitting a paper, authors are asked to
+upload their data, which are then integrated in \emph{e.g.} FigShare widgets,
+the DOI of which are given in the paper when the data are first mentionned.
+The licensing of the data is similar to the one used by FigShare, meaning that
+the articles are free to access, and can be redistributed readily. By putting
+much effort in integrating data to the paper, F1000Research is working to make
+science more reproducible and open.
 
@@
 versions. For example, during the development of this manuscript, one author
-would fork the project (i.e.: make a personal copy), modify it, and then the
+would fork the project (\emph{i.e.} make a personal copy), modify it, and then the
 changes were merged back into the main branch. These techniques are widely used

### 2012-10-01 ms.tex

@@
 PDP is supported by an Alexander Graham Bell scholarship from the National
-Sciences and Engineering Council of Canada. JJA is supported by NSF DEB-0614166
-and NSF DEB-0919018. DG is funded by a Discovery Grand from the National
-Sciences and Engineering Council of Canada and by the Canada Research Chair
-program.
+Sciences and Engineering Council of Canada. EPW is supported by a CAREER Award
+from the National Science Foundation (DEB-0953694). JJA is supported by NSF
+DEB-0614166 and NSF DEB-0919018. KR is supported by NSF DEB-1021553. DG is
+funded by a Discovery Grand from the National Sciences and Engineering Council
+of Canada and by the Canada Research Chair program.
 

### 2012-10-01 ms.tex
add hochberg ref

@@
 increases, and because of an effect dubbed ``the tragedy of the reviewers
-commons'' REF.  At the same time, rejection rates are high in most journals
+commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
 (REF), and when not invited to submit a revision, authors must start the whole

### 2012-10-02 ms.tex
add references

@@
 commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
-(REF), and when not invited to submit a revision, authors must start the whole
+\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the whole
 process all over again.  Initiatives to reduce time from submission to
-publication have emerged across the scientific community. XXX et coll.  (TREE
-paper recylce, reuse, ...) called for the recycling and reuse of peer-reviews:
+publication have emerged across the scientific community. Rohr et al.
+\cite{roh09} called for the recycling and reuse of peer-reviews:
 by attaching previous reviews and detailed replies to a new submission, both

### 2012-10-02 ms.tex

@@
 than to wait until the peer-review process is fully completed. The goal of arXiv
-and open preprint servers is not to avoid the peer-review process; almost all
+and open preprint servers is not to circumvent the peer-review process; almost all
 manuscripts on arXiv are submitted to peer-review.  Sharing ideas as quickly as
 possible using preprint servers has numerous advantages.  These include rapid
-dissemination of work in progress to a wider audience, including readers in
+dissemination of work-in-progress to a wider audience, including readers in
 developing countries where access to subscription journals is often a limiting
@@
 fields, most manuscripts in biology are not submitted to a public archive before
-being submitted to peer-review.  In this article, we will first highlight the
-advantages of open preprint servers for both scientists and publishers. We will
-also debunk a few misconceptions, discuss the policies of major publishers in
-biology, and briefly review the most popular open preprint servers.
+being submitted to peer-review.  In this article, we first highlight the
+advantages of open preprint servers for both scientists and publishers. We
+then debunk a few misconceptions, discuss the policies of major publishers in
+biology, and briefly review the most popular open preprint servers currently available.
 
@@
 \cite{cal12}. Most scientific journals are preprint-friendly: Nature, PLOS, BMC,
-PNAS, Science (mostly) \ref{table:policies}, and all the journals from Elsevier
+PNAS, Science (mostly) \ref{table:policies}, and all the journals from Elsevier %something is off in the formatting here
 and Springer.  The Ecological Society of America and the Genetics Society of
@@
 PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new publishing system
-that provides both a preprint server, and a peer reviewed journal.  It is
+that combines both a preprint server, and a peer reviewed journal.  It is
 focused on the biological and medical sciences, which may help overcome the
@@
 
-\subsection{Github et al.?}
+\subsection{Github}
 
@@
 one of several hosting services for collaborative development using the git
-revision control software.  git is a decentralized revision control system
+version control system (VCS).  git is a decentralized revision control system
 created by Linus Torvalds and is used primarily to develop software, including
-the Linux kernel. It allows the users to share code, track changes, and merge
-versions. For example, during the development of this manuscript, one author
-would fork the project (\emph{i.e.} make a personal copy), modify it, and then the
-changes were merged back into the main branch. These techniques are widely used
-in open source software development. It goes even farther than submitting
-preprints by opening the entire writing process.
+the Linux kernel.
+Git provides powerful features that allow numerous contributers to work asynchronously on the same project, often in parallel branches, all of which can be effortlessly merged and version controlled.
+Although created primarily for software development, git is ideal for academic research since it provides a way to version control and collaborate on every step of the manuscript development process, from data manipulation and analysis to writing and revision.
+For example, during the development of this manuscript, each author
+would clone the project (\emph{i.e.} make a personal copy), modify it, and then merge their changes into a master branch.This takes the preprint process to an entirely new level, where the entire writing process is open from the beginning.
+% I would avoid using the term forking since it is not a central piece of the section.
+It is one specific way of collaborating on a github repo when everyone does not have rights to it.
+People could just as easily work on a single branch, all with write access, either directly to the master branch or to individual branches that could be merged.
+So in other words, we should keep the language general so people don't get bogged down with trying to understand what a fork is.
+% also I changed one author clones, then submits pull request langauge a bit since the main point of using git is that we can all work simultaneously unlike svn.
+% I took out "These techniques are widely used in open source software development." because git can also be used for closed source software, offering the same advantages, where the repositories are private.
+Paid git accounts allow for private repos.
 
@@
 
+% Aren't we bridging more than cultural and geographic?
+I mean, we are essentially cross pollinating ideas.
+e.g.
+It took a lot time for MCMC to become popular in ecology even though it was widely used in other disciplines a decade or two earlier.
 Preprint servers also facilitate communication between disciplines, bridging

### 2012-10-05 ms.tex
Tightening the Introduction

@@
 peer-review. The rationale for preprint servers is fundamentally simple: to make
-the results available to the scientific community as soon as possible rather
-than to wait until the peer-review process is fully completed. The goal of arXiv
-and open preprint servers is not to circumvent the peer-review process; almost all
-manuscripts on arXiv are submitted to peer-review.  Sharing ideas as quickly as
-possible using preprint servers has numerous advantages.  These include rapid
-dissemination of work-in-progress to a wider audience, including readers in
-developing countries where access to subscription journals is often a limiting
-factor in scientific research.  Furthermore, preprints provide the opportunity
-to solicit feedback from a larger pool of reviewers and can be seen as an
-integral aspect of a vigorous peer-review process \cite{hoc12}.  Preprint
-servers therefore increase the number of opportunities for review and revision
-prior to publication, resulting in higher quality submissions and also could
-alleviate reviewer burden.
+the results of scientific research available to the scientific community as soon
+as possible, instead of waiting until the peer-review process is fully completed.
+Sharing manuscripts using preprint servers has numerous advantages including: 1) rapid
+dissemination of work-in-progress to a wider audience; 2) improved peer review by
+encouraging feedback from the entire research community;
+and 3) a fair and straightforward way to establish precedence.
 
-Preprints gained popularity 20 years ago with the advent of arXiv, an open
+Preprints began to gain popularity 20 years ago with the advent of arXiv, an open
 preprint server widely used in physics and mathematics \cite{gin11}. Preprints
@@
 in Economics) initiative, which aims to create an archive of working papers,
-manuscripts, and book chapters.  Despite the success of this approach in other
-fields, most manuscripts in biology are not submitted to a public archive before
-being submitted to peer-review.  In this article, we first highlight the
-advantages of open preprint servers for both scientists and publishers. We
-then debunk a few misconceptions, discuss the policies of major publishers in
-biology, and briefly review the most popular open preprint servers currently available.
+manuscripts, and book chapters.
+
+Despite the success of this approach in other
+fields, most manuscripts in biology are not posted to preprint servers and
+are therefore not seen by more than a handful of other scientists prior to
+publication. In this article, we: 1) highlight the
+advantages of open preprint servers for both scientists and publishers; 2)
+address several misconceptions about preprints that are common among biologists;
+3) discuss the preprint policies of major publishers in biology;
+and 4) review the most popular preprint servers currently available.
 

### 2012-10-05 ms.tex
Reorganizing and editing the Case for Public Preprints section

@@
 speed (Figure~\ref{fig:map}). The time between submission and the official
-publication of a manuscript can be measured in months, sometime in years. For
-all this time, the research is known only to a select few: colleagues, editors,
+publication of a manuscript can be measured in months or even years. During
+this time, the research is known only to a select few: colleagues, editors,
 reviewers.  Thus, the science cannot be used, discussed, or reviewed by the
-wider scientific community.  This stage of manuscript preparation is a problem
-for both scientists and publishers.  Manuscripts that are unknown cannot be used
-and thus take more time to be cited. It has been shown that high-energy physics,
-with its high arXiv submission rate, had the highest immediacy among physics and
-mathematics \cite{pra05}. Immediacy measures how quickly articles are cited.
+wider scientific community.  If the science being published is a year
+or more behind the cutting edge, then science will progress more slowly. While
+conferences and informal sharing of ideas among research groups may ameliorate
+this issue, this type of communication is inherently limited to a restricted
+subset of scienctists. Posting preprints ensures that science is not
+constrained by small networks of scientists exchanging ideas.  Paul Ginsparg
+created arXiv.org in part for democratic reasons: he wanted everyone from students
+in small universities to Ivy-League professors to have access to the most recent
+scientific \emph{ideas}. Ginsparg's revolutionary idea was simply to use the power
+of the internet for preprints, not just for the end product, so the scientific
+process can be open to all as soon as possible.
 
-Furthermore, the review process as a whole is critically over-loaded, because
-as the number of active scientists increases, because the pressure to publish
-increases, and because of an effect dubbed ``the tragedy of the reviewers
-commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
-\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the whole
-process all over again.  Initiatives to reduce time from submission to
+Posting manuscripts as preprints also has the potential to result in higher
+quality science, by allowing for pre-publication feedback
+from a large pool of reviewers. Prepublication reviews by a small network of
+colleagues are common in the biological sciences and are an important part of
+the scientific process. These "friendly" reviews increases the chances of errors
+being caught prior to publication, allow errors to be identified
+prior to spending months in review, and allows authors to improve how they
+communicate the results of their research by modifying their writing in response
+to early feedback. Preprint servers offer a way to extend this network of
+colleagues to the entire scientific
+community, increasing the number of opportunities for review and revision
+prior to publication, and resulting in higher quality submissions and publications.
+As such, preprints can be seen as an
+integral aspect of a vigorous peer-review process \cite{hoc12}.
+
+%It is unclear to me whether we should keep this full paragraph or try to distill
+%it to a sentence or two at the end of the previous paragraph.
+Furthermore, the formal peer-review process as a whole is critically over-loaded. As
+the number of active scientists increases and the pressure to publish
+increases, it has become increasingly difficult for journals to find
+reviewers \cite{hoc09}.  At the same time, rejection rates are high in most journals
+\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the
+process over again at another journal. As a result, initiatives to reduce time from submission to
 publication have emerged across the scientific community. Rohr et al.
@@
 outsourcing the review process. A widespread use of preprint servers can
-achieve the same goal of reducing the time spent in review. By putting a
-manuscript for open comments and criticisms, the authors will receive valuable
+achieve the same goal of reducing the time spent in review. By allowing
+open comments and criticisms prior to submission, the authors will receive valuable
 feedback and can improve the version which will be submitted. With a rich
 enough community of scientists depositing preprints, and commenting on them,
-the process of an open pre- review can become widespread and will overall
+the process of an open pre-review can become widespread and will overall
 increase the quality of first submissions.
@@
 
-Public preprint servers offer a much fairer way to establish intellectual
-priority by making the work available when done. Some manuscripts will spend
-much more time in the review process than others. Surprisingly, there is a
-perception in biology that public preprints make it easier to steal ideas, as if
-a scientific idea was only complete once published in a peer-reviewed journal
-\cite{gin11}. Ironically, mathematicians and physicists have embraced arXiv in
-part to establish priority in a fair way \cite{gin11,cal12}.
-
-Prepublication reviews by a small network of colleagues is an important part of
-the scientific process, attested by the fact that nearly all published papers
-acknowledge comments by people not listed as co-authors.  Preprint servers
-simply offer a way to extend this network of colleagues to the entire scientific
-community. It ensures that science is not constrained by small networks of
-scientists exchanging ideas.  Paul Ginsparg created arXiv.org in part for
-democratic reasons: he wanted everyone from students in small universities to
-Ivy-League professors to have access to the most recent scientific \emph{ideas}.
-Ginsparg's revolutionary idea was simply to use the power of the internet for
-preprints, not just for the end product, so the scientific process can be open
-as soon as possible.
+Finally, public preprint servers offer a fair way to establish intellectual
+priority by making the work available when immediately after it is complete.
+Some manuscripts will spend much more time in the review process and/or in
+production after acceptance, than others. This means that
+that publication and acceptance dates do not accurately characterize who
+came up with an idea first. For this reason, mathematicians and physicists
+have embraced arXiv in part to establish priority in a fair way \cite{gin11,cal12}.
+In contrast, there is a surprising perception in biology that public preprints
+make it easier to steal ideas. Since there is no evidence that this has happened
+in the numerous other fields that have adopted preprint servers, and since preprint
+servers create a clear record of who had the idea first, and when, this would
+appear to be a largely unfounded concern.
+%I'm torn over whether to keep the biology part in this paragraph where it is 
+%topically related, or to move it down into the biological sciences part of the ms
 

### 2012-10-05 ms.tex
merge DGs file

--- 2012-10-02 ms.tex
@@
 \affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
-\affiliation{D\'epartement des sciences biologiques, Universit\'e du Qu\'ebec \`a Montr\'eal, Canada.}
 
@@
 Furthermore, the review process as a whole is critically over-loaded, because
-as the number of active scientists increases, because the pressure to publish
+the number of active scientists increases, because the pressure to publish
 increases, and because of an effect dubbed ``the tragedy of the reviewers
@@
 \label{fig:map} \end{figure}
+% Dom : Do you have a reference for the stats in the legend?
 
@@
 part to establish priority in a fair way \cite{gin11,cal12}.
+% Dom: That's a very interesting statement, if not the best one to justify preprints. Could you develop just a bit more the argument?
 
@@
 as soon as possible.
+% Dom: I do accept this argument, although I have doubts it makes any difference. Just think about the number of comments posted on PLoS One...
 
@@
 manuscripts at time of submission and standard peer-reviews. Manuscripts are
-considered ``accepted'' and will only be indexed after two positive referee
+considered ``accepted'' and will only be indexed after two positive referee % What about corrections? There are exchanges between referees and the authors?
 response. F1000Research works closely with data providers to integrate raw
-data to the paper. Forinstance, upon submitting a paper, authors are asked to
+data to the paper. For instance, upon submitting a paper, authors are asked to
 upload their data, which are then integrated in \emph{e.g.} FigShare widgets,
@@
 
-\subsection{Github}
+\subsection{GitHub}
 
-This manuscript was developed entirely as an open project on github. github is
-one of several hosting services for collaborative development using the git
-version control system (VCS).  git is a decentralized revision control system
+This manuscript was developed entirely as an open project on GitHub. GitHub is
+one of several hosting services for collaborative development using the Git
+version control system (VCS).  Git is a decentralized revision control system
 created by Linus Torvalds and is used primarily to develop software, including
@@
 \section{Conclusion}
+
+% I added the following three paragraphs to the conclusion, offering also a discussion on the on going explosion of different publication models. Take what you want and remove what you don't need.
+% I also had the feeling we might want to include a single paragraph, very short, calling that evaluations (academia, grant agencies etc...) looking at publication records or report of scientific activities start to view preprints as a significant and sound scientific contribution.
+One of the most important benefit is again the speed of the publication process.
+Most grants are for three years or less.
+It makes it hard to have a published paper within the limits of the grant.
+Preprints could however speed the process and show that contributions were made during the time of the grant.
+The ongoing discussions on the publication process, peer-reviewing and alternative publication models are all symptoms of the current uneasiness of scientists with the ever growing obsession with bibliographic metrics such as the impact factor \cite{Fisher2012}.
+There is pressure on researchers, wether they are junior looking for an academic position or senior trying to secure funding for their team, to orient their publication strategy in order to maximize their number of publications and total citations.
+A well-known consequence is to submit manuscripts first to the most prestigious journals, and then resubmit to lower level journals as they are rejected.
+The numerous negative impacts of such behavior have been discussed in depth \cite{hoc09}.
+They all contribute somehow in a general slowing down of scientific progress.
+Research activities and the publication process are drifting away from their fundamental object, namely the diffusion of novel scientific discoveries.
+
+Developing a preprint culture in biology is not a final solution to the impact factor inflation, it might however reduce significantly its negative consequences.
+Preprints speed up publication, openly, with no judgement on pertinence and originality.
+Paradoxically, because peer-reviewing is conducted following this step in the process of a scientific communication, it might bring it closer to its fundamental objective.
+The role of peer-reviewing is to judge the scientific quality of a study, the match between its hypotheses, methods, results and conclusions.
+The peer review process is the first barrier against fraudulent or bad quality science, susceptible to impede scientific progress.
+It is however now dominated by subjective evaluations, where trendy contributions are promoted to increase the immediacy impact of the journal.
+Most journals have in their instructions for reviewers a section devoted to the evaluation of suitability for the journal, a task usually incumbent to editors.
+Preprints are by definition not evaluated, neither for their quality nor their pertinence.
+Technically, the difference between a preprint and a traditional publication should be that the latter as the approval stamp by pairs on its quality.
+The relevance of a study, its contribution to science, should only be judged post-publication by many more readers than the typical two-four anonymous reviewers.
+With a such a shift in the diffusion strategy, the role of traditional journals and their editors would be to showcase scientific discoveries for specialized readership.
+Such a process should improve even further their diffusion, not impede it.
+
+The current opening of the publication process we are currently witnessing with the arrival of new preprint systems and innovative publication models such as F1000, PLoS One, Nature Scientific Reports, might significantly bypass the inflation of bibliographic metrics.
+They not only promote scientific community by changing the focus of the peer-reviewing, they also favor the publication of results that might otherwise be rejected because of low interest, negative results, descriptive and quantitative studies and datasets.
+One of drawback of making publication easier is obviously the proliferation of studies of uneven quality.
+A tradeoff between the intensity of the peer-review filtering and the benefits to science has been hypothesized \cite{Aarssen2012}.
+With increasingly stringent peer reviewing, the quality of published papers and easiness of finding discoveries might increase, at the cost of censorship, increasing load on authors and reviewers and time for publication.
+Preprints are simply bypassing this model, for what we believe is the progress of science: they speed up the dissemination of scientific discoveries, impede censorship and put on reader's shoulders the responsibility to judge originality and pertinence.
+
+% Fisher, J, Ritchie, E.G., Hanspach, J. (2012). Academia's obsession with quantity. Trends in Ecology and Evolution, 27, 473-474.
+% Aarssen, L. (2012). Are peer-review filters optimal for the progress of science in ecology and evolution? Ideas in Ecology and Evolution, 5, 9–12.
 

### 2012-10-05 ms.tex
merge Dom, improve Git and figshare sections

@@
 We briefly discuss the main options to submit preprints to open servers:
-arXiv.org, Figshare, and the upcoming PeerJ and F1000Research.
+arXiv.org, figshare, and the upcoming PeerJ and F1000Research.
 
@@
 
-\subsection{Figshare}
+\subsection{figshare}
 
-Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
+figshare (\href{http://figshare.com}{http://figshare.com}) is an open server
 that allows scientists to submit any research output: manuscript, figures,
@@
 PeerJ uses the CC-BY-SA 3.0 license, which is similar to the CC-BY license used
-by Figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
+by figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
 need a license identical to the license that governs the original work.
@@
 F1000Research is not a public preprint server like the previous three servers.
-Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
-without having it reviewed, papers submitted to F1000Research will eventually
-be reviewed. Thus, F1000Research offers a hybrid model with publicly available
+Whereas arXiv, figshare, and PeerJ offer an option to submit a manuscript
+without having it reviewed, papers submitted to F1000Research will eventually be
+reviewed. Thus, F1000Research offers a hybrid model with publicly available
 manuscripts at time of submission and standard peer-reviews. Manuscripts are
-considered ``accepted'' and will only be indexed after two positive referee % What about corrections? There are exchanges between referees and the authors?
-response. F1000Research works closely with data providers to integrate raw
-data to the paper. For instance, upon submitting a paper, authors are asked to
-upload their data, which are then integrated in \emph{e.g.} FigShare widgets,
-the DOI of which are given in the paper when the data are first mentionned.
-The licensing of the data is similar to the one used by FigShare, meaning that
-the articles are free to access, and can be redistributed readily. By putting
-much effort in integrating data to the paper, F1000Research is working to make
+considered ``accepted'' and will only be indexed after two positive referee
+response. F1000Research works closely with data providers to integrate raw data
+to the paper. For instance, upon submitting a paper, authors are asked to upload
+their data, which are then integrated in \emph{e.g.} figshare widgets, the DOI
+of which are given in the paper when the data are first mentionned.  The
+licensing of the data is similar to the one used by figshare, meaning that the
+articles are free to access, and can be redistributed readily. By putting much
+effort in integrating data to the paper, F1000Research is working to make
 science more reproducible and open.
@@
 created by Linus Torvalds and is used primarily to develop software, including
-the Linux kernel.
-Git provides powerful features that allow numerous contributers to work asynchronously on the same project, often in parallel branches, all of which can be effortlessly merged and version controlled.
-Although created primarily for software development, git is ideal for academic research since it provides a way to version control and collaborate on every step of the manuscript development process, from data manipulation and analysis to writing and revision.
-For example, during the development of this manuscript, each author
-would clone the project (\emph{i.e.} make a personal copy), modify it, and then merge their changes into a master branch.This takes the preprint process to an entirely new level, where the entire writing process is open from the beginning.
-% I would avoid using the term forking since it is not a central piece of the section.
-It is one specific way of collaborating on a github repo when everyone does not have rights to it.
-People could just as easily work on a single branch, all with write access, either directly to the master branch or to individual branches that could be merged.
-So in other words, we should keep the language general so people don't get bogged down with trying to understand what a fork is.
-% also I changed one author clones, then submits pull request langauge a bit since the main point of using git is that we can all work simultaneously unlike svn.
-% I took out "These techniques are widely used in open source software development." because git can also be used for closed source software, offering the same advantages, where the repositories are private.
-Paid git accounts allow for private repos.
+the Linux kernel. Git provides powerful features that allow numerous
+contributers to work asynchronously on the same project, often in parallel
+branches, all of which can be effortlessly merged and version controlled.  While
+Git is created primarily for software development, where the use of version
+control systems is standard \cite{aru12}, it is ideal for academic research
+since it provides a way to collaborate on every step of the manuscript
+development process, from data manipulation and analysis to writing and
+revision. For example, during the development of this manuscript, each author
+would clone the project (\emph{i.e.} make a personal copy), modify it, and then
+merge their changes into a master branch. This takes the preprint process to an
+entirely new level, where the entire writing process is open from the beginning.
 
@@
 
-% I added the following three paragraphs to the conclusion, offering also a discussion on the on going explosion of different publication models. Take what you want and remove what you don't need.
-% I also had the feeling we might want to include a single paragraph, very short, calling that evaluations (academia, grant agencies etc...) looking at publication records or report of scientific activities start to view preprints as a significant and sound scientific contribution.
-One of the most important benefit is again the speed of the publication process.
-Most grants are for three years or less.
-It makes it hard to have a published paper within the limits of the grant.
-Preprints could however speed the process and show that contributions were made during the time of the grant.
-The ongoing discussions on the publication process, peer-reviewing and alternative publication models are all symptoms of the current uneasiness of scientists with the ever growing obsession with bibliographic metrics such as the impact factor \cite{Fisher2012}.
-There is pressure on researchers, wether they are junior looking for an academic position or senior trying to secure funding for their team, to orient their publication strategy in order to maximize their number of publications and total citations.
-A well-known consequence is to submit manuscripts first to the most prestigious journals, and then resubmit to lower level journals as they are rejected.
-The numerous negative impacts of such behavior have been discussed in depth \cite{hoc09}.
+% I added the following three paragraphs to the conclusion, offering also a
+% discussion on the on going explosion of different publication models. Take
+% what you want and remove what you don't need.  I also had the feeling we might
+% want to include a single paragraph, very short, calling that evaluations
+% (academia, grant agencies etc...) looking at publication records or report of
+% scientific activities start to view preprints as a significant and sound
+% scientific contribution. One of the most important benefit is again the speed
+% of the publication process. Most grants are for three years or less. It makes
+% it hard to have a published paper within the limits of the grant. Preprints
+% could however speed the process and show that contributions were made during
+% the time of the grant. 
+The ongoing discussions on the publication process, peer-reviewing and
+alternative publication models are all symptoms of the current uneasiness of
+scientists with the ever growing obsession with bibliographic metrics such as
+the impact factor \cite{Fisher2012}. There is pressure on researchers, wether
+they are junior looking for an academic position or senior trying to secure
+funding for their team, to orient their publication strategy in order to
+maximize their number of publications and total citations. A well-known
+consequence is to submit manuscripts first to the most prestigious journals, and
+then resubmit to lower level journals as they are rejected. The numerous
+negative impacts of such behavior have been discussed in depth \cite{hoc09}.
 They all contribute somehow in a general slowing down of scientific progress.
-Research activities and the publication process are drifting away from their fundamental object, namely the diffusion of novel scientific discoveries.
+Research activities and the publication process are drifting away from their
+fundamental object, namely the diffusion of novel scientific discoveries.
 
-Developing a preprint culture in biology is not a final solution to the impact factor inflation, it might however reduce significantly its negative consequences.
-Preprints speed up publication, openly, with no judgement on pertinence and originality.
-Paradoxically, because peer-reviewing is conducted following this step in the process of a scientific communication, it might bring it closer to its fundamental objective.
-The role of peer-reviewing is to judge the scientific quality of a study, the match between its hypotheses, methods, results and conclusions.
-The peer review process is the first barrier against fraudulent or bad quality science, susceptible to impede scientific progress.
-It is however now dominated by subjective evaluations, where trendy contributions are promoted to increase the immediacy impact of the journal.
-Most journals have in their instructions for reviewers a section devoted to the evaluation of suitability for the journal, a task usually incumbent to editors.
-Preprints are by definition not evaluated, neither for their quality nor their pertinence.
-Technically, the difference between a preprint and a traditional publication should be that the latter as the approval stamp by pairs on its quality.
-The relevance of a study, its contribution to science, should only be judged post-publication by many more readers than the typical two-four anonymous reviewers.
-With a such a shift in the diffusion strategy, the role of traditional journals and their editors would be to showcase scientific discoveries for specialized readership.
-Such a process should improve even further their diffusion, not impede it.
+Developing a preprint culture in biology is not a final solution to the impact
+factor inflation, it might however reduce significantly its negative
+consequences. Preprints speed up publication, openly, with no judgement on
+pertinence and originality. Paradoxically, because peer-reviewing is conducted
+following this step in the process of a scientific communication, it might bring
+it closer to its fundamental objective. The role of peer-reviewing is to judge
+the scientific quality of a study, the match between its hypotheses, methods,
+results and conclusions. The peer review process is the first barrier against
+fraudulent or bad quality science, susceptible to impede scientific progress. It
+is however now dominated by subjective evaluations, where trendy contributions
+are promoted to increase the immediacy impact of the journal. Most journals have
+in their instructions for reviewers a section devoted to the evaluation of
+suitability for the journal, a task usually incumbent to editors. Preprints are
+by definition not evaluated, neither for their quality nor their pertinence.
+Technically, the difference between a preprint and a traditional publication
+should be that the latter as the approval stamp by pairs on its quality. The
+relevance of a study, its contribution to science, should only be judged
+post-publication by many more readers than the typical two-four anonymous
+reviewers. With a such a shift in the diffusion strategy, the role of
+traditional journals and their editors would be to showcase scientific
+discoveries for specialized readership. Such a process should improve even
+further their diffusion, not impede it.
 
-The current opening of the publication process we are currently witnessing with the arrival of new preprint systems and innovative publication models such as F1000, PLoS One, Nature Scientific Reports, might significantly bypass the inflation of bibliographic metrics.
-They not only promote scientific community by changing the focus of the peer-reviewing, they also favor the publication of results that might otherwise be rejected because of low interest, negative results, descriptive and quantitative studies and datasets.
-One of drawback of making publication easier is obviously the proliferation of studies of uneven quality.
-A tradeoff between the intensity of the peer-review filtering and the benefits to science has been hypothesized \cite{Aarssen2012}.
-With increasingly stringent peer reviewing, the quality of published papers and easiness of finding discoveries might increase, at the cost of censorship, increasing load on authors and reviewers and time for publication.
-Preprints are simply bypassing this model, for what we believe is the progress of science: they speed up the dissemination of scientific discoveries, impede censorship and put on reader's shoulders the responsibility to judge originality and pertinence.
-
-% Fisher, J, Ritchie, E.G., Hanspach, J. (2012). Academia's obsession with quantity. Trends in Ecology and Evolution, 27, 473-474.
-% Aarssen, L. (2012). Are peer-review filters optimal for the progress of science in ecology and evolution? Ideas in Ecology and Evolution, 5, 9–12.
+The current opening of the publication process we are currently witnessing with
+the arrival of new preprint systems and innovative publication models such as
+F1000, PLoS One, Nature Scientific Reports, might significantly bypass the
+inflation of bibliographic metrics. They not only promote scientific community
+by changing the focus of the peer-reviewing, they also favor the publication of
+results that might otherwise be rejected because of low interest, negative
+results, descriptive and quantitative studies and datasets. One of drawback of
+making publication easier is obviously the proliferation of studies of uneven
+quality. A tradeoff between the intensity of the peer-review filtering and the
+benefits to science has been hypothesized \cite{Aarssen2012}. With increasingly
+stringent peer reviewing, the quality of published papers and easiness of
+finding discoveries might increase, at the cost of censorship, increasing load
+on authors and reviewers and time for publication. Preprints are simply
+bypassing this model, for what we believe is the progress of science: they speed
+up the dissemination of scientific discoveries, impede censorship and put on
+reader's shoulders the responsibility to judge originality and pertinence.
 
@@
 
-% Aren't we bridging more than cultural and geographic?
-I mean, we are essentially cross pollinating ideas.
-e.g.
-It took a lot time for MCMC to become popular in ecology even though it was widely used in other disciplines a decade or two earlier.
+% Aren't we bridging more than cultural and geographic? I mean, we are
+% essentially cross pollinating ideas. e.g. It took a lot time for MCMC to
+% become popular in ecology even though it was widely used in other disciplines
+% a decade or two earlier.
 Preprint servers also facilitate communication between disciplines, bridging
@@
 
-We thank Carl Boettiger for helpful comments on an earlier version of this
-manuscript.
+We thank Carl Boettiger and Mark Hahnel for helpful comments on an earlier
+version of this manuscript.
 

### 2012-10-05 ms.tex
minor

@@
 
+% Dominique:
 % I added the following three paragraphs to the conclusion, offering also a
@@
 % the time of the grant.
+
 The ongoing discussions on the publication process, peer-reviewing and
@@
 then resubmit to lower level journals as they are rejected. The numerous
-negative impacts of such behavior have been discussed in depth \cite{hoc09}.
-They all contribute somehow in a general slowing down of scientific progress.
-Research activities and the publication process are drifting away from their
-fundamental object, namely the diffusion of novel scientific discoveries.
+negative impacts of such behavior have been discussed in depth \cite{hoc09} and
+include a long delay between the time a manuscript is finished to its
+publication.  They all contribute somehow in a general slowing down of
+scientific progress.  Research activities and the publication process are
+drifting away from their fundamental object, namely the diffusion of novel
+scientific discoveries.
 
@@
 the arrival of new preprint systems and innovative publication models such as
-F1000, PLoS One, Nature Scientific Reports, might significantly bypass the
+F1000, PLOS One, Nature Scientific Reports, might significantly bypass the
 inflation of bibliographic metrics. They not only promote scientific community

### 2012-10-05 ms.tex
add refs
Restructuring Biological Sciences section

--- 2012-10-05 ms.tex
@@
 \affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
+\affiliation{D\'epartement des sciences biologiques, Universit\'e du Qu\'ebec \`a Montr\'eal, Canada.}
 
@@
 in Economics) initiative, which aims to create an archive of working papers,
-manuscripts, and book chapters.  Despite the success of this approach in other
-fields, most manuscripts in biology are not submitted to a public archive before
-being submitted to peer-review. In this article, we first highlight the
-advantages of open preprint servers for both scientists and publishers. We
-then debunk a few misconceptions, discuss the policies of major publishers in
-biology, and briefly review the most popular open preprint servers currently available.
+manuscripts, and book chapters.
+
+Despite the success of this approach in other
+fields, most manuscripts in biology are not posted to preprint servers and
+are therefore not seen by more than a handful of other scientists prior to
+publication. In this article, we: 1) highlight the
+advantages of open preprint servers for both scientists and publishers; 2)
+address several misconceptions about preprints that are common among biologists;
+3) discuss the preprint policies of major publishers in biology;
+and 4) review the most popular preprint servers currently available.
 
@@
 speed (Figure~\ref{fig:map}). The time between submission and the official
-publication of a manuscript can be measured in months, sometime in years. For
-all this time, the research is known only to a select few: colleagues, editors,
+publication of a manuscript can be measured in months or even years. During
+this time, the research is known only to a select few: colleagues, editors,
 reviewers.  Thus, the science cannot be used, discussed, or reviewed by the
-wider scientific community. This stage of manuscript preparation is a problem
-for both scientists and publishers. Manuscripts that are unknown cannot be used
-and thus take more time to be cited. It has been shown that high-energy physics,
-with its high arXiv submission rate, had the highest immediacy among physics and
-mathematics \cite{pra05}. Immediacy measures how quickly articles are cited.
+wider scientific community.  If the science being published is a year
+or more behind the cutting edge, then science will progress more slowly. While
+conferences and informal sharing of ideas among research groups may ameliorate
+this issue, this type of communication is inherently limited to a restricted
+subset of scienctists. Posting preprints ensures that science is not
+constrained by small networks of scientists exchanging ideas.  Paul Ginsparg
+created arXiv.org in part for democratic reasons: he wanted everyone from students
+in small universities to Ivy-League professors to have access to the most recent
+scientific \emph{ideas}. Ginsparg's revolutionary idea was simply to use the power
+of the internet for preprints, not just for the end product, so the scientific
+process can be open to all as soon as possible.
 
-Furthermore, the review process as a whole is critically over-loaded, because
-the number of active scientists increases, because the pressure to publish
-increases, and because of an effect dubbed ``the tragedy of the reviewers
-commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
-\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the whole
-process all over again.  Initiatives to reduce time from submission to
+Posting manuscripts as preprints also has the potential to result in higher
+quality science, by allowing for pre-publication feedback
+from a large pool of reviewers. Prepublication reviews by a small network of
+colleagues are common in the biological sciences and are an important part of
+the scientific process. These "friendly" reviews increases the chances of errors
+being caught prior to publication, allow errors to be identified
+prior to spending months in review, and allows authors to improve how they
+communicate the results of their research by modifying their writing in response
+to early feedback. Preprint servers offer a way to extend this network of
+colleagues to the entire scientific
+community, increasing the number of opportunities for review and revision
+prior to publication, and resulting in higher quality submissions and publications.
+As such, preprints can be seen as an
+integral aspect of a vigorous peer-review process \cite{hoc12}.
+
+%It is unclear to me whether we should keep this full paragraph or try to distill
+%it to a sentence or two at the end of the previous paragraph.
+Furthermore, the formal peer-review process as a whole is critically over-loaded. As
+the number of active scientists increases and the pressure to publish
+increases, it has become increasingly difficult for journals to find
+reviewers \cite{hoc09}.  At the same time, rejection rates are high in most journals
+\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the
+process over again at another journal. As a result, initiatives to reduce time from submission to
 publication have emerged across the scientific community. Rohr et al.
@@
 \label{fig:map} \end{figure}
-% Dom : Do you have a reference for the stats in the legend?
 
-Public preprint servers offer a much fairer way to establish intellectual
-priority by making the work available when done. Some manuscripts will spend
-much more time in the review process than others. Surprisingly, there is a
-perception in biology that public preprints make it easier to steal ideas, as if
-a scientific idea was only complete once published in a peer-reviewed journal
-\cite{gin11}. Ironically, mathematicians and physicists have embraced arXiv in
-part to establish priority in a fair way \cite{gin11,cal12}.
-% Dom: That's a very interesting statement, if not the best one to justify preprints. Could you develop just a bit more the argument?
-
-Prepublication reviews by a small network of colleagues is an important part of
-the scientific process, attested by the fact that nearly all published papers
-acknowledge comments by people not listed as co-authors.  Preprint servers
-simply offer a way to extend this network of colleagues to the entire scientific
-community. It ensures that science is not constrained by small networks of
-scientists exchanging ideas.  Paul Ginsparg created arXiv.org in part for
-democratic reasons: he wanted everyone from students in small universities to
-Ivy-League professors to have access to the most recent scientific \emph{ideas}.
-Ginsparg's revolutionary idea was simply to use the power of the internet for
-preprints, not just for the end product, so the scientific process can be open
-as soon as possible.
-% Dom: I do accept this argument, although I have doubts it makes any difference. Just think about the number of comments posted on PLoS One...
+Finally, public preprint servers offer a fair way to establish intellectual
+priority by making the work available when immediately after it is complete.
+Some manuscripts will spend much more time in the review process and/or in
+production after acceptance, than others. This means that
+that publication and acceptance dates do not accurately characterize who
+came up with an idea first. For this reason, mathematicians and physicists
+have embraced arXiv in part to establish priority in a fair way \cite{gin11,cal12}.
 
@@
 
-Submitting to a preprint server is becoming more common in biology, even though
-it still involves a minority of papers. The quantitative biology section in
-arXiv is experiencing faster growth in submissions than any other field
-\cite{cal12}. Most scientific journals are preprint-friendly: Nature, PLOS, BMC,
-PNAS, Science (mostly) \ref{table:policies}, and all the journals from Elsevier %something is off in the formatting here
+In contrast to other disciplines, the field of biology has effectively no preprint
+culture, with the exception of small pockets of primarily highly quantitative
+research (e.g., epidemiology). While, submitting to preprint servers has become
+more common in the past few years, and the quantitative biology section in arXiv
+is experiencing rapid growth in submissions \cite{cal12}, the number of biology
+papers submitted to preprint servers still represents only a small fraction of
+the total research produced in biology.
+
+There are a number of reasons that biologists have not traditionally had a
+culture of sharing preprints, many of which are based on common misconceptions
+regarding the costs and benefits of sharing preprints. For example, in contrast
+to other fields there is a perception in biology that public preprints
+make it easier to steal ideas. However, there is no evidence of this happening
+in the numerous other fields that have adopted preprint servers, and since preprint
+servers create a clear record of who had the idea first, and when, this
+appears to be a largely unfounded concern. In other fields preprints serve the
+opposite role, they allow straightforward establishment of precendence, letting
+researchs lay claim to an idea thus prevening it from being "stolen".
+
+Another major concern is that if a researcher posts a public preprint that they
+will not be allowed to submit their paper to their journal of choice. This is 
+based on a certain interpretation
+of the Ingelfinger rule: scientists should not publish the same manuscript twice
+\cite{alt96}. However, preprints are not peer-reviewed papers and posting to a
+public server does not constitute publication in a peer-reviewed journal.
+A preprint is simply a document that allows ideas to spread and be discussed, 
+but it is not yet formally validated by the peer-review system. This is why the
+majority of publishers do not see arXiv and similar services as a violation of the
+Ingelfinger rule. Almost all of the major publishers in biology are preprint-friendly,
+including: Nature Publishing Group, PLOS, BMC, PNAS, Science (mostly) \ref{table:policies},
+and all the journals from Elsevier %something is off in the formatting here
 and Springer.  The Ecological Society of America and the Genetics Society of
-America recently changed their policies to allow public preprints.  Few
+America also recently changed their policies to allow public preprints.  Few
 scientific publications will not consider a manuscript submitted to a public
-preprint server.  Still, a few journals adopt a ``by default'' hostile attitude
+preprint server. In fact, \emph{Nature} responded to the rumour that they refused
+manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
+stand in the way of communication between researchers. We seek rather to add
+value for authors and the community at large in our peer review, selection and
+editing'' \cite{nat05}. Still, a few journals adopt a ``by default'' hostile attitude
 towards preprints, mostly due to the lack of clear policy of the publishers, or
@@
 is still considered unusual. As an example, Wiley-Blackwell, which publishes
-some leading journals, has no official policy on the subject
+some leading journals, has no official policy on the matter.
+
 \ref{table:policies}.
-
-Part of the hostility to preprints servers comes from a certain interpretation
-of the Ingelfinger rule: scientists should not publish the same manuscript twice
-\cite{alt96}. However, papers submitted to arXiv or other preprints servers are
-only published in one peer-reviewed journal. A preprint is just a preprint, it
-is a document that allows ideas to spread and be discussed, but it is not yet
-formally validated by the peer-review system, which is why the majority of
-publishers does not see arXiv and similar services as a violation of the
-Ingelfinger rule. \emph{Nature} responded to the rumour that they refused
-manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
-stand in the way of communication between researchers. We seek rather to add
-value for authors and the community at large in our peer review, selection and
-editing'' \cite{nat05}.
 
@@
 manuscripts at time of submission and standard peer-reviews. Manuscripts are
-considered ``accepted'' and will only be indexed after two positive referee % What about corrections? There are exchanges between referees and the authors?
+considered ``accepted'' and will only be indexed after two positive referee
 response. F1000Research works closely with data providers to integrate raw
-data to the paper. For instance, upon submitting a paper, authors are asked to
+data to the paper. Forinstance, upon submitting a paper, authors are asked to
 upload their data, which are then integrated in \emph{e.g.} FigShare widgets,
@@
 
-\subsection{GitHub}
+\subsection{Github}
 
-This manuscript was developed entirely as an open project on GitHub. GitHub is
-one of several hosting services for collaborative development using the Git
-version control system (VCS).  Git is a decentralized revision control system
+This manuscript was developed entirely as an open project on github. github is
+one of several hosting services for collaborative development using the git
+version control system (VCS).  git is a decentralized revision control system
 created by Linus Torvalds and is used primarily to develop software, including
@@
 \section{Conclusion}
-
-% I added the following three paragraphs to the conclusion, offering also a discussion on the on going explosion of different publication models. Take what you want and remove what you don't need.
-% I also had the feeling we might want to include a single paragraph, very short, calling that evaluations (academia, grant agencies etc...) looking at publication records or report of scientific activities start to view preprints as a significant and sound scientific contribution.
-One of the most important benefit is again the speed of the publication process.
-Most grants are for three years or less.
-It makes it hard to have a published paper within the limits of the grant.
-Preprints could however speed the process and show that contributions were made during the time of the grant.
-The ongoing discussions on the publication process, peer-reviewing and alternative publication models are all symptoms of the current uneasiness of scientists with the ever growing obsession with bibliographic metrics such as the impact factor \cite{Fisher2012}.
-There is pressure on researchers, wether they are junior looking for an academic position or senior trying to secure funding for their team, to orient their publication strategy in order to maximize their number of publications and total citations.
-A well-known consequence is to submit manuscripts first to the most prestigious journals, and then resubmit to lower level journals as they are rejected.
-The numerous negative impacts of such behavior have been discussed in depth \cite{hoc09}.
-They all contribute somehow in a general slowing down of scientific progress.
-Research activities and the publication process are drifting away from their fundamental object, namely the diffusion of novel scientific discoveries.
-
-Developing a preprint culture in biology is not a final solution to the impact factor inflation, it might however reduce significantly its negative consequences.
-Preprints speed up publication, openly, with no judgement on pertinence and originality.
-Paradoxically, because peer-reviewing is conducted following this step in the process of a scientific communication, it might bring it closer to its fundamental objective.
-The role of peer-reviewing is to judge the scientific quality of a study, the match between its hypotheses, methods, results and conclusions.
-The peer review process is the first barrier against fraudulent or bad quality science, susceptible to impede scientific progress.
-It is however now dominated by subjective evaluations, where trendy contributions are promoted to increase the immediacy impact of the journal.
-Most journals have in their instructions for reviewers a section devoted to the evaluation of suitability for the journal, a task usually incumbent to editors.
-Preprints are by definition not evaluated, neither for their quality nor their pertinence.
-Technically, the difference between a preprint and a traditional publication should be that the latter as the approval stamp by pairs on its quality.
-The relevance of a study, its contribution to science, should only be judged post-publication by many more readers than the typical two-four anonymous reviewers.
-With a such a shift in the diffusion strategy, the role of traditional journals and their editors would be to showcase scientific discoveries for specialized readership.
-Such a process should improve even further their diffusion, not impede it.
-
-The current opening of the publication process we are currently witnessing with the arrival of new preprint systems and innovative publication models such as F1000, PLoS One, Nature Scientific Reports, might significantly bypass the inflation of bibliographic metrics.
-They not only promote scientific community by changing the focus of the peer-reviewing, they also favor the publication of results that might otherwise be rejected because of low interest, negative results, descriptive and quantitative studies and datasets.
-One of drawback of making publication easier is obviously the proliferation of studies of uneven quality.
-A tradeoff between the intensity of the peer-review filtering and the benefits to science has been hypothesized \cite{Aarssen2012}.
-With increasingly stringent peer reviewing, the quality of published papers and easiness of finding discoveries might increase, at the cost of censorship, increasing load on authors and reviewers and time for publication.
-Preprints are simply bypassing this model, for what we believe is the progress of science: they speed up the dissemination of scientific discoveries, impede censorship and put on reader's shoulders the responsibility to judge originality and pertinence.
-
-% Fisher, J, Ritchie, E.G., Hanspach, J. (2012). Academia's obsession with quantity. Trends in Ecology and Evolution, 27, 473-474.
-% Aarssen, L. (2012). Are peer-review filters optimal for the progress of science in ecology and evolution? Ideas in Ecology and Evolution, 5, 9–12.
 

### 2012-10-05 ms.tex
One more minor editorial change to Biological Sciences section
Minor edits to the arXiv section

@@
 is still considered unusual. As an example, Wiley-Blackwell, which publishes
-some leading journals, has no official policy on the matter.
+some of the leading journals in biology, has no official policy on the matter.
 
@@
 rights to distribute submitted articles in perpetuity. Thus, submitting to arXiv
-does not in itself prevent the authors from transferring their rights to a
-publisher, which is why most publishers tolerate arXiv, even though they ask the
-authors to transfer their right to them upon acceptance of the article.
+does not prevent the authors from transferring their rights to a
+publisher.
 
 Most papers posted to arXiv are eventually printed in journals but there are
-notable exceptions, such as Perelman's landmark paper leading to the proof of
+notable exceptions including Perelman's landmark paper leading to the proof of
 the Poincar\'{e} conjecture \cite{2002math.....11159P}.  However, arXiv has

### 2012-10-05 ms.tex
Minor edits on the figshare section

@@
 Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
-that allows scientists to submit any research output: manuscript, figures,
+that allows scientists to submit any research output: manuscripts, figures,
 datasets, videos, theses, presentations, and so on. There are no rules to limit
@@
 any journal article, thus offering a permanent and stable link to the content.
-A flexible tag system is used to classify each item. All content can be
-commented and is licensed under the Creative Commons (CC-BY) license, except
+A flexible tag system is used to classify each item. All content
+is licensed under the Creative Commons (CC-BY) license, except
 datasets which are published under CC0. The CC-BY license grants rights to
@@
 provides an archive for early results (e.g.: figures, lab presentations).
+figshare also supports commenting on preprints.
 

### 2012-10-05 ms.tex
Minor edits on the peerj section

@@
 dialog. In addition, preprints can be made private if the authors choose, and
-shared only with selected colleagues. While this reduces some of the benefits of
+shared only with selected colleagues. While this reduces many of the benefits of
 preprints described above, it may allow some researchers who would not otherwise
@@
 preprints for free. One preprint per year can be posted for free and a onetime
-(i.e. lifetime) fee of 99 dollars allows the posting of unlimited public
+(i.e. lifetime) fee of 99 dollars allows the submitting author to post unlimited public
 preprints. It is also worth noting that the preprint server is not tied to the

### 2012-10-05 ms.tex
PeerJ uses CC-BY not CC-BY-SA see https://peerj.com/FAQ/#license
Minor edits to Fac1000 and Conclusions sections

@@
 journal, so preprints can be posted regardless of where they will eventually be
-submitted for publication.
-
-PeerJ uses the CC-BY-SA 3.0 license, which is similar to the CC-BY license used
-by Figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
-need a license identical to the license that governs the original work.
+submitted for publication. PeerJ uses the same CC-BY license used by Figshare.
 
@@
 response. F1000Research works closely with data providers to integrate raw
-data to the paper. Forinstance, upon submitting a paper, authors are asked to
-upload their data, which are then integrated in \emph{e.g.} FigShare widgets,
+data to the paper. For instance, upon submitting a paper, authors are asked to
+upload their data, which are then integrated in \emph{e.g.} figshare widgets,
 the DOI of which are given in the paper when the data are first mentionned.
-The licensing of the data is similar to the one used by FigShare, meaning that
-the articles are free to access, and can be redistributed readily. By putting
-much effort in integrating data to the paper, F1000Research is working to make
+The licensing of the data is similar to that used by FigShare, meaning that
+the articles are free to access, and can be redistributed readily. By
+integrating data to the paper, F1000Research is working to make
 science more reproducible and open.
@@
 
-Open preprint servers offer a great opportunity for open science, especially if
-the community embraces the idea of discussing preprints. Initiatives like
+Open preprint servers offer a great opportunity for science, especially if
+the community embraces the idea of openly discussing preprints. Initiatives like
 Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a

### 2012-10-05 ms.tex
fix typo

--- 2012-10-05 ms.tex
@@
 peer-review. The rationale for preprint servers is fundamentally simple: to make
-the results of scientific research available to the scientific community as soon
-as possible, instead of waiting until the peer-review process is fully completed.
-Sharing manuscripts using preprint servers has numerous advantages including: 1) rapid
-dissemination of work-in-progress to a wider audience; 2) improved peer review by
-encouraging feedback from the entire research community;
-and 3) a fair and straightforward way to establish precedence.
+the results available to the scientific community as soon as possible rather
+than to wait until the peer-review process is fully completed. The goal of arXiv
+and open preprint servers is not to circumvent the peer-review process; almost all
+manuscripts on arXiv are submitted to peer-review.  Sharing ideas as quickly as
+possible using preprint servers has numerous advantages.  These include rapid
+dissemination of work-in-progress to a wider audience, including readers in
+developing countries where access to subscription journals is often a limiting
+factor in scientific research.  Furthermore, preprints provide the opportunity
+to solicit feedback from a larger pool of reviewers and can be seen as an
+integral aspect of a vigorous peer-review process \cite{hoc12}.  Preprint
+servers therefore increase the number of opportunities for review and revision
+prior to publication, resulting in higher quality submissions and also could
+alleviate reviewer burden.
 
-Preprints began to gain popularity 20 years ago with the advent of arXiv, an open
-preprint server widely used in physics and mathematics \cite{gin11}. Preprints
+Preprints gained popularity 20 years ago with the advent of arXiv, an open
+preprint server widely used in physics and mathematics \cite{nie08,gin11}. Preprints
 are also integral to the culture of other scientific fields.  Paul Krugman noted
@@
 in Economics) initiative, which aims to create an archive of working papers,
-manuscripts, and book chapters.
-
-Despite the success of this approach in other
-fields, most manuscripts in biology are not posted to preprint servers and
-are therefore not seen by more than a handful of other scientists prior to
-publication. In this article, we: 1) highlight the
-advantages of open preprint servers for both scientists and publishers; 2)
-address several misconceptions about preprints that are common among biologists;
-3) discuss the preprint policies of major publishers in biology;
-and 4) review the most popular preprint servers currently available.
+manuscripts, and book chapters.  Despite the success of this approach in other
+fields, most manuscripts in biology are not submitted to a public archive before
+being submitted to peer-review. In this article, we first highlight the
+advantages of open preprint servers for both scientists and publishers. We
+then debunk a few misconceptions, discuss the policies of major publishers in
+biology, and briefly review the most popular open preprint servers currently available.
 
@@
 speed (Figure~\ref{fig:map}). The time between submission and the official
-publication of a manuscript can be measured in months or even years. During
-this time, the research is known only to a select few: colleagues, editors,
+publication of a manuscript can be measured in months, sometime in years. For
+all this time, the research is known only to a select few: colleagues, editors,
 reviewers. Thus, the science cannot be used, discussed, or reviewed by the
-wider scientific community.  If the science being published is a year
-or more behind the cutting edge, then science will progress more slowly. While
-conferences and informal sharing of ideas among research groups may ameliorate
-this issue, this type of communication is inherently limited to a restricted
-subset of scienctists. Posting preprints ensures that science is not
-constrained by small networks of scientists exchanging ideas.  Paul Ginsparg
-created arXiv.org in part for democratic reasons: he wanted everyone from students
-in small universities to Ivy-League professors to have access to the most recent
-scientific \emph{ideas}. Ginsparg's revolutionary idea was simply to use the power
-of the internet for preprints, not just for the end product, so the scientific
-process can be open to all as soon as possible.
+wider scientific community. This stage of manuscript preparation is a problem
+for both scientists and publishers. Manuscripts that are unknown cannot be used
+and thus take more time to be cited. It has been shown that high-energy physics,
+with its high arXiv submission rate, had the highest immediacy among physics and
+mathematics \cite{pra05}. Immediacy measures how quickly articles are cited.
 
-Posting manuscripts as preprints also has the potential to result in higher
-quality science, by allowing for pre-publication feedback
-from a large pool of reviewers. Prepublication reviews by a small network of
-colleagues are common in the biological sciences and are an important part of
-the scientific process. These "friendly" reviews increases the chances of errors
-being caught prior to publication, allow errors to be identified
-prior to spending months in review, and allows authors to improve how they
-communicate the results of their research by modifying their writing in response
-to early feedback. Preprint servers offer a way to extend this network of
-colleagues to the entire scientific
-community, increasing the number of opportunities for review and revision
-prior to publication, and resulting in higher quality submissions and publications.
-As such, preprints can be seen as an
-integral aspect of a vigorous peer-review process \cite{hoc12}.
-
-%It is unclear to me whether we should keep this full paragraph or try to distill
-%it to a sentence or two at the end of the previous paragraph.
-Furthermore, the formal peer-review process as a whole is critically over-loaded. As
-the number of active scientists increases and the pressure to publish
-increases, it has become increasingly difficult for journals to find
-reviewers \cite{hoc09}.  At the same time, rejection rates are high in most journals
-\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the
-process over again at another journal. As a result, initiatives to reduce time from submission to
+Furthermore, the review process as a whole is critically over-loaded, because
+the number of active scientists increases, because the pressure to publish
+increases, and because of an effect dubbed ``the tragedy of the reviewers
+commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
+\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the whole
+process all over again.  Initiatives to reduce time from submission to
 publication have emerged across the scientific community. Rohr et al.
@@
 outsourcing the review process. A widespread use of preprint servers can
-achieve the same goal of reducing the time spent in review. By allowing
-open comments and criticisms prior to submission, the authors will receive valuable
+achieve the same goal of reducing the time spent in review. By putting a
+manuscript for open comments and criticisms, the authors will receive valuable
 feedback and can improve the version which will be submitted. With a rich
 enough community of scientists depositing preprints, and commenting on them,
-the process of an open pre-review can become widespread and will overall
+the process of an open pre- review can become widespread and will overall
 increase the quality of first submissions.
@@
 \label{fig:map} \end{figure}
+% Dom : Do you have a reference for the stats in the legend?
 
-Finally, public preprint servers offer a fair way to establish intellectual
-priority by making the work available when immediately after it is complete.
-Some manuscripts will spend much more time in the review process and/or in
-production after acceptance, than others. This means that
-that publication and acceptance dates do not accurately characterize who
-came up with an idea first. For this reason, mathematicians and physicists
-have embraced arXiv in part to establish priority in a fair way \cite{gin11,cal12}.
+Public preprint servers offer a much fairer way to establish intellectual
+priority by making the work available when done. Some manuscripts will spend
+much more time in the review process than others. Surprisingly, there is a
+perception in biology that public preprints make it easier to steal ideas, as if
+a scientific idea was only complete once published in a peer-reviewed journal
+\cite{gin11}. Ironically, mathematicians and physicists have embraced arXiv in
+part to establish priority in a fair way \cite{gin11,cal12}.
+% Dom: That's a very interesting statement, if not the best one to justify preprints. Could you develop just a bit more the argument?
+
+Prepublication reviews by a small network of colleagues is an important part of
+the scientific process, attested by the fact that nearly all published papers
+acknowledge comments by people not listed as co-authors.  Preprint servers
+simply offer a way to extend this network of colleagues to the entire scientific
+community. It ensures that science is not constrained by small networks of
+scientists exchanging ideas.  Paul Ginsparg created arXiv.org in part for
+democratic reasons: he wanted everyone from students in small universities to
+Ivy-League professors to have access to the most recent scientific \emph{ideas}.
+Ginsparg's revolutionary idea was simply to use the power of the internet for
+preprints, not just for the end product, so the scientific process can be open
+as soon as possible.
+% Dom: I do accept this argument, although I have doubts it makes any difference. Just think about the number of comments posted on PLoS One...
 
@@
 
-In contrast to other disciplines, the field of biology has effectively no preprint
-culture, with the exception of small pockets of primarily highly quantitative
-research (e.g., epidemiology). While, submitting to preprint servers has become
-more common in the past few years, and the quantitative biology section in arXiv
-is experiencing rapid growth in submissions \cite{cal12}, the number of biology
-papers submitted to preprint servers still represents only a small fraction of
-the total research produced in biology.
+Submitting to a preprint server is becoming more common in biology, even though
+it still involves a minority of papers. The quantitative biology section in
+arXiv is experiencing faster growth in submissions than any other field
+\cite{cal12}. Most scientific journals are preprint-friendly: Nature, PLOS, BMC,
+PNAS, Science (mostly) \ref{table:policies}, and all the journals from Elsevier %something is off in the formatting here
+and Springer.  The Ecological Society of America and the Genetics Society of
+America recently changed their policies to allow public preprints.  Few
+scientific publications will not consider a manuscript submitted to a public
+preprint server.  Still, a few journals adopt a ``by default'' hostile attitude
+towards preprints, mostly due to the lack of clear policy of the publishers, or
+perhaps because a preprint culture has not developed in biology and the practice
+is still considered unusual. As an example, Wiley-Blackwell, which publishes
+some leading journals, has no official policy on the subject
+\ref{table:policies}.
 
-There are a number of reasons that biologists have not traditionally had a
-culture of sharing preprints, many of which are based on common misconceptions
-regarding the costs and benefits of sharing preprints. For example, in contrast
-to other fields there is a perception in biology that public preprints
-make it easier to steal ideas. However, there is no evidence of this happening
-in the numerous other fields that have adopted preprint servers, and since preprint
-servers create a clear record of who had the idea first, and when, this
-appears to be a largely unfounded concern. In other fields preprints serve the
-opposite role, they allow straightforward establishment of precendence, letting
-researchs lay claim to an idea thus prevening it from being "stolen".
-
-Another major concern is that if a researcher posts a public preprint that they
-will not be allowed to submit their paper to their journal of choice. This is 
-based on a certain interpretation
+Part of the hostility to preprints servers comes from a certain interpretation
 of the Ingelfinger rule: scientists should not publish the same manuscript twice
-\cite{alt96}. However, preprints are not peer-reviewed papers and posting to a
-public server does not constitute publication in a peer-reviewed journal.
-A preprint is simply a document that allows ideas to spread and be discussed, 
-but it is not yet formally validated by the peer-review system. This is why the
-majority of publishers do not see arXiv and similar services as a violation of the
-Ingelfinger rule. Almost all of the major publishers in biology are preprint-friendly,
-including: Nature Publishing Group, PLOS, BMC, PNAS, Science (mostly) \ref{table:policies},
-and all the journals from Elsevier %something is off in the formatting here
-and Springer.  The Ecological Society of America and the Genetics Society of
-America also recently changed their policies to allow public preprints.  Few
-scientific publications will not consider a manuscript submitted to a public
-preprint server. In fact, \emph{Nature} responded to the rumour that they refused
+\cite{alt96}. However, papers submitted to arXiv or other preprints servers are
+only published in one peer-reviewed journal. A preprint is just a preprint, it
+is a document that allows ideas to spread and be discussed, but it is not yet
+formally validated by the peer-review system, which is why the majority of
+publishers does not see arXiv and similar services as a violation of the
+Ingelfinger rule. \emph{Nature} responded to the rumour that they refused
 manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
@@
 value for authors and the community at large in our peer review, selection and
-editing'' \cite{nat05}. Still, a few journals adopt a ``by default'' hostile attitude
-towards preprints, mostly due to the lack of clear policy of the publishers, or
-perhaps because a preprint culture has not developed in biology and the practice
-is still considered unusual. As an example, Wiley-Blackwell, which publishes
-some of the leading journals in biology, has no official policy on the matter.
-
-\ref{table:policies}.
+editing'' \cite{nat05}.
 
@@
 rights to distribute submitted articles in perpetuity. Thus, submitting to arXiv
-does not prevent the authors from transferring their rights to a
-publisher.
+does not in itself prevent the authors from transferring their rights to a
+publisher, which is why most publishers tolerate arXiv, even though they ask the
+authors to transfer their right to them upon acceptance of the article.
 
 Most papers posted to arXiv are eventually printed in journals but there are
-notable exceptions including Perelman's landmark paper leading to the proof of
+notable exceptions, such as Perelman's landmark paper leading to the proof of
 the Poincar\'{e} conjecture \cite{2002math.....11159P}.  However, arXiv has
@@
 
-\subsection{Figshare}
+\subsection{figshare}
 
-Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
-that allows scientists to submit any research output: manuscripts, figures,
+figshare (\href{http://figshare.com}{http://figshare.com}) is an open server
+that allows scientists to submit any research output: manuscript, figures,
 datasets, videos, theses, presentations, and so on. There are no rules to limit
@@
 any journal article, thus offering a permanent and stable link to the content.
-A flexible tag system is used to classify each item. All content
-is licensed under the Creative Commons (CC-BY) license, except
+A flexible tag system is used to classify each item. All content can be
+commented and is licensed under the Creative Commons (CC-BY) license, except
 datasets which are published under CC0. The CC-BY license grants rights to
@@
 provides an archive for early results (e.g.: figures, lab presentations).
-figshare also supports commenting on preprints.
 
@@
 F1000Research is not a public preprint server like the previous three servers.
-Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
-without having it reviewed, papers submitted to F1000Research will eventually
-be reviewed. Thus, F1000Research offers a hybrid model with publicly available
+Whereas arXiv, figshare, and PeerJ offer an option to submit a manuscript
+without having it reviewed, papers submitted to F1000Research will eventually be
+reviewed. Thus, F1000Research offers a hybrid model with publicly available
 manuscripts at time of submission and standard peer-reviews. Manuscripts are
 considered ``accepted'' and will only be indexed after two positive referee
-response. F1000Research works closely with data providers to integrate raw
-data to the paper. Forinstance, upon submitting a paper, authors are asked to
-upload their data, which are then integrated in \emph{e.g.} FigShare widgets,
-the DOI of which are given in the paper when the data are first mentionned.
-The licensing of the data is similar to the one used by FigShare, meaning that
-the articles are free to access, and can be redistributed readily. By putting
-much effort in integrating data to the paper, F1000Research is working to make
+response. F1000Research works closely with data providers to integrate raw data
+to the paper. For instance, upon submitting a paper, authors are asked to upload
+their data, which are then integrated in \emph{e.g.} figshare widgets, the DOI
+of which are given in the paper when the data are first mentionned.  The
+licensing of the data is similar to the one used by figshare, meaning that the
+articles are free to access, and can be redistributed readily. By putting much
+effort in integrating data to the paper, F1000Research is working to make
 science more reproducible and open.
 
-\subsection{Github}
+\subsection{GitHub}
 
-This manuscript was developed entirely as an open project on github. github is
-one of several hosting services for collaborative development using the git
-version control system (VCS).  git is a decentralized revision control system
+This manuscript was developed entirely as an open project on GitHub. GitHub is
+one of several hosting services for collaborative development using the Git
+version control system (VCS).  Git is a decentralized revision control system
 created by Linus Torvalds and is used primarily to develop software, including
-the Linux kernel.
-Git provides powerful features that allow numerous contributers to work asynchronously on the same project, often in parallel branches, all of which can be effortlessly merged and version controlled.
-Although created primarily for software development, git is ideal for academic research since it provides a way to version control and collaborate on every step of the manuscript development process, from data manipulation and analysis to writing and revision.
-For example, during the development of this manuscript, each author
-would clone the project (\emph{i.e.} make a personal copy), modify it, and then merge their changes into a master branch.This takes the preprint process to an entirely new level, where the entire writing process is open from the beginning.
-% I would avoid using the term forking since it is not a central piece of the section.
-It is one specific way of collaborating on a github repo when everyone does not have rights to it.
-People could just as easily work on a single branch, all with write access, either directly to the master branch or to individual branches that could be merged.
-So in other words, we should keep the language general so people don't get bogged down with trying to understand what a fork is.
-% also I changed one author clones, then submits pull request langauge a bit since the main point of using git is that we can all work simultaneously unlike svn.
-% I took out "These techniques are widely used in open source software development." because git can also be used for closed source software, offering the same advantages, where the repositories are private.
-Paid git accounts allow for private repos.
+the Linux kernel. Git provides powerful features that allow numerous
+contributers to work asynchronously on the same project, often in parallel
+branches, all of which can be effortlessly merged and version controlled.  While
+Git is created primarily for software development, where the use of version
+control systems is standard \cite{aru12}, it is ideal for academic research
+since it provides a way to collaborate on every step of the manuscript
+development process, from data manipulation and analysis to writing and
+revision. For example, during the development of this manuscript, each author
+would clone the project (\emph{i.e.} make a personal copy), modify it, and then
+merge their changes into a master branch. This takes the preprint process to an
+entirely new level, where the entire writing process is open from the beginning.
 
 \section{Conclusion}
+
+% Dominique:
+% I added the following three paragraphs to the conclusion, offering also a
+% discussion on the on going explosion of different publication models. Take
+% what you want and remove what you don't need.  I also had the feeling we might
+% want to include a single paragraph, very short, calling that evaluations
+% (academia, grant agencies etc...) looking at publication records or report of
+% scientific activities start to view preprints as a significant and sound
+% scientific contribution. One of the most important benefit is again the speed
+% of the publication process. Most grants are for three years or less. It makes
+% it hard to have a published paper within the limits of the grant. Preprints
+% could however speed the process and show that contributions were made during
+% the time of the grant.
+
+The ongoing discussions on the publication process, peer-reviewing and
+alternative publication models are all symptoms of the current uneasiness of
+scientists with the ever growing obsession with bibliographic metrics such as
+the impact factor \cite{Fisher2012}. There is pressure on researchers, wether
+they are junior looking for an academic position or senior trying to secure
+funding for their team, to orient their publication strategy in order to
+maximize their number of publications and total citations. A well-known
+consequence is to submit manuscripts first to the most prestigious journals, and
+then resubmit to lower level journals as they are rejected. The numerous
+negative impacts of such behavior have been discussed in depth \cite{hoc09} and
+include a long delay between the time a manuscript is finished to its
+publication.  They all contribute somehow in a general slowing down of
+scientific progress.  Research activities and the publication process are
+drifting away from their fundamental object, namely the diffusion of novel
+scientific discoveries.
+
+Developing a preprint culture in biology is not a final solution to the impact
+factor inflation, it might however reduce significantly its negative
+consequences. Preprints speed up publication, openly, with no judgement on
+pertinence and originality. Paradoxically, because peer-reviewing is conducted
+following this step in the process of a scientific communication, it might bring
+it closer to its fundamental objective. The role of peer-reviewing is to judge
+the scientific quality of a study, the match between its hypotheses, methods,
+results and conclusions. The peer review process is the first barrier against
+fraudulent or bad quality science, susceptible to impede scientific progress. It
+is however now dominated by subjective evaluations, where trendy contributions
+are promoted to increase the immediacy impact of the journal. Most journals have
+in their instructions for reviewers a section devoted to the evaluation of
+suitability for the journal, a task usually incumbent to editors. Preprints are
+by definition not evaluated, neither for their quality nor their pertinence.
+Technically, the difference between a preprint and a traditional publication
+should be that the latter as the approval stamp by pairs on its quality. The
+relevance of a study, its contribution to science, should only be judged
+post-publication by many more readers than the typical two-four anonymous
+reviewers. With a such a shift in the diffusion strategy, the role of
+traditional journals and their editors would be to showcase scientific
+discoveries for specialized readership. Such a process should improve even
+further their diffusion, not impede it.
+
+The current opening of the publication process we are currently witnessing with
+the arrival of new preprint systems and innovative publication models such as
+F1000, PLOS One, Nature Scientific Reports, might significantly bypass the
+inflation of bibliographic metrics. They not only promote scientific communications
+by changing the focus of peer-reviewing, they also favor the publication of
+results that might otherwise be rejected because of low interest, negative
+results, descriptive and quantitative studies and datasets. One of drawback of
+making publication easier is obviously the proliferation of studies of uneven
+quality. A tradeoff between the intensity of the peer-review filtering and the
+benefits to science has been hypothesized \cite{Aarssen2012}. With increasingly
+stringent peer reviewing, the quality of published papers and easiness of
+finding discoveries might increase, at the cost of censorship, increasing load
+on authors and reviewers and time for publication. Preprints are simply
+bypassing this model, for what we believe is the progress of science: they speed
+up the dissemination of scientific discoveries, impede censorship and put on
+reader's shoulders the responsibility to judge originality and pertinence.
 

### 2012-10-05 ms.tex
add Titus story

@@
 all this time, the research is known only to a select few: colleagues, editors,
-reviewers. Thus, the science cannot be used, discussed, or reviewed by the
-wider scientific community. This stage of manuscript preparation is a problem
-for both scientists and publishers. Manuscripts that are unknown cannot be used
-and thus take more time to be cited. It has been shown that high-energy physics,
-with its high arXiv submission rate, had the highest immediacy among physics and
-mathematics \cite{pra05}. Immediacy measures how quickly articles are cited.
+reviewers. Thus, the science cannot be used, discussed, or reviewed by the wider
+scientific community. In a recent blog post, C Titus Brown noted how posting a
+paper on preprint lead to a quick citation (arXiv papers can be cited) and his
+research was integrated by another researcher \cite{bro12}. The current system
+of hiding manuscripts before acceptance pose problems for both scientists and
+publishers. Manuscripts that are unknown cannot be used and thus take more time
+to be cited. It has been shown that high-energy physics, with its high arXiv
+submission rate, had the highest immediacy among physics and mathematics
+\cite{pra05}. Immediacy measures how quickly articles are cited.
 

### 2012-10-05 ms.tex
fix titus part

@@
 reviewers. Thus, the science cannot be used, discussed, or reviewed by the wider
-scientific community. In a recent blog post, C Titus Brown noted how posting a
-paper on preprint lead to a quick citation (arXiv papers can be cited) and his
-research was integrated by another researcher \cite{bro12}. The current system
-of hiding manuscripts before acceptance pose problems for both scientists and
+scientific community. In a recent blog post, C. Titus Brown noted how posting a
+paper on arXiv quickly led to a citation (arXiv papers can be cited) and his
+research was used by another researcher \cite{bro12}. The current system of
+hiding manuscripts before acceptance pose problems for both scientists and
 publishers. Manuscripts that are unknown cannot be used and thus take more time

### 2012-10-05 ms.tex
merge

@@
 peer-review. The rationale for preprint servers is fundamentally simple: to make
-the results available to the scientific community as soon as possible rather
-than to wait until the peer-review process is fully completed. The goal of arXiv
-and open preprint servers is not to circumvent the peer-review process; almost all
-manuscripts on arXiv are submitted to peer-review.  Sharing ideas as quickly as
-possible using preprint servers has numerous advantages.  These include rapid
-dissemination of work-in-progress to a wider audience, including readers in
-developing countries where access to subscription journals is often a limiting
-factor in scientific research.  Furthermore, preprints provide the opportunity
-to solicit feedback from a larger pool of reviewers and can be seen as an
-integral aspect of a vigorous peer-review process \cite{hoc12}.  Preprint
-servers therefore increase the number of opportunities for review and revision
-prior to publication, resulting in higher quality submissions and also could
-alleviate reviewer burden.
+the results of scientific research available to the scientific community as soon
+as possible, instead of waiting until the peer-review process is fully completed.
+Sharing manuscripts using preprint servers has numerous advantages including: 1) rapid
+dissemination of work-in-progress to a wider audience; 2) improved peer review by
+encouraging feedback from the entire research community;
+and 3) a fair and straightforward way to establish precedence.
 
-Preprints gained popularity 20 years ago with the advent of arXiv, an open
-preprint server widely used in physics and mathematics \cite{nie08,gin11}. Preprints
+Preprints began to gain popularity 20 years ago with the advent of arXiv, an open
+preprint server widely used in physics and mathematics \cite{gin11}. Preprints
 are also integral to the culture of other scientific fields.  Paul Krugman noted
@@
 in Economics) initiative, which aims to create an archive of working papers,
-manuscripts, and book chapters.  Despite the success of this approach in other
-fields, most manuscripts in biology are not submitted to a public archive before
-being submitted to peer-review. In this article, we first highlight the
-advantages of open preprint servers for both scientists and publishers. We
-then debunk a few misconceptions, discuss the policies of major publishers in
-biology, and briefly review the most popular open preprint servers currently available.
+manuscripts, and book chapters.
+
+Despite the success of this approach in other fields, most manuscripts in
+biology are not posted to preprint servers and are therefore not seen by more
+than a handful of other scientists prior to publication. In this article, we: 1)
+highlight the advantages of open preprint servers for both scientists and
+publishers; 2) address several misconceptions about preprints that are common
+among biologists; 3) discuss the preprint policies of major publishers in
+biology; and 4) review the most popular preprint servers currently available.
 
@@
 
-Furthermore, the review process as a whole is critically over-loaded, because
-the number of active scientists increases, because the pressure to publish
-increases, and because of an effect dubbed ``the tragedy of the reviewers
-commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
-\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the whole
-process all over again.  Initiatives to reduce time from submission to
+Posting manuscripts as preprints also has the potential to result in higher
+quality science, by allowing for pre-publication feedback
+from a large pool of reviewers. Prepublication reviews by a small network of
+colleagues are common in the biological sciences and are an important part of
+the scientific process. These "friendly" reviews increases the chances of errors
+being caught prior to publication, allow errors to be identified
+prior to spending months in review, and allows authors to improve how they
+communicate the results of their research by modifying their writing in response
+to early feedback. Preprint servers offer a way to extend this network of
+colleagues to the entire scientific
+community, increasing the number of opportunities for review and revision
+prior to publication, and resulting in higher quality submissions and publications.
+As such, preprints can be seen as an
+integral aspect of a vigorous peer-review process \cite{hoc12}.
+
+%It is unclear to me whether we should keep this full paragraph or try to distill
+%it to a sentence or two at the end of the previous paragraph.
+Furthermore, the formal peer-review process as a whole is critically over-loaded. As
+the number of active scientists increases and the pressure to publish
+increases, it has become increasingly difficult for journals to find
+reviewers \cite{hoc09}.  At the same time, rejection rates are high in most journals
+\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the
+process over again at another journal. As a result, initiatives to reduce time from submission to
 publication have emerged across the scientific community. Rohr et al.
@@
 is still considered unusual. As an example, Wiley-Blackwell, which publishes
-some leading journals, has no official policy on the subject
+some of the leading journals in biology, has no official policy on the matter.
+
 \ref{table:policies}.
-
-Part of the hostility to preprints servers comes from a certain interpretation
-of the Ingelfinger rule: scientists should not publish the same manuscript twice
-\cite{alt96}. However, papers submitted to arXiv or other preprints servers are
-only published in one peer-reviewed journal. A preprint is just a preprint, it
-is a document that allows ideas to spread and be discussed, but it is not yet
-formally validated by the peer-review system, which is why the majority of
-publishers does not see arXiv and similar services as a violation of the
-Ingelfinger rule. \emph{Nature} responded to the rumour that they refused
-manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
-stand in the way of communication between researchers. We seek rather to add
-value for authors and the community at large in our peer review, selection and
-editing'' \cite{nat05}.
 
@@
 considered ``accepted'' and will only be indexed after two positive referee
-response. F1000Research works closely with data providers to integrate raw data
-to the paper. For instance, upon submitting a paper, authors are asked to upload
-their data, which are then integrated in \emph{e.g.} figshare widgets, the DOI
-of which are given in the paper when the data are first mentionned.  The
-licensing of the data is similar to the one used by figshare, meaning that the
-articles are free to access, and can be redistributed readily. By putting much
-effort in integrating data to the paper, F1000Research is working to make
+response. F1000Research works closely with data providers to integrate raw
+data to the paper. For instance, upon submitting a paper, authors are asked to
+upload their data, which are then integrated in \emph{e.g.} figshare widgets,
+the DOI of which are given in the paper when the data are first mentionned.
+The licensing of the data is similar to that used by FigShare, meaning that
+the articles are free to access, and can be redistributed readily. By
+integrating data to the paper, F1000Research is working to make
 science more reproducible and open.

### 2012-10-05 ms.tex
TP funding

@@
 
+Open preprint servers offer a great opportunity for open science, especially if
+the community embraces the idea of discussing preprints. Initiatives like
+Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
+new blog discussing arXiv papers in population genetics, will help make arXiv
+attractive for scientists looking to promote their work. These initiatives are
+important to fully exploit the potential of open preprints servers. Posting
+preprints online increases the community of available informal peer reviewers,
+and uses the internet for its original community-building purposes.
+
 Preprints began to gain popularity 20 years ago with the advent of arXiv, an open
@@
 Posting manuscripts as preprints also has the potential to result in higher
-quality science, by allowing for pre-publication feedback
-from a large pool of reviewers. Prepublication reviews by a small network of
-colleagues are common in the biological sciences and are an important part of
-the scientific process. These "friendly" reviews increases the chances of errors
-being caught prior to publication, allow errors to be identified
-prior to spending months in review, and allows authors to improve how they
-communicate the results of their research by modifying their writing in response
-to early feedback. Preprint servers offer a way to extend this network of
-colleagues to the entire scientific
-community, increasing the number of opportunities for review and revision
-prior to publication, and resulting in higher quality submissions and publications.
-As such, preprints can be seen as an
-integral aspect of a vigorous peer-review process \cite{hoc12}.
+quality science, by allowing for pre-publication feedback from a large pool of
+reviewers. Prepublication reviews by a small network of colleagues are common in
+the biological sciences and are an important part of the scientific process.
+These "friendly" reviews increases the chances of errors being caught prior to
+publication, allow errors to be identified prior to spending months in review,
+and allows authors to improve how they communicate the results of their research
+by modifying their writing in response to early feedback. Preprint servers offer
+a way to extend this network of colleagues to the entire scientific community,
+increasing the number of opportunities for review and revision prior to
+publication, and resulting in higher quality submissions and publications.  As
+such, preprints can be seen as an integral aspect of a vigorous peer-review
+process \cite{hoc12}.
 
-%It is unclear to me whether we should keep this full paragraph or try to distill
-%it to a sentence or two at the end of the previous paragraph.
-Furthermore, the formal peer-review process as a whole is critically over-loaded. As
-the number of active scientists increases and the pressure to publish
-increases, it has become increasingly difficult for journals to find
-reviewers \cite{hoc09}.  At the same time, rejection rates are high in most journals
-\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the
-process over again at another journal. As a result, initiatives to reduce time from submission to
-publication have emerged across the scientific community. Rohr et al.
-\cite{roh09} called for the recycling and reuse of peer-reviews:
-by attaching previous reviews and detailed replies to a new submission, both
-the editor and the referees can gauge the work done on the manuscript, and
-perhaps evaluate it with less prejudice. In a similar way, the \emph{Peerage
-of Science} initiative allows authors to seek anonymous pre-review by their
-peers. Some journals now accept to publish papers which received good
+Furthermore, the formal peer-review process as a whole is critically
+over-loaded. As the number of active scientists increases and the pressure to
+publish increases, it has become increasingly difficult for journals to find
+reviewers \cite{hoc09}.  At the same time, rejection rates are high in most
+journals \cite{aar08,roh09}, and when not invited to submit a revision, authors
+must start the process over again at another journal. As a result, initiatives
+to reduce time from submission to publication have emerged across the scientific
+community. Rohr et al.  \cite{roh09} called for the recycling and reuse of
+peer-reviews: by attaching previous reviews and detailed replies to a new
+submission, both the editor and the referees can gauge the work done on the
+manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
+\emph{Peerage of Science} initiative allows authors to seek anonymous pre-review
+by their peers. Some journals now accept to publish papers which received good
 evaluations, with \emph{Animal Biology} having recently accepted first a paper
 reviewed entirely with the \emph{Peerage of Science} \cite{abb12}, effectively
-outsourcing the review process. A widespread use of preprint servers can
-achieve the same goal of reducing the time spent in review. By allowing
-open comments and criticisms prior to submission, the authors will receive valuable
-feedback and can improve the version which will be submitted. With a rich
-enough community of scientists depositing preprints, and commenting on them,
-the process of an open pre-review can become widespread and will overall
-increase the quality of first submissions.
+outsourcing the review process. A widespread use of preprint servers can achieve
+the same goal of reducing the time spent in review. By allowing open comments
+and criticisms prior to submission, the authors will receive valuable feedback
+and can improve the version which will be submitted. With a rich enough
+community of scientists depositing preprints, and commenting on them, the
+process of an open pre-review can become widespread and will overall increase
+the quality of first submissions.
 
@@
 will not be allowed to submit their paper to their journal of choice. This is
-based on a certain interpretation
-of the Ingelfinger rule: scientists should not publish the same manuscript twice
-\cite{alt96}. However, preprints are not peer-reviewed papers and posting to a
-public server does not constitute publication in a peer-reviewed journal.
-A preprint is simply a document that allows ideas to spread and be discussed, 
-but it is not yet formally validated by the peer-review system. This is why the
-majority of publishers do not see arXiv and similar services as a violation of the
-Ingelfinger rule. Almost all of the major publishers in biology are preprint-friendly,
-including: Nature Publishing Group, PLOS, BMC, PNAS, Science (mostly) \ref{table:policies},
-and all the journals from Elsevier %something is off in the formatting here
-and Springer.  The Ecological Society of America and the Genetics Society of
-America also recently changed their policies to allow public preprints.  Few
-scientific publications will not consider a manuscript submitted to a public
-preprint server. In fact, \emph{Nature} responded to the rumour that they refused
-manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
-stand in the way of communication between researchers. We seek rather to add
-value for authors and the community at large in our peer review, selection and
-editing'' \cite{nat05}. Still, a few journals adopt a ``by default'' hostile attitude
-towards preprints, mostly due to the lack of clear policy of the publishers, or
-perhaps because a preprint culture has not developed in biology and the practice
-is still considered unusual. As an example, Wiley-Blackwell, which publishes
-some of the leading journals in biology, has no official policy on the matter.
-
-\ref{table:policies}.
+based on a certain interpretation of the Ingelfinger rule: scientists should not
+publish the same manuscript twice \cite{alt96}. However, preprints are not
+peer-reviewed papers and posting to a public server does not constitute
+publication in a peer-reviewed journal.  A preprint is simply a document that
+allows ideas to spread and be discussed, but it is not yet formally validated by
+the peer-review system. This is why the majority of publishers do not see arXiv
+and similar services as a violation of the Ingelfinger rule. Almost all of the
+major publishers in biology are preprint-friendly, including: Nature Publishing
+Group, PLOS, BMC, PNAS, Science (mostly) \ref{table:policies}, and all the
+journals from Elsevier and Springer.  The Ecological Society of America and the
+Genetics Society of America also recently changed their policies to allow public
+preprints.  Few scientific publications will not consider a manuscript submitted
+to a public preprint server. In fact, \emph{Nature} responded to the rumour that
+they refused manuscripts submitted to arXiv by saying that ``\emph{Nature} never
+wishes to stand in the way of communication between researchers. We seek rather
+to add value for authors and the community at large in our peer review,
+selection and editing'' \cite{nat05}. Still, a few journals adopt a ``by
+default'' hostile attitude towards preprints, mostly due to the lack of clear
+policy of the publishers, or perhaps because a preprint culture has not
+developed in biology and the practice is still considered unusual. As an
+example, Wiley-Blackwell, which publishes some of the leading journals in
+biology, has no official policy on the matter.
 
@@
 
-% Dominique:
-% I added the following three paragraphs to the conclusion, offering also a
-% discussion on the on going explosion of different publication models. Take
-% what you want and remove what you don't need.  I also had the feeling we might
-% want to include a single paragraph, very short, calling that evaluations
-% (academia, grant agencies etc...) looking at publication records or report of
-% scientific activities start to view preprints as a significant and sound
-% scientific contribution. One of the most important benefit is again the speed
-% of the publication process. Most grants are for three years or less. It makes
-% it hard to have a published paper within the limits of the grant. Preprints
-% could however speed the process and show that contributions were made during
-% the time of the grant.
-
 The ongoing discussions on the publication process, peer-reviewing and
@@
 
-Open preprint servers offer a great opportunity for open science, especially if
-the community embraces the idea of discussing preprints. Initiatives like
-Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
-new blog discussing arXiv papers in population genetics, will help make arXiv
-attractive for scientists looking to promote their work. These initiatives are
-important to fully exploit the potential of open preprints servers. Posting
-preprints online increases the community of available informal peer reviewers,
-and uses the internet for its original community-building purposes.
-
-% Aren't we bridging more than cultural and geographic? I mean, we are
-% essentially cross pollinating ideas. e.g. It took a lot time for MCMC to
-% become popular in ecology even though it was widely used in other disciplines
-% a decade or two earlier.
-Preprint servers also facilitate communication between disciplines, bridging
-cultural as well as geographic divides. Examples include a recent series of
-papers on the theory of natural selection that was posted to arXiv
-simultaneously with its publication in the \emph{Journal of Evolutionary
-Biology} \cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}. Other
-submissions in this category include evolutionary and ecological theory by
-authors trained in physics and computer science.  Since authors in these fields
-regularly check arXiv, submitting preprints may be the most effective way
-biologists can help others avoid ``repeated work'' \cite{de2011contribution} and
-form a synthetic community of evolutionary theorists from disparate backgrounds.
-The advantages are clear and the costs are low.
-
 \section{Funding}
@@
 from the National Science Foundation (DEB-0953694). JJA is supported by NSF
-DEB-0614166 and NSF DEB-0919018. KR is supported by NSF DEB-1021553. DG is
-funded by a Discovery Grand from the National Sciences and Engineering Council
-of Canada and by the Canada Research Chair program.
+DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
+scholarship and 25 cents found by a coffee machine.  KR is supported by NSF
+DEB-1021553. DG is funded by a Discovery Grand from the National Sciences and
+Engineering Council of Canada and by the Canada Research Chair program.
 

### 2012-10-06 ms.tex

@@
 
-Submission to arXiv is fully automated.  Authors can submit \TeX{}/\LaTeX{}
-documents that are compiled on the server or directly submit in PDF/PS format
-(for example, as exported by a word processor).  A moderation system was put in
-place in 2004: papers must be categorized by an endorser. At least one author of
-a paper must be an endorser that has previously submitted a paper or has
-received permission to submit to a particular category.  Many authors in
-mathematics and physics submit papers as soon as they are ready for review by
-colleagues, although another popular option is submitting simultaneously to a
-journal and arXiv.
-
-Authors must either have their arXiv submission available under an open license
-or grant arXiv a non-exclusive and irrevocable license to distribute the work.
-In either case, arXiv does not require copyright transfer and only requires the
-rights to distribute submitted articles in perpetuity. Thus, submitting to arXiv
-does not prevent the authors from transferring their rights to a
-publisher.
-
-Most papers posted to arXiv are eventually printed in journals but there are
-notable exceptions including Perelman's landmark paper leading to the proof of
-the Poincar\'{e} conjecture \cite{2002math.....11159P}.  However, arXiv has
-never sought to replace scientific journals and explicitly states that it serves
-a different function as ``an openly accessible, moderated repository for
-scholarly articles in specific scientific disciplines.'' arXiv is now
+One aspect of arXiv that differs from other options is that it has a moderation
+system, which requires that papers must be categorized by an endorser.
+At least one author of a paper must be an endorser that has previously submitted
+a paper or has received permission to submit to a particular category. arXiv is now
 administered by the Cornell University Libraries, with funding coming from
 voluntary pledges by academic institutions along with matching funds from the
-Simons Foundation \cite{arxiv_future}.  One-hundred twenty six of the top
-two-hundred institutions in terms of downloads have provided the operating
-budget for arXiv over the next five years.  This plan reduces the financial
-burden on Cornell University and transfers governance to a collaborative
-community in accordance with arXiv's key principles.  arXiv takes numerous
-measures to ensure that the repository will remain permanently available and
-submissions will be readable.
+Simons Foundation \cite{arxiv_future}. This approach to financing is one of
+the numerous measures that arXiv takes to ensure that the repository will remain
+permanently available and submissions will be readable.
 
@@
 any journal article, thus offering a permanent and stable link to the content.
-A flexible tag system is used to classify each item. All content can be
-commented and is licensed under the Creative Commons (CC-BY) license, except
-datasets which are published under CC0. The CC-BY license grants rights to
-\emph{copy, distribute, display and perform the work and make derivative works
-based on it only if they give the author or licensor the credits in the manner
-specified by these.}  CC0 is the most permissive license and effectively puts
-the work in public domain (no rights reserved) or, if it is not possible in the
-given jurisdiction, provides a simple permissive license.
+A flexible tag system is used to classify each item. Comments can be made on all
+content allowing for centralized discussion related to the material.
 
-One of the biggest advantage of figshare over arXiv is that is it not limited to
-quantitative sciences. arXiv.org has sections on quantitative biology but might
+One of the advantages of figshare over arXiv for biologists is that is it not limited
+to quantitative sciences. arXiv.org has sections on quantitative biology but might
 not be appropriate for non-quantitative work. With its flexible approach to
-preprints, figshare offers an important alternative to arXiv for empirical
-biologists. Furthermore, by allowing all types of content, figshare arguably
+preprints, figshare offers an alternative to arXiv for empirical
+biologists. Furthermore, by allowing all types of content, figshare also
 provides an archive for early results (e.g.: figures, lab presentations).
-figshare also supports commenting on preprints.
 
@@
 
-PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new publishing system
-that combines both a preprint server, and a peer reviewed journal.  It is
-focused on the biological and medical sciences, which may help overcome the
-perception that preprints do not have a home in biology.  PeerJ allows
-commenting on posted preprints, improving the potential for pre-publication
+PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new Open Access
+publisher that combines both a preprint server, and a peer reviewed journal.
+It is focused on the biological and medical sciences, which may help overcome the
+perception that preprints do not have a place in biology. Like figshare this is
+an advantage relative to arXiv for biologists doing non-quantitative work.
+Also like figshare PeerJ allows commenting on posted preprints, improving the
+potential for pre-publication
 dialog. In addition, preprints can be made private if the authors choose, and
@@
 In contrast to other preprint servers users cannot post unlimited public
-preprints for free. One preprint per year can be posted for free and a onetime
-(i.e. lifetime) fee of 99 dollars allows the submitting author to post unlimited public
-preprints. It is also worth noting that the preprint server is not tied to the
-journal, so preprints can be posted regardless of where they will eventually be
-submitted for publication.
-
-PeerJ uses the CC-BY-SA 3.0 license, which is similar to the CC-BY license used
-by figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
-need a license identical to the license that governs the original work.
+preprints for free. One preprint per year can be posted for free, with a onetime
+(i.e. lifetime) fee of 99 dollars required to allow an author to post unlimited public
+preprints. The preprint server is not tied to the journal, so preprints can be posted
+regardless of where they will eventually be submitted for publication.
 
@@
 reviewed. Thus, F1000Research offers a hybrid model with publicly available
-manuscripts at time of submission and standard peer-reviews. Manuscripts are
+manuscripts at time of submission and standard peer-reviews that occur as part
+of the submission process. Manuscripts are
 considered ``accepted'' and will only be indexed after two positive referee
-response. F1000Research works closely with data providers to integrate raw
+responses. F1000Research works closely with data providers to integrate raw
 data to the paper. For instance, upon submitting a paper, authors are asked to
@@
 the DOI of which are given in the paper when the data are first mentionned.
-The licensing of the data is similar to that used by FigShare, meaning that
-the articles are free to access, and can be redistributed readily. By
-integrating data to the paper, F1000Research is working to make
+By integrating data to the paper, F1000Research is working to make
 science more reproducible and open.

### 2012-10-07 ms.tex
fixed several small typos

--- 2012-10-05 ms.tex
@@
 peer-review. The rationale for preprint servers is fundamentally simple: to make
-the results of scientific research available to the scientific community as soon
-as possible, instead of waiting until the peer-review process is fully completed.
-Sharing manuscripts using preprint servers has numerous advantages including: 1) rapid
-dissemination of work-in-progress to a wider audience; 2) improved peer review by
-encouraging feedback from the entire research community;
-and 3) a fair and straightforward way to establish precedence.
+the results available to the scientific community as soon as possible rather
+than to wait until the peer-review process is fully completed. The goal of arXiv
+and open preprint servers is not to circumvent the peer-review process; almost all
+manuscripts on arXiv are submitted to peer-review.  Sharing ideas as quickly as
+possible using preprint servers has numerous advantages.  These include rapid
+dissemination of work-in-progress to a wider audience, including readers in
+developing countries where access to subscription journals is often a limiting
+factor in scientific research.  Furthermore, preprints provide the opportunity
+to solicit feedback from a larger pool of reviewers and can be seen as an
+integral aspect of a vigorous peer-review process \cite{hoc12}.  Preprint
+servers therefore increase the number of opportunities for review and revision
+prior to publication, resulting in higher quality submissions and also could
+alleviate reviewer burden.
 
-Preprints began to gain popularity 20 years ago with the advent of arXiv, an open
+Preprints gained popularity 20 years ago with the advent of arXiv, an open
 preprint server widely used in physics and mathematics \cite{gin11}. Preprints
@@
 in Economics) initiative, which aims to create an archive of working papers,
-manuscripts, and book chapters.
-
-Despite the success of this approach in other fields, most manuscripts in
-biology are not posted to preprint servers and are therefore not seen by more
-than a handful of other scientists prior to publication. In this article, we: 1)
-highlight the advantages of open preprint servers for both scientists and
-publishers; 2) address several misconceptions about preprints that are common
-among biologists; 3) discuss the preprint policies of major publishers in
-biology; and 4) review the most popular preprint servers currently available.
+manuscripts, and book chapters.  Despite the success of this approach in other
+fields, most manuscripts in biology are not submitted to a public archive before
+being submitted to peer-review.  In this article, we first highlight the
+advantages of open preprint servers for both scientists and publishers. We
+then debunk a few misconceptions, discuss the policies of major publishers in
+biology, and briefly review the most popular open preprint servers currently available.
 
@@
 all this time, the research is known only to a select few: colleagues, editors,
-reviewers. Thus, the science cannot be used, discussed, or reviewed by the wider
-scientific community. In a recent blog post, C. Titus Brown noted how posting a
-paper on arXiv quickly led to a citation (arXiv papers can be cited) and his
-research was used by another researcher \cite{bro12}. The current system of
-hiding manuscripts before acceptance pose problems for both scientists and
-publishers. Manuscripts that are unknown cannot be used and thus take more time
-to be cited. It has been shown that high-energy physics, with its high arXiv
-submission rate, had the highest immediacy among physics and mathematics
-\cite{pra05}. Immediacy measures how quickly articles are cited.
+reviewers.  Thus, the science cannot be used, discussed, or reviewed by the
+wider scientific community.  This stage of manuscript preparation is a problem
+for both scientists and publishers.  Manuscripts that are unknown cannot be used
+and thus take more time to be cited. It has been shown that high-energy physics,
+with its high arXiv submission rate, had the highest immediacy among physics and
+mathematics \cite{pra05}. Immediacy measures how quickly articles are cited.
 
-Posting manuscripts as preprints also has the potential to result in higher
-quality science, by allowing for pre-publication feedback
-from a large pool of reviewers. Prepublication reviews by a small network of
-colleagues are common in the biological sciences and are an important part of
-the scientific process. These "friendly" reviews increases the chances of errors
-being caught prior to publication, allow errors to be identified
-prior to spending months in review, and allows authors to improve how they
-communicate the results of their research by modifying their writing in response
-to early feedback. Preprint servers offer a way to extend this network of
-colleagues to the entire scientific
-community, increasing the number of opportunities for review and revision
-prior to publication, and resulting in higher quality submissions and publications.
-As such, preprints can be seen as an
-integral aspect of a vigorous peer-review process \cite{hoc12}.
-
-%It is unclear to me whether we should keep this full paragraph or try to distill
-%it to a sentence or two at the end of the previous paragraph.
-Furthermore, the formal peer-review process as a whole is critically over-loaded. As
-the number of active scientists increases and the pressure to publish
-increases, it has become increasingly difficult for journals to find
-reviewers \cite{hoc09}.  At the same time, rejection rates are high in most journals
-\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the
-process over again at another journal. As a result, initiatives to reduce time from submission to
+Furthermore, the review process as a whole is critically over-loaded, because
+as the number of active scientists increases, because the pressure to publish
+increases, and because of an effect dubbed ``the tragedy of the reviewers
+commons'' \cite{hoc09}.  At the same time, rejection rates are high in most journals
+\cite{aar08,roh09}, and when not invited to submit a revision, authors must start the whole
+process all over again.  Initiatives to reduce time from submission to
 publication have emerged across the scientific community. Rohr et al.
@@
 
-Finally, public preprint servers offer a fair way to establish intellectual
-priority by making the work available when immediately after it is complete.
-Some manuscripts will spend much more time in the review process and/or in
-production after acceptance, than others. This means that
-that publication and acceptance dates do not accurately characterize who
-came up with an idea first. For this reason, mathematicians and physicists
-have embraced arXiv in part to establish priority in a fair way \cite{gin11,cal12}.
+Public preprint servers offer a much fairer way to establish intellectual
+priority by making the work available when done. Some manuscripts will spend
+much more time in the review process than others. Surprisingly, there is a
+perception in biology that public preprints make it easier to steal ideas, as if
+a scientific idea was only complete once published in a peer-reviewed journal
+\cite{gin11}. Ironically, mathematicians and physicists have embraced arXiv in
+part to establish priority in a fair way \cite{gin11,cal12}.
+
+Prepublication reviews by a small network of colleagues is an important part of
+the scientific process, attested by the fact that nearly all published papers
+acknowledge comments by people not listed as co-authors.  Preprint servers
+simply offer a way to extend this network of colleagues to the entire scientific
+community. It ensures that science is not constrained by small networks of
+scientists exchanging ideas.  Paul Ginsparg created arXiv.org in part for
+democratic reasons: he wanted everyone from students in small universities to
+Ivy-League professors to have access to the most recent scientific \emph{ideas}.
+Ginsparg's revolutionary idea was simply to use the power of the internet for
+preprints, not just for the end product, so the scientific process can be open
+as soon as possible.
 
@@
 We briefly discuss the main options to submit preprints to open servers:
-arXiv.org, figshare, and the upcoming PeerJ and F1000Research.
+arXiv.org, Figshare, and the upcoming PeerJ and F1000Research.
 
@@
 
-\subsection{figshare}
+\subsection{FigShare}
 
-figshare (\href{http://figshare.com}{http://figshare.com}) is an open server
+FigShare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
 that allows scientists to submit any research output: manuscript, figures,
@@
 what constitutes a research output and, unlike arXiv, there is no endorser
-system. All figshare content has a unique digital object identifier (DOI) like
+system. All FigShare content has a unique digital object identifier (DOI) like
 any journal article, thus offering a permanent and stable link to the content.
@@
 
-One of the biggest advantage of figshare over arXiv is that is it not limited to
+One of the biggest advantage of FigShare over arXiv is that is it not limited to
 quantitative sciences. arXiv.org has sections on quantitative biology but might
 not be appropriate for non-quantitative work. With its flexible approach to
-preprints, figshare offers an important alternative to arXiv for empirical
-biologists. Furthermore, by allowing all types of content, figshare arguably
+preprints, FigShare offers an important alternative to arXiv for empirical
+biologists. Furthermore, by allowing all types of content, FigShare arguably
 provides an archive for early results (e.g.: figures, lab presentations).
-figshare also supports commenting on preprints.
 
@@
 dialog. In addition, preprints can be made private if the authors choose, and
-shared only with selected colleagues. While this reduces many of the benefits of
+shared only with selected colleagues. While this reduces some of the benefits of
 preprints described above, it may allow some researchers who would not otherwise
@@
 preprints for free. One preprint per year can be posted for free and a onetime
-(i.e. lifetime) fee of 99 dollars allows the submitting author to post unlimited public
+(i.e. lifetime) fee of 99 dollars allows the posting of unlimited public
 preprints. It is also worth noting that the preprint server is not tied to the
@@
 PeerJ uses the CC-BY-SA 3.0 license, which is similar to the CC-BY license used
-by figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
+by Figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
 need a license identical to the license that governs the original work.
@@
 F1000Research is not a public preprint server like the previous three servers.
-Whereas arXiv, figshare, and PeerJ offer an option to submit a manuscript
-without having it reviewed, papers submitted to F1000Research will eventually be
-reviewed. Thus, F1000Research offers a hybrid model with publicly available
+Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
+without having it reviewed, papers submitted to F1000Research will eventually
+be reviewed. Thus, F1000Research offers a hybrid model with publicly available
 manuscripts at time of submission and standard peer-reviews. Manuscripts are
@@
 data to the paper. For instance, upon submitting a paper, authors are asked to
-upload their data, which are then integrated in \emph{e.g.} figshare widgets,
-the DOI of which are given in the paper when the data are first mentionned.
-The licensing of the data is similar to that used by FigShare, meaning that
-the articles are free to access, and can be redistributed readily. By
-integrating data to the paper, F1000Research is working to make
+upload their data, which are then integrated in \emph{e.g.} FigShare widgets,
+the DOI of which are given in the paper when the data are first mentioned.
+The licensing of the data is similar to the one used by FigShare, meaning that
+the articles are free to access, and can be redistributed readily. By putting
+much effort in integrating data to the paper, F1000Research is working to make
 science more reproducible and open.
 
-\subsection{GitHub}
+\subsection{Github}
 
 This manuscript was developed entirely as an open project on GitHub. GitHub is
-one of several hosting services for collaborative development using the Git
-version control system (VCS).  Git is a decentralized revision control system
+one of several hosting services for collaborative development using the git
+version control system (VCS).  git is a decentralized revision control system
 created by Linus Torvalds and is used primarily to develop software, including
-the Linux kernel. Git provides powerful features that allow numerous
-contributers to work asynchronously on the same project, often in parallel
-branches, all of which can be effortlessly merged and version controlled.  While
-Git is created primarily for software development, where the use of version
-control systems is standard \cite{aru12}, it is ideal for academic research
-since it provides a way to collaborate on every step of the manuscript
-development process, from data manipulation and analysis to writing and
-revision. For example, during the development of this manuscript, each author
-would clone the project (\emph{i.e.} make a personal copy), modify it, and then
-merge their changes into a master branch. This takes the preprint process to an
-entirely new level, where the entire writing process is open from the beginning.
+the Linux kernel.
+Git provides powerful features that allow numerous contributers to work asynchronously on the same project, often in parallel branches, all of which can be effortlessly merged and version controlled.
+Although created primarily for software development, git is ideal for academic research since it provides a way to version control and collaborate on every step of the manuscript development process, from data manipulation and analysis to writing and revision.
+For example, during the development of this manuscript, each author
+would clone the project (\emph{i.e.} make a personal copy), modify it, and then merge their changes into a master branch.This takes the preprint process to an entirely new level, where the entire writing process is open from the beginning.
+% I would avoid using the term forking since it is not a central piece of the section.
+It is one specific way of collaborating on a github repo when everyone does not have rights to it.
+People could just as easily work on a single branch, all with write access, either directly to the master branch or to individual branches that could be merged.
+So in other words, we should keep the language general so people don't get bogged down with trying to understand what a fork is.
+% also I changed one author clones, then submits pull request langauge a bit since the main point of using git is that we can all work simultaneously unlike svn.
+% I took out "These techniques are widely used in open source software development." because git can also be used for closed source software, offering the same advantages, where the repositories are private.
+Paid git accounts allow for private repos.
 
 \section{Conclusion}
-
-% Dominique:
-% I added the following three paragraphs to the conclusion, offering also a
-% discussion on the on going explosion of different publication models. Take
-% what you want and remove what you don't need.  I also had the feeling we might
-% want to include a single paragraph, very short, calling that evaluations
-% (academia, grant agencies etc...) looking at publication records or report of
-% scientific activities start to view preprints as a significant and sound
-% scientific contribution. One of the most important benefit is again the speed
-% of the publication process. Most grants are for three years or less. It makes
-% it hard to have a published paper within the limits of the grant. Preprints
-% could however speed the process and show that contributions were made during
-% the time of the grant.
-
-The ongoing discussions on the publication process, peer-reviewing and
-alternative publication models are all symptoms of the current uneasiness of
-scientists with the ever growing obsession with bibliographic metrics such as
-the impact factor \cite{Fisher2012}. There is pressure on researchers, wether
-they are junior looking for an academic position or senior trying to secure
-funding for their team, to orient their publication strategy in order to
-maximize their number of publications and total citations. A well-known
-consequence is to submit manuscripts first to the most prestigious journals, and
-then resubmit to lower level journals as they are rejected. The numerous
-negative impacts of such behavior have been discussed in depth \cite{hoc09} and
-include a long delay between the time a manuscript is finished to its
-publication.  They all contribute somehow in a general slowing down of
-scientific progress.  Research activities and the publication process are
-drifting away from their fundamental object, namely the diffusion of novel
-scientific discoveries.
-
-Developing a preprint culture in biology is not a final solution to the impact
-factor inflation, it might however reduce significantly its negative
-consequences. Preprints speed up publication, openly, with no judgement on
-pertinence and originality. Paradoxically, because peer-reviewing is conducted
-following this step in the process of a scientific communication, it might bring
-it closer to its fundamental objective. The role of peer-reviewing is to judge
-the scientific quality of a study, the match between its hypotheses, methods,
-results and conclusions. The peer review process is the first barrier against
-fraudulent or bad quality science, susceptible to impede scientific progress. It
-is however now dominated by subjective evaluations, where trendy contributions
-are promoted to increase the immediacy impact of the journal. Most journals have
-in their instructions for reviewers a section devoted to the evaluation of
-suitability for the journal, a task usually incumbent to editors. Preprints are
-by definition not evaluated, neither for their quality nor their pertinence.
-Technically, the difference between a preprint and a traditional publication
-should be that the latter as the approval stamp by pairs on its quality. The
-relevance of a study, its contribution to science, should only be judged
-post-publication by many more readers than the typical two-four anonymous
-reviewers. With a such a shift in the diffusion strategy, the role of
-traditional journals and their editors would be to showcase scientific
-discoveries for specialized readership. Such a process should improve even
-further their diffusion, not impede it.
-
-The current opening of the publication process we are currently witnessing with
-the arrival of new preprint systems and innovative publication models such as
-F1000, PLOS One, Nature Scientific Reports, might significantly bypass the
-inflation of bibliographic metrics. They not only promote scientific communications
-by changing the focus of peer-reviewing, they also favor the publication of
-results that might otherwise be rejected because of low interest, negative
-results, descriptive and quantitative studies and datasets. One of drawback of
-making publication easier is obviously the proliferation of studies of uneven
-quality. A tradeoff between the intensity of the peer-review filtering and the
-benefits to science has been hypothesized \cite{Aarssen2012}. With increasingly
-stringent peer reviewing, the quality of published papers and easiness of
-finding discoveries might increase, at the cost of censorship, increasing load
-on authors and reviewers and time for publication. Preprints are simply
-bypassing this model, for what we believe is the progress of science: they speed
-up the dissemination of scientific discoveries, impede censorship and put on
-reader's shoulders the responsibility to judge originality and pertinence.
 
@@
 
-% Aren't we bridging more than cultural and geographic? I mean, we are
-% essentially cross pollinating ideas. e.g. It took a lot time for MCMC to
-% become popular in ecology even though it was widely used in other disciplines
-% a decade or two earlier.
+% Aren't we bridging more than cultural and geographic?
+I mean, we are essentially cross pollinating ideas.
+e.g.
+It took a lot time for MCMC to become popular in ecology even though it was widely used in other disciplines a decade or two earlier.
 Preprint servers also facilitate communication between disciplines, bridging
@@
 
-We thank Carl Boettiger and Mark Hahnel for helpful comments on an earlier
-version of this manuscript.
+We thank Carl Boettiger for helpful comments on an earlier version of this
+manuscript.
 

### 2012-10-08 ms.tex
editing

--- 2012-10-06 ms.tex
@@
 the results of scientific research available to the scientific community as soon
-as possible, instead of waiting until the peer-review process is fully completed.
-Sharing manuscripts using preprint servers has numerous advantages including: 1) rapid
-dissemination of work-in-progress to a wider audience; 2) improved peer review by
-encouraging feedback from the entire research community;
+as possible, instead of waiting until the peer-review process is fully
+completed.  Sharing manuscripts using preprint servers has numerous advantages
+including: 1) rapid dissemination of work-in-progress to a wider audience; 2)
+improved peer review by encouraging feedback from the entire research community;
 and 3) a fair and straightforward way to establish precedence.
@@
 speed (Figure~\ref{fig:map}). The time between submission and the official
-publication of a manuscript can be measured in months, sometime in years. For
+publication of a manuscript can be measured in months, sometimes in years. For
 all this time, the research is known only to a select few: colleagues, editors,
@@
 These "friendly" reviews increases the chances of errors being caught prior to
-publication, allow errors to be identified prior to spending months in review,
-and allows authors to improve how they communicate the results of their research
-by modifying their writing in response to early feedback. Preprint servers offer
-a way to extend this network of colleagues to the entire scientific community,
-increasing the number of opportunities for review and revision prior to
-publication, and resulting in higher quality submissions and publications.  As
-such, preprints can be seen as an integral aspect of a vigorous peer-review
-process \cite{hoc12}.
-
-Furthermore, the formal peer-review process as a whole is critically
-over-loaded. As the number of active scientists increases and the pressure to
-publish increases, it has become increasingly difficult for journals to find
-reviewers \cite{hoc09}.  At the same time, rejection rates are high in most
-journals \cite{aar08,roh09}, and when not invited to submit a revision, authors
-must start the process over again at another journal. As a result, initiatives
-to reduce time from submission to publication have emerged across the scientific
-community. Rohr et al.  \cite{roh09} called for the recycling and reuse of
-peer-reviews: by attaching previous reviews and detailed replies to a new
-submission, both the editor and the referees can gauge the work done on the
-manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
-\emph{Peerage of Science} initiative allows authors to seek anonymous pre-review
-by their peers. Some journals now accept to publish papers which received good
-evaluations, with \emph{Animal Biology} having recently accepted first a paper
-reviewed entirely with the \emph{Peerage of Science} \cite{abb12}, effectively
-outsourcing the review process. A widespread use of preprint servers can achieve
-the same goal of reducing the time spent in review. By allowing open comments
-and criticisms prior to submission, the authors will receive valuable feedback
-and can improve the version which will be submitted. With a rich enough
-community of scientists depositing preprints, and commenting on them, the
-process of an open pre-review can become widespread and will overall increase
-the quality of first submissions.
+publication. Furthermore, the formal peer-review process as a whole is
+critically over-loaded. As the number of active scientists increases and the
+pressure to publish increases, it has become increasingly difficult for journals
+to find reviewers \cite{hoc09}.  At the same time, rejection rates are high in
+most journals \cite{aar08,roh09}, and when not invited to submit a revision,
+authors must start the process over again at another journal. As a result,
+initiatives to reduce time from submission to publication have emerged across
+the scientific community. Rohr et al.  \cite{roh09} called for the recycling and
+reuse of peer-reviews: by attaching previous reviews and detailed replies to a
+new submission, both the editor and the referees can gauge the work done on the
+manuscript, and perhaps evaluate it with less prejudice. A widespread use of
+preprint servers can achieve the same goal of reducing the time spent in review.
+With a rich enough community of scientists depositing preprints, and commenting
+on them, the process of an open pre-review can become widespread and will
+overall increase the quality of first submissions \cite{hoc12}.
 
@@
 Finally, public preprint servers offer a fair way to establish intellectual
-priority by making the work available when immediately after it is complete.
-Some manuscripts will spend much more time in the review process and/or in
-production after acceptance, than others. This means that
-that publication and acceptance dates do not accurately characterize who
-came up with an idea first. For this reason, mathematicians and physicists
-have embraced arXiv in part to establish priority in a fair way \cite{gin11,cal12}.
+priority by making the work available when it is complete.  Some manuscripts
+will spend much more time in the review process and/or in production after
+acceptance, than others. This means that publication and acceptance dates do not
+accurately characterize who came up with an idea first.  For this reason,
+mathematicians and physicists have embraced arXiv in part to establish priority
+in a fair way \cite{gin11,cal12}.
 
@@
 
-In contrast to other disciplines, the field of biology has effectively no preprint
-culture, with the exception of small pockets of primarily highly quantitative
-research (e.g., epidemiology). While, submitting to preprint servers has become
-more common in the past few years, and the quantitative biology section in arXiv
-is experiencing rapid growth in submissions \cite{cal12}, the number of biology
-papers submitted to preprint servers still represents only a small fraction of
-the total research produced in biology.
+In contrast to other disciplines, the field of biology has effectively no
+preprint culture, with the exception of small pockets of primarily highly
+quantitative research (e.g., epidemiology). Submitting to preprint servers has
+become more common in the past few years, and the quantitative biology section
+in arXiv is experiencing the fastest growth in submissions \cite{cal12}. Yet,
+the number of biology papers submitted to preprint servers still represents only
+a small fraction of the total research produced in biology.
 
@@
 appears to be a largely unfounded concern. In other fields preprints serve the
-opposite role, they allow straightforward establishment of precendence, letting
-researchs lay claim to an idea thus prevening it from being "stolen".
+opposite role, they allow straightforward establishment of precedence, letting
+research lay claim to an idea thus preventing it from being "stolen".
 
@@
 based on a certain interpretation of the Ingelfinger rule: scientists should not
-publish the same manuscript twice \cite{alt96}. However, preprints are not
-peer-reviewed papers and posting to a public server does not constitute
-publication in a peer-reviewed journal.  A preprint is simply a document that
-allows ideas to spread and be discussed, but it is not yet formally validated by
-the peer-review system. This is why the majority of publishers do not see arXiv
-and similar services as a violation of the Ingelfinger rule. Almost all of the
-major publishers in biology are preprint-friendly, including: Nature Publishing
-Group, PLOS, BMC, PNAS, Science (mostly) \ref{table:policies}, and all the
-journals from Elsevier and Springer.  The Ecological Society of America and the
-Genetics Society of America also recently changed their policies to allow public
-preprints.  Few scientific publications will not consider a manuscript submitted
-to a public preprint server. In fact, \emph{Nature} responded to the rumour that
-they refused manuscripts submitted to arXiv by saying that ``\emph{Nature} never
-wishes to stand in the way of communication between researchers. We seek rather
-to add value for authors and the community at large in our peer review,
-selection and editing'' \cite{nat05}. Still, a few journals adopt a ``by
-default'' hostile attitude towards preprints, mostly due to the lack of clear
-policy of the publishers, or perhaps because a preprint culture has not
-developed in biology and the practice is still considered unusual. As an
-example, Wiley-Blackwell, which publishes some of the leading journals in
-biology, has no official policy on the matter.
+publish the same manuscript twice \cite{alt96}. A preprint is simply a document
+that allows ideas to spread and be discussed, it is not yet formally validated
+by the peer-review system. This is why the majority of publishers do not see
+arXiv and similar services as a violation of the Ingelfinger rule. Almost all of
+the major publishers in biology are preprint-friendly, including: Nature
+Publishing Group, PLOS, BMC, PNAS, Elsevier, and Springer \ref{table:policies}.
+The Ecological Society of America and the Genetics Society of America also
+recently changed their policies to allow public preprints. In fact,
+\emph{Nature} responded to the rumour that they refused manuscripts submitted to
+arXiv by saying that ``\emph{Nature} never wishes to stand in the way of
+communication between researchers. We seek rather to add value for authors and
+the community at large in our peer review, selection and editing'' \cite{nat05}.
+Still, a few journals adopt a ``by default'' hostile attitude towards preprints,
+mostly due to the lack of clear policy of the publishers, or perhaps because a
+preprint culture has not developed in biology and the practice is still
+considered unusual. As an example, Wiley-Blackwell, which publishes some of the
+leading journals in biology, has no official policy on the matter.
 
@@
 
-One of the advantages of figshare over arXiv for biologists is that is it not limited
-to quantitative sciences. arXiv.org has sections on quantitative biology but might
-not be appropriate for non-quantitative work. With its flexible approach to
-preprints, figshare offers an alternative to arXiv for empirical
+One of the advantages of figshare over arXiv for biologists is that is it not
+limited to quantitative sciences. arXiv.org has sections on quantitative biology
+but might not be appropriate for non-quantitative work. With its flexible
+approach to preprints, figshare offers an alternative to arXiv for empirical
 biologists. Furthermore, by allowing all types of content, figshare also
@@
 PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new Open Access
-publisher that combines both a preprint server, and a peer reviewed journal.
-It is focused on the biological and medical sciences, which may help overcome the
+publisher that combines both a preprint server, and a peer reviewed journal.  It
+is focused on the biological and medical sciences, which may help overcome the
 perception that preprints do not have a place in biology. Like figshare this is
-an advantage relative to arXiv for biologists doing non-quantitative work.
-Also like figshare PeerJ allows commenting on posted preprints, improving the
-potential for pre-publication
-dialog. In addition, preprints can be made private if the authors choose, and
-shared only with selected colleagues. While this reduces many of the benefits of
-preprints described above, it may allow some researchers who would not otherwise
-post preprints to begin to explore the possibility in a manner appropriate to
-their current circumstances.
+an advantage relative to arXiv for biologists doing non-quantitative work.  Also
+like figshare, PeerJ allows commenting on posted preprints, improving the
+potential for pre-publication dialog. In addition, preprints can be made private
+if the authors choose, and shared only with selected colleagues. While this
+reduces many of the benefits of preprints described above, it may allow some
+researchers who would not otherwise post preprints to begin to explore the
+possibility in a manner appropriate to their current circumstances.
 
@@
 preprints for free. One preprint per year can be posted for free, with a onetime
-(i.e. lifetime) fee of 99 dollars required to allow an author to post unlimited public
-preprints. The preprint server is not tied to the journal, so preprints can be posted
-regardless of where they will eventually be submitted for publication.
+(i.e. lifetime) fee of 99 dollars required to allow an author to post unlimited
+public preprints. The preprint server is not tied to the journal, so preprints
+can be posted regardless of where they will eventually be submitted for
+publication.
 
@@
 Whereas arXiv, figshare, and PeerJ offer an option to submit a manuscript
-without having it reviewed, papers submitted to F1000Research will eventually be
-reviewed. Thus, F1000Research offers a hybrid model with publicly available
+without having it reviewed, papers submitted to F1000Research will eventually
+be reviewed. Thus, F1000Research offers a hybrid model with publicly available
 manuscripts at time of submission and standard peer-reviews that occur as part
-of the submission process. Manuscripts are
-considered ``accepted'' and will only be indexed after two positive referee
-responses. F1000Research works closely with data providers to integrate raw
-data to the paper. For instance, upon submitting a paper, authors are asked to
-upload their data, which are then integrated in \emph{e.g.} figshare widgets,
-the DOI of which are given in the paper when the data are first mentionned.
-By integrating data to the paper, F1000Research is working to make
-science more reproducible and open.
+of the submission process. Manuscripts are considered ``accepted'' and will
+only be indexed after two positive referee responses. F1000Research works
+closely with data providers to integrate raw data to the paper. For instance,
+upon submitting a paper, authors are asked to upload their data, which are then
+integrated in \emph{e.g.} figshare widgets, the DOI of which are given in the
+paper when the data are first mentioned.  By integrating data to the paper,
+F1000Research is working to make science more reproducible and open.
 
@@
 scientists with the ever growing obsession with bibliographic metrics such as
-the impact factor \cite{Fisher2012}. There is pressure on researchers, wether
-they are junior looking for an academic position or senior trying to secure
-funding for their team, to orient their publication strategy in order to
-maximize their number of publications and total citations. A well-known
-consequence is to submit manuscripts first to the most prestigious journals, and
-then resubmit to lower level journals as they are rejected. The numerous
-negative impacts of such behavior have been discussed in depth \cite{hoc09} and
-include a long delay between the time a manuscript is finished to its
-publication.  They all contribute somehow in a general slowing down of
-scientific progress.  Research activities and the publication process are
-drifting away from their fundamental object, namely the diffusion of novel
+the impact factor \cite{Fisher2012}. There is pressure on researchers to orient
+their publication strategy in order to maximize their number of publications and
+total citations. A well-known consequence is to submit manuscripts first to the
+most prestigious journals, and then resubmit to ``lower level'' journals as they
+are rejected. The numerous negative impacts of such behavior have been discussed
+in depth \cite{hoc09} and include a long delay between the time a manuscript is
+finished to its publication.  They all contribute somehow in a general slowing
+down of scientific progress.  Research activities and the publication process
+are drifting away from their fundamental object, namely the diffusion of novel
 scientific discoveries.
 
-Developing a preprint culture in biology is not a final solution to the impact
-factor inflation, it might however reduce significantly its negative
-consequences. Preprints speed up publication, openly, with no judgement on
+Developing a preprint culture in biology will not solve all problems with the
+current publication process. It might however reduce significantly its negative
+consequences. Preprint servers speed up publication and make no judgement on
 pertinence and originality. Paradoxically, because peer-reviewing is conducted
-following this step in the process of a scientific communication, it might bring
-it closer to its fundamental objective. The role of peer-reviewing is to judge
-the scientific quality of a study, the match between its hypotheses, methods,
-results and conclusions. The peer review process is the first barrier against
-fraudulent or bad quality science, susceptible to impede scientific progress. It
-is however now dominated by subjective evaluations, where trendy contributions
-are promoted to increase the immediacy impact of the journal. Most journals have
-in their instructions for reviewers a section devoted to the evaluation of
-suitability for the journal, a task usually incumbent to editors. Preprints are
-by definition not evaluated, neither for their quality nor their pertinence.
+\emph{after} this step in the process of scientific communication, it might
+bring it closer to its fundamental objective. The role of peer-reviewing is to
+judge the scientific quality of a study. The peer review process is the first
+barrier against the fraudulent and poor quality science susceptible to impede
+scientific progress. However, it is now dominated by subjective evaluations,
+where trendy contributions are promoted to increase impact factors. Preprints
+are by definition not evaluated, neither for their quality nor their pertinence.
 Technically, the difference between a preprint and a traditional publication
@@
 
-The current opening of the publication process we are currently witnessing with
-the arrival of new preprint systems and innovative publication models such as
-F1000, PLOS One, Nature Scientific Reports, might significantly bypass the
-inflation of bibliographic metrics. They not only promote scientific communications
-by changing the focus of peer-reviewing, they also favor the publication of
-results that might otherwise be rejected because of low interest, negative
-results, descriptive and quantitative studies and datasets. One of drawback of
-making publication easier is obviously the proliferation of studies of uneven
-quality. A tradeoff between the intensity of the peer-review filtering and the
-benefits to science has been hypothesized \cite{Aarssen2012}. With increasingly
-stringent peer reviewing, the quality of published papers and easiness of
-finding discoveries might increase, at the cost of censorship, increasing load
-on authors and reviewers and time for publication. Preprints are simply
-bypassing this model, for what we believe is the progress of science: they speed
-up the dissemination of scientific discoveries, impede censorship and put on
-reader's shoulders the responsibility to judge originality and pertinence.
+One of drawback of making publication easier is the proliferation of studies of
+uneven quality. A trade-off between the intensity of the peer-review filtering
+and the benefits to science has been hypothesized \cite{Aarssen2012}.  With
+increasingly stringent peer reviewing, the quality of published papers and
+easiness of finding discoveries might increase, at the cost of censorship, an
+increased load on authors and reviewers, and more delays for publication.
+Preprints are simply bypassing this model for what we believe is the progress of
+science: they speed up the dissemination of scientific discoveries, impede
+censorship and put on reader's shoulders the responsibility to judge originality
+and pertinence.
 

### 2012-10-11 ms.tex

@@
 preprints for free. One preprint per year can be posted for free, with a onetime
-(i.e. lifetime) fee of 99 dollars required to allow an author to post unlimited
+(\emph{i.e.} lifetime) fee of 99 dollars required to allow an author to post unlimited
 public preprints. The preprint server is not tied to the journal, so preprints
@@
 easiness of finding discoveries might increase, at the cost of censorship, an
-increased load on authors and reviewers, and more delays for publication.
+increased load on authors and reviewers, and greater delays for publication.
 Preprints are simply bypassing this model for what we believe is the progress of

### 2012-10-11 ms.tex
A bit about early career, and a few comments early in the text. Also minor edits, and a modification to the title

@@
 
-\title{Developing a preprint culture in biology}
+\title{Developing a public preprint culture in biology}
 
@@
 \section{Introduction}
+
+%%% TP Oct 11 2012
+%%% Just something I am thinking about now
+%%% We are not a good sample of biologists. We are mostly evolutionary ecologists,
+%%% and perhaps having the input of a "real" (labcoat wearing) biologist can help.
 
@@
 Finally, public preprint servers offer a fair way to establish intellectual
-priority by making the work available when it is complete.  Some manuscripts
-will spend much more time in the review process and/or in production after
-acceptance, than others. This means that publication and acceptance dates do not
-accurately characterize who came up with an idea first.  For this reason,
-mathematicians and physicists have embraced arXiv in part to establish priority
-in a fair way \cite{gin11,cal12}.
+priority by making the work available as soon as it is complete. Some
+manuscripts will spend much more time in the review process and/or in
+production after acceptance, than others. This means that publication and
+acceptance dates do not accurately characterize who came up with an idea
+first. For this reason, mathematicians and physicists have embraced arXiv in
+part to establish priority in a fair way \cite{gin11,cal12}. This can be
+especially crucial to early-career scientists. The sometimes long delay before
+publication is seldom compatible with the pressure to show an impressive
+publication record when applying for a scholarship or a position. Increasing
+the perceived value of pre-prints as close, or equal, to journal articles (a
+point we discuss in the conclusion) will allow young researchers to put their
+research outcome in the open, and build a reputation for themselves through
+the diffusion of their work, without the fear that this work will not be
+recognized by grant or job commitees.
+
+%%% TP Oct 11 2012
+%%% Important to appeal to the young folks, while at the same time calling for
+%%% more recognition of preprints. Feel free to rephrase, but don't remove!
 
@@
 In contrast to other disciplines, the field of biology has effectively no
+%%% TP
+%%% As good a place as any to define biology... PLoS Biology, for example,
+%%% is mostly cell biol stuff. We are not a typical subset of biologists!
 preprint culture, with the exception of small pockets of primarily highly
-quantitative research (e.g., epidemiology). Submitting to preprint servers has
-become more common in the past few years, and the quantitative biology section
-in arXiv is experiencing the fastest growth in submissions \cite{cal12}. Yet,
-the number of biology papers submitted to preprint servers still represents only
-a small fraction of the total research produced in biology.
+quantitative research (\emph{e.g.}, epidemiology, population genetics).
+Submitting to preprint servers has become more common in the past few years,
+and the quantitative biology section in arXiv is experiencing the fastest
+growth in submissions \cite{cal12}. Yet, the number of biology papers
+submitted to preprint servers still represents only a small fraction of the
+total research produced in biology.
 
@@
 culture of sharing preprints, many of which are based on common misconceptions
-regarding the costs and benefits of sharing preprints. For example, in contrast
+regarding the costs and benefits associated with the practice. For example, in contrast
 to other fields there is a perception in biology that public preprints
@@
 research lay claim to an idea thus preventing it from being "stolen".
+%%% TP
+%%% Most refs will ask for a ref at that point. At least, I will, but I'm so
+%%% demanding that I'm part of why the review process sucks ;-)
 
-Another major concern is that if a researcher posts a public preprint that they
-will not be allowed to submit their paper to their journal of choice. This is
-based on a certain interpretation of the Ingelfinger rule: scientists should not
-publish the same manuscript twice \cite{alt96}. A preprint is simply a document
-that allows ideas to spread and be discussed, it is not yet formally validated
-by the peer-review system. This is why the majority of publishers do not see
-arXiv and similar services as a violation of the Ingelfinger rule. Almost all of
-the major publishers in biology are preprint-friendly, including: Nature
-Publishing Group, PLOS, BMC, PNAS, Elsevier, and Springer \ref{table:policies}.
-The Ecological Society of America and the Genetics Society of America also
-recently changed their policies to allow public preprints. In fact,
+Another major concern is that if a researcher posts a public preprint that
+they will not be allowed to submit their paper to their journal of choice.
+This is based on a certain interpretation of the Ingelfinger rule: scientists
+should not publish the same manuscript twice \cite{alt96}. A preprint is
+simply a document that allows ideas to spread and be discussed, it is not yet
+formally validated by the peer-review system. This is why the majority of
+publishers do not see arXiv and similar services as a violation of the
+Ingelfinger rule, and it is not unseen to have a preprint reproduced almost
+exactly in the published version.
+%%% TP
+%%% Steve Frank papers on ArXiV often end up almost unmodified in JEB
+%%% I can dig up the two version so that we can cite them
+Almost all of the major publishers in
+biology are preprint-friendly, including: Nature Publishing Group, PLOS, BMC,
+PNAS, Elsevier, and Springer \ref{table:policies}. The Ecological Society of
+America and the Genetics Society of America recently changed their
+policies to allow public preprints. In fact,
 \emph{Nature} responded to the rumour that they refused manuscripts submitted to

### 2012-10-11 ms.tex
minor edits

@@
 
-%%% TP Oct 11 2012
-%%% Important to appeal to the young folks, while at the same time calling for
-%%% more recognition of preprints. Feel free to rephrase, but don't remove!
-
 \section{Preprints in biological sciences}
@@
 opposite role, they allow straightforward establishment of precedence, letting
-research lay claim to an idea thus preventing it from being "stolen".
+research lay claim to an idea thus preventing it from being "stolen" \cite{gin11}
 %%% TP

### 2012-10-11 ms.tex
editing, title

@@
 
-\title{Developing a public preprint culture in biology}
+\title{Developing a preprint culture in biology}
 
@@
 \section{Introduction}
-
-%%% TP Oct 11 2012
-%%% Just something I am thinking about now
-%%% We are not a good sample of biologists. We are mostly evolutionary ecologists,
-%%% and perhaps having the input of a "real" (labcoat wearing) biologist can help.
 
@@
 In contrast to other disciplines, the field of biology has effectively no
-%%% TP
-%%% As good a place as any to define biology... PLoS Biology, for example,
-%%% is mostly cell biol stuff. We are not a typical subset of biologists!
 preprint culture, with the exception of small pockets of primarily highly
@@
 research lay claim to an idea thus preventing it from being "stolen" \cite{gin11}
-%%% TP
-%%% Most refs will ask for a ref at that point. At least, I will, but I'm so
-%%% demanding that I'm part of why the review process sucks ;-)
 

### 2012-10-17 ms.tex

@@
 including: 1) rapid dissemination of work-in-progress to a wider audience; 2)
-improved peer review by encouraging feedback from the entire research community;
-and 3) a fair and straightforward way to establish precedence.
+... %% Tim???
+3) improved peer review by encouraging feedback from the entire research community;
+and 4) a fair and straightforward way to establish precedence.
 
@@
 
+Public preprints can be especially crucial to early-career scientists. The
+sometimes long delay before publication is seldom compatible with the pressure
+to show an impressive publication record when applying for a scholarship or a
+position. Increasing the perceived value of pre-prints as close, or equal, to
+journal articles (a point we discuss in the conclusion) will allow young
+researchers to put their research outcome in the open, and build a reputation
+for themselves through the diffusion of their work, without the fear that this
+work will not be recognized by grant or job commitees.
+
 Posting manuscripts as preprints also has the potential to result in higher
@@
 first. For this reason, mathematicians and physicists have embraced arXiv in
-part to establish priority in a fair way \cite{gin11,cal12}. This can be
-especially crucial to early-career scientists. The sometimes long delay before
-publication is seldom compatible with the pressure to show an impressive
-publication record when applying for a scholarship or a position. Increasing
-the perceived value of pre-prints as close, or equal, to journal articles (a
-point we discuss in the conclusion) will allow young researchers to put their
-research outcome in the open, and build a reputation for themselves through
-the diffusion of their work, without the fear that this work will not be
-recognized by grant or job commitees.
+part to establish priority in a fair way \cite{gin11,cal12}.
 

### 2012-10-17 ms.tex

--- 2012-10-11 ms.tex
@@
-\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4-1}
+\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4}
 \usepackage[utf8]{inputenc}
@@
 
+\author{Karthik Ram}
+\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley, United-States of America.}
+
 \author{Timoth\'ee Poisot}
@@
 \affiliation{International Network for Next-Generation Ecology.}
-
-\author{Karthik Ram}
-\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley, United-States of America.}
 
@@
 Public preprint servers allow authors to make manuscripts publicly available
-before, or in parallel to, submitting them to journals for traditional
-peer-review. The rationale for preprint servers is fundamentally simple: to make
-the results of scientific research available to the scientific community as soon
-as possible, instead of waiting until the peer-review process is fully
+before, or in parallel to, submitting them to journals for traditional peer-
+review. The rationale for preprint servers is fundamentally simple: to make
+the results of scientific research available to the scientific community as
+soon as possible, instead of waiting until the peer-review process is fully
 completed.  Sharing manuscripts using preprint servers has numerous advantages
 including: 1) rapid dissemination of work-in-progress to a wider audience; 2)
-improved peer review by encouraging feedback from the entire research community;
-and 3) a fair and straightforward way to establish precedence.
+immediate visibility of the research output for early-carreer scientsits; 3)
+improved peer review by encouraging feedback from the entire research
+community; and 4) a fair and straightforward way to establish precedence.
 
@@
 
+Public preprints can be crucial to early-career scientists. The delay before
+publication is seldom compatible with the pressure to show an impressive
+publication record when applying for a scholarship or a position. Increasing
+the perceived value of pre-prints as close, or equal, to journal articles (a
+point we discuss in the conclusion) will allow young researchers to put their
+research outcome in the open, and build a reputation for themselves through
+the diffusion of their work, without the fear that this work will not be
+recognized by grant or job commitees. In this perspective, mixed publication
+systems like experimented by F1000Research (see below) should be encouraged as
+they combine the best of both worlds: contributions are initally considered
+preprints, but acquire full article status after positive reviews are
+received.
+
 Posting manuscripts as preprints also has the potential to result in higher
@@
 the biological sciences and are an important part of the scientific process.
-These "friendly" reviews increases the chances of errors being caught prior to
+These ``friendly'' reviews increases the chances of errors being caught prior to
 publication. Furthermore, the formal peer-review process as a whole is
@@
 tolerate preprints except for a few of their medical journals, e.g.: Journal
-of the National Cancer Institute from Oxford and The Lancer from Elsevier.}
+of the National Cancer Institute from Oxford and The Lancet from Elsevier.}
     \label{table:policies}

### 2012-10-17 ms.tex
revtex 4.1 format
Add Liza Gross's suggested reference

@@
-\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4}
+\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4-1}
 \usepackage[utf8]{inputenc}
@@
 new blog discussing arXiv papers in population genetics, will help make arXiv
-attractive for scientists looking to promote their work. These initiatives are
+attractive for scientists looking to promote their work \cite{lom12}. These initiatives are
 important to fully exploit the potential of open preprints servers. Posting
@@
 
-Another major concern is that if a researcher posts a public preprint that
-they will not be allowed to submit their paper to their journal of choice.
-This is based on a certain interpretation of the Ingelfinger rule: scientists
-should not publish the same manuscript twice \cite{alt96}. A preprint is
-simply a document that allows ideas to spread and be discussed, it is not yet
-formally validated by the peer-review system. This is why the majority of
-publishers do not see arXiv and similar services as a violation of the
-Ingelfinger rule, and it is not unseen to have a preprint reproduced almost
-exactly in the published version.
-%%% TP
-%%% Steve Frank papers on ArXiV often end up almost unmodified in JEB
-%%% I can dig up the two version so that we can cite them
-Almost all of the major publishers in
-biology are preprint-friendly, including: Nature Publishing Group, PLOS, BMC,
-PNAS, Elsevier, and Springer \ref{table:policies}. The Ecological Society of
-America and the Genetics Society of America recently changed their
-policies to allow public preprints. In fact,
-\emph{Nature} responded to the rumour that they refused manuscripts submitted to
-arXiv by saying that ``\emph{Nature} never wishes to stand in the way of
-communication between researchers. We seek rather to add value for authors and
-the community at large in our peer review, selection and editing'' \cite{nat05}.
-Still, a few journals adopt a ``by default'' hostile attitude towards preprints,
-mostly due to the lack of clear policy of the publishers, or perhaps because a
-preprint culture has not developed in biology and the practice is still
-considered unusual. As an example, Wiley-Blackwell, which publishes some of the
-leading journals in biology, has no official policy on the matter.
+Another major concern is that if a researcher posts a public preprint that they
+will not be allowed to submit their paper to their journal of choice.  This is
+based on a certain interpretation of the Ingelfinger rule: scientists should not
+publish the same manuscript twice \cite{alt96}. A preprint is simply a document
+that allows ideas to spread and be discussed, it is not yet formally validated
+by the peer-review system. This is why the majority of publishers do not see
+arXiv and similar services as a violation of the Ingelfinger rule. Almost all of
+the major publishers in biology are preprint-friendly, including: Nature
+Publishing Group, PLOS, BMC, PNAS, Elsevier, and Springer \ref{table:policies}.
+The Ecological Society of America and the Genetics Society of America recently
+changed their policies to allow public preprints. In fact, \emph{Nature}
+responded to the rumour that they refused manuscripts submitted to arXiv by
+saying that ``\emph{Nature} never wishes to stand in the way of communication
+between researchers. We seek rather to add value for authors and the community
+at large in our peer review, selection and editing'' \cite{nat05}.  Still, a few
+journals adopt a ``by default'' hostile attitude towards preprints, mostly due
+to the lack of clear policy of the publishers, or perhaps because a preprint
+culture has not developed in biology and the practice is still considered
+unusual. As an example, Wiley-Blackwell, which publishes some of the leading
+journals in biology, has no official policy on the matter.
 
@@
 ftp, and soon thereafter adopted the newly created world-wide
-web\cite{jackson2002preprints}.  arXiv now receives over 7 000 submissions per
+web \cite{jackson2002preprints}.  arXiv now receives over 7 000 submissions per
 month (\url{http://arxiv.org/show_monthly_submissions}) and divides its
@@
 Developing a preprint culture in biology will not solve all problems with the
-current publication process. It might however reduce significantly its negative
+current publication process. However, It might significantly reduce its negative
 consequences. Preprint servers speed up publication and make no judgement on
@@
 barrier against the fraudulent and poor quality science susceptible to impede
-scientific progress. However, it is now dominated by subjective evaluations,
-where trendy contributions are promoted to increase impact factors. Preprints
-are by definition not evaluated, neither for their quality nor their pertinence.
-Technically, the difference between a preprint and a traditional publication
-should be that the latter as the approval stamp by pairs on its quality. The
-relevance of a study, its contribution to science, should only be judged
-post-publication by many more readers than the typical two-four anonymous
-reviewers. With a such a shift in the diffusion strategy, the role of
+scientific progress. Preprints are not filtered, neither for their quality nor
+their pertinence.  Technically, the difference between a preprint and a
+traditional publication should be that the latter as the approval stamp by pairs
+on its quality. The relevance of a study, its contribution to science, should
+only be judged post-publication by many more readers than the typical two-four
+anonymous reviewers. With a such a shift in the diffusion strategy, the role of
 traditional journals and their editors would be to showcase scientific
@@
 
-We thank Carl Boettiger and Mark Hahnel for helpful comments on an earlier
+We thank Carl Boettiger, Mark Hahnel, and Hedvig Nenz\'en for helpful comments on an earlier
 version of this manuscript.

### 2012-10-18 ms.tex
First round of small editions

@@
 review. The rationale for preprint servers is fundamentally simple: to make
-the results of scientific research available to the scientific community as
+the results of research available to the scientific community as
 soon as possible, instead of waiting until the peer-review process is fully
@@
 including: 1) rapid dissemination of work-in-progress to a wider audience; 2)
-immediate visibility of the research output for early-carreer scientsits; 3)
+immediate visibility of the research output for early-career scientists; 3)
 improved peer review by encouraging feedback from the entire research
@@
 attractive for scientists looking to promote their work \cite{lom12}. These initiatives are
-important to fully exploit the potential of open preprints servers. Posting
+important to fully exploit the potential of open preprint servers. Posting
 preprints online increases the community of available informal peer reviewers,
@@
 
-Preprints began to gain popularity 20 years ago with the advent of arXiv, an open
-preprint server widely used in physics and mathematics \cite{gin11}. Preprints
-are also integral to the culture of other scientific fields.  Paul Krugman noted
-that, in economics, the \emph{traditional model of submit, get refereed,
-publish, and then people will read your work broke down a long time ago. In
-fact, it had more or less fallen apart by the early 80s} \cite{kru12}. In
-addition to a section in arXiv, economists have also the RePEc (Research Papers
-in Economics) initiative, which aims to create an archive of working papers,
+Preprints began to gain popularity 20 years ago with the advent of arXiv, an
+open preprint server widely used in physics and mathematics \cite{gin11}.
+Preprints are also integral to the culture of other scientific fields.  Paul
+Krugman noted that, in economics, the \emph{traditional model of submit, get
+refereed, publish, and then people will read your work broke down a long time
+ago. In fact, it had more or less fallen apart by the early 80s} \cite{kru12}.
+In addition to a section in arXiv, economists have the RePEc (Research Papers in
+Economics) initiative, which aims to create an archive of working papers,
 manuscripts, and book chapters.
@@
 highlight the advantages of open preprint servers for both scientists and
-publishers; 2) address several misconceptions about preprints that are common
-among biologists; 3) discuss the preprint policies of major publishers in
-biology; and 4) review the most popular preprint servers currently available.
+publishers; 2) discuss the preprint policies of major publishers in biology; and
+3) review the most popular preprint servers currently available.
 
@@
 publication record when applying for a scholarship or a position. Increasing
-the perceived value of pre-prints as close, or equal, to journal articles (a
-point we discuss in the conclusion) will allow young researchers to put their
+the perceived value of pre-prints as close, or equal, to journal articles 
+will allow young researchers to put their
 research outcome in the open, and build a reputation for themselves through
-the diffusion of their work, without the fear that this work will not be
-recognized by grant or job commitees. In this perspective, mixed publication
-systems like experimented by F1000Research (see below) should be encouraged as
-they combine the best of both worlds: contributions are initally considered
+the diffusion of their work without fear that this work will not be
+recognized by grant or job committees. In this perspective, mixed publication
+systems like F1000Research [\ref{f1000r}] should be encouraged as
+they combine the best of both worlds: contributions are initially considered
 preprints, but acquire full article status after positive reviews are
@@
 Posting manuscripts as preprints also has the potential to result in higher
-quality science, by allowing for pre-publication feedback from a large pool of
+quality science by allowing prepublication feedback from a large pool of
 reviewers. Prepublication reviews by a small network of colleagues are common in
-the biological sciences and are an important part of the scientific process.
+the biological sciences and form an important part of the scientific process.
 These ``friendly'' reviews increases the chances of errors being caught prior to
@@
 critically over-loaded. As the number of active scientists increases and the
-pressure to publish increases, it has become increasingly difficult for journals
+pressure to publish increases, it is becoming difficult for journals
 to find reviewers \cite{hoc09}.  At the same time, rejection rates are high in
@@
 priority by making the work available as soon as it is complete. Some
-manuscripts will spend much more time in the review process and/or in
-production after acceptance, than others. This means that publication and
+manuscripts will spend much more time than others in the review process and/or in
+production after acceptance. This means that publication and
 acceptance dates do not accurately characterize who came up with an idea
@@
 opposite role, they allow straightforward establishment of precedence, letting
-research lay claim to an idea thus preventing it from being "stolen" \cite{gin11}
+research lay claim to an idea thus preventing it from being ``stolen'' \cite{gin11}
 
@@
 The Ecological Society of America and the Genetics Society of America recently
-changed their policies to allow public preprints. In fact, \emph{Nature}
+changed their policies to allow public preprints. \emph{Nature}
 responded to the rumour that they refused manuscripts submitted to arXiv by
@@
 biologists. Furthermore, by allowing all types of content, figshare also
-provides an archive for early results (e.g.: figures, lab presentations).
+provides an archive for early results (\emph{e.g.}: figures, lab presentations).
 
@@
 
-PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new Open Access
-publisher that combines both a preprint server, and a peer reviewed journal.  It
+PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new open access
+publisher that combines both a preprint server and a peer reviewed journal.  It
 is focused on the biological and medical sciences, which may help overcome the
@@
 reduces many of the benefits of preprints described above, it may allow some
-researchers who would not otherwise post preprints to begin to explore the
+researchers who would not otherwise post preprints to begin exploring the
 possibility in a manner appropriate to their current circumstances.
 
-In contrast to other preprint servers users cannot post unlimited public
+In contrast to other preprint servers, users cannot post unlimited public
 preprints for free. One preprint per year can be posted for free, with a onetime
@@
 
-\subsection{F1000Research}
+\subsection{F1000Research}\label{f1000r}
 
@@
 merge their changes into a master branch. This takes the preprint process to an
-entirely new level, where the entire writing process is open from the beginning.
+new level, where the entire writing process is open from the beginning.
 
@@
 pertinence and originality. Paradoxically, because peer-reviewing is conducted
-\emph{after} this step in the process of scientific communication, it might
-bring it closer to its fundamental objective. The role of peer-reviewing is to
-judge the scientific quality of a study. The peer review process is the first
-barrier against the fraudulent and poor quality science susceptible to impede
-scientific progress. Preprints are not filtered, neither for their quality nor
-their pertinence.  Technically, the difference between a preprint and a
-traditional publication should be that the latter as the approval stamp by pairs
-on its quality. The relevance of a study, its contribution to science, should
-only be judged post-publication by many more readers than the typical two-four
-anonymous reviewers. With a such a shift in the diffusion strategy, the role of
-traditional journals and their editors would be to showcase scientific
-discoveries for specialized readership. Such a process should improve even
-further their diffusion, not impede it.
+\emph{after} the manuscript is made public, preprint servers might bring it
+closer to its fundamental objective. The role of peer-reviewing is to judge the
+scientific quality of a study. It is the first barrier against the fraudulent
+and poor quality science susceptible to impede scientific progress. Preprints
+are not filtered, neither for their quality nor their pertinence.  Technically,
+the difference between a preprint and a traditional publication should be that
+the latter as the approval stamp by pairs on its quality. The relevance of a
+study, its contribution to science, should only be judged post-publication by
+many more readers than the typical two-four anonymous reviewers. With a such a
+shift in the diffusion strategy, the role of traditional journals and their
+editors would be to showcase scientific discoveries for specialized readership.
+Such a process should improve even further their diffusion, not impede it.
 

### 2012-10-18 ms.tex
finish editing

@@
 new blog discussing arXiv papers in population genetics, will help make arXiv
-attractive for scientists looking to promote their work \cite{lom12}. These initiatives are
-important to fully exploit the potential of open preprint servers. Posting
-preprints online increases the community of available informal peer reviewers,
-and uses the internet for its original community-building purposes.
+attractive for scientists looking to promote their work \cite{lom12}. These
+initiatives are important to fully exploit the potential of open preprint
+servers. Posting preprints online increases the community of available informal
+peer reviewers, and uses the internet for its original community-building
+purposes.
 
@@
 publication is seldom compatible with the pressure to show an impressive
-publication record when applying for a scholarship or a position. Increasing
-the perceived value of pre-prints as close, or equal, to journal articles 
-will allow young researchers to put their
-research outcome in the open, and build a reputation for themselves through
-the diffusion of their work without fear that this work will not be
-recognized by grant or job committees. In this perspective, mixed publication
-systems like F1000Research [\ref{f1000r}] should be encouraged as
-they combine the best of both worlds: contributions are initially considered
-preprints, but acquire full article status after positive reviews are
-received.
+publication record when applying for a scholarship or a position. Increasing the
+perceived value of pre-prints as close, or equal, to journal articles will allow
+young researchers to put their research outcome in the open, and build a
+reputation for themselves through the diffusion of their work without fear that
+this work will not be recognized by grant or job committees. In this
+perspective, mixed publication systems like F1000Research [\ref{f1000r}] should
+be encouraged as they combine the best of both worlds: contributions are
+initially considered preprints, but acquire full article status after positive
+reviews are received.
 
@@
 
-There are a number of reasons that biologists have not traditionally had a
-culture of sharing preprints, many of which are based on common misconceptions
-regarding the costs and benefits associated with the practice. For example, in contrast
-to other fields there is a perception in biology that public preprints
-make it easier to steal ideas. However, there is no evidence of this happening
-in the numerous other fields that have adopted preprint servers, and since preprint
-servers create a clear record of who had the idea first, and when, this
-appears to be a largely unfounded concern. In other fields preprints serve the
-opposite role, they allow straightforward establishment of precedence, letting
-research lay claim to an idea thus preventing it from being ``stolen'' \cite{gin11}
+There are a number of reasons why biologists did not develop the reflex of
+sharing preprints, many of which are based on common misconceptions. For
+example, in contrast to other fields there is a perception in biology that
+public preprints make it easier to steal ideas \cite{gin11}. However, there is
+no evidence of this happening in the numerous other fields that have adopted
+preprint servers, and since preprint servers create a clear record of who had
+the idea first, and when, this appears to be a largely unfounded concern. In
+other fields preprints serve the opposite role, they allow straightforward
+establishment of precedence, letting research lay claim to an idea thus
+preventing it from being ``stolen'' \cite{gin11}
 
-Another major concern is that if a researcher posts a public preprint that they
-will not be allowed to submit their paper to their journal of choice.  This is
-based on a certain interpretation of the Ingelfinger rule: scientists should not
-publish the same manuscript twice \cite{alt96}. A preprint is simply a document
-that allows ideas to spread and be discussed, it is not yet formally validated
-by the peer-review system. This is why the majority of publishers do not see
-arXiv and similar services as a violation of the Ingelfinger rule. Almost all of
-the major publishers in biology are preprint-friendly, including: Nature
-Publishing Group, PLOS, BMC, PNAS, Elsevier, and Springer \ref{table:policies}.
-The Ecological Society of America and the Genetics Society of America recently
-changed their policies to allow public preprints. \emph{Nature}
-responded to the rumour that they refused manuscripts submitted to arXiv by
-saying that ``\emph{Nature} never wishes to stand in the way of communication
-between researchers. We seek rather to add value for authors and the community
-at large in our peer review, selection and editing'' \cite{nat05}.  Still, a few
-journals adopt a ``by default'' hostile attitude towards preprints, mostly due
-to the lack of clear policy of the publishers, or perhaps because a preprint
-culture has not developed in biology and the practice is still considered
-unusual. As an example, Wiley-Blackwell, which publishes some of the leading
-journals in biology, has no official policy on the matter.
+Another major concern is based on a certain interpretation of the Ingelfinger
+rule: scientists should not publish the same manuscript twice \cite{alt96}. A
+preprint is simply a document that allows ideas to spread and be discussed, it
+is not yet formally validated by the peer-review system. This is why the
+majority of publishers do not see arXiv and similar services as a violation of
+the Ingelfinger rule. Almost all of the major publishers in biology are
+preprint-friendly, including: Nature Publishing Group, PLOS, BMC, PNAS,
+Elsevier, and Springer \ref{table:policies}. This year, both the Ecological
+Society of America and the Genetics Society of America changed their policies to
+allow public preprints. \emph{Nature} even felt compelled to respond to the
+rumour that they refused manuscripts submitted to arXiv by saying that
+``\emph{Nature} never wishes to stand in the way of communication between
+researchers. We seek rather to add value for authors and the community at large
+in our peer review, selection and editing'' \cite{nat05}.  Still, a few journals
+adopt a ``by default'' hostile attitude towards preprints, mostly due to the
+lack of clear policy of the publishers, or perhaps because a preprint culture
+has not developed in biology and the practice is still considered unusual. As an
+example, Wiley-Blackwell, which publishes some of the leading journals in
+biology, has no official policy on the matter.
 
@@
     \caption{Policies for important publishers in biology. Some publishers
-tolerate preprints except for a few of their medical journals, e.g.: Journal
-of the National Cancer Institute from Oxford and The Lancet from Elsevier.}
+tolerate preprints except for a few of their medical journals, for example the
+\emph{ Journal of the National Cancer Institute} from Oxford and \emph{The
+Lancet} from Elsevier.}
     \label{table:policies}
@@
 for theoretical high-energy physicists to communicate preprints via email and
-ftp, and soon thereafter adopted the newly created world-wide
-web \cite{jackson2002preprints}.  arXiv now receives over 7 000 submissions per
+ftp, and soon thereafter adopted the newly created world-wide web
+\cite{jackson2002preprints}.  arXiv now receives over 7 000 submissions per
 month (\url{http://arxiv.org/show_monthly_submissions}) and divides its
@@
 One aspect of arXiv that differs from other options is that it has a moderation
-system, which requires that papers must be categorized by an endorser.
-At least one author of a paper must be an endorser that has previously submitted
-a paper or has received permission to submit to a particular category. arXiv is now
+system, which requires that papers must be categorized by an endorser.  At least
+one author of a paper must be an endorser that has previously submitted a paper
+or has received permission to submit to a particular category. arXiv is now
 administered by the Cornell University Libraries, with funding coming from
 voluntary pledges by academic institutions along with matching funds from the
-Simons Foundation \cite{arxiv_future}. This approach to financing is one of
-the numerous measures that arXiv takes to ensure that the repository will remain
+Simons Foundation \cite{arxiv_future}. This approach to financing is one of the
+numerous measures that arXiv takes to ensure that the repository will remain
 permanently available and submissions will be readable.
@@
 preprints for free. One preprint per year can be posted for free, with a onetime
-(\emph{i.e.} lifetime) fee of 99 dollars required to allow an author to post unlimited
-public preprints. The preprint server is not tied to the journal, so preprints
-can be posted regardless of where they will eventually be submitted for
-publication.
+(\emph{i.e.} lifetime) fee of 99 dollars required to allow an author to post
+unlimited public preprints. The preprint server is not tied to the journal, so
+preprints can be posted regardless of where they will eventually be submitted
+for publication.
 
@@
 Whereas arXiv, figshare, and PeerJ offer an option to submit a manuscript
-without having it reviewed, papers submitted to F1000Research will eventually
-be reviewed. Thus, F1000Research offers a hybrid model with publicly available
+without having it reviewed, papers submitted to F1000Research will eventually be
+reviewed. Thus, F1000Research offers a hybrid model with publicly available
 manuscripts at time of submission and standard peer-reviews that occur as part
-of the submission process. Manuscripts are considered ``accepted'' and will
-only be indexed after two positive referee responses. F1000Research works
-closely with data providers to integrate raw data to the paper. For instance,
-upon submitting a paper, authors are asked to upload their data, which are then
+of the submission process. Manuscripts are considered ``accepted'' and will only
+be indexed after two positive referee responses. F1000Research works closely
+with data providers to integrate raw data to the paper. For instance, upon
+submitting a paper, authors are asked to upload their data, which are then
 integrated in \emph{e.g.} figshare widgets, the DOI of which are given in the
@@
 current publication process. However, It might significantly reduce its negative
-consequences. Preprint servers speed up publication and make no judgement on
-pertinence and originality. Paradoxically, because peer-reviewing is conducted
-\emph{after} the manuscript is made public, preprint servers might bring it
-closer to its fundamental objective. The role of peer-reviewing is to judge the
-scientific quality of a study. It is the first barrier against the fraudulent
-and poor quality science susceptible to impede scientific progress. Preprints
-are not filtered, neither for their quality nor their pertinence.  Technically,
-the difference between a preprint and a traditional publication should be that
-the latter as the approval stamp by pairs on its quality. The relevance of a
-study, its contribution to science, should only be judged post-publication by
-many more readers than the typical two-four anonymous reviewers. With a such a
-shift in the diffusion strategy, the role of traditional journals and their
-editors would be to showcase scientific discoveries for specialized readership.
-Such a process should improve even further their diffusion, not impede it.
+consequences. The role of peer-reviewing is to judge the scientific quality of a
+study. It is the first barrier against the fraudulent and poor quality science
+susceptible to impede scientific progress. In practice, the peer-review system
+is not only used to evaluate scientific quality but also to judge pertinence. On
+the other hand, preprints are not filtered, neither for their quality nor their
+pertinence. Widespread adoption of preprint servers has the potential to shift
+the diffusion strategy: journals would remain important to validate
+publications, but the relevance of a study, its contribution to science, should
+only be judged by many more readers than the typical two-four anonymous
+reviewers. With a shift in the diffusion strategy, the role of traditional
+journals and their editors would be to showcase scientific discoveries for
+specialized readership.
 
@@
 
-We thank Carl Boettiger, Mark Hahnel, and Hedvig Nenz\'en for helpful comments on an earlier
-version of this manuscript.
+We thank Carl Boettiger, Mark Hahnel, and Hedvig Nenz\'en for helpful comments
+on an earlier version of this manuscript.
 

### 2012-10-18 ms.tex
final final editing
Add ref to Haldane's sieve

@@
 the community embraces the idea of discussing preprints. Initiatives like
-Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
+Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}) \cite{coo12}, a
 new blog discussing arXiv papers in population genetics, will help make arXiv
@@
 in depth \cite{hoc09} and include a long delay between the time a manuscript is
-finished to its publication.  They all contribute somehow in a general slowing
-down of scientific progress.  Research activities and the publication process
-are drifting away from their fundamental object, namely the diffusion of novel
+finished to its publication.  They all contribute in a general slowing down of
+scientific progress.  Research activities and the publication process are
+drifting away from their fundamental object, namely the diffusion of novel
 scientific discoveries.
@@
 Developing a preprint culture in biology will not solve all problems with the
-current publication process. However, It might significantly reduce its negative
+current publication process. However, it might significantly reduce its negative
 consequences. The role of peer-reviewing is to judge the scientific quality of a

### 2012-10-21 ms.tex
rm arXiv from keywords
first commit

--- 2012-10-18 ms.tex
@@
-\documentclass[letterpaper,twocolumn,superscriptaddress,showkeys,longbibliography]{revtex4-1}
-\usepackage[utf8]{inputenc}
-\usepackage{color,dcolumn,graphicx,hyperref}
-\hypersetup
-{
-    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
-}
+% Template for PLoS
+% Version 1.0 January 2009
+%
+% To compile to pdf, run:
+% latex ms.tex
+% bibtex plos.template
+% latex plos.template
+% latex plos.template
+% dvipdf plos.template
+
+\documentclass[10pt]{article}
+
+% amsmath package, useful for mathematical formulas
+\usepackage{amsmath}
+% amssymb package, useful for mathematical symbols
+\usepackage{amssymb}
+
+% graphicx package, useful for including eps and pdf graphics
+% include graphics with the command \includegraphics
+\usepackage{graphicx}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+\usepackage{color}
+
+% Use doublespacing - comment out for single spacing
+\usepackage{setspace}
+\usepackage{hyperref} 
+\doublespacing
+
+% Text layout
+\topmargin 0.0cm
+\oddsidemargin 0.5cm
+\evensidemargin 0.5cm
+\textwidth 16cm 
+\textheight 21cm
+
+% Bold the 'Figure #' in the caption and separate it with a period
+% Captions will be left justified
+\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
+
+% Use the PLoS provided bibtex style
+\bibliographystyle{plos2009}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+%\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Leave date blank
+\date{}
+
+\pagestyle{myheadings}
+%% ** EDIT HERE **
+
+%% ** EDIT HERE **
+%% PLEASE INCLUDE ALL MACROS BELOW
+
+%% END MACROS SECTION
 
@@
 
-\title{Developing a preprint culture in biology}
+% Title must be 150 characters or less
+\begin{flushleft}
+{\Large
+\textbf{Developing a preprint culture in biology}
+}
+% Insert Author names, affiliations and corresponding author email.
+\\
+Philippe Desjardins-Proulx$^{1, 2,\ast}$, 
+Ethan P. White$^{3}$, 
+Joel J. Adamson$^{4}$,
+Karthik Ram$^{5}$,
+Timoth\'ee Poisot$^{1,2,6}$,
+Dominique Gravel$^{1,2}$
+\\
+\bf{1} Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Quebec, Canada.
+\\
+\bf{2} Quebec Center for Biodiversity Science, McGill University, Quebec, Canada.
+\\
+\bf{3} Departement of Bology, Utah State University, Utah, United-States of America.
+\\
+\bf{4} Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill, North Carolina, United-States of America
+\\
+\bf{5} Environmental Science, Policy, and Management. University of California, Berkeley, California, United-States of America.
+\\
+\bf{6} International Network for Next-Generation Ecology.
+\\
+$\ast$ E-mail: philippe.d.proulx@gmail.com
+\end{flushleft}
 
-\author{Philippe Desjardins-Proulx}
-\email[E-mail: ]{philippe.d.proulx@gmail.com}
-\affiliation{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
-\affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
-
-\author{Ethan P. White}
-\affiliation{Departement of Bology, Utah State University, United-States of America.}
-
-\author{Joel J. Adamson}
-\affiliation{Ecology, Evolution and Organismic Biology, University of North 
-Carolina at Chapel Hill, United-States of America}
-
-\author{Karthik Ram}
-\affiliation{Environmental Science, Policy, and Management. University of California, Berkeley, United-States of America.}
-
-\author{Timoth\'ee Poisot}
-\affiliation{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
-\affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
-\affiliation{International Network for Next-Generation Ecology.}
-
-\author{Dominique Gravel}
-\affiliation{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
-\affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
-
-\keywords{Publishing; Preprint servers; Green Open Access; arXiv.}
-
-\maketitle
-
-\section{Introduction}
+\section*{Introduction}
 
@@
 
-\section{The case for public preprints}
+\section*{The case for public preprints}
 
@@
 this work will not be recognized by grant or job committees. In this
-perspective, mixed publication systems like F1000Research [\ref{f1000r}] should
+perspective, mixed publication systems like F1000Research should
 be encouraged as they combine the best of both worlds: contributions are
@@
 
-\begin{figure}[ht!] \centering\includegraphics[width=0.50\textwidth]{map.pdf}
-\caption { It can take several months, and even a few years, before a submitted
-paper is officially published and citable.  The average time to publication
-varies greatly between journals and can be as low as 104 days (Evolution for
-2011) to 213 (PLOS One in 2010).  Meanwhile, few people are aware of the
-research that has been done since, typically, only close colleagues are given
-access to the preprints. With public preprint servers, the science is
-immediately available and can be openly discussed, analyzed, and integrated into
-current research. It benefits both science and publishers. Both want the papers
-to be well-known and cited, and public preprints make it possible to integrate
-research even before publication, greatly improving immediacy.  }
-\label{fig:map} \end{figure}
-
 Finally, public preprint servers offer a fair way to establish intellectual
@@
 
-\section{Preprints in biological sciences}
+\section*{Preprints in biological sciences}
 
@@
 
-\begin{table*}
-    \centering
-    \begin{tabular}{|ll|}
-    \hline
-    Publisher                                   & Policy \\
-    \hline
-    Springer                            	& Accept \\
-    BMC                                 	& Accept \\
-    Elsevier                            	& Accept \\
-    Nature Publishing Group             	& Accept \\
-    Public Library of Science           	& Accept \\
-    Genetics Society of America                 & Accept \\
-    Royal Society                       	& Accept \\
-    National Academy of Science (USA)           & Accept \\
-    Ecological Society of America       	& Accept \\
-    Oxford Journals                             & Accept \\
-    Science                             	& Ambiguous \\
-    Wiley-Blackwell                       	& No general policy \\
-    British Ecological Society                  & No answer to our query \\
-    \hline
-    \end{tabular}
-    \caption{Policies for important publishers in biology. Some publishers
-tolerate preprints except for a few of their medical journals, for example the
-\emph{ Journal of the National Cancer Institute} from Oxford and \emph{The
-Lancet} from Elsevier.}
-    \label{table:policies}
-\end{table*}
-
-\section{Current offerings}
+\section*{Current offerings}
 
@@
 
-\subsection{arXiv}
+\subsection*{arXiv}
 
@@
 
-\subsection{figshare}
+\subsection*{figshare}
 
@@
 
-\subsection{PeerJ}
+\subsection*{PeerJ}
 
@@
 
-\subsection{F1000Research}\label{f1000r}
+\subsection*{F1000Research}\label{f1000r}
 
@@
 
-\subsection{GitHub}
+\subsection*{GitHub}
 
@@
 
-\section{Conclusion}
+\section*{Conclusion}
 
@@
 
-\section{Funding}
+\section*{Funding}
 
@@
 DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
-scholarship and 25 cents found by a coffee machine.  KR is supported by NSF
+scholarship. KR is supported by NSF
 DEB-1021553. DG is funded by a Discovery Grand from the National Sciences and
@@
 
-\section{Acknowledgements}
+\section*{Acknowledgements}
 
@@
 
-\newpage
+\section*{References}
+% The bibtex filename
 \bibliography{refs}
 
+\newpage
+\section*{Figure Legends}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=4in]{map.eps}
+\end{center}
+\caption { {\bf It can take several months, and even a few years, before a submitted
+paper is officially published and citable.}  The average time to publication
+varies greatly between journals and can be as low as 104 days (Evolution for
+2011) to 213 (PLOS One in 2010).  Meanwhile, few people are aware of the
+research that has been done since, typically, only close colleagues are given
+access to the preprints. With public preprint servers, the science is
+immediately available and can be openly discussed, analyzed, and integrated into
+current research. It benefits both science and publishers. Both want the papers
+to be well-known and cited, and public preprints make it possible to integrate
+research even before publication, greatly improving immediacy.  }
+\label{fig:map}
+\end{figure}
+
+\newpage
+\section*{Tables}
+
+\begin{table}[!ht]
+    \caption{\bf{Policies for important publishers in biology.}}
+    \begin{tabular}{|ll|}
+    \hline
+    Publisher                                   & Policy \\
+    \hline
+    Springer                            	& Accept \\
+    BMC                                 	& Accept \\
+    Elsevier                            	& Accept \\
+    Nature Publishing Group             	& Accept \\
+    Public Library of Science           	& Accept \\
+    Genetics Society of America                 & Accept \\
+    Royal Society                       	& Accept \\
+    National Academy of Science (USA)           & Accept \\
+    Ecological Society of America       	& Accept \\
+    Oxford Journals                             & Accept \\
+    Science                             	& Ambiguous \\
+    Wiley-Blackwell                       	& No general policy \\
+    British Ecological Society                  & No answer to our query \\
+    \hline
+    \end{tabular}
+    \begin{flushleft}
+    Some publishers
+tolerate preprints except for a few of their medical journals, for example the
+\emph{ Journal of the National Cancer Institute} from Oxford and \emph{The
+Lancet} from Elsevier.
+    \end{flushleft}
+    \label{table:policies}
+\end{table}
+
 \end{document}

### 2012-10-21 ms.tex
small edits

@@
 % To compile to pdf, run:
-% latex ms.tex
-% bibtex plos.template
-% latex plos.template
-% latex plos.template
-% dvipdf plos.template
+% latex ms
+% bibtex ms
+% latex ms
+% latex ms
+% dvipdf ms
 
@@
 reputation for themselves through the diffusion of their work without fear that
-this work will not be recognized by grant or job committees. In this
-perspective, mixed publication systems like F1000Research should
-be encouraged as they combine the best of both worlds: contributions are
-initially considered preprints, but acquire full article status after positive
-reviews are received.
+this work will not be recognized by grant or job committees.
 
@@
 example, in contrast to other fields there is a perception in biology that
-public preprints make it easier to steal ideas \cite{gin11}. However, there is
-no evidence of this happening in the numerous other fields that have adopted
-preprint servers, and since preprint servers create a clear record of who had
-the idea first, and when, this appears to be a largely unfounded concern. In
-other fields preprints serve the opposite role, they allow straightforward
-establishment of precedence, letting research lay claim to an idea thus
-preventing it from being ``stolen'' \cite{gin11}
+public preprints make it easier to steal ideas \cite{gin11}. In other fields
+preprints serve the opposite role, they allow straightforward establishment of
+precedence, letting research lay claim to an idea thus preventing it from being
+``stolen'' \cite{gin11}
 
@@
 preprint is simply a document that allows ideas to spread and be discussed, it
-is not yet formally validated by the peer-review system. This is why the
-majority of publishers do not see arXiv and similar services as a violation of
-the Ingelfinger rule. Almost all of the major publishers in biology are
-preprint-friendly, including: Nature Publishing Group, PLOS, BMC, PNAS,
-Elsevier, and Springer \ref{table:policies}. This year, both the Ecological
-Society of America and the Genetics Society of America changed their policies to
-allow public preprints. \emph{Nature} even felt compelled to respond to the
-rumour that they refused manuscripts submitted to arXiv by saying that
-``\emph{Nature} never wishes to stand in the way of communication between
-researchers. We seek rather to add value for authors and the community at large
-in our peer review, selection and editing'' \cite{nat05}.  Still, a few journals
-adopt a ``by default'' hostile attitude towards preprints, mostly due to the
-lack of clear policy of the publishers, or perhaps because a preprint culture
-has not developed in biology and the practice is still considered unusual. As an
-example, Wiley-Blackwell, which publishes some of the leading journals in
-biology, has no official policy on the matter.
+is not yet formally validated by the peer-review system. This is why almost all
+the major publishers in biology are preprint-friendly, including: Nature
+Publishing Group, PLOS, BMC, PNAS, Elsevier, and Springer \ref{table:policies}.
+This year, both the Ecological Society of America and the Genetics Society of
+America changed their policies to allow public preprints. \emph{Nature} even
+felt compelled to respond to the rumour that they refused manuscripts submitted
+to arXiv by saying that ``\emph{Nature} never wishes to stand in the way of
+communication between researchers. We seek rather to add value for authors and
+the community at large in our peer review, selection and editing'' \cite{nat05}.
+Still, a few journals adopt a ``by default'' hostile attitude towards preprints,
+mostly due to the lack of clear policy of the publishers. As an example,
+Wiley-Blackwell, which publishes some of the leading journals in biology, has no
+official policy on the matter.
 
@@
 
-One of the advantages of figshare over arXiv for biologists is that is it not
-limited to quantitative sciences. arXiv.org has sections on quantitative biology
-but might not be appropriate for non-quantitative work. With its flexible
-approach to preprints, figshare offers an alternative to arXiv for empirical
-biologists. Furthermore, by allowing all types of content, figshare also
-provides an archive for early results (\emph{e.g.}: figures, lab presentations).
+Unlike arXiv, figshare is not limited to quantitative sciences. arXiv.org has
+sections on quantitative biology but might not be appropriate for
+non-quantitative work. With its flexible approach to preprints, figshare offers
+an alternative to arXiv for empirical biologists. Furthermore, by allowing all
+types of content, figshare also provides an archive for early results
+(\emph{e.g.}: figures, lab presentations).
 
@@
 is focused on the biological and medical sciences, which may help overcome the
-perception that preprints do not have a place in biology. Like figshare this is
-an advantage relative to arXiv for biologists doing non-quantitative work.  Also
-like figshare, PeerJ allows commenting on posted preprints, improving the
-potential for pre-publication dialog. In addition, preprints can be made private
-if the authors choose, and shared only with selected colleagues. While this
-reduces many of the benefits of preprints described above, it may allow some
-researchers who would not otherwise post preprints to begin exploring the
-possibility in a manner appropriate to their current circumstances.
+perception that preprints do not have a place in biology. Like figshare, PeerJ
+allows commenting on posted preprints, improving the potential for
+pre-publication dialog. In addition, preprints can be made private if the
+authors choose, and shared only with selected colleagues. While this reduces
+many of the benefits of preprints described above, it may allow some researchers
+who would not otherwise post preprints to begin exploring the possibility in a
+manner appropriate to their current circumstances.
 
@@
 since it provides a way to collaborate on every step of the manuscript
-development process, from data manipulation and analysis to writing and
-revision. For example, during the development of this manuscript, each author
-would clone the project (\emph{i.e.} make a personal copy), modify it, and then
-merge their changes into a master branch. This takes the preprint process to an
-new level, where the entire writing process is open from the beginning.
+development process. For example, during the development of this manuscript,
+each author would clone the project (\emph{i.e.} make a personal copy), modify
+it, and then merge their changes into a master branch. This takes the preprint
+process to an new level, where the entire writing process is open from the
+beginning.
 
@@
 DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
-scholarship. KR is supported by NSF
-DEB-1021553. DG is funded by a Discovery Grand from the National Sciences and
-Engineering Council of Canada and by the Canada Research Chair program.
+scholarship. KR is supported by NSF DEB-1021553. DG is funded by a Discovery
+Grand from the National Sciences and Engineering Council of Canada and by the
+Canada Research Chair program.
 
@@
 \caption { {\bf It can take several months, and even a few years, before a submitted
-paper is officially published and citable.}  The average time to publication
-varies greatly between journals and can be as low as 104 days (Evolution for
-2011) to 213 (PLOS One in 2010).  Meanwhile, few people are aware of the
+paper is officially published and citable.} Meanwhile, few people are aware of the
 research that has been done since, typically, only close colleagues are given
@@
 immediately available and can be openly discussed, analyzed, and integrated into
-current research. It benefits both science and publishers. Both want the papers
-to be well-known and cited, and public preprints make it possible to integrate
-research even before publication, greatly improving immediacy.  }
+current research. }
 \label{fig:map}
@@
     \end{tabular}
-    \begin{flushleft}
-    Some publishers
-tolerate preprints except for a few of their medical journals, for example the
-\emph{ Journal of the National Cancer Institute} from Oxford and \emph{The
-Lancet} from Elsevier.
-    \end{flushleft}
+    \begin{flushleft} Some publishers tolerate preprints except for a few of
+their medical journals, for example the \emph{ Journal of the National Cancer
+Institute} from Oxford and \emph{The Lancet} from Elsevier.  \end{flushleft}
     \label{table:policies}

### 2012-10-21 ms.tex
fix typo

--- 2012-10-18 ms.tex
@@
 
-\keywords{Publishing; Preprint servers; Green Open Access; arXiv.}
+\keywords{Publishing; Preprint servers; Green Open Access}
 
@@
 scholarship and 25 cents found by a coffee machine.  KR is supported by NSF
-DEB-1021553. DG is funded by a Discovery Grand from the National Sciences and
+DEB-1021553. DG is funded by a Discovery Grant from the National Sciences and
 Engineering Council of Canada and by the Canada Research Chair program.

### 2012-10-30 ms.tex
fix refs
fix typo in Ethan's address

--- 2012-10-21 ms.tex
@@
 \\
-\bf{3} Departement of Bology, Utah State University, Utah, United-States of America.
+\bf{3} Departement of Biology, Utah State University, Utah, United-States of America.
 \\
@@
 scholarship. KR is supported by NSF DEB-1021553. DG is funded by a Discovery
-Grand from the National Sciences and Engineering Council of Canada and by the
+Grant from the National Sciences and Engineering Council of Canada and by the
 Canada Research Chair program.

### 2013-01-24 ms.tex
commit rev 1

@@
 {\Large
-\textbf{Developing a preprint culture in biology}
+\textbf{The Case for Preprints in Biology}
 }
@@
 \\
-\bf{4} Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill, North Carolina, United-States of America
+\bf{4} Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill, North Carolina, United-States of America.
 \\
-\bf{5} Environmental Science, Policy, and Management. University of California, Berkeley, California, United-States of America.
+\bf{5} Environmental Science, Policy, and Management, University of California, Berkeley, California, United-States of America.
 \\
@@
 Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
-new blog discussing arXiv papers in population genetics, will help make arXiv
+new blog discussing arXiv papers in population genetics, can help make arXiv
 attractive for scientists looking to promote their work \cite{lom12}. These
@@
 ago. In fact, it had more or less fallen apart by the early 80s} \cite{kru12}.
-In addition to a section in arXiv, economists have the RePEc (Research Papers in
+In addition to a section on arXiv, economists have the RePEc (Research Papers in
 Economics) initiative, which aims to create an archive of working papers,
@@
 publishers; 2) discuss the preprint policies of major publishers in biology; and
-3) review the most popular preprint servers currently available.
+3) review popular options to submit preprints.
 
@@
 
-The first and most often discussed advantage of arXiv and open preprints is
+The first and most often discussed advantage of open preprints is
 speed (Figure~\ref{fig:map}). The time between submission and the official
@@
 
-Posting manuscripts as preprints also has the potential to result in higher
-quality science by allowing prepublication feedback from a large pool of
-reviewers. Prepublication reviews by a small network of colleagues are common in
-the biological sciences and form an important part of the scientific process.
-These ``friendly'' reviews increases the chances of errors being caught prior to
-publication. Furthermore, the formal peer-review process as a whole is
-critically over-loaded. As the number of active scientists increases and the
-pressure to publish increases, it is becoming difficult for journals
-to find reviewers \cite{hoc09}.  At the same time, rejection rates are high in
-most journals \cite{aar08,roh09}, and when not invited to submit a revision,
-authors must start the process over again at another journal. As a result,
-initiatives to reduce time from submission to publication have emerged across
-the scientific community. Rohr et al.  \cite{roh09} called for the recycling and
-reuse of peer-reviews: by attaching previous reviews and detailed replies to a
-new submission, both the editor and the referees can gauge the work done on the
-manuscript, and perhaps evaluate it with less prejudice. A widespread use of
-preprint servers can achieve the same goal of reducing the time spent in review.
-With a rich enough community of scientists depositing preprints, and commenting
+Posting manuscripts as preprints also has the potential to improve the 
+quality of science by allowing prepublication feedback from a large pool of 
+reviewers. In our experience, prepublication reviews by a small network of 
+colleagues are common in the biological sciences and form an important part 
+of the scientific process. These ``friendly'' reviews increases the chances 
+of errors being caught prior to publication. Furthermore, the formal 
+peer-review process as a whole is critically over-loaded. As the number of 
+active scientists increases and the pressure to publish increases, it is 
+becoming difficult for journals to find reviewers \cite{hoc09}.  At the same 
+time, rejection rates are high in most journals \cite{aar08,roh09}, and when 
+not invited to submit a revision, authors must start the process over again 
+at another journal. As a result, initiatives to reduce time from submission 
+to publication have emerged across the scientific community. Rohr et al.  
+\cite{roh09} called for the recycling and reuse of peer-reviews: by 
+attaching previous reviews and detailed replies to a new submission, both 
+the editor and the referees can gauge the work done on the manuscript, and 
+perhaps evaluate it with less prejudice. A widespread use of preprint 
+servers can achieve the same goal of reducing the time spent in review. With 
+a rich enough community of scientists depositing preprints, and commenting 
 on them, the process of an open pre-review can become widespread and will 
@@
 preprint culture, with the exception of small pockets of primarily highly
-quantitative research (\emph{e.g.}, epidemiology, population genetics).
-Submitting to preprint servers has become more common in the past few years,
-and the quantitative biology section in arXiv is experiencing the fastest
-growth in submissions \cite{cal12}. Yet, the number of biology papers
-submitted to preprint servers still represents only a small fraction of the
-total research produced in biology.
+quantitative research (\emph{e.g.}, epidemiology, population genetics).  While
+submitting to preprint servers has become more common in the past few years, the
+number of biology papers submitted to preprint servers still represents only a
+small fraction of the total research produced in biology (Fig.~\ref{arxiv}).
 
@@
 
-We briefly discuss the main options to submit preprints to open servers:
+We briefly discuss several options to submit preprints to open servers:
 arXiv.org, figshare, and the upcoming PeerJ and F1000Research.
@@
 and its use is almost universal in some branches of mathematics and physics.
-arXiv provides a reliable citation system for all eprints and is especially
-popular in high-energy physics. Physicist Paul Ginsparg created arXiv in 1991
-for theoretical high-energy physicists to communicate preprints via email and
-ftp, and soon thereafter adopted the newly created world-wide web
-\cite{jackson2002preprints}.  arXiv now receives over 7 000 submissions per
-month (\url{http://arxiv.org/show_monthly_submissions}) and divides its
-submissions into subcategories of physics, mathematics, computer science,
-quantitative biology, finance and statistics.  The quantitative biology category
-includes subcategories for Populations and Evolution, Quantitative Methods and
-other categories that may be of interest to biologists.
+arXiv provides a reliable citation system for all eprints. Physicist Paul
+Ginsparg created arXiv in 1991 for theoretical high-energy physicists to
+communicate preprints via email and ftp, and soon thereafter adopted the newly
+created world-wide web \cite{jackson2002preprints}.  arXiv now receives over 7
+000 submissions per month (\url{http://arxiv.org/show_monthly_submissions}) and
+divides its submissions into subcategories of physics, mathematics, computer
+science, quantitative biology, finance and statistics.  The quantitative biology
+category includes subcategories for Populations and Evolution, Quantitative
+Methods and other categories that may be of interest to biologists.
 
-One aspect of arXiv that differs from other options is that it has a moderation
-system, which requires that papers must be categorized by an endorser.  At least
-one author of a paper must be an endorser that has previously submitted a paper
-or has received permission to submit to a particular category. arXiv is now
-administered by the Cornell University Libraries, with funding coming from
-voluntary pledges by academic institutions along with matching funds from the
-Simons Foundation \cite{arxiv_future}. This approach to financing is one of the
-numerous measures that arXiv takes to ensure that the repository will remain
-permanently available and submissions will be readable.
+Unlike the other options presented here, arXiv has a system of moderators 
+and endorsors. At least one author of a paper must be an endorser that has 
+previously submitted a paper or has received permission to submit. 
+Moderators have the power to change the classification of a paper. 
+arXiv is now administered by the Cornell University Libraries, with funding 
+coming from voluntary pledges by academic institutions along with matching 
+funds from the Simons Foundation \cite{arxiv_future}. This approach to 
+financing is one of the numerous measures that arXiv takes to ensure that 
+the repository will remain permanently available and submissions will be 
+readable.
 
@@
 
+\subsection*{Other options}
+
+Scientific publishing is more diversified than ever and there are many
+alternative options to submit articles before formal publications. 
+Social networks such as ResearchGate can be used to submit preprints
+\cite{lin12}. Also, if GitHub pushes openness further by opening the writing process,
+open notebooks go even further by opening the entire scientific process
+\cite{san11}.
+
 \section*{Conclusion}
@@
 The ongoing discussions on the publication process, peer-reviewing and
-alternative publication models are all symptoms of the current uneasiness of
-scientists with the ever growing obsession with bibliographic metrics such as
-the impact factor \cite{Fisher2012}. There is pressure on researchers to orient
-their publication strategy in order to maximize their number of publications and
+alternative publication models are all symptoms of the current uneasiness
+with the ever growing obsession with bibliographic metrics such as
+the impact factor \cite{Fisher2012}. Researchers are pressured to orient
+their publication strategy to maximize their number of publications and
 total citations. A well-known consequence is to submit manuscripts first to the
@@
 in depth \cite{hoc09} and include a long delay between the time a manuscript is
-finished to its publication.  They all contribute somehow in a general slowing
-down of scientific progress.  Research activities and the publication process
+finished to its publication. Research activities and the publication process
 are drifting away from their fundamental object, namely the diffusion of novel
@@
 the diffusion strategy: journals would remain important to validate
-publications, but the relevance of a study, its contribution to science, should
+publications, but the relevance of a study should
 only be judged by many more readers than the typical two-four anonymous
@@
 
-One of drawback of making publication easier is the proliferation of studies of
-uneven quality. A trade-off between the intensity of the peer-review filtering
-and the benefits to science has been hypothesized \cite{Aarssen2012}.  With
-increasingly stringent peer reviewing, the quality of published papers and
-easiness of finding discoveries might increase, at the cost of censorship, an
-increased load on authors and reviewers, and greater delays for publication.
-Preprints are simply bypassing this model for what we believe is the progress of
-science: they speed up the dissemination of scientific discoveries, impede
-censorship and put on reader's shoulders the responsibility to judge originality
-and pertinence.
+Making publication easier can lead to the proliferation of studies of uneven
+quality. A trade-off between the intensity of the peer-review filtering and the
+benefits to science has been hypothesized \cite{Aarssen2012}.  With increasingly
+stringent peer reviewing, the quality of published papers can improve at the
+cost of censorship, an increased load on authors and reviewers, and greater
+delays for publication.  Preprints are simply bypassing this model for what we
+believe is the progress of science: they speed up the dissemination of
+scientific discoveries and put on reader's shoulders the responsibility to judge
+originality and pertinence.
 
@@
 
-We thank Carl Boettiger, Mark Hahnel, and Hedvig Nenz\'en for helpful comments
-on an earlier version of this manuscript.
+We dedicate this article to Aaron H. Swartz (1986-2013).  We thank Carl
+Boettiger, Mark Hahnel, and Hedvig Nenz\'en for helpful comments on an earlier
+version of this manuscript.
 
 \section*{References}
-% The bibtex filename
 \bibliography{refs}
@@
 \end{center}
-\caption { {\bf It can take several months, and even a few years, before a submitted
-paper is officially published and citable.} Meanwhile, few people are aware of the
-research that has been done since, typically, only close colleagues are given
-access to the preprints. With public preprint servers, the science is
-immediately available and can be openly discussed, analyzed, and integrated into
-current research. }
+\caption { {\bf It can take several months before a submitted paper is
+officially published and citable.} Meanwhile, few people are aware of the
+research that has been done since, typically, only close colleagues are
+given access to the preprints. With public preprint servers, the science is
+immediately available and can be openly discussed, analyzed, and integrated
+into current research. }
 \label{fig:map}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=4in]{figure_2.png}
+\end{center}
+\caption { Submissions to the quantitative biology section lag behind
+physics, mathematics, and computer science.
+}
+\label{fig:arxiv}
 \end{figure}

### 2013-01-26 ms.tex
add figure

@@
 figshare (\href{http://figshare.com}{http://figshare.com}) is an open server
-that allows scientists to submit any research output: manuscript, figures,
+allowing scientists to submit any research output: manuscript, figures,
 datasets, videos, theses, presentations, and so on. There are no rules to limit

### 2013-01-26 ms.tex
fix figure

@@
 number of biology papers submitted to preprint servers still represents only a
-small fraction of the total research produced in biology (Fig.~\ref{arxiv}).
+small fraction of the total research produced in biology (Fig.~\ref{fig:arxiv}).
 
@@
 \begin{center}
-\includegraphics[width=4in]{figure_2.png}
+\includegraphics[width=4in]{figure_2.eps}
 \end{center}

### 2013-01-26 arxiv_figure/figure.R
switched figure to eps as requested by PhDP

@@ -2,7 +2,7 @@ library(plyr)
 library(reshape2)
 library(ggplot2)
 library(RColorBrewer)
-# setwd('~/Desktop/Outbox/article_preprint/arxiv_figure/')
+setwd('~/Desktop/article_preprint/arxiv_figure/')
 # year,astronomy_and_astrophysics biology computer_science condensed_matter finance high-energy_physics mathematics other_physics statistics TOTAL
 yearly <- read.csv('submissions_by_area_by_year_to_2011.dat', header = F)
 yearly <- yearly[, -ncol(yearly)]
@@ -27,4 +27,4 @@ pcolor[9] <- "#d53d4e"
 
 figure_2 <-  ggplot(cleaned_df[complete.cases(cleaned_df),], aes(year, value, group = variable,color = variable)) + geom_line() + geom_line(aes(linetype = shape), size = 1, show_guide = FALSE) + expand_limits(0,0) + labs(y="Cumulative submissions", x="Year") + ggtitle("arXiv submissions by discipline") + guides(colour = guide_legend(title = "Disciplines", title.hjust = 0.5, keywidth = 1, keyheight = 1, override.aes = list(size = 4))) + scale_color_manual(values = pcolor,  name = "Discipline") + theme_gray()
 
-ggsave(figure_2, file = "figure_2.png", width = 6, height = 4)
+ggsave(figure_2, file = "figure_2.eps", width = 6, height = 4)

### 2013-01-27 ms.tex
minor

@@
 
-Scientific publishing is more diversified than ever and there are many
-alternative options to submit articles before formal publications. 
-Social networks such as ResearchGate can be used to submit preprints
-\cite{lin12}. Also, if GitHub pushes openness further by opening the writing process,
-open notebooks go even further by opening the entire scientific process
-\cite{san11}.
+Scientific publishing is more diversified than ever. There are now many 
+alternative options to submit articles before formal publications. For 
+example, social networks such as ResearchGate can be used to submit 
+preprints \cite{lin12}. Also, if GitHub pushes openness further by opening 
+the writing process, open notebooks go even further by opening the entire 
+scientific process \cite{san11}.
 
@@
 alternative publication models are all symptoms of the current uneasiness 
-with the ever growing obsession with bibliographic metrics such as
-the impact factor \cite{Fisher2012}. Researchers are pressured to orient
-their publication strategy to maximize their number of publications and
-total citations. A well-known consequence is to submit manuscripts first to the
-most prestigious journals, and then resubmit to ``lower level'' journals as they
-are rejected. The numerous negative impacts of such behavior have been discussed
-in depth \cite{hoc09} and include a long delay between the time a manuscript is
-finished to its publication. Research activities and the publication process
-are drifting away from their fundamental object, namely the diffusion of novel
-scientific discoveries.
+with the ever growing obsession with bibliographic metrics such as the 
+impact factor \cite{Fisher2012}. Researchers are pressured to orient their 
+publication strategy to maximize their number of publications and total 
+citations. A well-known consequence is to submit manuscripts first to the 
+most prestigious journals, and then resubmit to ``lower level'' journals as 
+they are rejected. The numerous negative impacts of such behavior have been 
+discussed in depth \cite{hoc09} and include a long delay between the time a 
+manuscript is finished to its publication. Research activities and the 
+publication process are drifting away from their fundamental object, namely 
+the diffusion of novel scientific discoveries.
 
-Developing a preprint culture in biology will not solve all problems with the
-current publication process. However, it might significantly reduce its negative
-consequences. The role of peer-reviewing is to judge the scientific quality of a
-study. It is the first barrier against the fraudulent and poor quality science
-susceptible to impede scientific progress. In practice, the peer-review system
-is not only used to evaluate scientific quality but also to judge pertinence. On
-the other hand, preprints are not filtered, neither for their quality nor their
-pertinence. Widespread adoption of preprint servers has the potential to shift
-the diffusion strategy: journals would remain important to validate
-publications, but the relevance of a study should
-only be judged by many more readers than the typical two-four anonymous
-reviewers. With a shift in the diffusion strategy, the role of traditional
-journals and their editors would be to showcase scientific discoveries for
-specialized readership.
+Developing a preprint culture in biology will not solve all problems with 
+the current publication process. However, it might significantly reduce its 
+negative consequences. The role of peer-reviewing is to judge the scientific 
+quality of a study. It is the first barrier against the fraudulent and poor 
+quality science susceptible to impede scientific progress. In practice, the 
+peer-review system is not only used to evaluate scientific quality but also 
+to judge pertinence. On the other hand, preprints are not filtered, neither 
+for their quality nor their pertinence. Widespread adoption of preprint 
+servers has the potential to shift the diffusion strategy: journals would 
+remain important to validate publications, but the relevance of a study 
+should only be judged by many more readers than the typical two-four 
+anonymous reviewers. With a shift in the diffusion strategy, the role of 
+traditional journals and their editors would be to showcase scientific 
+discoveries for specialized readership.
 
 Making publication easier can lead to the proliferation of studies of uneven 
-quality. A trade-off between the intensity of the peer-review filtering and the
-benefits to science has been hypothesized \cite{Aarssen2012}.  With increasingly
-stringent peer reviewing, the quality of published papers can improve at the
-cost of censorship, an increased load on authors and reviewers, and greater
-delays for publication.  Preprints are simply bypassing this model for what we
-believe is the progress of science: they speed up the dissemination of
-scientific discoveries and put on reader's shoulders the responsibility to judge
-originality and pertinence.
+quality. A trade-off between the intensity of the peer-review filtering and 
+the benefits to science has been hypothesized \cite{Aarssen2012}.  With 
+increasingly stringent peer reviewing, the quality of published papers can 
+improve at the cost of censorship, an increased load on authors and 
+reviewers, and greater delays for publication.  Preprints are simply 
+bypassing this model for what we believe is the progress of science: they 
+speed up the dissemination of scientific discoveries and put on reader's 
+shoulders the responsibility to judge originality and pertinence.
 

### 2013-02-25 ms.tex
rev following Dr. Gross' email

@@
 {\Large
-\textbf{The Case for Preprints in Biology}
+\textbf{The Case for Open Preprints in Biology}
 }
@@
 
-\section*{Current offerings}
+\section*{Box: Preprint Server Roundup}
 
-We briefly discuss several options to submit preprints to open servers:
-arXiv.org, figshare, and the upcoming PeerJ and F1000Research.
+% Table 2 should start here.
 
@@
 and its use is almost universal in some branches of mathematics and physics.
-arXiv provides a reliable citation system for all eprints. Physicist Paul
-Ginsparg created arXiv in 1991 for theoretical high-energy physicists to
-communicate preprints via email and ftp, and soon thereafter adopted the newly
-created world-wide web \cite{jackson2002preprints}.  arXiv now receives over 7
-000 submissions per month (\url{http://arxiv.org/show_monthly_submissions}) and
-divides its submissions into subcategories of physics, mathematics, computer
-science, quantitative biology, finance and statistics.  The quantitative biology
-category includes subcategories for Populations and Evolution, Quantitative
-Methods and other categories that may be of interest to biologists.
-
-Unlike the other options presented here, arXiv has a system of moderators 
-and endorsors. At least one author of a paper must be an endorser that has 
-previously submitted a paper or has received permission to submit. 
-Moderators have the power to change the classification of a paper. 
-arXiv is now administered by the Cornell University Libraries, with funding 
-coming from voluntary pledges by academic institutions along with matching 
-funds from the Simons Foundation \cite{arxiv_future}. This approach to 
-financing is one of the numerous measures that arXiv takes to ensure that 
-the repository will remain permanently available and submissions will be 
-readable.
+arXiv has a system of moderators and endorsers. At least one author of a paper
+must be an endorser that has previously submitted a paper or has received
+permission to submit.  Moderators have the power to change the classification of
+a manuscript.
 
@@
 what constitutes a research output and, unlike arXiv, there is no endorser
-system. All figshare content has a unique digital object identifier (DOI) like
-any journal article, thus offering a permanent and stable link to the content.
-A flexible tag system is used to classify each item. Comments can be made on all
-content allowing for centralized discussion related to the material.
-
-Unlike arXiv, figshare is not limited to quantitative sciences. arXiv.org has
-sections on quantitative biology but might not be appropriate for
-non-quantitative work. With its flexible approach to preprints, figshare offers
-an alternative to arXiv for empirical biologists. Furthermore, by allowing all
-types of content, figshare also provides an archive for early results
-(\emph{e.g.}: figures, lab presentations).
+system. A flexible tag system is used to classify each item.
 
@@
 
-PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new open access
-publisher that combines both a preprint server and a peer reviewed journal.  It
-is focused on the biological and medical sciences, which may help overcome the
-perception that preprints do not have a place in biology. Like figshare, PeerJ
-allows commenting on posted preprints, improving the potential for
-pre-publication dialog. In addition, preprints can be made private if the
-authors choose, and shared only with selected colleagues. While this reduces
-many of the benefits of preprints described above, it may allow some researchers
-who would not otherwise post preprints to begin exploring the possibility in a
-manner appropriate to their current circumstances.
-
-In contrast to other preprint servers, users cannot post unlimited public
-preprints for free. One preprint per year can be posted for free, with a onetime
-(\emph{i.e.} lifetime) fee of 99 dollars required to allow an author to post
-unlimited public preprints. The preprint server is not tied to the journal, so
-preprints can be posted regardless of where they will eventually be submitted
-for publication.
+PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new commercial open
+access publisher that combines both a preprint server and a peer reviewed
+journal. Preprints can be made private and shared only with selected colleagues.
+Only one preprint per year can be posted for free, with a onetime (\emph{i.e.}
+lifetime) fee required to allow an author to post unlimited public preprints.
+Preprints can be posted to PeerJ regardless of where they will eventually be
+submitted for publication.
 
@@
 
-F1000Research is not a public preprint server like the previous three servers.
 Whereas arXiv, figshare, and PeerJ offer an option to submit a manuscript
@@
 of the submission process. Manuscripts are considered ``accepted'' and will only
-be indexed after two positive referee responses. F1000Research works closely
-with data providers to integrate raw data to the paper. For instance, upon
-submitting a paper, authors are asked to upload their data, which are then
-integrated in \emph{e.g.} figshare widgets, the DOI of which are given in the
-paper when the data are first mentioned.  By integrating data to the paper,
-F1000Research is working to make science more reproducible and open.
+be indexed after two positive referee responses.
 
@@
 one of several hosting services for collaborative development using the Git
-version control system (VCS).  Git is a decentralized revision control system
-created by Linus Torvalds and is used primarily to develop software, including
-the Linux kernel. Git provides powerful features that allow numerous
-contributers to work asynchronously on the same project, often in parallel
-branches, all of which can be effortlessly merged and version controlled.  While
-Git is created primarily for software development, where the use of version
-control systems is standard \cite{aru12}, it is ideal for academic research
-since it provides a way to collaborate on every step of the manuscript
-development process. For example, during the development of this manuscript,
-each author would clone the project (\emph{i.e.} make a personal copy), modify
-it, and then merge their changes into a master branch. This takes the preprint
-process to an new level, where the entire writing process is open from the
-beginning.
+version control system (VCS). It allows numerous contributers to work
+asynchronously on the same project, often in parallel branches, all of which can
+be effortlessly merged and version controlled.  Git is primarily used for
+software development \cite{aru12} but it provides a powerful tool way to
+collaborate on every step of the manuscript development process.
 
@@
 
+\section*{Competing interests}
+
+DG is an associate falculty of F1000, EW is an academic editor for PeerJ, and TP
+is an advisor for figshare.
+
 \section*{References}
@@
 
+\begin{table}[!ht]
+    \caption{\bf{Popular options for preprints}}}
+    \begin{tabular}{|l|cccccccc|}
+    \hline
+    Website               & Free & Comments & Private preprints & Moderated & Peer-reviewed & DOI & Version-Control & Other Content\\
+    \hline
+    arXiv.org             & Yes & No & No & Yes & No & No & No & No\\
+    figshare.com          & Yes & Yes & No & No & No & Yes & No & Yes\\
+    peerj.com             & No & Yes & Yes & No & No & Yes & No & No\\
+    f1000research.com     & No & Yes & No & Yes & Yes & Yes & No & No\\
+    github.com            & Yes & Yes & Yes & No & No & No & Yes & Yes\\
+    \hline
+    \end{tabular}
+    \label{table:box1}
+\end{table}
+
 \end{document}

### 2013-02-26 ms.tex
fix compilation issue;
Revising PeerJ box section to include biology focus

@@
 PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new commercial open
-access publisher that combines both a preprint server and a peer reviewed
-journal. Preprints can be made private and shared only with selected colleagues.
-Only one preprint per year can be posted for free, with a onetime (\emph{i.e.}
-lifetime) fee required to allow an author to post unlimited public preprints.
-Preprints can be posted to PeerJ regardless of where they will eventually be
-submitted for publication.
+access publisher that provides a preprint server and a peer reviewed journal. It
+is focused on the biological sciences, which may counter the perception that
+preprints do not have a place in biology. Preprints can optionally be made
+private.  One preprint per year can be posted for free, with a onetime
+(\emph{i.e.}  lifetime) fee for unlimited public preprints. Preprints can be
+posted to PeerJ regardless of where they will be submitted for publication.
 
@@
 \begin{table}[!ht]
-    \caption{\bf{Popular options for preprints}}}
+    \caption{\bf{Popular options for preprints}}
     \begin{tabular}{|l|cccccccc|}

### 2013-02-26 ms.tex

@@
     figshare.com          & Yes & Yes & No & No & No & Yes & No & Yes\\
-    peerj.com             & No & Yes & Yes & No & No & Yes & No & No\\
+    peerj.com             & 1/yr & Yes & Yes & No & No & Yes & No & No\\
     f1000research.com     & No & Yes & No & Yes & Yes & Yes & No & No\\

### 2013-02-26 ms.tex
Some minor editorial work

@@
 colleagues are common in the biological sciences and form an important part 
-of the scientific process. These ``friendly'' reviews increases the chances 
+of the scientific process. These ``friendly'' reviews increase the chance 
 of errors being caught prior to publication. Furthermore, the formal 
@@
 
-There are a number of reasons why biologists did not develop the reflex of
+There are a number of reasons why biologists have not developed a culture of
 sharing preprints, many of which are based on common misconceptions. For
@@
 precedence, letting research lay claim to an idea thus preventing it from being
-``stolen'' \cite{gin11}
-
-Another major concern is based on a certain interpretation of the Ingelfinger
+``stolen'' \cite{gin11}. Another major concern is based on a certain
+interpretation of the Ingelfinger
 rule: scientists should not publish the same manuscript twice \cite{alt96}. A
@@
 arXiv has a system of moderators and endorsers. At least one author of a paper
-must be an endorser that has previously submitted a paper or has received
+must be an endorser that has either previously submitted a paper or has received
 permission to submit.  Moderators have the power to change the classification of
@@
 
-The ongoing discussions on the publication process, peer-reviewing and 
-alternative publication models are all symptoms of the current uneasiness 
-with the ever growing obsession with bibliographic metrics such as the 
-impact factor \cite{Fisher2012}. Researchers are pressured to orient their 
-publication strategy to maximize their number of publications and total 
-citations. A well-known consequence is to submit manuscripts first to the 
-most prestigious journals, and then resubmit to ``lower level'' journals as 
-they are rejected. The numerous negative impacts of such behavior have been 
-discussed in depth \cite{hoc09} and include a long delay between the time a 
-manuscript is finished to its publication. Research activities and the 
-publication process are drifting away from their fundamental object, namely 
-the diffusion of novel scientific discoveries.
+The ongoing discussions on the scientific publication process, peer-review and
+alternative publication models are all symptoms of the current uneasiness with
+the ever growing obsession with bibliographic metrics such as the impact factor
+\cite{Fisher2012}. Researchers are pressured to orient their publication
+strategy to maximize their number of publications and total citations. A
+well-known consequence is the initial submition of manuscripts to the most
+prestigious journals, followed by resubmission to progressively ``lower level''
+journals as they are rejected. The numerous negative impacts of such behavior
+have been discussed in depth \cite{hoc09} and include a long delay between the
+time a manuscript is finished and its publication. Research activities and the
+publication process are drifting away from their fundamental objective, namely
+the distribution of novel scientific discoveries.
 
-Developing a preprint culture in biology will not solve all problems with 
-the current publication process. However, it might significantly reduce its 
-negative consequences. The role of peer-reviewing is to judge the scientific 
+Developing a preprint culture in biology will not solve all of the problems with
+the current publication process. However, it might significantly reduce the
+negative consequences. The role of peer-review is to judge the scientific
 quality of a study. It is the first barrier against the fraudulent and poor
-quality science susceptible to impede scientific progress. In practice, the 
-peer-review system is not only used to evaluate scientific quality but also 
-to judge pertinence. On the other hand, preprints are not filtered, neither 
-for their quality nor their pertinence. Widespread adoption of preprint 
-servers has the potential to shift the diffusion strategy: journals would 
-remain important to validate publications, but the relevance of a study 
-should only be judged by many more readers than the typical two-four 
-anonymous reviewers. With a shift in the diffusion strategy, the role of 
-traditional journals and their editors would be to showcase scientific 
-discoveries for specialized readership.
+quality science that could impede scientific progress. In practice, the
+peer-review system is not only used to evaluate scientific quality but also to
+judge pertinence. On the other hand, preprints are not filtered on either
+quality or pertinence. Widespread adoption of preprint servers has the potential
+to shift the distribution strategy: journals would remain important to validate
+publications, but the relevance of a study should only be judged by many more
+readers than the typical two to four anonymous reviewers. With a shift in the
+diffusion strategy, the role of traditional journals and their editors would be
+to showcase scientific discoveries for specialized readership.
 
@@
 the benefits to science has been hypothesized \cite{Aarssen2012}.  With 
-increasingly stringent peer reviewing, the quality of published papers can 
-improve at the cost of censorship, an increased load on authors and 
-reviewers, and greater delays for publication.  Preprints are simply 
-bypassing this model for what we believe is the progress of science: they 
+increasingly stringent peer review, the quality of published papers can 
+improve at the cost of an increased load on authors and 
+reviewers, and greater delays for publication.  By
+bypassing this model preprints 
 speed up the dissemination of scientific discoveries and put on reader's 

### 2013-02-26 ms.tex
Fixing spelling error

@@
 strategy to maximize their number of publications and total citations. A
-well-known consequence is the initial submition of manuscripts to the most
+well-known consequence is the initial submission of manuscripts to the most
 prestigious journals, followed by resubmission to progressively ``lower level''

### 2013-02-26 ms.tex

@@
 \cite{Fisher2012}. Researchers are pressured to orient their publication
-strategy to maximize their number of publications and total citations. A
+strategy to maximize their number of publications in top journals and total citations. A
 well-known consequence is the initial submission of manuscripts to the most
@@
 negative consequences. The role of peer-review is to judge the scientific
-quality of a study. It is the first barrier against the fraudulent and poor
-quality science that could impede scientific progress. In practice, the
-peer-review system is not only used to evaluate scientific quality but also to
-judge pertinence. On the other hand, preprints are not filtered on either
-quality or pertinence. Widespread adoption of preprint servers has the potential
-to shift the distribution strategy: journals would remain important to validate
+quality of a study. It is the first barrier against fraudulent and poor quality
+science that could impede scientific progress. In practice, the peer-review
+system is not only used to evaluate scientific quality but also to judge
+pertinence. In contrast, preprints are not filtered based on either quality or
+pertinence. Widespread adoption of preprint servers has the potential to shift
+the distribution strategy: journals would remain important for validating
 publications, but the relevance of a study should only be judged by many more

### 2013-02-26 ms.tex
Softening on the Conclusions intended to make the paper more generally appealing

@@
 \cite{Fisher2012}. Researchers are pressured to orient their publication
-strategy to maximize their number of publications in top journals and total citations. A
-well-known consequence is the initial submission of manuscripts to the most
-prestigious journals, followed by resubmission to progressively ``lower level''
-journals as they are rejected. The numerous negative impacts of such behavior
-have been discussed in depth \cite{hoc09} and include a long delay between the
-time a manuscript is finished and its publication. Research activities and the
-publication process are drifting away from their fundamental objective, namely
-the distribution of novel scientific discoveries.
+strategy to maximize their number of publications in top journals and total
+citations. A well-known consequence is the initial submission of manuscripts to
+the most prestigious journals, followed by resubmission to progressively ``lower
+level'' journals as they are rejected. The numerous negative impacts of such
+behavior have been discussed in depth \cite{hoc09} and include a long delay
+between the time a manuscript is finished and its publication. Research
+activities and the publication process are drifting away from their fundamental
+objective, namely the distribution of novel scientific discoveries.
 
@@
 pertinence. Widespread adoption of preprint servers has the potential to shift
-the distribution strategy: journals would remain important for validating
-publications, but the relevance of a study should only be judged by many more
-readers than the typical two to four anonymous reviewers. With a shift in the
-diffusion strategy, the role of traditional journals and their editors would be
-to showcase scientific discoveries for specialized readership.
+the distribution strategy making scientific results immediately available to the
+community, while allowing traditional journals to validate the results and
+showcase scientific discoveries for their readership.
 
 Making publication easier can lead to the proliferation of studies of uneven
-quality. A trade-off between the intensity of the peer-review filtering and 
-the benefits to science has been hypothesized \cite{Aarssen2012}.  With 
-increasingly stringent peer review, the quality of published papers can 
-improve at the cost of an increased load on authors and 
-reviewers, and greater delays for publication.  By
-bypassing this model preprints 
-speed up the dissemination of scientific discoveries and put on reader's 
-shoulders the responsibility to judge originality and pertinence.
+quality. A trade-off between the intensity of the peer-review filtering and the
+benefits to science has been hypothesized \cite{Aarssen2012}.  With increasingly
+stringent peer review, the quality and perceived importance of published papers
+may be improved, but at the cost of an increased load on authors and reviewers,
+and greater delays for publication.  By developing a preprint culture in biology
+we can speed up the dissemination of scientific discoveries and potentially
+improve the quality of initial submissions to journals through pre-publication
+peer-review.
 

### 2013-02-27 ms.tex
edit Ethan's edits :P

--- 2013-02-26 ms.tex
@@
 PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new commercial open
-access publisher that provides a preprint server and a peer reviewed journal. It
-is focused on the biological sciences, which may counter the perception that
-preprints do not have a place in biology. Preprints can optionally be made
-private.  One preprint per year can be posted for free, with a onetime
-(\emph{i.e.}  lifetime) fee for unlimited public preprints. Preprints can be
-posted to PeerJ regardless of where they will be submitted for publication.
+access publisher focused on the biological sciences that provides a preprint
+server and a peer reviewed journal. Preprints can optionally be made private.
+One preprint per year can be posted for free, with a onetime (\emph{i.e.}
+lifetime) fee for unlimited public preprints. Preprints can be posted to PeerJ
+regardless of where they will be submitted for publication.
 
@@
 
-The ongoing discussions on the scientific publication process, peer-review and
-alternative publication models are all symptoms of the current uneasiness with
-the ever growing obsession with bibliographic metrics such as the impact factor
-\cite{Fisher2012}. Researchers are pressured to orient their publication
-strategy to maximize their number of publications and total citations. A
-well-known consequence is the initial submission of manuscripts to the most
-prestigious journals, followed by resubmission to progressively ``lower level''
-journals as they are rejected. The numerous negative impacts of such behavior
-have been discussed in depth \cite{hoc09} and include a long delay between the
-time a manuscript is finished and its publication. Research activities and the
-publication process are drifting away from their fundamental objective, namely
-the distribution of novel scientific discoveries.
+The ongoing discussions on the publication process, peer-reviewing and 
+alternative publication models are all symptoms of the current uneasiness 
+with the ever growing obsession with bibliographic metrics such as the 
+impact factor \cite{Fisher2012}. Researchers are pressured to orient their 
+publication strategy to maximize their number of publications and total 
+citations. A well-known consequence is to submit manuscripts first to the 
+most prestigious journals, and then resubmit to ``lower level'' journals as 
+they are rejected. The numerous negative impacts of such behavior have been 
+discussed in depth \cite{hoc09} and include a long delay between the time a 
+manuscript is finished to its publication. Research activities and the 
+publication process are drifting away from their fundamental object, namely 
+the diffusion of novel scientific discoveries.
 
-Developing a preprint culture in biology will not solve all of the problems with
-the current publication process. However, it might significantly reduce the
-negative consequences. The role of peer-review is to judge the scientific
+Developing a preprint culture in biology will not solve all problems with 
+the current publication process. However, it might significantly reduce its 
+negative consequences. The role of peer-reviewing is to judge the scientific 
 quality of a study. It is the first barrier against the fraudulent and poor 
-quality science that could impede scientific progress. In practice, the
-peer-review system is not only used to evaluate scientific quality but also to
-judge pertinence. On the other hand, preprints are not filtered on either
-quality or pertinence. Widespread adoption of preprint servers has the potential
-to shift the distribution strategy: journals would remain important to validate
-publications, but the relevance of a study should only be judged by many more
-readers than the typical two to four anonymous reviewers. With a shift in the
-diffusion strategy, the role of traditional journals and their editors would be
-to showcase scientific discoveries for specialized readership.
+quality science susceptible to impede scientific progress. In practice, the 
+peer-review system is not only used to evaluate scientific quality but also 
+to judge pertinence. On the other hand, preprints are not filtered, neither 
+for their quality nor their pertinence. Widespread adoption of preprint 
+servers has the potential to shift the diffusion strategy: journals would 
+remain important to validate publications, but the relevance of a study 
+should only be judged by many more readers than the typical two-four 
+anonymous reviewers. With a shift in the diffusion strategy, the role of 
+traditional journals and their editors would be to showcase scientific 
+discoveries for specialized readership.
 
@@
 the benefits to science has been hypothesized \cite{Aarssen2012}.  With 
-increasingly stringent peer review, the quality of published papers can 
+increasingly stringent peer reviewing, the quality of published papers can 
 improve at the cost of an increased load on authors and 
-reviewers, and greater delays for publication.  By
-bypassing this model preprints 
+reviewers and greater delays for publication.  Preprints are simply 
+bypassing this model for what we believe is the progress of science: they 
 speed up the dissemination of scientific discoveries and put on reader's 
@@
 
-DG is an associate falculty of F1000, EW is an academic editor for PeerJ, and TP
-is an advisor for figshare.
+EW is an academic editor for PeerJ and TP is a member of the figshare advisors
+program.
 

### 2013-02-27 ms.tex
Add Ram's paper

@@
 software development \cite{aru12} but it provides a powerful tool way to
-collaborate on every step of the manuscript development process.
+collaborate on every step of the manuscript development process \cite{ram13}.
 

### 2013-03-05 ms.tex
legend for the table

@@
 biology are not posted to preprint servers and are therefore not seen by more
-than a handful of other scientists prior to publication. In this article, we: 1)
+than a handful of other scientists prior to publication. In this article, we
 highlight the advantages of open preprint servers for both scientists and
-publishers; 2) discuss the preprint policies of major publishers in biology; and
-3) review popular options to submit preprints.
+publishers and discuss the preprint policies of major publishers in biology.
 
@@
     \hline
-    Website               & Free & Comments & Private preprints & Moderated & Peer-reviewed & DOI & Version-Control & Other Content\\
+    Website               & Free & Comments & Private preprints & Peer-reviewed & DOI & Version-Control & Other Content\\
     \hline
-    arXiv.org             & Yes & No & No & Yes & No & No & No & No\\
-    figshare.com          & Yes & Yes & No & No & No & Yes & No & Yes\\
-    peerj.com             & 1/yr & Yes & Yes & No & No & Yes & No & No\\
-    f1000research.com     & No & Yes & No & Yes & Yes & Yes & No & No\\
-    github.com            & Yes & Yes & Yes & No & No & No & Yes & Yes\\
+    arXiv.org             & Yes & No & No & No & No & No & No\\
+    figshare.com          & Yes & Yes & No & No & Yes & No & Yes\\
+    peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
+    f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
+    github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
     \hline
     \end{tabular}
+    \begin{flushleft}
+    \textbf{Free:} Whether preprints can be submitted for free.
+    \textbf{Comments:} Support for online comments on the item.
+    \textbf{Private:} Support for private preprints.
+    \textbf{Peer-reviewed:} Whether the preprints are peer-reviewed on the server.
+    \textbf{DOI:} Each item is assigned a unique digital object identifier.
+    \texbbf{Version-Control:} Is the preprint stored with a version-control system with the complete history of modifications?
+    \textbf{Other content:} Can upload figures, videos, datasets, code.
+    \end{flushleft}
     \label{table:box1}

### 2013-03-06 ms.tex
last corrections

@@
     \caption{\bf{Popular options for preprints}}
-    \begin{tabular}{|l|cccccccc|}
+    \begin{tabular}{|l|ccccccc|}
     \hline
-    Website               & Free & Comments & Private preprints & Peer-reviewed & DOI & Version-Control & Other Content\\
+    Website               & Free & Comments & Private & Peer-reviewed & DOI & Version-Control & Other Content\\
     \hline
@@
     \begin{flushleft}
-    \textbf{Free:} Whether preprints can be submitted for free.
-    \textbf{Comments:} Support for online comments on the item.
+    \textbf{Free:} Can preprints be submitted for free.
+    \textbf{Comments:} Support for online comments.
     \textbf{Private:} Support for private preprints.
@@
     \textbf{DOI:} Each item is assigned a unique digital object identifier.
-    \texbbf{Version-Control:} Is the preprint stored with a version-control system with the complete history of modifications?
+    \textbf{Version-Control:} Is the preprint stored using a version-control system with the complete history of modifications?
     \textbf{Other content:} Can upload figures, videos, datasets, code.

### 2013-03-20 ms.tex
edition for plos

@@
 highlight the advantages of open preprint servers for both scientists and
-publishers and discuss the preprint policies of major publishers in biology.
+publishers, discuss the preprint policies of major publishers in biology, and
+describe the main options to publish preprints (Box 1, Table 2).
 
@@
 The first and most often discussed advantage of open preprints is
-speed (Figure~\ref{fig:map}). The time between submission and the official
+speed (Figure 1). The time between submission and the official
 publication of a manuscript can be measured in months, sometimes in years. For
@@
 number of biology papers submitted to preprint servers still represents only a
-small fraction of the total research produced in biology (Fig.~\ref{fig:arxiv}).
+small fraction of the total research produced in biology (Figure 2).
 
@@
 public preprints make it easier to steal ideas \cite{gin11}. In other fields
-preprints serve the opposite role, they allow straightforward establishment of
-precedence, letting research lay claim to an idea thus preventing it from being
-``stolen'' \cite{gin11}. Another major concern is based on a certain
-interpretation of the Ingelfinger
-rule: scientists should not publish the same manuscript twice \cite{alt96}. A
-preprint is simply a document that allows ideas to spread and be discussed, it
-is not yet formally validated by the peer-review system. This is why almost all
-the major publishers in biology are preprint-friendly, including: Nature
-Publishing Group, PLOS, BMC, PNAS, Elsevier, and Springer \ref{table:policies}.
-This year, both the Ecological Society of America and the Genetics Society of
-America changed their policies to allow public preprints. \emph{Nature} even
-felt compelled to respond to the rumour that they refused manuscripts submitted
-to arXiv by saying that ``\emph{Nature} never wishes to stand in the way of
-communication between researchers. We seek rather to add value for authors and
-the community at large in our peer review, selection and editing'' \cite{nat05}.
-Still, a few journals adopt a ``by default'' hostile attitude towards preprints,
-mostly due to the lack of clear policy of the publishers. As an example,
-Wiley-Blackwell, which publishes some of the leading journals in biology, has no
-official policy on the matter.
+preprints serve the opposite role, they allow straightforward establishment
+of precedence, letting research lay claim to an idea thus preventing it from
+being ``stolen'' \cite{gin11}. Another major concern is based on a certain
+interpretation of the Ingelfinger rule: scientists should not publish the
+same manuscript twice \cite{alt96}. A preprint is simply a document that
+allows ideas to spread and be discussed, it is not yet formally validated by
+the peer-review system. This is why almost all the major publishers in
+biology are preprint-friendly, including: Nature Publishing Group, PLOS,
+BMC, PNAS, Elsevier, and Springer (Table 1). This year, both the Ecological
+Society of America and the Genetics Society of America changed their
+policies to allow public preprints. \emph{Nature} even felt compelled to
+respond to the rumour that they refused manuscripts submitted to arXiv by
+saying that ``\emph{Nature} never wishes to stand in the way of
+communication between researchers. We seek rather to add value for authors
+and the community at large in our peer review, selection and editing'' \cite
+{nat05}. Still, a few journals adopt a ``by default'' hostile attitude
+towards preprints, mostly due to the lack of clear policy of the publishers.
+As an example, Wiley-Blackwell, which publishes some of the leading journals
+in biology, has no official policy on the matter.
 
-\section*{Box: Preprint Server Roundup}
-
-% Table 2 should start here.
+\section*{Box 1: Preprint Server Roundup}
 
@@
 
-\section*{Funding}
-
-PDP is supported by an Alexander Graham Bell scholarship from the National
-Sciences and Engineering Council of Canada. EPW is supported by a CAREER Award
-from the National Science Foundation (DEB-0953694). JJA is supported by NSF
-DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
-scholarship. KR is supported by NSF DEB-1021553. DG is funded by a Discovery
-Grant from the National Sciences and Engineering Council of Canada and by the
-Canada Research Chair program.
-
 \section*{Acknowledgements}
@@
 version of this manuscript.
-
-\section*{Competing interests}
-
-EW is an academic editor for PeerJ and TP is a member of the figshare advisors
-program.
 
@@
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=4in]{map.eps}
-\end{center}
-\caption { {\bf It can take several months before a submitted paper is
+\subsection{Figure 1 (map.tiff)}
+
+It can take several months before a submitted paper is
 officially published and citable.} Meanwhile, few people are aware of the
@@
 immediately available and can be openly discussed, analyzed, and integrated
-into current research. }
-\label{fig:map}
-\end{figure}
+into current research.
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=4in]{figure_2.eps}
-\end{center}
-\caption { Submissions to the quantitative biology section lag behind
+\subsection{Figure 2 (arxiv.tiff)}
+
+Submissions to the quantitative biology section lag behind
 physics, mathematics, and computer science.
-}
-\label{fig:arxiv}
-\end{figure}
 
@@
   \end{tabular}
-    \begin{flushleft} Some publishers tolerate preprints except for a few of
-their medical journals, for example the \emph{ Journal of the National Cancer
-Institute} from Oxford and \emph{The Lancet} from Elsevier.  \end{flushleft}
   \label{table:policies}
@@
   \end{tabular}
-    \begin{flushleft}
+  \label{table:box1}
+\end{table}
+
+\newpage
+\section*{Table Legends}
+
+\subsection*{Table 1}
+
+Some publishers tolerate preprints except for a few of their medical
+journals, for example the \emph{ Journal of the National Cancer Institute}
+from Oxford and \emph{The Lancet} from Elsevier.
+
+\subsection*{Table 2}
+
 \textbf{Free:} Can preprints be submitted for free.
@@
 \textbf{Other content:} Can upload figures, videos, datasets, code.
-    \end{flushleft}
-    \label{table:box1}
-\end{table}
 

### 2013-03-20 ms.tex
master branch

@@
-% Template for PLoS
-% Version 1.0 January 2009
-%
-% To compile to pdf, run:
-% latex ms
-% bibtex ms
-% latex ms
-% latex ms
-% dvipdf ms
-
-\documentclass[10pt]{article}
-
-% amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
-
-% graphicx package, useful for including eps and pdf graphics
-% include graphics with the command \includegraphics
-\usepackage{graphicx}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-\usepackage{color}
-
-% Use doublespacing - comment out for single spacing
-\usepackage{setspace}
-\usepackage{hyperref} 
-\doublespacing
-
-% Text layout
-\topmargin 0.0cm
-\oddsidemargin 0.5cm
-\evensidemargin 0.5cm
-\textwidth 16cm 
-\textheight 21cm
-
-% Bold the 'Figure #' in the caption and separate it with a period
-% Captions will be left justified
-\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
-
-% Use the PLoS provided bibtex style
-\bibliographystyle{plos2009}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-%\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-\pagestyle{myheadings}
-%% ** EDIT HERE **
-
-%% ** EDIT HERE **
-%% PLEASE INCLUDE ALL MACROS BELOW
-
-%% END MACROS SECTION
-
+\documentclass[letterpaper]{article}
+\usepackage[utf8]{inputenc}
+\usepackage{color,graphicx,hyperref,authblk}
+\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}
+\renewcommand\Affilfont{\itshape\small}
 \begin{document}
 
-% Title must be 150 characters or less
-\begin{flushleft}
-{\Large
-\textbf{The Case for Open Preprints in Biology}
-}
-% Insert Author names, affiliations and corresponding author email.
-\\
-Philippe Desjardins-Proulx$^{1, 2,\ast}$, 
-Ethan P. White$^{3}$, 
-Joel J. Adamson$^{4}$,
-Karthik Ram$^{5}$,
-Timoth\'ee Poisot$^{1,2,6}$,
-Dominique Gravel$^{1,2}$
-\\
-\bf{1} Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Quebec, Canada.
-\\
-\bf{2} Quebec Center for Biodiversity Science, McGill University, Quebec, Canada.
-\\
-\bf{3} Departement of Biology, Utah State University, Utah, United-States of America.
-\\
-\bf{4} Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill, North Carolina, United-States of America.
-\\
-\bf{5} Environmental Science, Policy, and Management, University of California, Berkeley, California, United-States of America.
-\\
-\bf{6} International Network for Next-Generation Ecology.
-\\
-$\ast$ E-mail: philippe.d.proulx@gmail.com
-\end{flushleft}
+\title{The case for open preprints in biology}
 
-\section*{Introduction}
+\author[1,2,3]{Philippe Desjardins-Proulx}
+\author[4]{Ethan P. White}
+\author[5]{Joel J. Adamson}
+\author[6]{Karthik Ram}
+\author[2,3,7]{Timoth\'ee Poisot}
+\author[2,3]{Dominique Gravel}
+\affil[1]{email: \href{philippe.d.proulx@gmail.com}{philippe.d.proulx@gmail.com}}
+\affil[2]{Quebec Center for Biodiversity Science, McGill University, Montr\'eal, Canada.}
+\affil[3]{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
+\affil[4]{Departement of Biology, Utah State University, United-States of America.}
+\affil[5]{Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill, United-States of America}
+\affil[6]{Environmental Science, Policy, and Management. University of California, Berkeley, United-States of America.}
+\affil[7]{International Network for Next-Generation Ecology.}
+
+\maketitle
+
+\section{Introduction}
 
@@
 publishers, discuss the preprint policies of major publishers in biology, and
-describe the main options to publish preprints (Box 1, Table 2).
+describe the main options to publish preprints (Table \ref{table:options}).
 
-\section*{The case for public preprints}
+\section{The case for public preprints}
+
+\begin{figure}[ht!] \centering\includegraphics[width=0.90\textwidth]
+{map.pdf} \caption {It can take several months before a submitted paper is
+officially published and citable. Meanwhile, few people are aware of the
+research that has been done since, typically, only close colleagues are
+given access to the preprints. With public preprint servers, the science is
+immediately available and can be openly discussed, analyzed, and integrated
+into current research.} \label{fig:map} \end{figure}
 
 The first and most often discussed advantage of open preprints is
-speed (Figure 1). The time between submission and the official
+speed (Figure \ref{fig:map}). The time between submission and the official
 publication of a manuscript can be measured in months, sometimes in years. For
@@
 
-\section*{Preprints in biological sciences}
+\section{Preprints in biological sciences}
+
+\begin{figure}[ht!] \centering\includegraphics[width=0.90\textwidth]
+{arxiv.pdf} \caption {Submissions to the quantitative biology section lag behind
+physics, mathematics, and computer science.} \label{fig:arxiv} \end{figure}
 
@@
 number of biology papers submitted to preprint servers still represents only a
-small fraction of the total research produced in biology (Figure 2).
+small fraction of the total research produced in biology (Figure \ref{fig:arxiv}).
 
@@
 
-\section*{Box 1: Preprint Server Roundup}
+\begin{table}[!ht]
+  \caption{\bf{Policies for important publishers in biology.}}
+  \begin{tabular}{|ll|}
+  \hline
+  Publisher                             & Policy \\
+  \hline
+  Springer                              & Accept \\
+  BMC                                   & Accept \\
+  Elsevier                              & Accept \\
+  Nature Publishing Group               & Accept \\
+  Public Library of Science             & Accept \\
+  Genetics Society of America           & Accept \\
+  Royal Society                         & Accept \\
+  National Academy of Science (USA)     & Accept \\
+  Ecological Society of America         & Accept \\
+  Oxford Journals                       & Accept \\
+  Science                               & Ambiguous \\
+  Wiley-Blackwell                       & No general policy \\
+  British Ecological Society            & No answer to our query \\
+  \hline
+  \end{tabular}
+  \caption{Some publishers tolerate preprints except for a few of their medical
+journals, for example the \emph{ Journal of the National Cancer Institute}
+from Oxford and \emph{The Lancet} from Elsevier.}
+  \label{table:policies}
+\end{table}
 
-\subsection*{arXiv}
+\section{Preprint Server Roundup}
+
+\begin{table}[!ht]
+  \caption{\bf{Popular options for preprints}}
+  \begin{tabular}{|l|ccccccc|}
+  \hline
+  Website               & Free & Comments & Private & P.-R. & DOI & V.C. & O.C.\\
+  \hline
+  arXiv.org             & Yes & No & No & No & No & No & No\\
+  figshare.com          & Yes & Yes & No & No & Yes & No & Yes\\
+  peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
+  f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
+  github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
+  \hline
+  \end{tabular}
+  \caption{
+    \textbf{Free:} Can preprints be submitted for free.
+    \textbf{Comments:} Support for online comments.
+    \textbf{Private:} Support for private preprints.
+    \textbf{P.-R.:} Whether the preprints are peer-reviewed on the server.
+    \textbf{DOI:} Each item is assigned a unique digital object identifier.
+    \textbf{V.C.:} Is the preprint stored using a version-control system with the complete history of modifications?
+    \textbf{O.C.:} Can upload figures, videos, datasets, code.
+  }
+  \label{table:options}
+\end{table}
+
+\subsection{arXiv}
 
@@
 
-\subsection*{figshare}
+\subsection{figshare}
 
@@
 
-\subsection*{PeerJ}
+\subsection{PeerJ}
 
@@
 
-\subsection*{F1000Research}\label{f1000r}
+\subsection{F1000Research}\label{f1000r}
 
@@
 
-\subsection*{GitHub}
+\subsection{GitHub}
 
@@
 
-\subsection*{Other options}
+\subsection{Other options}
 
@@
 
-\section*{Conclusion}
+\section{Conclusion}
 
@@
 
-\section*{Acknowledgements}
+\section{Acknowledgements}
 
@@
 
-\section*{References}
+\section{Funding}
+
+PDP is supported by an Alexander Graham Bell scholarship from the National
+Sciences and Engineering Council of Canada. EPW is supported by a CAREER Award
+from the National Science Foundation (DEB-0953694). JJA is supported by NSF
+DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
+scholarship and 25 cents found by a coffee machine.  KR is supported by NSF
+DEB-1021553. DG is funded by a Discovery Grant from the National Sciences and
+Engineering Council of Canada and by the Canada Research Chair program.
+
 \bibliography{refs}
-
-\newpage
-\section*{Figure Legends}
-
-\subsection{Figure 1 (map.tiff)}
-
-It can take several months before a submitted paper is
-officially published and citable.} Meanwhile, few people are aware of the
-research that has been done since, typically, only close colleagues are
-given access to the preprints. With public preprint servers, the science is
-immediately available and can be openly discussed, analyzed, and integrated
-into current research.
-
-\subsection{Figure 2 (arxiv.tiff)}
-
-Submissions to the quantitative biology section lag behind
-physics, mathematics, and computer science.
-
-\newpage
-\section*{Tables}
-
-\begin{table}[!ht]
-  \caption{\bf{Policies for important publishers in biology.}}
-  \begin{tabular}{|ll|}
-  \hline
-  Publisher                             & Policy \\
-  \hline
-  Springer                              & Accept \\
-  BMC                                   & Accept \\
-  Elsevier                              & Accept \\
-  Nature Publishing Group               & Accept \\
-  Public Library of Science             & Accept \\
-  Genetics Society of America           & Accept \\
-  Royal Society                         & Accept \\
-  National Academy of Science (USA)     & Accept \\
-  Ecological Society of America         & Accept \\
-  Oxford Journals                       & Accept \\
-  Science                               & Ambiguous \\
-  Wiley-Blackwell                       & No general policy \\
-  British Ecological Society            & No answer to our query \\
-  \hline
-  \end{tabular}
-  \label{table:policies}
-\end{table}
-
-\begin{table}[!ht]
-  \caption{\bf{Popular options for preprints}}
-  \begin{tabular}{|l|ccccccc|}
-  \hline
-  Website               & Free & Comments & Private & Peer-reviewed & DOI & Version-Control & Other Content\\
-  \hline
-  arXiv.org             & Yes & No & No & No & No & No & No\\
-  figshare.com          & Yes & Yes & No & No & Yes & No & Yes\\
-  peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
-  f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
-  github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
-  \hline
-  \end{tabular}
-  \label{table:box1}
-\end{table}
-
-\newpage
-\section*{Table Legends}
-
-\subsection*{Table 1}
-
-Some publishers tolerate preprints except for a few of their medical
-journals, for example the \emph{ Journal of the National Cancer Institute}
-from Oxford and \emph{The Lancet} from Elsevier.
-
-\subsection*{Table 2}
-
-\textbf{Free:} Can preprints be submitted for free.
-\textbf{Comments:} Support for online comments.
-\textbf{Private:} Support for private preprints.
-\textbf{Peer-reviewed:} Whether the preprints are peer-reviewed on the server.
-\textbf{DOI:} Each item is assigned a unique digital object identifier.
-\textbf{Version-Control:} Is the preprint stored using a version-control system with the complete history of modifications?
-\textbf{Other content:} Can upload figures, videos, datasets, code.
+\bibliographystyle{plain}
 

### 2013-03-20 ms.tex
url to href

@@
 
-arXiv (\url{http://arxiv.org/}) is the most widely-used preprint server today,
+arXiv (\href{http://arxiv.org}{http://arxiv.org}) is the most widely-used preprint server today,
 and its use is almost universal in some branches of mathematics and physics.
@@
 
-PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new commercial open
+PeerJ (\href{https://peerj.com}{https://peerj.com}) is a new commercial open
 access publisher focused on the biological sciences that provides a preprint

### 2013-03-20 ms.tex
figshare now supports private documents

@@
   \hline
-  Website               & Free & Comments & Private & P.-R. & DOI & V.C. & O.C.\\
+  Website               & Free & Comments & Private & P.-R. & DOI & V.C.& O.C.\\
   \hline
   arXiv.org             & Yes  & No       & No      & No    & No  & No  & No\\
-  figshare.com          & Yes & Yes & No & No & Yes & No & Yes\\
+  figshare.com          & Yes  & Yes      & Yes     & No    & Yes & No  & Yes\\
   peerj.com             & 1/yr & Yes      & Yes     & No    & Yes & No  & No\\

### 2013-03-20 ms.tex
edit ms

--- 2013-03-20 ms.tex
@@
-\documentclass[letterpaper]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{color,graphicx,hyperref,authblk}
-\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}
-\renewcommand\Affilfont{\itshape\small}
+% Template for PLoS
+% Version 1.0 January 2009
+%
+% To compile to pdf, run:
+% latex ms
+% bibtex ms
+% latex ms
+% latex ms
+% dvipdf ms
+
+\documentclass[10pt]{article}
+
+% amsmath package, useful for mathematical formulas
+\usepackage{amsmath}
+% amssymb package, useful for mathematical symbols
+\usepackage{amssymb}
+
+% graphicx package, useful for including eps and pdf graphics
+% include graphics with the command \includegraphics
+\usepackage{graphicx}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+\usepackage{color}
+
+% Use doublespacing - comment out for single spacing
+\usepackage{setspace}
+\usepackage{hyperref} 
+\doublespacing
+
+% Text layout
+\topmargin 0.0cm
+\oddsidemargin 0.5cm
+\evensidemargin 0.5cm
+\textwidth 16cm 
+\textheight 21cm
+
+% Bold the 'Figure #' in the caption and separate it with a period
+% Captions will be left justified
+\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
+
+% Use the PLoS provided bibtex style
+\bibliographystyle{plos2009}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+%\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Leave date blank
+\date{}
+
+\pagestyle{myheadings}
+%% ** EDIT HERE **
+
+%% ** EDIT HERE **
+%% PLEASE INCLUDE ALL MACROS BELOW
+
+%% END MACROS SECTION
+
 \begin{document}
 
-\title{The case for open preprints in biology}
+% Title must be 150 characters or less
+\begin{flushleft}
+{\Large
+\textbf{The Case for Open Preprints in Biology}
+}
+% Insert Author names, affiliations and corresponding author email.
+\\
+Philippe Desjardins-Proulx$^{1, 2,\ast}$, 
+Ethan P. White$^{3}$, 
+Joel J. Adamson$^{4}$,
+Karthik Ram$^{5}$,
+Timoth\'ee Poisot$^{1,2,6}$,
+Dominique Gravel$^{1,2}$
+\\
+\bf{1} Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Quebec, Canada.
+\\
+\bf{2} Quebec Center for Biodiversity Science, McGill University, Quebec, Canada.
+\\
+\bf{3} Departement of Biology, Utah State University, Utah, United-States of America.
+\\
+\bf{4} Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill, North Carolina, United-States of America.
+\\
+\bf{5} Environmental Science, Policy, and Management, University of California, Berkeley, California, United-States of America.
+\\
+\bf{6} International Network for Next-Generation Ecology.
+\\
+$\ast$ E-mail: philippe.d.proulx@gmail.com
+\end{flushleft}
 
-\author[1,2,3]{Philippe Desjardins-Proulx}
-\author[4]{Ethan P. White}
-\author[5]{Joel J. Adamson}
-\author[6]{Karthik Ram}
-\author[2,3,7]{Timoth\'ee Poisot}
-\author[2,3]{Dominique Gravel}
-\affil[1]{email: \href{philippe.d.proulx@gmail.com}{philippe.d.proulx@gmail.com}}
-\affil[2]{Quebec Center for Biodiversity Science, McGill University, Montr\'eal, Canada.}
-\affil[3]{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
-\affil[4]{Departement of Biology, Utah State University, United-States of America.}
-\affil[5]{Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill, United-States of America}
-\affil[6]{Environmental Science, Policy, and Management. University of California, Berkeley, United-States of America.}
-\affil[7]{International Network for Next-Generation Ecology.}
-
-\maketitle
-
-\section{Introduction}
+\section*{Introduction}
 
@@
 publishers, discuss the preprint policies of major publishers in biology, and
-describe the main options to publish preprints (Table \ref{table:options}).
+describe the main options to publish preprints (Box 1, Table 2).
 
-\section{The case for public preprints}
-
-\begin{figure}[ht!] \centering\includegraphics[width=0.90\textwidth]
-{map.pdf} \caption {It can take several months before a submitted paper is
-officially published and citable. Meanwhile, few people are aware of the
-research that has been done since, typically, only close colleagues are
-given access to the preprints. With public preprint servers, the science is
-immediately available and can be openly discussed, analyzed, and integrated
-into current research.} \label{fig:map} \end{figure}
+\section*{The case for public preprints}
 
 The first and most often discussed advantage of open preprints is
-speed (Figure \ref{fig:map}). The time between submission and the official
+speed (Figure 1). The time between submission and the official
 publication of a manuscript can be measured in months, sometimes in years. For
@@
 
-\section{Preprints in biological sciences}
-
-\begin{figure}[ht!] \centering\includegraphics[width=0.90\textwidth]
-{arxiv.pdf} \caption {Submissions to the quantitative biology section lag behind
-physics, mathematics, and computer science.} \label{fig:arxiv} \end{figure}
+\section*{Preprints in biological sciences}
 
@@
 number of biology papers submitted to preprint servers still represents only a
-small fraction of the total research produced in biology (Figure \ref{fig:arxiv}).
+small fraction of the total research produced in biology (Figure 2).
 
@@
 
-\begin{table}[!ht]
-  \caption{\bf{Policies for important publishers in biology.}}
-  \begin{tabular}{|ll|}
-  \hline
-  Publisher                             & Policy \\
-  \hline
-  Springer                              & Accept \\
-  BMC                                   & Accept \\
-  Elsevier                              & Accept \\
-  Nature Publishing Group               & Accept \\
-  Public Library of Science             & Accept \\
-  Genetics Society of America           & Accept \\
-  Royal Society                         & Accept \\
-  National Academy of Science (USA)     & Accept \\
-  Ecological Society of America         & Accept \\
-  Oxford Journals                       & Accept \\
-  Science                               & Ambiguous \\
-  Wiley-Blackwell                       & No general policy \\
-  British Ecological Society            & No answer to our query \\
-  \hline
-  \end{tabular}
-  \caption{Some publishers tolerate preprints except for a few of their medical
-journals, for example the \emph{ Journal of the National Cancer Institute}
-from Oxford and \emph{The Lancet} from Elsevier.}
-  \label{table:policies}
-\end{table}
+\section*{Box 1: Preprint Server Roundup}
 
-\section{Preprint Server Roundup}
-
-\begin{table}[!ht]
-  \caption{\bf{Popular options for preprints}}
-  \begin{tabular}{|l|ccccccc|}
-  \hline
-  Website               & Free & Comments & Private & P.-R. & DOI & V.C. & O.C.\\
-  \hline
-  arXiv.org             & Yes & No & No & No & No & No & No\\
-  figshare.com          & Yes & Yes & No & No & Yes & No & Yes\\
-  peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
-  f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
-  github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
-  \hline
-  \end{tabular}
-  \caption{
-    \textbf{Free:} Can preprints be submitted for free.
-    \textbf{Comments:} Support for online comments.
-    \textbf{Private:} Support for private preprints.
-    \textbf{P.-R.:} Whether the preprints are peer-reviewed on the server.
-    \textbf{DOI:} Each item is assigned a unique digital object identifier.
-    \textbf{V.C.:} Is the preprint stored using a version-control system with the complete history of modifications?
-    \textbf{O.C.:} Can upload figures, videos, datasets, code.
-  }
-  \label{table:options}
-\end{table}
-
-\subsection{arXiv}
+\subsection*{arXiv}
 
@@
 
-\subsection{Other options}
+\subsection*{Other options}
 
@@
 
-\section{Funding}
+\section*{References}
+\bibliography{refs}
 
-PDP is supported by an Alexander Graham Bell scholarship from the National
-Sciences and Engineering Council of Canada. EPW is supported by a CAREER Award
-from the National Science Foundation (DEB-0953694). JJA is supported by NSF
-DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
-scholarship and 25 cents found by a coffee machine.  KR is supported by NSF
-DEB-1021553. DG is funded by a Discovery Grant from the National Sciences and
-Engineering Council of Canada and by the Canada Research Chair program.
+\newpage
+\section*{Figure Legends}
 
-\bibliography{refs}
-\bibliographystyle{plain}
+\subsection*{Figure 1 (map.tiff)}
+
+It can take several months before a submitted paper is officially published and
+citable. Meanwhile, few people are aware of the research that has been done
+since, typically, only close colleagues are given access to the preprints. With
+public preprint servers, the science is immediately available and can be openly
+discussed, analyzed, and integrated into current research.
+
+\subsection*{Figure 2 (arxiv.tiff)}
+
+Submissions to the quantitative biology section lag behind
+physics, mathematics, and computer science.
+
+\newpage
+\section*{Tables}
+
+\begin{table}[!ht]
+  \caption{\bf{Policies for important publishers in biology.}}
+  \begin{tabular}{|ll|}
+  \hline
+  Publisher                             & Policy \\
+  \hline
+  Springer                              & Accept \\
+  BMC                                   & Accept \\
+  Elsevier                              & Accept \\
+  Nature Publishing Group               & Accept \\
+  Public Library of Science             & Accept \\
+  Genetics Society of America           & Accept \\
+  Royal Society                         & Accept \\
+  National Academy of Science (USA)     & Accept \\
+  Ecological Society of America         & Accept \\
+  Oxford Journals                       & Accept \\
+  Science                               & Ambiguous \\
+  Wiley-Blackwell                       & No general policy \\
+  British Ecological Society            & No answer to our query \\
+  \hline
+  \end{tabular}
+  \label{table:policies}
+\end{table}
+
+\begin{table}[!ht]
+  \caption{\bf{Popular options for preprints}}
+  \begin{tabular}{|l|ccccccc|}
+  \hline
+  Website               & Free & Comments & Private & Peer-reviewed & DOI & Version-Control & Other Content\\
+  \hline
+  arXiv.org             & Yes & No & No & No & No & No & No\\
+  figshare.com          & Yes & Yes & Yes & No & Yes & No & Yes\\
+  peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
+  f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
+  github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
+  \hline
+  \end{tabular}
+  \label{table:box1}
+\end{table}
+
+\newpage
+\section*{Table Legends}
+
+\subsection*{Table 1}
+
+Some publishers tolerate preprints except for a few of their medical
+journals, for example the \emph{ Journal of the National Cancer Institute}
+from Oxford and \emph{The Lancet} from Elsevier.
+
+\subsection*{Table 2}
+
+\textbf{Free:} Can preprints be submitted for free.
+\textbf{Comments:} Support for online comments.
+\textbf{Private:} Support for private preprints.
+\textbf{Peer-reviewed:} Whether the preprints are peer-reviewed on the server.
+\textbf{DOI:} Each item is assigned a unique digital object identifier.
+\textbf{Version-Control:} Is the preprint stored using a version-control system with the complete history of modifications?
+\textbf{Other content:} Can upload figures, videos, datasets, code.
 

### 2013-03-28 ms.tex
add ref

@@
 publishers, discuss the preprint policies of major publishers in biology, and
-describe the main options to publish preprints (Box 1, Table 2).
+describe the main options to publish preprints (Box 1, Table 1).
 
@@
 biology are preprint-friendly, including: Nature Publishing Group, PLOS,
-BMC, PNAS, Elsevier, and Springer (Table 1). This year, both the Ecological
+BMC, PNAS, Elsevier, and Springer (Table 2). This year, both the Ecological
 Society of America and the Genetics Society of America changed their
@@
 
-\subsection*{Figure 1 (map.tiff)}
+\subsection*{Figure 1 (map.tif)}
 
@@
 
-\subsection*{Figure 2 (arxiv.tiff)}
+\subsection*{Figure 2 (arxiv.tif)}
 
@@
 \section*{Tables}
+
+\begin{table}[!ht]
+  \caption{\bf{Popular options for preprints}}
+  \begin{tabular}{|l|ccccccc|}
+  \hline
+  Website               & Free & Comments & Private & Peer-reviewed & DOI & Version-Control & Other Content\\
+  \hline
+  arXiv.org             & Yes & No & No & No & No & No & No\\
+  figshare.com          & Yes & Yes & Yes & No & Yes & No & Yes\\
+  peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
+  f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
+  github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
+  \hline
+  \end{tabular}
+  \label{table:box1}
+\end{table}
 
@@
 
-\begin{table}[!ht]
-  \caption{\bf{Popular options for preprints}}
-  \begin{tabular}{|l|ccccccc|}
-  \hline
-  Website               & Free & Comments & Private & Peer-reviewed & DOI & Version-Control & Other Content\\
-  \hline
-  arXiv.org             & Yes & No & No & No & No & No & No\\
-  figshare.com          & Yes & Yes & Yes & No & Yes & No & Yes\\
-  peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
-  f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
-  github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
-  \hline
-  \end{tabular}
-  \label{table:box1}
-\end{table}
-
 \newpage
@@
 \subsection*{Table 1}
-
-Some publishers tolerate preprints except for a few of their medical
-journals, for example the \emph{ Journal of the National Cancer Institute}
-from Oxford and \emph{The Lancet} from Elsevier.
-
-\subsection*{Table 2}
 
@@
 
+\subsection*{Table 2}
+
+Some publishers tolerate preprints except for a few of their medical
+journals, for example the \emph{ Journal of the National Cancer Institute}
+from Oxford and \emph{The Lancet} from Elsevier. Data from \cite{war12}.
+
 \end{document}

### 2013-03-28 ms.tex
update ith refs

--- 2013-03-20 ms.tex
@@
 \usepackage[utf8]{inputenc}
-\usepackage{color,graphicx,hyperref,authblk}
+\usepackage{url,color,graphicx,hyperref,authblk}
 \hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}
@@
 biology are preprint-friendly, including: Nature Publishing Group, PLOS,
-BMC, PNAS, Elsevier, and Springer (Table 1). This year, both the Ecological
+BMC, PNAS, Elsevier, and Springer (Table \ref{table:policies}). This year, both the Ecological
 Society of America and the Genetics Society of America changed their
@@
 journals, for example the \emph{ Journal of the National Cancer Institute}
-from Oxford and \emph{The Lancet} from Elsevier.}
+from Oxford and \emph{The Lancet} from Elsevier. Data from \cite{war12}.}
   \label{table:policies}

### 2013-03-28 ms.tex
fix ref

@@
 \begin{figure}[ht!] \centering\includegraphics[width=0.90\textwidth]
-{arxiv.pdf} \caption {Submissions to the quantitative biology section lag behind
-physics, mathematics, and computer science.} \label{fig:arxiv} \end{figure}
+{arxiv.pdf} \caption {Submissions to the quantitative biology section lag
+behind physics, mathematics, and computer science. Data from \cite{war12}.}
+\label{fig:arxiv} \end{figure}
 
@@
 journals, for example the \emph{ Journal of the National Cancer Institute}
-from Oxford and \emph{The Lancet} from Elsevier. Data from \cite{war12}.}
+from Oxford and \emph{The Lancet} from Elsevier.}
   \label{table:policies}
